### 2022-09-01 labs/CSGameLogRegression.Rmd
Added folders and files

---
title: "Stat 495 - Logistic Regression Practice - CS Game"
author: "A.S. Wagaman"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

## Stat 495 - CS Game

```{r, include = FALSE}
library(mosaic)
library(readr)
library(broom)
```

```{r}
csgame <- read.csv("https://awagaman.people.amherst.edu/stat495/csgame.csv", header = T)
```

A student at Amherst has written a portion of a video game while studying the behavior of some computer algorithms. For a particular encounter in the video game, ten different inputs are used to determine the outcome of the encounter - i.e. whether the player wins or loses a fight against a monster. A set of 190 test instances of the encounter have had their inputs recorded, as well as the outcome. The data set is available as csgame.csv.

The inputs are: BaseAttack, BaseDefense, Charisma, Constitution, Dexterity, Intelligence, MagicDefense, MonsterAttack, MonsterMagic, and ZoneLevel. The first 7 inputs are player attributes and higher values denote a stronger player character. You should note that BaseDefense is based on armor, and MagicDefense is not, and also that it is usually the case that characters in plate armor (the strongest usually available in these sorts of games) are usually not strong magic users, and vice versa (magic users often wear cloth armor, generally the weakest available). The 8th and 9th input variables are monster attributes where higher values indicate a stronger, more powerful monster. Finally, ZoneLevel is an indication of how hard the zone where the encounter takes place is (higher values should be a harder zone). Some of the input names are based on concepts from Dungeons and Dragons.

The outcome variable is provided both numerically as 0 and 1 and categorically as Loss and Win (Loss=0; Win=1) in the variables OutcomeNum and Outcome, respectively.

Another student wants to play the game and win the encounter, and is looking for guidance as to how to approach that. For example, should they develop a character with high Dexterity or one with high Charisma if they want to win the encounter?

Your task is to examine the data set and perform a relevant analysis to assist the students (predict the outcome using the input variables).  Provide relevant interpretations of your findings for the student who wants to win the encounter as well as for the student who has written the game.

### Analysis

### 2022-09-07 homework/hmk1Stat495F22.Rmd
Added some files

---
title: "Homework 1 - Stat 495"
author: "YourNameGoesHere"
date: "Due Monday, Sept. 12th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
options(digits = 6)
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

*

\newpage

# PROBLEMS TO TURN IN:  Vis 1, Vis 2, CASI 1.1, CASI 1.4, Portfolio Reflection

## Visualization Problems (Adapted from an assignment by Prof. Horton)

The first two ``problems'' require you to find two visuals to discuss, and incorporate them in a .Rmd file. To find these visuals, we will practice finding journal articles from two sources - the JSTOR database and Google Scholar.

Your task is to select two visual displays from journal articles that apply statistics (they do not need to be in statistics research journals, but could be). One should be selected as a visual display that you find compelling. The other should be a visual display that you believe is suboptimal or could be improved.

One visual must come from JSTOR and the other from Google Scholar. You must include the article citation and figure information (which figure is it in the article) with each figure. (Citations are more than a URL.)

You should include both images below and a brief commentary for each on why you picked them and why they are compelling or suboptimal, respectively.

Instructions for accessing and using JSTOR and Google Scholar:

Google Scholar can be found at the link here [Google Scholar](https://scholar.google.com/).

JSTOR is one of the journal databases available through the College. To get to it, you can:

* Head to the [Library](https://www.amherst.edu/library) page. 
* Click the link (roughly in middle of page) to Browse 'A-Z Databases'.
* Head to the J's and click JSTOR.

What should you search for in these two places to find visuals for this assignment?

* Think of a statistical method you are comfortable reading about. Examples - regression, ANOVA, etc.
* Think of an application area you'd like to find an article in. 
* Put the application area in a search field (or in JSTOR, select journals from that field - left menu) and the topic in another field
* Look at the search results this generates and pick an article to look at.
* See if any of the figures in the article strike you. If not, go look at another article.

Instructions to include visuals in a .Rmd:

Once you identify appropriate visuals, you need to save them in a format that can be put in RMarkdown. .png files work, but other file formats can work as well.

Below are two examples of how visuals can be included in a .Rmd. Part of the purpose of this assignment is so that you learn how to add images to .Rmds looking ahead to the final paper. The image file should be in the current directory (see the output of "getwd()"). See http://rmarkdown.rstudio.com/authoring_basics.html for more details. DELETE these examples before submission.

![Visual of Tukey Transform Suggestions - Method 1](tukey_bulge.png)

\begin{figure}[htbp] 
\centering 
\includegraphics[width=4in]{tukey_bulge.png} 
\caption{Visual of Tukey Transform Suggestions - Method 2}
\end{figure}

## Vis 1 - Compelling

```{r, include = FALSE}
#Be sure to add your commentary!

#And the citation information.

#Was this from JSTOR or Google Scholar?
```

## Vis 2 - Suboptimal

```{r, include = FALSE}
#Be sure to add your commentary!

#And the citation information.

#Was this from JSTOR or Google Scholar?
```

\newpage

## CASI 1.1

```{r}
kidney <- read.table("http://web.stanford.edu/~hastie/CASI_files/DATA/kidney.txt", header = TRUE)
```

> (a) Fit a cubic regression, as a function of age, to the kidney data of Figures 1.1 and 1.2, calculating estimates and standard errors at ages 20, 30, 40, 50, 60, 70, 80.

SOLUTION:

```{r}
# Hint, augment is likely to be useful here (loaded in broom package above)
# Do you remember how to add powers to a regression? You can also use mutate. 
# Be sure you actually get a cubic regression! 
# The model must show the appropriate terms.
```

> (b) How do the results compare with those in Table 1.1?

SOLUTION:

\newpage

## CASI 1.4 - Slightly Modified

```{r, cache = TRUE}
# Load and format data
leukemia_big <- read.csv("http://web.stanford.edu/~hastie/CASI_files/DATA/leukemia_big.csv")
# says pictures from row 136
gene136 <- t(leukemia_big[136, ]) #says pictures from row 136
# Need to get ALL and AML tags in
type <- c(rep("ALL", 20), rep("AML", 14), rep("ALL", 27), rep("AML", 11))

# Set up dataset
leukemia <- data.frame(gene136, type)
leukemia <- rename(leukemia, gene136 = X136)
favstats(~ gene136 | type, data = leukemia)
```

We want to see if there is a significant difference in mean gene expression for gene 136 for the ALL and AML groups.

> (a) Record the means of the ALL and AML groups for the gene 136 data available for reference.

SOLUTION:

> (b) Perform 1000 nonparametric bootstrap replications for the mean of ALL for gene 136. Describe the distribution of the resulting means. You can perform the bootstrap in any way you see fit (the functions do and resample might prove useful).

SOLUTION:

> (c) Repeat (b) for AML.

SOLUTION:

> (d) Suggest an inference. In other words, what do your results in (b) and (c) suggest about whether there is a difference in means for the ALL and AML groups for gene 136?

SOLUTION:

> (e) Brainstorm an alternative way to approach the problem via a randomization/permutation test. Describe what you would do in a way that someone else could code it up. (You do not need to actually code this up, but you can if you want to see what the result is.)

SOLUTION:

\newpage

## Portfolio Reflection

Look at our portfolio review and in-class activities. In a separate word or pdf document, in a few paragraphs, reflect on how the items in your portfolio demonstrate:

* how your statistical analytical skills have developed over time
* how your statistical writing skills have developed over time
* skills you have a solid grasp of (such as R code or visuals or regression)
* skills you would like to improve on

Then, set some goals for what you'd like to work on improving in future statistical reports. (Yes, you brainstormed some before, this is asking you to pick some to really focus on!)

Upload this portfolio reflection and goals document for future reports to your portfolio folder in your personal class repo.

Given what you are asked to include, I expect the document to have at least 3 paragraphs and contain at least 3 goals for future work.

### 2022-09-07 labs/CSGameLogRegression.Rmd
Added some files

@@
 library(broom)
+library(mosaic)
+library(Stat2Data)
+library(lmtest)
+library("DescTools")
 ```
@@
 ### Analysis
+
+```{r}
+glimpse(csgame)
+```
+
+```{r}
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = BaseAttack)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Charisma)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MonsterMagic)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Dexterity)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Intelligence)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Constitution)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MonsterAttack)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = BaseDefense)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = ZoneLevel)) + geom_boxplot() + labs(x = "Outcome Num")
+ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MagicDefense)) + geom_boxplot() + labs(x = "Outcome Num")
+```
+
+```{r}
+# Add log Price
+csgame <- mutate(csgame, logBaseDefense = log(BaseDefense))
+csgame <- mutate(csgame, logMagicDefense = log(MagicDefense))
+#Fit model and get basic output
+logm <- glm(OutcomeNum ~ logBaseDefense + logMagicDefense,
+            data = csgame, family = binomial(logit))
+msummary(logm)
+```
+
+```{r}
+lrtest(logm)
+```
+```{r}
+exp(confint(logm))
+```
+```{r}
+logmaugment <- logm %>% augment(type.predict = "response")
+names(logmaugment)
+```
+
+```{r}
+logmaugment <- mutate(logmaugment, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = logmaugment)
+
+tally(~ OutcomeNum, data = csgame)
+```

### 2022-09-14 homework/hmk1/hmk1Stat495F22.Rmd
Working on Hw1

--- 2022-09-07 homework/hmk1Stat495F22.Rmd
@@
 title: "Homework 1 - Stat 495"
-author: "YourNameGoesHere"
+author: "Justin Papagelis"
 date: "Due Monday, Sept. 12th by midnight"
@@
 library(broom)
+library(tidyverse)
+library(ggplot2)
+
 options(digits = 6)
@@
 # Hint, augment is likely to be useful here (loaded in broom package above)
+lm2 = lm(tot ~ poly(age, degree = 3), data = kidney)
+
+ggplot(data = kidney, aes(x = age, y = tot)) +
+  geom_point()
+
+msummary(lm2)
+
+ages = data.frame(age = c(20, 30, 40, 50, 60, 70, 80))
+
+pred = augment(x = lm2, data = kidney, newdata = ages, se_fit = TRUE) %>%
+  rename("Age" = age, "Estimation" = .fitted, "Standard Errors"= .se.fit)
+
+pred %>% knitr::kable(bookends = TRUE)
 # Do you remember how to add powers to a regression? You can also use mutate. 
@@
 
-SOLUTION:
+SOLUTION: Compared to the results in Table 1.1, the estimates using the cubic model are similar to the ones in Table 1.1.
+It does seem that the estimates tend to be lower than the other estimates for smaller ages using the cubic model.
+But as the ages increase, the estimated overall function of the kidneys is closer to the estimates of the first model.
+In general, the standard errors of the cubic model are higher than the standard errors of the estimates using the previous model.
 
@@
 
-SOLUTION:
+SOLUTION: The mean of the ALL group for the gene 136 is 0.752 and the mean of the AML group for the gene 136 is 0.950.
 
@@
 
-SOLUTION:
+```{r}
+leukemia_ALL <- leukemia %>%
+  filter(type == "ALL")
+
+# resample(filter(leukemia, type == "ALL"))
+
+set.seed = 0
+results_ALL <- do(1000)*mean(~gene136, data = mosaic::resample(leukemia_ALL, replace = T))
+
+ggplot(data = results_ALL, aes(x = mean)) +
+  geom_density()
+
+```
+
+SOLUTION: The distribution of the means is unimodal and symmetric while centered around 0.76. The distribution appears to be relatively Normal.
 
@@
 
-SOLUTION:
+```{r}
+leukemia_AML <- leukemia %>%
+  filter(type == "AML")
+
+set.seed = 0
+results_AML <- do(1000)*mean(~gene136, data = mosaic::resample(leukemia_AML, replace = T))
+
+ggplot(data = results_AML, aes(x = mean)) +
+  geom_density()
+```
+
+SOLUTION: The distribution of the means of AML is unimodal and relatively symmetric. The distribution is centered around approximately 0.95.
 
@@
 
-SOLUTION:
+```{r}
+results_ALL <- results_ALL %>%
+  mutate(type = "ALL")
+
+results_AML <- results_AML %>%
+  mutate(type = "AML")
+
+results_both <- rbind(results_ALL, results_AML)
+
+ggplot(data = results_both, aes(x = mean, color = type)) +
+  geom_density()
+```
+
+SOLUTION: From the density plots above, it appears that there is a difference in means for the ALL and the AML groups for gene 136.
+Specifically, a hypothesis could be that the mean of the AML group is greater than the mean of the ALL group for gene 136.
 
@@
 
-SOLUTION:
+SOLUTION: some sort of randomization procedure that compares the two groups directly
+
+2-sample permuation test --> describe it good.
 

### 2022-09-15 homework/hmk1/hmk1Stat495F22.Rmd
Finish Hmk1

@@
 author: "Justin Papagelis"
-date: "Due Monday, Sept. 12th by midnight"
+date: "Due Weds, Sept. 14th by midnight"
 output:
@@
 
-*
+* https://www.rdocumentation.org/packages/broom/versions/0.4.1/topics/augment, CASI 1.1
+* https://rdrr.io/cran/mosaic/man/resample.html, CASI 1.4
+* https://datascienceplus.com/fitting-polynomial-regression-r/, CASI 1.1
+* https://en.wikipedia.org/wiki/Permutation_test, CASI 1.4
 
@@
 
-The first two ``problems'' require you to find two visuals to discuss, and incorporate them in a .Rmd file.
-To find these visuals, we will practice finding journal articles from two sources - the JSTOR database and Google Scholar.
+## Vis 1 - Compelling
 
-Your task is to select two visual displays from journal articles that apply statistics (they do not need to be in statistics research journals, but could be).
-One should be selected as a visual display that you find compelling.
-The other should be a visual display that you believe is suboptimal or could be improved.
+![Compelling Graphic](images/good.png){#id .class width=50% height=50%}
 
-One visual must come from JSTOR and the other from Google Scholar.
-You must include the article citation and figure information (which figure is it in the article) with each figure.
-(Citations are more than a URL.)
+Frey, Carl Benedikt, and Michael Osborne. "The future of employment." (2013). Accessed 15 Sep. 2022.
+This graphic was found through Google Scholar
 
-You should include both images below and a brief commentary for each on why you picked them and why they are compelling or suboptimal, respectively.
-
-Instructions for accessing and using JSTOR and Google Scholar:
-
-Google Scholar can be found at the link here [Google Scholar](https://scholar.google.com/).
-
-JSTOR is one of the journal databases available through the College. To get to it, you can:
-
-* Head to the [Library](https://www.amherst.edu/library) page. 
-* Click the link (roughly in middle of page) to Browse 'A-Z Databases'.
-* Head to the J's and click JSTOR.
-
-What should you search for in these two places to find visuals for this assignment?
-
-* Think of a statistical method you are comfortable reading about. Examples - regression, ANOVA, etc.
-* Think of an application area you'd like to find an article in. 
-* Put the application area in a search field (or in JSTOR, select journals from that field - left menu) and the topic in another field
-* Look at the search results this generates and pick an article to look at.
-* See if any of the figures in the article strike you. If not, go look at another article.
-
-Instructions to include visuals in a .Rmd:
-
-Once you identify appropriate visuals, you need to save them in a format that can be put in RMarkdown. .png files work, but other file formats can work as well.
-
-Below are two examples of how visuals can be included in a .Rmd.
-Part of the purpose of this assignment is so that you learn how to add images to .Rmds looking ahead to the final paper.
-The image file should be in the current directory (see the output of "getwd()").
-See http://rmarkdown.rstudio.com/authoring_basics.html for more details.
-DELETE these examples before submission.
-
-![Visual of Tukey Transform Suggestions - Method 1](tukey_bulge.png)
-
-\begin{figure}[htbp] 
-\centering 
-\includegraphics[width=4in]{tukey_bulge.png} 
-\caption{Visual of Tukey Transform Suggestions - Method 2}
-\end{figure}
-
-## Vis 1 - Compelling
+I found this graphic to be compelling because right from the start, it pops off of the page with lots of different colors.
+The graph contains many different components and is interesting to take in.
+In particular, I found it interesting how the different industries vary with the probability of computerization.
+Overall, this graphic combines a lot of different perspectives to look at while being visually appealing.
 
@@
 ## Vis 2 - Suboptimal
+
+![Suboptimal Graphic](images/improvement.png){#id .class width=50% height=50%}
+\newline Vega-Camarena, José Pablo, et al.
+“Contrasting Rainfall Behavior between the Pacific Coast and the Mexican Altiplano.” Climate Research, vol.
+76, no.
+3, 2018, pp.
+225–40.
+JSTOR, https://www.jstor.org/stable/26626182.
+Accessed 15 Sep.
+2022.
+
+This graphic was found through JSTOR
+
+I found this graphic to be suboptimal because it didn't really stand out to me as a reader and could definitely use some improvements.
+The type of graph that was used is not that helpful when compare the years because they do not all lie along a common axis.
+It is also difficult to see how distict the peaks are because there are not many axis labels.
 
@@
 ```{r}
-# Hint, augment is likely to be useful here (loaded in broom package above)
 lm2 = lm(tot ~ poly(age, degree = 3), data = kidney)
@@
 ggplot(data = kidney, aes(x = age, y = tot)) +
-  geom_point()
+  geom_point() +
+  labs(title = "Scatterplot of Age and Total Kidney Function", x = "Age",
+       y = "Total Kidney Function")
 
@@
 pred %>% knitr::kable(bookends = TRUE)
-# Do you remember how to add powers to a regression? You can also use mutate. 
-# Be sure you actually get a cubic regression! 
-# The model must show the appropriate terms.
 ```
@@
 
-# resample(filter(leukemia, type == "ALL"))
-
 set.seed = 0
@@
 ggplot(data = results_ALL, aes(x = mean)) +
-  geom_density()
-
+  geom_density() +
+  labs(title = "Bootstrap Distribution of means of ALL")
 ```
 
-SOLUTION: The distribution of the means is unimodal and symmetric while centered around 0.76. The distribution appears to be relatively Normal.
+SOLUTION: The distribution of the means is unimodal and symmetric while centered around 0.76. The distribution appears to be relatively normal.
 
@@
 ggplot(data = results_AML, aes(x = mean)) +
-  geom_density()
+  geom_density() +
+  labs(title = "Bootstrap Distribution of means of AML")
 ```
 
-SOLUTION: The distribution of the means of AML is unimodal and relatively symmetric. The distribution is centered around approximately 0.95.
+SOLUTION: The distribution of the means of AML is unimodal and relatively symmetric. It appears to be relatively normal. The distribution is centered around approximately 0.95.
 
@@
 ggplot(data = results_both, aes(x = mean, color = type)) +
-  geom_density()
+  geom_density()  +
+  labs(title = "Bootstrap Distribution of means of ALL and AML")
 ```
@@
 
-SOLUTION: some sort of randomization procedure that compares the two groups directly
-
-2-sample permuation test --> describe it good.
+SOLUTION: In order to compare the two groups directly, you could perform a 2-sample permutation test.
+First, we would calculate the difference in means between the two sample of gene 136 for AML and ALL.
+Next, we woudl combine the two samples into a single dataset.
+Then, we randomly assign the observations from the pooled dataset into either either AML or ALL.
+Then we calculate the difference in these means.
+We would repeat this until we have sufficient number of statistics (around 1000).
+This way, we can have lots of different permutations of ALL and AML for gene 136.
+The means we collected would be the distribution of of possible differences under a null hypothesis that the groups AML and ALL are the same.
+Then, a p-value can be calculated by finding the proportion of sampled permutations where the absolute value of the difference was greater than the difference in sample means from our original dataset.
+If we reject the null hypothesis, then we have significant evidence that the two groups, ALL and AML are not the same.
 

### 2022-09-22 homework/hmk2Stat495F22.Rmd
Finished Hwk2

---
title: "Homework 2 - Stat 495"
author: "Justin Papagelis"
date: "Due Wednesday, Sept. 21st by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
library(mvtnorm)
library(ggplot2)
options(digits = 6)
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

*

\newpage

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
```

For this assignment, you may do some of the problems on paper if you like, then scan in your solutions and merge with the Integrity page as a cover sheet and any work you are leaving in the .Rmd, such as your work for CASI 5.3. If you decide to type in your answers, you will need to use LaTeX to show your work for some problems.

Because you may merge files into a pdf to submit in any order, be sure to assign pages in Gradescope so I can find work for each problem!

# PROBLEMS TO TURN IN: CASI 2.1, CASI 3.1, Add 1, CASI 4.4 a, Add 2, Add 3, CASI 5.3 (modified)

## CASI 2.1

A coin with probability of heads $\theta$ is independently flipped $n$ times, after which $\theta$ is
estimated by

\[
\hat{\theta} = \frac{s+1}{n+2};
\]

with $s$ equal to the number of heads observed.  $\hat{\theta}$ will be referred to as the estimator below.

> (a) What are the bias and variance of the estimator?

SOLUTION: 
$$E(\hat{\theta}) = E\left(\frac{s+1}{n+2}\right) = \frac{E(s+1)}{E(n+2)} = \frac{E(s)+1}{n+2} = \frac{n\theta+1}{n+2}$$

$$Bias(\hat{\theta}) = E(\hat{\theta}) - \theta = \frac{n\theta+1}{n+2} - \theta = \frac{n\theta +1 - n\theta-2\theta}{n+2} = \frac{1-2\theta}{n+2}$$

$$Var(\hat{\theta}) = Var\left(\frac{s+1}{n+2}\right) = \left(\frac{1}{(n+2)^2}\right)Var(s) = \frac{n\theta(1-\theta)}{(n+2)^2}$$

> (b) How would you apply the plug-in principle to get a practical estimate of the standard error of the estimator?

SOLUTION: 
You could apply the plug-in-principle to get a practical estimate of the standard error by using $SE(\theta) = \sqrt{\frac{Var(\theta)}{n}}$ and plugging in the observed $\hat{\theta}$ for $\theta$. This would yield $SE(\hat{\theta}) = \sqrt{\frac{Var(\hat{\theta})}{n}} = \sqrt{\frac{\frac{n\theta(1-\theta)}{(n+2)^2}}{n}} = \sqrt{\frac{n^2\theta(1-\theta)}{(n+2)^2}}$.

\newpage

## CASI 3.1

Suppose the parameter $\mu$ in the Poisson density (3.3, pg. 23 or 24, depending on your version) is known to have prior density
$g(\mu) = e^{-\mu}$. What is the posterior density of $\mu$ given $x$ (a single observation)?

SOLUTION:
The distribution of a single $x$:
$$f(x|\mu) = \frac{e^{-\mu}\mu^x}{x!} \propto e^{-\mu}\mu^x$$
The prior density:
$$g(\mu) = e^{-\mu}$$
So the posterior density:
$$g(\mu|x) \propto g(\mu)f(x|\mu) = (e^{-\mu})(e^{-\mu}\mu^x) = e^{-2\mu}\mu^x$$
Which is a Gamma distribution:
$$\mu^xe^{-2\mu} \sim Gamma(x+1,2)$$

\newpage

## Add 1

Suppose you have a random sample of $n$ observations drawn from a Bernoulli distribution with parameter $\theta$. Further suppose that $\theta$ is unknown, but has a prior density of a Beta($\alpha$, $\beta$) distribution, with both $\alpha$ and $\beta$ greater than 0.

> part a: Find the posterior density for theta given the data. Be sure to fully specify/identify the posterior density in your solution.

SOLUTION: 
The distribution of a single $x$ drawn from Bernoulli distribution:
$$f(x|\theta) = \theta^x(1-\theta)^{1-x}$$
The joint distribution of all the $x$'s:
$$f_n(x|\theta) = \binom nx\theta^x(1-\theta)^{n-x} \propto \theta^x(1-\theta)^{n-x} $$
The prior distribution:
$$g(\theta) = \left[\frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}\right]\theta^{\alpha-1}(1-\theta)^{\beta-1} \propto \theta^{\alpha-1}(1-\theta)^{\beta-1}$$
So the posterior distribution is:
$$g(\theta|x) \propto f_n(x|\theta)g(\theta) \propto \theta^x(1-\theta)^{n-x}\theta^{\alpha-1}(1-\theta)^{\beta-1} = \theta^{x+\alpha-1}(1-\theta)^{n-x+\beta-1}$$
Which is a Beta distribution:
$$g(\theta|x) \propto\theta^{x+\alpha-1}(1-\theta)^{n-x+\beta-1} \sim Beta(\alpha+x,n-x+\beta)$$
> part b: Find the Bayesian estimator for theta (i.e. the posterior mean).

SOLUTION:

Since $g(\theta|x) \sim Beta(\alpha+x,n-x+\beta)$, the posterior mean for $\theta$ is $$\frac{\alpha+x}{\alpha+x+n-x+\beta} = \frac{\alpha+x}{\alpha+n+\beta}$$

\newpage

## CASI 4.4 a

A coin with unknown probability of heads $\theta$ is flipped $n$ times, yielding $x_1$ heads;
then it is flipped another $x_1$ times, yielding $x_2$ heads.

> (a)  What is an intuitively plausible estimate of theta?

SOLUTION: An intuitively plausible estimate of theta is $$\hat{\theta} = \frac{x_1+x_2}{n+x_1}$$.

\newpage

## Add 2

Suppose $X_1 \dots X_n$ are iid from an Exponential distribution with parameter $\beta$, with pdf:

\[
f(x| \beta) = \frac{1}{\beta}exp^{-x/ \beta}, x>0, \beta>0,
\]
and 0, otherwise.

> (a) Find the MLE for beta.

SOLUTION: 
$$f_n(x| \beta) = {\displaystyle \prod_{i=1}^{n}\left(\frac{1}{\beta}e^{-x/ \beta}\right)} = \frac{1}{\beta^n}e^{-(\sum_{i=1}^{n}x)/ \beta}$$

$$\ell(x| \beta) = log(\frac{1}{\beta^n}) + log(e^{-(\sum_{i=1}^{n}x)/ \beta}) = log(1) - nlog(\beta) - \frac{\sum_{i=1}^{n}x}{\beta}$$

$$\ell'(x| \beta) = -\frac{n}{\beta} + \frac{\sum_{i=1}^{n}x}{\beta^2}$$

so $$-\frac{n}{\hat{\beta}_{mle}} + \frac{\sum_{i=1}^{n}x}{\hat{\beta}_{mle}^2} = 0$$

$$\frac{n}{\hat{\beta}_{mle}} = \frac{\sum_{i=1}^{n}x}{\hat{\beta}_{mle}^2}$$

$$\hat{\beta}_{mle} = \frac{\sum_{i=1}^{n}x}{n} = \bar{x}$$

> (b) Verify the MLE is unbiased.

SOLUTION:

$Bias(\hat{\beta}_{mle}) = E(\hat{\beta}_{mle}) - \beta = E(\bar{x}) - \beta = \beta - \beta = 0$. So the MLE is unbiased.

> (c) Find the Fisher information for a single observation.

SOLUTION:
$$f_n(x| \beta) =\frac{1}{\beta}e^{-x/ \beta}$$
$$\ell(x| \beta) = log(\frac{1}{\beta}) + log(e^{-x/ \beta}) = log(1) - log(\beta) - \frac{x}{\beta}$$
$$\ell'(x| \beta) = -\frac{1}{\beta} + \frac{x}{\beta^2}$$
$$\ell''(x| \beta) = \frac{1}{\beta^2} - \frac{2x}{\beta^3}$$
$$E(\ell''(x| \beta)) = E\left(\frac{1}{\beta^2} - \frac{2x}{\beta^3}\right) = \frac{1}{\beta^2} - \frac{2E(x)}{\beta^3} = \frac{1}{\beta^2} - \frac{2\beta}{\beta^3} = \frac{1-2}{\beta^2} = \frac{-1}{\beta^2}$$
$$I_o = -E(\ell''(x| \beta)) = \frac{1}{\beta^2}$$

> (d) Find the Cramer Rao lower bound on variance for unbiased estimators of beta.

SOLUTION:

$I_n(\beta) = nI(\beta) = \frac{n}{\beta^2}$

so the CRLB is $\frac{1}{nI_o} = \frac{1}{I_n(\beta)} = \frac{\beta^2}{n}$

And $Var(\hat{\beta}_{mle})=Var(\bar{x}) = Var\left(\frac{\sum_{i=1}^{n}x}{n}\right) = \frac{1}{n^2}Var\left(\sum_{i=1}^{n}x\right) = \frac{1}{n}Var(x_i) = \frac{\beta^2}{n}$.

Therefore, $\hat{\beta}_{mle}$ is the MVUE.

\newpage

## Add 3

In a few sentences and in your own words, explain what the Neyman-Pearson lemma tells us and why it is important/useful in the context of hypothesis testing.

SOLUTION: The Neyman-Pearson Lemma is a method to determine if the hypothesis test that you are using is the one with the most power at a certain $\alpha$ level. The Neyman-Pearson Lemma can also be used to construct the most powerful test for $\alpha$ using the liklihood ratio. This is useful in the context of hypothesis tests because we can create tests that maximize the power of the test against an alternative hypothesis while minimizing the type II error.

\newpage

## CASI 5.3 (modified)

Note: This problem is only visible in the Student edition of the text, not the pdf, but is typed out for you here since I am modifying it anyway.

Draw a sample of 1000 bivariate normal vectors $x = (x_1, x_2)'$, with
each variable having a mean of 0, a standard deviation of 1, and with a correlation between them of 0.5. Be sure your process is reproducible.

Review the chapter 4 and 5 practice problems for assistance with code.

> (a) Plot your sample of data points.

```{r}
set.seed(3)
sigma <- matrix(c(1, 0.5, 0.5, 1), ncol = 2)
NormData <- as.data.frame(rmvnorm(1000, mean = c(0,0), sigma = sigma))
gf_point(V2 ~ V1, data = NormData)
with(NormData, cor(V1, V2))
```

SOLUTION:

> (b) Following equation 5.19, what should the theoretical distribution of $x_2 | x_1$ be here?

SOLUTION: The theoretical distribution of $x_2 | x_1$ should be:

$$x_2 | x_1 \sim \mathcal{N}\left(\mu_2 + \frac{\sigma_{12}}{\sigma_{11}}(x_1-\mu_1), \sigma_{22}-\frac{\sigma_{12}^2}{\sigma_{11}}\right)$$
$$x_2 | x_1 \sim \mathcal{N}\left(1 + \frac{0.5}{1}(x_1-1), 1-\frac{0.5^2}{1}\right)$$
$$x_2 | x_1 \sim \mathcal{N}\left(1 + 0.5x_1-0.5), 1-0.25\right)$$
$$x_2 | x_1 \sim \mathcal{N}\left(0.5x_1+0.5, 0.75\right)$$

> (c) Regress $x_2$ on $x_1$ and numerically check equation 5.19.

```{r}
lm1 = lm(V1 ~ V2, data = NormData)
msummary(lm1)
```

Hint: Reading the text will help you understand what two things to check in the regression output.

SOLUTION: 
The linear regression coefficient of V2 as a function of V1 is 0.5065 which is close to our theoretical value of $\frac{\sigma_{12}}{\sigma_{11}\sigma_{22}} = \frac{0.5}{1\times1} = 0.5.$ The variance term can also be written as $\sigma_{22}(1-R^2)$ which using the $R^2$ value from the regression output, we get $1(1-0.25) = 0.75$ which is the same variance from our theoretical distribution.

### 2022-09-26 labs/Regularization Lab.Rmd
Clean up

---
title: "Stat 495 - Regularization Lab - Ridge and LASSO"
author: "A.S. Wagaman"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
library(glmnet)
library(ISLR)
library(lars)    # you may need to install some of these (one time only)
library(leaps)   # to use variable selection methods if desired
```

## Ridge Regression

This first example is adapted from ISLR, pages 251-255, from the reproduction of that lab by McNamara and Crouser.

```{r}
data(Hitters)
?Hitters # MLB data from 1986 and 1987; 322 obs on 20 variables
```

We want to predict Salary, which is missing for 59 players. The ridge regression function won't automatically remove NAs, so we do it.

```{r}
Hitters <- na.omit(Hitters) #263 obs now
```

We demo the new functions and code below. Normally, we'd split into a training/test data set here, but we'll do that below after checking out these functions.

The function we'll be using is *glmnet* which can do more than just ridge regression, or *cv.glmnet* for cross-validation.

The format these functions require is not the usual Y ~ X format we are used to. Instead, we need to pass in the X matrix, and Y vector.

```{r}
x <- model.matrix(Salary ~ ., Hitters)[, -1] # trim off the first column

y <- Hitters %>% select(Salary) %>%  unlist() %>%  as.numeric()
```

The `model.matrix()` function is particularly useful for creating X; not only does it produce a matrix corresponding to the 19 predictors but it also automatically transforms any qualitative variables into dummy variables as shown below (if you aren't sure what this means, please ask). The latter property is important because `glmnet()` can only take numerical, quantitative inputs.

```{r}
head(Hitters)
head(x)
```

## Fitting the Ridge Model via an Example

*glmnet* can be used to fit several types of models, so there is an argument to the function governing what type of model is fit. That parameter is $\alpha$, and you want $\alpha=0$ for ridge regression, so you will see that below.

Most of the text and code for the rest of this example is taken from the McNamara and Crouser reproduced lab, though it has been edited to change assignment operators to <- instead of =, and other similar changes/extra comments.

```{r}
grid <- 10^seq(10, -2, length = 100)
ridge_mod <- glmnet(x, y, alpha = 0, lambda = grid)
```

By default the `glmnet()` function performs ridge regression for an automatically
selected range of $\lambda$ values. However, here we have chosen to implement
the function over a grid of values ranging from $\lambda = 10^{10}$ to $\lambda = 10^{-2}$, essentially covering the full range of scenarios from the null model containing
only the intercept, to the least squares fit.

As we will see, we can also compute
model fits for a particular value of $\lambda$ that is not one of the original
grid values. Note that by default, the `glmnet()` function standardizes the
variables so that they are on the same scale. To turn off this default setting,
use the argument `standardize = FALSE`.

(Note: this can have severe implications for your coefficient estimates, which is why TRUE is the default.)

Associated with each value of $\lambda$ is a vector of ridge regression coefficients,
stored in a matrix that can be accessed by `coef()`. In this case, it is a $20 \times 100$
matrix, with 20 rows (one for each predictor, plus an intercept) and 100
columns (one for each value of $\lambda$).

```{r}
dim(coef(ridge_mod))
plot(ridge_mod, label = TRUE)    # Draw plot of coefficients; can label them by variable #
```

We expect the coefficient estimates to be much smaller, in terms of $l_2$ norm,
when a large value of $\lambda$ is used, as compared to when a small value of $\lambda$ is
used. These are the coefficients when $\lambda = 11498$, along with their $l_2$ norm:

```{r}
ridge_mod$lambda[50] #Display 50th lambda value
coef(ridge_mod)[, 50] # Display coefficients associated with 50th lambda value
sqrt(sum(coef(ridge_mod)[-1, 50]^2)) # Calculate l2 norm
```

In contrast, here are the coefficients when $\lambda = 705$, along with their $l_2$
norm. Note the much larger $l_2$ norm of the coefficients associated with this
smaller value of $\lambda$.

```{r}
ridge_mod$lambda[60] #Display 60th lambda value
coef(ridge_mod)[, 60] # Display coefficients associated with 60th lambda value
sqrt(sum(coef(ridge_mod)[-1, 60]^2)) # Calculate l2 norm
```

We can use the `predict()` function for a number of purposes. For instance,
we can obtain the ridge regression coefficients for a new value of $\lambda$, say 50:

```{r}
round(predict(ridge_mod, s = 50, type = "coefficients")[1:20, ], 3)
```

We now split the samples into a training set and a test set in order
to estimate the test error of ridge regression. This uses a 50-50 split. There are multiple ways to do this.

```{r}
set.seed(1) #set in ISLR lab
n <- nrow(Hitters)
train_index <- sample(1:n, 0.5 * n)
test_index <- setdiff(1:n, train_index)

train <- Hitters[train_index, ] 
test <- Hitters[test_index, ]

#further set up for using glmnet
x_train <- model.matrix(Salary ~ ., train)[, -1]
x_test <- model.matrix(Salary ~ ., test)[, -1]

y_train <- train %>%
  select(Salary) %>%
  unlist() %>%
  as.numeric()

y_test <- test %>%
  select(Salary) %>%
  unlist() %>%
  as.numeric()
```

Next we fit a ridge regression model on the training set, and evaluate its MSE on the test set, using $\lambda = 4$. Note the use of the `predict()` function again: this time we get predictions for a test set, by replacing `type="coefficients"` with the `newx` argument.

```{r}
ridge_mod <- glmnet(x_train, y_train, alpha = 0, lambda = grid, thresh = 1e-12)
ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
mean((ridge_pred - y_test)^2)
```

The test MSE is 142199.2. Note that if we had instead simply fit a model
with just an intercept, we would have predicted each test observation using
the mean of the training observations. In that case, we could compute the
test set MSE like this:

```{r}
mean((mean(y_train) - y_test)^2)
```

Comparing the MSEs tells us that the ridge regression is doing better than a model with no predictors.

(If you have any questions about this comparison, please ask for assistance.)

To compare MSEs, we could also get MSE for a model with just an intercept by fitting a ridge regression model with a very large value of $\lambda$. Note that `1e10` means $10^{10}$.

```{r}
ridge_pred <- predict(ridge_mod, s = 1e10, newx = x_test)
mean((ridge_pred - y_test)^2)
```

So fitting a ridge regression model with $\lambda = 4$ leads to a much lower test
MSE than fitting a model with just an intercept. We now check whether
there is any benefit to performing ridge regression with $\lambda = 4$ instead of
just performing least squares regression. Recall that least squares is simply
ridge regression with $\lambda = 0$.

Note: In order for `glmnet()` to yield the exact least squares coefficients when $\lambda = 0$,
we use the argument `exact=T` when calling the `predict()` function. Otherwise, the
`predict()` function will interpolate over the grid of $\lambda$ values used in fitting the
`glmnet()` model, yielding approximate results. Even when we use `exact = T`, there remains
a slight discrepancy in the third decimal place between the output of `glmnet()` when
$\lambda = 0$ and the output of `lm()`; this is due to numerical approximation on the part of
`glmnet()`.

```{r}
#compare coefficients first
lm(Salary ~ ., data = train)
predict(ridge_mod, s = 0, exact = T,  x = x_train, y = y_train, type = "coefficients")[1:20, ]

#this code required some editing due to changes in the functions. The training data had to be added as arguments.
ridge_pred <- predict(ridge_mod, s = 0, newx = x_test, exact = T, x = x_train, y = y_train)
mean((ridge_pred - y_test)^2)
```

It looks like we are indeed improving over regular least-squares!

> What two values are being compared to argue this?

The test set MSE for the lm and for the ridge regression are being compared. The values are 168588.6 for the lm and 142199.2 for the ridge regression with $\lambda = 4$.

Side note: in general, if we want to fit a (unpenalized) least squares model, then we should use the `lm()` function, since that function provides more useful outputs, such as standard errors and $p$-values for the coefficients.

Instead of arbitrarily choosing $\lambda = 4$, it would be better to
use cross-validation to choose the tuning parameter $\lambda$. We can do this using
the built-in cross-validation function, `cv.glmnet()`. By default, the function
performs 10-fold cross-validation, though this can be changed using the
argument `folds`. Note that we set a random seed first so our results will be
reproducible, since the choice of the cross-validation folds is random.

```{r}
set.seed(1)
cv.out <- cv.glmnet(x_train, y_train, alpha = 0) # Fit ridge regression model on training data
bestlam <- cv.out$lambda.min  # Select lambda that minimizes training MSE
bestlam
```

Therefore, we see that the value of $\lambda$ that results in the smallest cross-validation
error is 326.0828. We can also plot the MSE as a function of log($\lambda$):

```{r}
plot(cv.out) # Draw plot of training MSE as a function of log(lambda)
```

Now, we want to find out what the test MSE associated with this value of
$\lambda$ is.

```{r}
ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test) # Use best lambda to predict test data
mean((ridge_pred - y_test)^2) # Calculate test MSE
```

This represents a further improvement over the test MSE that we got using
$\lambda = 4$. Finally, we refit our ridge regression model on the full data set,
using the value of $\lambda$ chosen by cross-validation, and examine the coefficient
estimates.

```{r}
out <- glmnet(x, y, alpha = 0) # Fit ridge regression model on full dataset
predict(out, type = "coefficients", s = bestlam)[1:20,] # Display coefficients using lambda chosen by CV
```

As expected, none of the coefficients are exactly zero - ridge regression does not
perform variable selection!

## Example Lasso Fitting

Lasso stands for least absolute shrinkage and selection operator and was developed by Tibshirani.

We can fit these models with either the lars package or glmnet.

```{r, message=FALSE}
data(diabetes)
head(diabetes, 2)
```

We demo the lasso code on the same data set used in the original LARS paper (2002) with the lars package. Note the setup (you can check the help file for details) uses a matrix of predictors and then the response as we saw before with glmnet.

```{r}
object1 <- with(diabetes, lars(x, y, type = "lasso"))
plot(object1)
coef(object1)
summary(object1)
```

The type you set has implications for the solution. The lasso option is the default. But you can also get the lar (without the lasso modification for if a nonzero coefficient hits zero) solution and forward stagewise solution (forward but in very small steps) via the lars algorithm (not quite forward selection).

```{r}
object2 <- with(diabetes, lars(x, y, type = "lar"))
summary(object2)
plot(object2)
object3 <- with(diabetes, lars(x, y, type = "forward.stagewise"))
summary(object3)
plot(object3)
```

What differences do you see in the solutions here based on type? Which models would you pick for each option of "type"? How do those models differ?

## Your turn - Boston crime

Now that you've seen how to fit ridge and lasso models, let's try it out on another data set. Work in groups of 2 or 3 to help each other and discuss your results.

Your goal is to predict per capita crime rate in the Boston data set using ridge regression, lasso, and MLR model(s) of your choosing. How do the models compare? Which do you prefer? Feel free to look up the help file on the data set for more information about the variables.

```{r}
Boston <- MASS::Boston #do NOT load the MASS library - it causes conflicts with dplyr
names(Boston)
```

a) Start by fitting and comparing ridge and LASSO regressions. The Ridge regression (chapter 7 for code) has been fit for you, with a training data set of 50% of the observations.

```{r}
set.seed(495)
xBos <- model.matrix(crim ~ ., Boston)[ , -1]  
yBos <- Boston$crim
grid <- 10^seq(10, -2, length = 100)

n <- nrow(Boston)
train_index <- sample(1:n, 0.5 * n)
test_index <- setdiff(1:n, train_index)
trainBos <- Boston[train_index, ] 
testBos <- Boston[test_index, ]
yBos.test <- yBos[test_index]
```

That was the data setup for the glmnet function. Here is the ridge fit with cross-validation used to choose the tuning parameter.

```{r}
ridgeBos.mod <- glmnet(xBos[train_index,], yBos[train_index], alpha = 0, lambda = grid)
set.seed(495)
cvBos.out <- cv.glmnet(xBos[train_index,], yBos[train_index], alpha = 0)
plot(cvBos.out)
bestlamBos <- cvBos.out$lambda.min
bestlamBos
```

Once we have the best lambda chosen by CV, we can look at the test MSE, etc.

```{r}
ridgeBos.pred <- predict(ridgeBos.mod, s = bestlamBos, newx = xBos[test_index,])
mean((ridgeBos.pred - yBos.test)^2)
plot(ridgeBos.mod)
#coef(ridgeBos.mod) #can see coefs for all lambdas...
predict(ridgeBos.mod, type = "coefficients", s = bestlamBos)[1:14,]
```

Now you should fit the lasso model. Try fitting it via both the glmnet (change the alpha!) and lars functions.

```{r}

```

What differences do you see in the models? Between the ridge and lasso fits?

b) Propose a model (or set of models) that seem to perform well on this data set, and justify your answer. Make sure that you are evaluating model performance using validation set error, cross- validation, or some other reasonable alternative, as opposed to using training error.

SOLUTION:

```{r}

```

(c) Does your chosen model involve all of the features in the data set? Why or why not?

```{r}

```

### 2022-10-05 Midterm Materials/MidtermPracticeQuestions.Rmd
Upload various hmks

---
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

# Stat 495 - Midterm Practice Questions

```{r, include = FALSE}
library(mosaic)
library(glmnet)
library(ISLR)
library(rpart)
library(rpart.plot)
options(digits = 6)
```

## Add 1

A random variable $X$ is a member of an exponential family if its density $f(x| \theta)$ can be written as:

\[
f(x | \theta) = a(\theta)b(x) \exp \left[ c(\theta) d(x) \right],
\]

where $a()$ and $c()$ are functions only of the parameter $\theta$, and $b()$ and $d()$ are functions of $x$.

Verify that the Binomial distribution is an exponential family. Note, $X ~ Bin(n,p)$ has pmf given by:

\[
P(X=x|p) =(n \; \mbox{choose} \; x)p^x(1-p)^{n-x}. 
\]

## Add 2

Describe how to obtain a bootstrap distribution for a chosen statistic and obtain a (say) 95 percent confidence interval for its related parameter of interest.

## Add 3

Explain the plug-in principle in relation to obtaining the standard error of a sample proportion.

## Add 4

Explain what a Bayesian conjugate family is and what its benefits are.

## Add 5

Using the Chapter 8 Lab data set for context, explain how to perform a permutation test to see whether the mean age differs for individuals with monthly income > 7500 versus individuals with less than that monthly income.

```{r}
credit <- read.csv("https://awagaman.people.amherst.edu/stat495/creditsample.csv", header = T)
```

## Add 6

The diabetes data set (loaded below) is used to demonstrate ridge regression in Chapter 7.

```{r}
diabetes <- read.csv("http://web.stanford.edu/~hastie/CASI_files/DATA/diabetes.csv", header = TRUE)
diabetes <- select(diabetes, -X)
```

The data was pre-processed. The text states that the predictors were standardized to mean 0 and sum of squares 1, and the response had it's mean subtracted off (i.e. it was centered), but not scaled.

```{r}
n <- nrow(diabetes)
diabetes2 <- mutate(diabetes, prog = scale(prog, scale = FALSE),
                    age = scale(age)/sqrt(n-1),
                    sex = scale(sex)/sqrt(n-1),
                    bmi = scale(bmi)/sqrt(n-1),
                    map = scale(map)/sqrt(n-1),
                    tc = scale(tc)/sqrt(n-1),
                    ldl = scale(ldl)/sqrt(n-1),
                    hdl = scale(hdl)/sqrt(n-1),
                    tch = scale(tch)/sqrt(n-1),
                    ltg = scale(ltg)/sqrt(n-1),
                    glu = scale(glu)/sqrt(n-1))
```

```{r}
#so you can see the matrix algebra to verify sum of squares 1
x <- model.matrix(prog ~ ., diabetes2)[, ]
y <- diabetes2 %>% select(prog) %>%  unlist() %>%  as.numeric()
S <- t(x) %*% x
diag(S)
```

Note that while you'd usually want a training/test set here, the book used the entire data set, so you should do that to try to verify their work.

(a) Use OLS to predict *prog* using *diabetes2* and verify you obtain the results in Table 7.3.
(b) Use ridge regression with lambda = 0.1 and verify you obtain the results in Table 7.3.
(c) Explain what cross-validation is (generally), and how it can be used to help choose a lambda in ridge regression.
(d) Use CV with ridge regression to select your lambda running the default grid through glmnet (i.e. don't specify a grid). What lambda is selected?
(e) Implement LASSO with CV to select your lambda running the default grid through glmnet. What lambda is selected? 
(f) Implement a regression tree to predict *prog*. What cp corresponds to the default tree? 
(g) Explain why we don't need a *glm* here to predict *prog*. 
(h) Which model of these do you prefer? How do the fits differ? (Hint: Besides comparing coefficients/involved variables, you can compare MSEs.)

## Add 7

The Spam email data set (loaded below) is used to demonstrate logistic regression and classification trees in Chapter 8. Note that while you'd usually want a training/test set here, the book used the entire data set, so you should do that to try to verify their work.

```{r}
spam <- read.csv("http://web.stanford.edu/~hastie/CASI_files/DATA/SPAM.csv", header = TRUE)
```

(a) Why does it not make sense to use OLS to predict *spam*?
(b) Use logistic regression to predict *spam*. Verify you obtain the results in Table 8.3.
(c) Obtain a confusion matrix for the logistic regression. How well is the model doing?
(d) Use a classification tree to predict *spam*. Attempt to obtain the tree in Figure 8.7. Note that you may need to prune or adjust control parameters to obtain this tree. If you cannot obtain the tree, obtain one you want to work with for part e below.
(e) Obtain a confusion matrix for your classification tree. How do your error rates compare to those reported in Figure 8.7? 
(f) Which method do you prefer for predicting *spam*?

## CASI 8.6

```{r}
galaxy <- read.table("http://web.stanford.edu/~hastie/CASI_files/DATA/galaxy.txt", header = TRUE)
```

Data set description: Table of counts of galaxies binned into categories defined by redshift and magnitude. The column labels are log-redshift values, and the row labels magnitude.

Fit the Poisson regression model (8.39) to the galaxy data.

(Note that some data wrangling is required based on how the data is provided.)

## Add 8

```{r}
data(Credit)
Credit <- select(Credit, -ID)
```

You may want to look over the help file for this data set. Note that the number of observations stated there is inaccurate. Our goal is to predict Balance. Do not worry about transforming Balance or any of the other predictors here.

(a) Create an appropriate training/test split using a 75/25 percent split. 
(b) Perform best subsets and choose a model based on an appropriate descriptive statistic. Compute the test MSE.  
(c) Perform forward selection and choose a model based on an appropriate descriptive statistic. Compute the test MSE.  
(d) Perform the lasso and choose a model based on an appropriate descriptive statistic. Compute the test MSE.  
(e) Fit an elastic-net penalty with alpha = 0.5, and choose a model based on an appropriate descriptive statistic. Compute the test MSE.  
(f) How do your models compare? Which model do you prefer? Why? (Should be able to compare coefficients.)

## Add 9

```{r, fig.width = 6, fig.height = 4}
data(iris)
glimpse(iris)

# for parts a and b
iris.control <- rpart.control(minbucket = 10, minsplit = 30)
iris.rpart <- rpart(Petal.Length ~ . - Species, data = iris, method = "anova",
                  control = iris.control)
rpart.plot(iris.rpart)

# for part c
iris[121,]

# for part d sketch
favstats(~ Petal.Width, data = iris)
favstats(~ Sepal.Length, data = iris)
```

(a) Is this a classification or a regression tree? How do you know?
(b) Explain what the minbucket and minsplit control options do.
(c) What is the residual for observation 121? (Residual = observed - predicted response value) 
(d) Only 2 variables are used in the tree. Sketch the hypercubes formed in 2-D space, labeling them with their predicted response values.

### 2022-10-05 homework/hmk1/hmk1Stat495F22.tex
Upload various hmks

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Homework 1 - Stat 495},
  pdfauthor={Justin Papagelis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Homework 1 - Stat 495}
\author{Justin Papagelis}
\date{Due Monday, Sept.~12th by midnight}

\begin{document}
\maketitle

\hypertarget{practicing-academic-integrity}{%
\section{Practicing Academic
Integrity}\label{practicing-academic-integrity}}

If you worked with others or used resources outside of provided course
material (anything besides our textbook(s), course materials in Moodle,
R help menu) to complete this assignment, please acknowledge them below
using a bulleted list.

\emph{I acknowledge the following individuals with whom I worked on this
assignment:}

Name(s) and corresponding problem(s)

\begin{itemize}
\tightlist
\item
\end{itemize}

\emph{I used the following sources to help complete this assignment:}

Source(s) and corresponding problem(s)

\begin{itemize}
\tightlist
\item
\end{itemize}

\newpage

\hypertarget{problems-to-turn-in-vis-1-vis-2-casi-1.1-casi-1.4-portfolio-reflection}{%
\section{PROBLEMS TO TURN IN: Vis 1, Vis 2, CASI 1.1, CASI 1.4,
Portfolio
Reflection}\label{problems-to-turn-in-vis-1-vis-2-casi-1.1-casi-1.4-portfolio-reflection}}

\hypertarget{visualization-problems-adapted-from-an-assignment-by-prof.-horton}{%
\subsection{Visualization Problems (Adapted from an assignment by
Prof.~Horton)}\label{visualization-problems-adapted-from-an-assignment-by-prof.-horton}}

The first two ``problems'\,' require you to find two visuals to discuss,
and incorporate them in a .Rmd file. To find these visuals, we will
practice finding journal articles from two sources - the JSTOR database
and Google Scholar.

Your task is to select two visual displays from journal articles that
apply statistics (they do not need to be in statistics research
journals, but could be). One should be selected as a visual display that
you find compelling. The other should be a visual display that you
believe is suboptimal or could be improved.

One visual must come from JSTOR and the other from Google Scholar. You
must include the article citation and figure information (which figure
is it in the article) with each figure. (Citations are more than a URL.)

You should include both images below and a brief commentary for each on
why you picked them and why they are compelling or suboptimal,
respectively.

Instructions for accessing and using JSTOR and Google Scholar:

Google Scholar can be found at the link here
\href{https://scholar.google.com/}{Google Scholar}.

JSTOR is one of the journal databases available through the College. To
get to it, you can:

\begin{itemize}
\tightlist
\item
  Head to the \href{https://www.amherst.edu/library}{Library} page.
\item
  Click the link (roughly in middle of page) to Browse `A-Z Databases'.
\item
  Head to the J's and click JSTOR.
\end{itemize}

What should you search for in these two places to find visuals for this
assignment?

\begin{itemize}
\tightlist
\item
  Think of a statistical method you are comfortable reading about.
  Examples - regression, ANOVA, etc.
\item
  Think of an application area you'd like to find an article in.
\item
  Put the application area in a search field (or in JSTOR, select
  journals from that field - left menu) and the topic in another field
\item
  Look at the search results this generates and pick an article to look
  at.
\item
  See if any of the figures in the article strike you. If not, go look
  at another article.
\end{itemize}

Instructions to include visuals in a .Rmd:

Once you identify appropriate visuals, you need to save them in a format
that can be put in RMarkdown. .png files work, but other file formats
can work as well.

Below are two examples of how visuals can be included in a .Rmd. Part of
the purpose of this assignment is so that you learn how to add images to
.Rmds looking ahead to the final paper. The image file should be in the
current directory (see the output of ``getwd()''). See
\url{http://rmarkdown.rstudio.com/authoring_basics.html} for more
details. DELETE these examples before submission.

\begin{figure}
\centering
\includegraphics{tukey_bulge.png}
\caption{Visual of Tukey Transform Suggestions - Method 1}
\end{figure}

\begin{figure}[htbp] 
\centering 
\includegraphics[width=4in]{tukey_bulge.png} 
\caption{Visual of Tukey Transform Suggestions - Method 2}
\end{figure}

\hypertarget{vis-1---compelling}{%
\subsection{Vis 1 - Compelling}\label{vis-1---compelling}}

\hypertarget{vis-2---suboptimal}{%
\subsection{Vis 2 - Suboptimal}\label{vis-2---suboptimal}}

\newpage

\hypertarget{casi-1.1}{%
\subsection{CASI 1.1}\label{casi-1.1}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{kidney }\OtherTok{\textless{}{-}} \FunctionTok{read.table}\NormalTok{(}\StringTok{"http://web.stanford.edu/\textasciitilde{}hastie/CASI\_files/DATA/kidney.txt"}\NormalTok{, }\AttributeTok{header =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  Fit a cubic regression, as a function of age, to the kidney data of
  Figures 1.1 and 1.2, calculating estimates and standard errors at ages
  20, 30, 40, 50, 60, 70, 80.
\end{enumerate}
\end{quote}

SOLUTION:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Hint, augment is likely to be useful here (loaded in broom package above)}

\NormalTok{kidney }\OtherTok{\textless{}{-}} \FunctionTok{mutate}\NormalTok{(kidney, }\AttributeTok{totSq =}\NormalTok{ (tot)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{, }\AttributeTok{totCu =}\NormalTok{ (tot)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}

\NormalTok{lm1 }\OtherTok{=} \FunctionTok{lm}\NormalTok{(age }\SpecialCharTok{\textasciitilde{}}\NormalTok{ tot }\SpecialCharTok{+}\NormalTok{ totSq }\SpecialCharTok{+}\NormalTok{ totCu, }\AttributeTok{data =}\NormalTok{ kidney)}

\FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ kidney, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ age, }\AttributeTok{y =}\NormalTok{ tot)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{hmk1Stat495F22_files/figure-latex/unnamed-chunk-5-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(lm1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = age ~ tot + totSq + totCu, data = kidney)
## 
## Residuals:
##    Min     1Q Median     3Q    Max 
## -27.69  -7.95  -2.19   4.86  39.66 
## 
## Coefficients:
##             Estimate Std. Error t value Pr(>|t|)    
## (Intercept) 33.75153    1.23179   27.40  < 2e-16 ***
## tot         -3.94479    0.79948   -4.93  2.1e-06 ***
## totSq        0.55736    0.15557    3.58  0.00046 ***
## totCu        0.00403    0.04498    0.09  0.92879    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 12.6 on 153 degrees of freedom
## Multiple R-squared:  0.385,  Adjusted R-squared:  0.373 
## F-statistic: 31.9 on 3 and 153 DF,  p-value: 4.5e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pred }\OtherTok{=} \FunctionTok{augment}\NormalTok{(lm1, }\AttributeTok{se\_fit =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(age}\SpecialCharTok{\%\%}\DecValTok{10} \SpecialCharTok{==} \DecValTok{0}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(age, .fitted, .se.fit) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{rename}\NormalTok{(}\StringTok{"Age"} \OtherTok{=}\NormalTok{ age, }\StringTok{"Estimates"} \OtherTok{=}\NormalTok{ .fitted, }\StringTok{"Standard Errors"} \OtherTok{=}\NormalTok{ .se.fit)}

\NormalTok{ pred }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\AttributeTok{bookends =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}rrr@{}}
\toprule()
Age & Estimates & Standard Errors \\
\midrule()
\endhead
20 & 27.6760 & 1.68969 \\
30 & 29.0573 & 1.51572 \\
30 & 31.7179 & 1.29991 \\
30 & 33.5557 & 1.23420 \\
30 & 34.2329 & 1.22953 \\
60 & 34.1516 & 1.22955 \\
60 & 49.1481 & 1.99318 \\
60 & 42.1650 & 1.61062 \\
70 & 30.3400 & 1.39696 \\
80 & 68.2063 & 4.07611 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Do you remember how to add powers to a regression? You can also use mutate. }
\CommentTok{\# Be sure you actually get a cubic regression! }
\CommentTok{\# The model must show the appropriate terms.}
\end{Highlighting}
\end{Shaded}

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  How do the results compare with those in Table 1.1?
\end{enumerate}
\end{quote}

SOLUTION:

\newpage

\hypertarget{casi-1.4---slightly-modified}{%
\subsection{CASI 1.4 - Slightly
Modified}\label{casi-1.4---slightly-modified}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load and format data}
\NormalTok{leukemia\_big }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"http://web.stanford.edu/\textasciitilde{}hastie/CASI\_files/DATA/leukemia\_big.csv"}\NormalTok{)}
\CommentTok{\# says pictures from row 136}
\NormalTok{gene136 }\OtherTok{\textless{}{-}} \FunctionTok{t}\NormalTok{(leukemia\_big[}\DecValTok{136}\NormalTok{, ]) }\CommentTok{\#says pictures from row 136}
\CommentTok{\# Need to get ALL and AML tags in}
\NormalTok{type }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\StringTok{"ALL"}\NormalTok{, }\DecValTok{20}\NormalTok{), }\FunctionTok{rep}\NormalTok{(}\StringTok{"AML"}\NormalTok{, }\DecValTok{14}\NormalTok{), }\FunctionTok{rep}\NormalTok{(}\StringTok{"ALL"}\NormalTok{, }\DecValTok{27}\NormalTok{), }\FunctionTok{rep}\NormalTok{(}\StringTok{"AML"}\NormalTok{, }\DecValTok{11}\NormalTok{))}

\CommentTok{\# Set up dataset}
\NormalTok{leukemia }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(gene136, type)}
\NormalTok{leukemia }\OtherTok{\textless{}{-}} \FunctionTok{rename}\NormalTok{(leukemia, }\AttributeTok{gene136 =}\NormalTok{ X136)}
\FunctionTok{favstats}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ gene136 }\SpecialCharTok{|}\NormalTok{ type, }\AttributeTok{data =}\NormalTok{ leukemia)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   type      min       Q1   median       Q3     max     mean       sd  n missing
## 1  ALL 0.210578 0.560344 0.732703 0.855127 1.63400 0.752479 0.275342 47       0
## 2  AML 0.324703 0.771426 0.967796 1.096250 1.42548 0.949973 0.243019 25       0
\end{verbatim}

We want to see if there is a significant difference in mean gene
expression for gene 136 for the ALL and AML groups.

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  Record the means of the ALL and AML groups for the gene 136 data
  available for reference.
\end{enumerate}
\end{quote}

SOLUTION: The mean of the ALL group for the gene 136 is 0.752 and the
mean of the AML group for the gene 136 is 0.950.

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Perform 1000 nonparametric bootstrap replications for the mean of ALL
  for gene 136. Describe the distribution of the resulting means. You
  can perform the bootstrap in any way you see fit (the functions do and
  resample might prove useful).
\end{enumerate}
\end{quote}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{leukemia\_ALL }\OtherTok{\textless{}{-}}\NormalTok{ leukemia }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(type }\SpecialCharTok{==} \StringTok{"ALL"}\NormalTok{)}

\NormalTok{leukemia\_ALL}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##         gene136 type
## ALL    0.918695  ALL
## ALL.1  1.634002  ALL
## ALL.2  0.459587  ALL
## ALL.3  0.637966  ALL
## ALL.4  0.344038  ALL
## ALL.5  0.861478  ALL
## ALL.6  0.513218  ALL
## ALL.7  0.979090  ALL
## ALL.8  0.210578  ALL
## ALL.9  0.801607  ALL
## ALL.10 0.600695  ALL
## ALL.11 0.361437  ALL
## ALL.12 1.046320  ALL
## ALL.13 0.969763  ALL
## ALL.14 0.487316  ALL
## ALL.15 0.497636  ALL
## ALL.16 1.101717  ALL
## ALL.17 0.856394  ALL
## ALL.18 0.661415  ALL
## ALL.19 0.817711  ALL
## ALL.20 0.567954  ALL
## ALL.21 0.846290  ALL
## ALL.22 0.883862  ALL
## ALL.23 0.723993  ALL
## ALL.24 0.732703  ALL
## ALL.25 0.782362  ALL
## ALL.26 0.543540  ALL
## ALL.27 0.832537  ALL
## ALL.28 0.552733  ALL
## ALL.29 0.732703  ALL
## ALL.30 0.551095  ALL
## ALL.31 0.821401  ALL
## ALL.32 0.641850  ALL
## ALL.33 0.720798  ALL
## ALL.34 0.583100  ALL
## ALL.35 0.765757  ALL
## ALL.36 0.526298  ALL
## ALL.37 1.466999  ALL
## ALL.38 0.544559  ALL
## ALL.39 0.572505  ALL
## ALL.40 1.362768  ALL
## ALL.41 0.853353  ALL
## ALL.42 0.813298  ALL
## ALL.43 0.853860  ALL
## ALL.44 0.568988  ALL
## ALL.45 0.693035  ALL
## ALL.46 1.067526  ALL
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{boot }\OtherTok{\textless{}{-}} \FunctionTok{bootstrap}\NormalTok{(}\AttributeTok{data =}\NormalTok{ leukemia\_ALL, }\FunctionTok{mean}\NormalTok{(leukemia\_ALL}\SpecialCharTok{$}\NormalTok{gene136), }\AttributeTok{R =} \DecValTok{1000}\NormalTok{, }\AttributeTok{seed =} \DecValTok{0}\NormalTok{ )}

\CommentTok{\#resample(leukemia\_ALL, resampleFun = mean, replace = TRUE)}
\end{Highlighting}
\end{Shaded}

SOLUTION:

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  Repeat (b) for AML.
\end{enumerate}
\end{quote}

SOLUTION:

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  Suggest an inference. In other words, what do your results in (b) and
  (c) suggest about whether there is a difference in means for the ALL
  and AML groups for gene 136?
\end{enumerate}
\end{quote}

SOLUTION:

\begin{quote}
\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Brainstorm an alternative way to approach the problem via a
  randomization/permutation test. Describe what you would do in a way
  that someone else could code it up. (You do not need to actually code
  this up, but you can if you want to see what the result is.)
\end{enumerate}
\end{quote}

SOLUTION:

\newpage

\hypertarget{portfolio-reflection}{%
\subsection{Portfolio Reflection}\label{portfolio-reflection}}

Look at our portfolio review and in-class activities. In a separate word
or pdf document, in a few paragraphs, reflect on how the items in your
portfolio demonstrate:

\begin{itemize}
\tightlist
\item
  how your statistical analytical skills have developed over time
\item
  how your statistical writing skills have developed over time
\item
  skills you have a solid grasp of (such as R code or visuals or
  regression)
\item
  skills you would like to improve on
\end{itemize}

Then, set some goals for what you'd like to work on improving in future
statistical reports. (Yes, you brainstormed some before, this is asking
you to pick some to really focus on!)

Upload this portfolio reflection and goals document for future reports
to your portfolio folder in your personal class repo.

Given what you are asked to include, I expect the document to have at
least 3 paragraphs and contain at least 3 goals for future work.

\end{document}

### 2022-10-05 homework/hmk3/hmk3Stat495F22.Rmd
Upload various hmks

---
title: "Homework 3 - Stat 495"
author: "Justin Papagelis"
date: "Due Friday, Sept. 30th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(ISLR)
library(glmnet)

library(lars)    # you may need to install some of these (one time only)
library(leaps)   # to use variable selection methods if desired
options(digits = 6)
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle/Git repo, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

* https://glmnet.stanford.edu/articles/glmnet.html, 2. (g)

\newpage

# PROBLEMS TO TURN IN: Add(itional) 1-2

## Add 1 - Applications to College

Adapted from ISLR

```{r}
data(College)
```

This data set contains information from 1995 on US Colleges from US News and World Report (see help file for details). Our goal is to predict the number of applications received (Apps) using the other variables as potential predictors.

> part a: Split the data into training and test data sets. (2/3 - 1/3 split is fine.)

SOLUTION:
```{r}
set.seed(1)
n <- nrow(College)
train_index <- sample(1:n, 2/3 * n)
test_index <- setdiff(1:n, train_index)

train <- College[train_index, ]
test <- College[test_index, ]

xColl <- model.matrix(Apps ~ ., College)[, -1]
yColl <- College$Apps

yColl.test <- yColl[test_index]
#n

```

\newpage
> part b: Fit a "kitchen sink" linear regression model on the training set. Report the test error obtained, and comment on any issues with the model (such as conditions, etc.).

SOLUTION:

The test error that is obtained from this model is 1218487. From the residuals vs fitted plot, there appears to be some issues with linearity because the residuals are clumped to the left of the graph and fan out towards the right. There also appears to be some issues with the Normality condition because the Q-Q Plot deviates from a linear relationship.

```{r}
mod1 <- lm(Apps ~ ., data = train)
summary(mod1)

plot(mod1, 1)
plot(mod1, 2)

full_pred <- predict.lm(mod1, test)

mean((full_pred - yColl.test)^2)

```

\newpage
> part c: Fit a linear regression model using an automated variable selection method of your choice (from Stat 230) on the training set. Report the test error obtained, and comment on any issues with the model (such as conditions, etc.).

SOLUTION: The test error that is obtained from this model is 1200584. There appears to be similar issues with this model as the previous one with Linearity and Normality.

```{r}
intercept_only <- lm(Apps ~ 1, data = train)

all <- lm(Apps ~ ., data = train)

both <- MASS::stepAIC(intercept_only, direction = 'both', scope = list(upper = all, lower = ~1), trace = FALSE)

both$anova
#both$coefficients

summary(both)
plot(both, 1)
plot(both, 2)

selection_pred <- predict.lm(both, test)
mean((selection_pred - yColl.test)^2)
```

\newpage
> part d: Fit a ridge regression model on the training set, with lambda chosen by cross-validation. Report the lambda chosen and the test error obtained.

SOLUTION:

```{r}
xColl <- model.matrix(Apps ~ ., College)[, -1]
yColl <- College$Apps

x_train <- model.matrix(Apps ~ ., train)[, -1]
x_test <- model.matrix(Apps ~ ., test)[, -1]

y_train <- train %>%
  select(Apps) %>%
  unlist() %>%
  as.numeric()

y_test <- test %>%
  select(Apps) %>%
  unlist() %>%
  as.numeric()

grid <- 10^seq(10, -2, length = 100)

ridge_mod <- glmnet(x_train, y_train, alpha = 0, lambda = grid)

plot(ridge_mod, label = TRUE)
#ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
#mean((ridge_pred - y_test)^2)

set.seed(1)

cv.out <- cv.glmnet(x_train, y_train, alpha = 0)
bestlam <- cv.out$lambda.min
bestlam

plot(cv.out)

predict(cv.out, type = "coefficients", s = bestlam)[1:18,]

ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test)
mean((ridge_pred - y_test)^2)

```
The lambda that was chosen by cross-validation is 369.655 and the test error obtained was 1111300.

\newpage
> part e: Fit a lasso model on the training set, with lambda chosen by cross-validation. Report the lambda chosen and the test error obtained.

SOLUTION: The lambda that was chosen was 1.97274 and the test error obtained was 1210193.

```{r}
set.seed(1)
cvlassoCol.mod <- cv.glmnet(xColl[train_index,], yColl[train_index], alpha = 1)

plot(cvlassoCol.mod)

bestlamColl <- cvlassoCol.mod$lambda.min
bestlamColl

predict(cvlassoCol.mod, type = "coefficients", s = bestlamColl)[1:18,]
```
```{r}
lassoCol.pred <- predict(cvlassoCol.mod, s = bestlamColl, newx = xColl[test_index,])
mean((lassoCol.pred - yColl.test)^2)
```

\newpage
> part f: Comment on the results obtained across the four models. Address the following questions as part of your response. Do the test errors differ much? Do the coefficients differ greatly? In particular, if any variables were left out of the model in (c) or (e), is there any insight that they might have been removed based on the models in (b) or (d)? Which final model would you select here? Why?

SOLUTION:

The MSE for the "kitchen sink" model is 1,218,487. The MSE for the model that was obtained using Stepwise Regression has an MSE of 
1,200,584 which is a slight decrease from the kitchen sink model. The MSE for the ridge model is 1,111,300 which is a greater improvement on the Stepwise Regression model. Finally, the MSE for the lasso model is 1,210,193 which is worse than the ridge model. Relatively, the test MSEs were similar except for the ridge model which was lower than the rest. It appears the the coefficients for the linear regression models are similar, but the coefficients for the ridge and lasso models are different.

The variables that were left out of the model in (c) were `PrivateYes, F.Undergrad, Outstate, Books, Personal, Terminal, S.F.Ratio, perc.alumni` which are many of the predictors that are not significant in the kitchen sink model. In the ridge regression model, none of the coefficients are made too small, which might be why none of the predictors are removed in the lasso model. We would select the ridge regression model in this case because since it had the smallest MSE for the test set, the model had the best predictions.

\newpage

## Add 2 - Soil predictions

The data comes from a Kaggle competition: https://www.kaggle.com/c/afsis-soil-properties. The original data set contained 3600 variables, 3599 possible predictors (really, 3578 and some other variables) and a response, Sand. The 3599 predictors were reduced to 106 (methods to be taught later this semester) that can "best" distinguish between the two levels of Depth (another variable in the data set). The resulting data set of 107 variables (106 predictors and the response, Sand) was saved in the data set "newsoil". The row numbers should be removed as demonstrated below.

```{r}
newsoil <- read.csv("https://awagaman.people.amherst.edu/stat495/newsoil.csv",
                    header = T)
newsoil <- select(newsoil, -X)
#names(newsoil)
```

Our focus is on predicting the response variable Sand, using the selected variables from previous work.

\newpage

> part a: Split the data set into a training and test set (75/25), with a seed of your choice. (Hint: see lab for code.) You may also wish to create appropriate x and y matrices for future function inputs at the same time.

SOLUTION:

```{r}
set.seed(1)
n <- nrow(newsoil)
train_index_soil <- sample(1:n, 3/4 * n)
test_index_soil <- setdiff(1:n, train_index_soil)

train_soil <- newsoil[train_index_soil, ]
test_soil <- newsoil[test_index_soil, ]

xSoil <- model.matrix(Sand ~ ., newsoil)[, -1]
ySoil <- newsoil$Sand

ySoil.test <- ySoil[test_index_soil]

```

\newpage
> part b: Fit lasso models to predict Sand using all the possible predictors. Choose two lasso models - one that has a "best" lambda determined in some appropriate way, and another model with a different non-zero lambda of your choice. How many slope coefficients are set to 0 in each of your chosen lasso models?

SOLUTION: There are 37 coefficients set to 0 in the model with the "best" lambda of 0.000119548 which was found using cross-validation. We made another lasso model with a lambda of 0.001 which 79 of the coefficients were set to 0.

FINSIH ANSWER

```{r}
set.seed(1)
cvlassoSoil.mod <- cv.glmnet(xSoil[train_index_soil,], ySoil[train_index_soil], alpha = 1)

plot(cvlassoSoil.mod)

bestlamSoil <- cvlassoSoil.mod$lambda.min
bestlamSoil

predict(cvlassoSoil.mod, type = "coefficients", s = bestlamSoil)[1:107,]

```

```{r}
set.seed(1)
lassoSoil.mod <- glmnet(xSoil[train_index_soil,], ySoil[train_index_soil], alpha = 1, lambda = 0.001)

plot(lassoSoil.mod)

predict(lassoSoil.mod, type = "coefficients", s = 0.001)[1:107,]

```
\newpage
> part c: Fit a ridge model to predict Sand using all the possible predictors. How many slope coefficients are set to 0 in your ridge model?

SOLUTION: None of the slope coefficients are set to 0 in the ridge model.

```{r, fig.height = 4, fig.width = 6}

x_train_soil <- model.matrix(Sand ~ ., train_soil)[, -1]
x_test_soil <- model.matrix(Sand ~ ., test_soil)[, -1]

y_train_soil <- train_soil %>%
  select(Sand) %>%
  unlist() %>%
  as.numeric()

y_test_soil <- test_soil %>%
  select(Sand) %>%
  unlist() %>%
  as.numeric()

grid <- 10^seq(10, -2, length = 100)

ridge_mod_soil <- glmnet(x_train_soil, y_train_soil, alpha = 0, lambda = grid)

plot(ridge_mod_soil, label = TRUE)
```

```{r}
set.seed(1)

cv.out <- cv.glmnet(x_train_soil, y_train_soil, alpha = 0)
bestlam <- cv.out$lambda.min
bestlam

predict(cv.out, type = "coefficients", s = bestlam)[1:107,]

plot(cv.out)

```

\newpage
> part d: Compute test MSEs for both of your lasso models and your ridge model.

SOLUTION:

The test MSE for the Cross-Validated Lasso Model was 0.262755. The test MSE for the Lasso Model with a lambda of 0.001 is 0.30326. The test MSE for the ridge model is 0.349251.

```{r}
# test MSE for CV Lasso
cvlassoSoil.pred <- predict(cvlassoSoil.mod, s = bestlamSoil, newx = xSoil[test_index_soil,])
mean((cvlassoSoil.pred - ySoil.test)^2)

# test MSE for Lasso
lassoSoil.pred <- predict(lassoSoil.mod, s = 0.001, newx = xSoil[test_index_soil,])
mean((lassoSoil.pred - ySoil.test)^2)

# test MSE for ridge model
ridge_pred_soil <- predict(ridge_mod_soil, s = bestlam, newx = xSoil[test_index_soil,])
mean((ridge_pred_soil - ySoil.test)^2)
```

\newpage
> part e: Write a few sentences to address the following questions. Does the test MSE from the model with the "best" lambda suggest it is in fact a better predictive model than your other lasso model? Is ridge better than the lasso models? Which final model would you choose here from these three models? Why?

SOLUTION:
The test MSE for the model with the "best" lambda appears to be a better predictive model than the other lasso model because the test MSE for the cross-validated lambda model is 0.262755 whereas the test MSE for the other lasso model is 0.30326. It also appears that the lasso models are better predictive models than the ridge model because the test MSE of the ridge model is 0.349251 which is greater than that of both lasso models. The final model that we would choose is the cross-validated lasso model with a lambda of 0.000119548 because it did the best predictions.

> part f: What is the default setting for the normalize option in lars and the standardize option in glmnet? Why is this setting important to the model fit?

SOLUTION: The default setting for the normalize option in lars and the standardize option in glmnet is TRUE. This standardizes the variables so that they are on the same scale. This is important because id we did not standardize, then the variables that are on larger scales would cause their coefficient estimates to have a much larger impact on the model and potentially over influence the model.

> part g: Explain what option you would change in order to fit an elastic net penalty (not OLS or ridge) using glmnet.

SOLUTION: In order to fit an elastic net penalty, we would have to adjust $\alpha$. Since lasso regression has an $\alpha = 1$ and ridge regression has $\alpha = 0$, an $0 < \alpha < 1$ would cause a different behavior than both in selecting and removing predictors.

### 2022-10-05 homework/hmk4/hmk4Stat495F22.Rmd
Upload various hmks

---
title: "Homework 4 - Stat 495"
author: "Justin Papagelis"
date: "Due Wednesday, Oct. 5th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
library(rpart)
library(partykit)
library(GGally)
library(broom)
library(lmtest) # for likelihood ratio tests
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle/Git repo, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

*

\newpage

# Homework 4 and 5 Purpose

Homework 4 allows you to practice the two new methods from class recently - GLMs and regression/classification trees. Homework 5 serves as a way to practice our write-up of analyses.

In short, you will be performing some analysis in Homework 4 and then writing it up formally for Homework 5. You will receive some general feedback on Homework 4 as a class, and can use it to refine your models for the write-up in Homework 5. In other words, you may change your models between the two assignments, particularly if you find an issue as you review your work from Homework 4. However, you must submit Homework 4 with potential models for the write-up for both a GLM and tree as discussed below.

# Homework 4 - Analysis

For our analysis, we will use the King County, Washington (State) house sales data set, which I am re-hosting from Kaggle. The Kaggle reference is: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1

```{r}
kchouse <- read.csv("https://awagaman.people.amherst.edu/stat495/kc_house_data.csv", header = T)
```

A data dictionary taken from Kaggle is provided for your use (separate file).

## Motivation to predict when Price is greater than $500,000

A real estate developer is interested in understanding the features that are predictive of homes selling for more than half a million dollars, and has turned to you, a statistical consultant for help. He wants a model that can be applied to make predictions in this setting and wants to understand how the variables in the model are impacting it.

To practice new techniques from class, in your analysis, you are required to use both an appropriate generalized linear model and tree to address the developer's questions of interest, including a model comparison.

## Instructions for your Homework 4 submission

The outline for Homework 4 is next, but I want to include information here for you about what you'll need in Homework 5 so that you can include extra information for yourself in your Homework 4 submission, as desired. Look at the end of the assignment for this, and be sure to read it!

Homework 4 requires the following pieces:

* Exploratory Analysis
* GLM - at least 2 models fit with output and assessment
* Tree - at least 2 models fit with output and assessment

It doesn't matter which you tackle first, the GLMs or the trees.

Be sure you understand how to read output for both GLMs and trees, as this is material covered on the midterm.

\newpage

# Exploratory Analysis

```{r}
# explore the data 
# you need to do this before fitting anything!

# submission should demonstrate you explored the data somewhat before 
# fitting the models below

# If there is anything else you should do before fitting models,
# do it here

# we are only looking at prices greater than 500,00 and change date to a 
# date format
kchouse <- kchouse %>%
  filter(price > 500000) %>%
  mutate(date = lubridate::mdy(date))

# create a histogram
gf_dhistogram(~ price, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices Greater than $500,000")

gf_boxplot(~ price, data = kchouse)%>%
  gf_labs(title = "Boxplot of Prices Greater than $500,000")

favstats(~ price, data = kchouse)

```

The distribution of `price` is right-skewed with a median of \$690,000 and an IQR is \$294,000. There appears to be many outliers on the high end for `price`. We are only interested in predicting when `price` is greater than \$500,000, `price` is bounded on the lower end at \$500,000. Since the distribution is right-skewed, a log-transformation could be useful.

```{r}
# create the training and test set for price
set.seed(1)
n <- nrow(kchouse)
train_index <- sample(1:n, 3/4 * n)
test_index <- setdiff(1:n, train_index)

train <- kchouse[train_index, ]
test <- kchouse[test_index, ]

```

\newpage

# GLM Model Fitting

```{r}
# choose and fit at least 2 different models for your GLM
# include appropriate output and assessment of their performance

# think ahead: what does a reader need to know to follow your model fitting process?
# you may want to jot down notes for yourself that you'll need later!
```

We are going to first use Poisson Regression to predict `price`.

```{r}
# creating a poisson GLM 
poismod <- glm(price ~ ., data = train, family = poisson(link = log))
msummary(poismod)
```

```{r}
# likelihood ratio test
lrtest(poismod)
```

Using the Likelihood Ratio Test, it appears that the overall model is significant.

```{r, warning=FALSE}
# get MSE of training set
augprice1 <- augment(poismod, type.predict = "response")
mean((augprice1$.fitted - augprice1$price)^2)

#get MSE of test set
test4 <- mutate(test, fitted = predict(poismod, newdata = test, type = "response"))
test4 <-filter(test4, fitted != "NA")
mean((test4$fitted - test4$price)^2)

```
The MSE for the training set is 53,394,691,617 and the MSE for the test set is 49,118,687,275.

Next, we are going to use a Gamma Regression to predict `price`.

```{r}
# fit the gamma regression
gammamod <- glm(price ~ ., data = train, family = Gamma(link = log))
msummary(gammamod)
```
```{r}
# likelihood ratio test
lrtest(gammamod)
```

It appears the the overall model is significant as well.

```{r, warning=FALSE}
# get MSE of training set
augprice2 <- augment(gammamod, type.predict = "response")
mean((augprice2$.fitted - augprice2$price)^2)

#get MSE of test set
test5 <- mutate(test, fitted = predict(gammamod, newdata = test, type = "response"))
test5 <-filter(test5, fitted != "NA")
mean((test5$fitted - test5$price)^2)

```

The MSE for the training set is 55,085,101,906 and the MSE for the test set is 49,965,056,470 which are both higher than the respective values for the Poisson Regression so that model is better at predicting `price`.

\newpage

# Tree Fitting

```{r}
# choose and fit at least 2 different models for your tree
# include appropriate output and assessment of their performance

# think ahead: what does a reader need to know to follow your model fitting process?
# you may want to jot down notes for yourself that you'll need later!
```

```{r}
# create the regression tree
price.rpart1 <- rpart(price ~ ., data = train, method = "anova")
printcp(price.rpart1)

# print tree to pdf
pdf("price1.pdf", width = 14, height = 14)
plot(as.party(price.rpart1))
dev.off()

```
```{r}
# plot the cp of the regression tree
plotcp(price.rpart1)

# prune the tree
price.prune <- prune(price.rpart1, cp = 0.02)
printcp(price.prune)
```
After plotting the complexity parameter of the regression tree, we attempted to prune the tree.

```{r}
# find the MSE of the training set for default tree
train1 <- mutate(train, fittedtreetrain = predict(price.rpart1))
mean((train1$fittedtreetrain - train1$price)^2)

#find the MSE of the test set for default tree
test1 <- mutate(test, fittedtreetest = predict(price.rpart1, newdata = test))
mean((test1$fittedtreetest - test1$price)^2)
```

From the Regression Tree with default stopping criteria, we calculated the training set MSE to be 66,750,249,627 and the test set MSE to be 67,376,761,596 which are worse than the MSE's we calculated for the Generalized Linear Models.

```{r}
# find the MSE of the training set for the pruned tree
train1 <- mutate(train, fittedtreetrain = predict(price.prune))
mean((train1$fittedtreetrain - train1$price)^2)

# find the MSE of the test set for the pruned tree
test1 <- mutate(test, fittedtreetest = predict(price.prune, newdata = test))
mean((test1$fittedtreetest - test1$price)^2)
```
The MSE for the training set and test set from the pruned tree were 77,345,573,675 and 78,691,909,765, respectively. It appears that the pruned tree is worse at predicting price than the default tree we created so we'll stick with the default one.

Next, we tried taking the log of `price` and creating a new regression tree.

```{r}
# create the tree using log of price
price.rpart2 <- rpart(log(price) ~ ., data = train, method = "anova")
printcp(price.rpart2)

pdf("price2.pdf", width = 14, height = 14)
plot(as.party(price.rpart2))
dev.off()
```

```{r}
# calculate the MSE of the traning set using log price
train2 <- mutate(train, fittedtreetrain2 = predict(price.rpart2),
  traintree2pred = exp(fittedtreetrain2))

mean((train2$traintree2pred - train2$price)^2)
```
However, it appears that the MSE found from predicting the training set is much worse (83,573,000,000), so we will stick with the untransformed `price`.

Next, we will use some stopping critera.

```{r}
# create a regression tree using stopping criteria
price.control <- rpart.control(minbucket = 200, xval = 20, cp = 0.02)
price.rpart3 <- rpart(price ~ ., data = train, method = "anova", control = price.control)
printcp(price.rpart3)

pdf("price3.pdf", width = 14, height = 14)
plot(as.party(price.rpart3))
dev.off()
```

```{r}
# get the MSE of the training set
train3 <- mutate(train, fittedtreetrain = predict(price.rpart3))
mean((train3$fittedtreetrain - train3$price)^2)

# get the MSE of the test set
test3 <- mutate(test, fittedtreetest = predict(price.rpart3, newdata = test))
mean((test3$fittedtreetest - test3$price)^2)
```
The MSE of training set was 101,123,300,000 and the MSE of the test set was 96,700,246,800 which are both worse than the corresponding MSE values of the default regression tree so we would use that tree rather than this one.

\newpage

# Thinking about Homework 5

The eventual Homework 5 submission will include the following sections (along with all code necessary to reproduce your results):

* Introduction and Exploratory Data Analysis - could be two separate sections
* Your GLM and relevant details
* Your Tree and relevant details (can be before or after your GLM)
* Your Model Comparison (can be woven in sections above)
* Your Conclusion

Descriptions of the purpose for each section follow. The idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.

* Introduction - The real estate developer has interests, but will you be able to address them? How do you understand the tasks you are presented with? It's important to state what you will be doing in the analysis, so the reader can make sure their understanding lines up with what you will be doing. The reader also needs an introduction to your data, either in this section, or below. They need enough detail to be able to determine if your actions later in the analysis are reasonable.

* Exploratory Data Analysis - You are the analyst here. That means you can use variable re-expressions, subsets of observations, and employ other analytic practices (e.g. training/testing data sets) at your discretion to aid in your analysis, so long as you explain your rationale for them. The reader needs to know what you found and what you decided to do about it, because this has impacts on the rest of your analysis. Remember our lessons from the first classes - be sure you look at the data! Here's your chance to share what you found based on how it impacts your analysis.

* GLM and Tree sections - These are new techniques. By having each in their own section, you can focus on your explanation for them one at a time. The reader doesn't know when to use these methods or what they do. You have options that you need to pick for the different techniques (various tuning parameters) - for example, are you using a classification or a regression tree? What tree stopping options are being used? What input variables are you using and why? What type of GLM are you using? How will you be measuring performance? Be sure you discuss what options you are selecting and what made you choose those values. Helping explain this shows your understanding of the techniques (remember the class example that minbucket of 30 was nonsensical for the iris data).

You also want these sections to show off your ability to build models. It is not appropriate to just fit kitchen sink models (as your only model) or accept all default settings without exploring to see if that is really what is best for the task at hand. Your write-up should make it clear what you explored, but you don't have to show every model you considered.

Finally, remember to check out your "best" model for each technique. Did you check reasonable diagnostics? Does the model make sense? Are variables behaving as you expect? If you focus solely on model performance, that's missing the point. For example, you might find a model has very little error because a variant of the response was accidentally included as a predictor. You are responsible for checking over the model before reporting it. Your write-up should convey that you've done this (the reader can't read your mind to know you did it).

* Model Comparison - There are several ways to compare the models - performance, interpretability, variables involved, etc. Remember you are trying to address the real estate developer's questions of interest, so you probably need to focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree. The idea for this section is that you need to convey the process used to pick a final model(s) to use to answer those questions, with justification for your choices.

* Conclusion - This section should be a stand alone summary of your analysis. It is where you get to state your final model and a quick summary of the process used to get there. You also need to address the developer's questions, and this is your last place to do that! Remember to flush out the details here. If your final sentence is "Model 5 is the model I choose and it answers your questions", does it? Are you doing your job as the analyst to leave things at that? For that matter, what is Model 5?

* Printing Trees - It is fine to print your trees out to separate .pdfs (just be sure to include them in your submission!). Remember if you want to include the .pdf as an image, you have example code for that. Please do show your code though (so no echo = FALSE), and remember that your work should be reproducible.

* Audience - For purposes of this submission, remember that the audience is the real estate developer, so you'll probably need to include some explanations that you'd leave out of a normal homework. For example, the developer isn't going to know what a GLM is, or what type you are using, or why you'd use it. You should think about where that information should go, and do your best to explain what you need in order to report your findings. Similarly, assume that you found this data to assist the developer and they need basic details about it to understand the variables. They didn't hand it over to you.

### 2022-10-05 labs/Chapter 8 Lab.Rmd
Upload various hmks

---
title: "Stat 495 - Chapter 8 Practice"
author: "A.S. Wagaman"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(rpart)
library(partykit)
library(GGally)
library(lmtest) # for likelihood ratio tests
```

Now it's your turn to practice with GLMs and regression trees. The idea is to practice the methods and interpreting the results. You can pursue the questions below in any order, after doing Question 0, but may want to consult with others around you so you can assist each other.

### Data Set

For these problems we will be working with the Give Me Some Credit data set hosted by Kaggle. Reference for data: https://www.kaggle.com/c/GiveMeSomeCredit/data

We are only using a (random) subset of the training data set (20% is 30000 observations), so as not to bog down our computers.

```{r}
credit <- read.csv("https://awagaman.people.amherst.edu/stat495/creditsample.csv", header = T)
credit <- select(credit, -X) #remove row indices
```

You may opt to use rename to shorten the names of some the variables.

The data set contains the following variables:

* SeriousDlqin2yrs - Person experienced 90 days past due delinquency or worse - Y/N  
* RevolvingUtilizationOfUnsecuredLines - Total balance on credit cards and personal lines of credit except real estate and no installment debt like car loans divided by the sum of credit limits -	percentage  
* age	- Age of borrower in years	- integer  
* NumberOfTime30-59DaysPastDueNotWorse	- Number of times borrower has been 30-59 days past due but no worse in the last 2 years -	integer  
* DebtRatio -	Monthly debt payments, alimony,living costs divided by monthly gross income -	percentage  
* MonthlyIncome -	Monthly income -	real  
* NumberOfOpenCreditLinesAndLoans -	Number of Open loans (installment like car loan or mortgage) and Lines of credit (e.g. credit cards) -	integer  
* NumberOfTimes90DaysLate -	Number of times borrower has been 90 days or more past due -	integer
* NumberRealEstateLoansOrLines -	Number of mortgage and real estate loans including home equity lines of credit -	integer  
* NumberOfTime60-89DaysPastDueNotWorse -	Number of times borrower has been 60-89 days past due but no worse in the last 2 years -	integer  
* NumberOfDependents -	Number of dependents in family excluding themselves (spouse, children etc.) -	integer

### Question 0

You should create a training/test split for use in model evaluation below.

```{r}
set.seed(1)
n <- nrow(credit)
train_index <- sample(1:n, 3/4 * n)
test_index <- setdiff(1:n, train_index)

train <- credit[train_index, ]
test <- credit[test_index, ]

```

### Question 1

Use a regression tree to predict DebtRatio. How well does the tree do? Try out some of the tree control options.

```{r}
credit.rpart <- rpart(DebtRatio ~ ., data = train, method = "anova")
printcp(credit.rpart)

```

```{r}
pdf("credit.pdf", width = 14, height = 14)
plot(as.party(credit.rpart))
dev.off()
```
```{r}
train2 <- mutate(train, fittedtreetrain = predict(credit.rpart))
mean((train2$fittedtreetrain - train2$DebtRatio)^2)
```

```{r}
test2 <- mutate(test, fittedtreetest = predict(credit.rpart, newdata = test))
mean((test2$fittedtreetest - test2$DebtRatio)^2)
```

### Question 2

Use poisson regression to predict the NumberOfOpenCreditLinesAndLoans. Is the overall model useful?

```{r}
poisson.mod <- glm(NumberOfOpenCreditLinesAndLoans ~ age + NumberOfTime30.59DaysPastDueNotWorse + NumberOfTime60.89DaysPastDueNotWorse + NumberOfDependents, data = train, family = poisson (link = log))
msummary(poisson.mod)
```

```{r}
lrtest(poisson.mod)
```

```{r}
poisson.mod2
```

### Question 3

Use logistic regression and a classification tree to predict SeriousDlqin2yrs. This was the original Kaggle challenge. How do the models compare? How well is each doing? Which do you prefer?

```{r}

```

### 2022-10-09 Midterm Materials/MidtermPracticeQuestions.Rmd
Hwk 4 before changing

@@
 
+\newpage
 ## Add 2
@@
 
+\newpage
 ## Add 3
@@
 
+\newpage
 ## Add 4
@@
 
+\newpage
 ## Add 5
@@
 
+\newpage
 ## Add 6
@@
 (a) Use OLS to predict *prog* using *diabetes2* and verify you obtain the results in Table 7.3.
+
+```{r}
+mod1 <- lm(prog ~ ., data = diabetes2)
+msummary(mod1)
+round(coef(mod1), 2)
+```
+
 (b) Use ridge regression with lambda = 0.1 and verify you obtain the results in Table 7.3.
@@
 (d) Use CV with ridge regression to select your lambda running the default grid through glmnet (i.e. don't specify a grid). What lambda is selected?
+
+```{r}
+x2 <- model.matrix(prog ~ ., diabetes)[, -1]
+y2 <- diabetes %>% 
+  select(prog) %>%
+  unlist() %>%
+  as.numeric()
+
+set.seed(1)
+cv.out <- cv.glmnet(x2, y2, alpha = 0)
+bestlam <- cv.out$lambda.min
+bestlam
+
+ridge_mod <- glmnet(x2,y2, alpha = 0)
+round(coefficients(ridge_mod, s = bestlam), 3)
+```
+
 (e) Implement LASSO with CV to select your lambda running the default grid through glmnet. What lambda is selected?
+
+```{r}
+set.seed(1)
+cv.out1 <- cv.glmnet(x2, y2, alpha = 1)
+bestlam1 <- cv.out1$lambda.min
+bestlam1
+
+lasso_mod <- glmnet(x2,y2, alpha = 1)
+round(coefficients(lasso_mod, s = bestlam1), 3)
+```
+
 (f) Implement a regression tree to predict *prog*. What cp corresponds to the default tree? 
+```{r}
+set.seed(1)
+prog.rpart <- rpart(prog ~ ., data = diabetes2, method = "anova")
+printcp(prog.rpart)
+```
 (g) Explain why we don't need a *glm* here to predict *prog*. 
+`prog` is a continuous, numeric variable so OLS is fine. GLMs are used when there is logistic, poisson for counts, etc.
+
 (h) Which model of these do you prefer? How do the fits differ? (Hint: Besides comparing coefficients/involved variables, you can compare MSEs.)
 
+```{r}
+# for OLS
+54.16^2
+
+# for ridge
+ridge_pred <- predict(ridge_mod, s = bestlam, newx = x2)
+mean((ridge_pred - y2)^2)
+
+# for lasso
+lasso_pred <- predict(lasso_mod, s = bestlam1, newx = x2)
+mean((lasso_pred - y2)^2)
+
+# for tree
+fittedtree <- predict(prog.rpart)
+mean((fittedtree - diabetes2$prog)^2)
+```
+
+\newpage
 ## Add 7
@@
 (a) Why does it not make sense to use OLS to predict *spam*?
+It doesn't make sense to use OLS to predict spam because `spam` is a 0/1 variable and OLS doesn't have a way to constrain the response variable to be 0/1.
 (b) Use logistic regression to predict *spam*. Verify you obtain the results in Table 8.3.
+```{r}
+spamdata <- select(spam, -spam, -testid)
+spamdata <- data.frame(scale(spamdata))
+spamdata <- mutate(spamdata, spam = spam$spam)
+```
+
+```{r}
+loglm <- glm(spam ~ ., data = spamdata, family = "binomial")
+summary(loglm)
+```
+
+```{r}
+tally(~ spam, data = spamdata)
+1813/4601
+```
+
+```{r}
+logaug <- loglm %>%
+  broom::augment(type.predict = "response")
+logaug <- mutate(logaug, binprediction = round(.fitted,0))
+tally(~binprediction, data = logaug)
+```
+```{r}
+with(logaug, table(spam, binprediction))
+```
+
 (c) Obtain a confusion matrix for the logistic regression. How well is the model doing?
@@
 If you cannot obtain the tree, obtain one you want to work with for part e below.
+```{r}
+set.seed(495)
+spam.rpart <- rpart(factor(spam) ~ ., method = "class", data = spamdata)
+printcp(spam.rpart)
+#rplot.plot(spam.rpart)
+```
+
 (e) Obtain a confusion matrix for your classification tree. How do your error rates compare to those reported in Figure 8.7?
+
+```{r}
+spampredict <- predict(spam.rpart, type = "class")
+table(spampredict, spamdata$spam)
+```
+
 (f) Which method do you prefer for predicting *spam*?
-
+The tree has a little worse performance, but is much easier to understand so we would probably use thr tree.
+\newpage
 ## CASI 8.6
@@
 
+```{r}
+galaxy2 <- mutate(galaxy, m = 18:1)
+
+galaxydata <- galaxy2 %>%
+  tidyr::pivot_longer(-m, names_to = "log_r", values_to = "count")
+
+galaxydata <- mutate(galaxydata, r = c(rep(1:15, 18)))
+```
+
+```{r}
+myglm <- glm(count ~ r*m + I(r^2) + I(m^2), data = galaxydata, family = poisson)
+lmtest::lrtest(myglm)
+```
+
+\newpage
 ## Add 8
@@
 (a) Create an appropriate training/test split using a 75/25 percent split.
+
 (b) Perform best subsets and choose a model based on an appropriate descriptive statistic. Compute the test MSE.  
@@
 
+\newpage
 ## Add 9

### 2022-10-09 homework/hmk4/hmk4Stat495F22.Rmd
Hwk 4 before changing

@@
 
-# we are only looking at prices greater than 500,00 and change date to a 
+# change date to a 
 # date format
+
 kchouse <- kchouse %>%
-  filter(price > 500000) %>%
   mutate(date = lubridate::mdy(date))
@@
 gf_dhistogram(~ price, data = kchouse) %>%
-  gf_labs(title = "Histogram of Prices Greater than $500,000")
+  gf_labs(title = "Histogram of Prices")
 
 gf_boxplot(~ price, data = kchouse)%>%
-  gf_labs(title = "Boxplot of Prices Greater than $500,000")
+  gf_labs(title = "Boxplot of Prices")
 
@@
 
-The distribution of `price` is right-skewed with a median of \$690,000 and an IQR is \$294,000.
+```{r}
+645000-322000
+```
+
+The distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
 There appears to be many outliers on the high end for `price`.
-We are only interested in predicting when `price` is greater than \$500,000, `price` is bounded on the lower end at \$500,000.
+The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
 Since the distribution is right-skewed, a log-transformation could be useful.

### 2022-10-17 homework/hmk4/hmk4Stat495F22.Rmd
Work on Hmk5 and push lab for chapter 17

@@
 library(broom)
+library(ggplot2)
 library(lmtest) # for likelihood ratio tests
+
+library(ISLR)
+library(glmnet)
+
+library(lars)    # you may need to install some of these (one time only)
+library(leaps)   # to use variable selection methods if desired
+
 ```
@@
 
+For this analysis, we used the King County, Washington (State) house sales data set (`kchouse`).
+Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1.
+There is no information on the source of the data.
+The data set contains the following variables:
+\begin{itemize}
+\item id - notation for a specific house - Numeric
+\item date - date the house was sold - String
+\item price - price the house sold for in dollars - Numeric
+\item bedrooms - number of bedrooms in house - Numeric
+\item bathrooms- number of bathrooms per bedroom - Numeric
+\item sqft\textunderscore living - square footage of the home - Numeric
+\item sqft\textunderscore lot - square footage of the lot - Numeric
+\item floors - total floors (levels) in house - Numeric
+\item waterfront - house has a waterfront view - Y/N
+\item view - house has been viewed - Numeric
+\item condition - How good the condition is (overall) - Numeric
+\item grade - overall grade given to housing unit (based on King County grading system: 1 poor, 13 excellent) - Numeric
+\item sqft\textunderscore above - square footage of house apart from basement - Numeric
+\item yr\textunderscore built - the year the house was built - Numeric
+\item yr\textunderscore renovated - the year when the house was generated
+\item zipcode - the zipcode the house is in - Numeric
+\item lat - Latitude coordinate of house - Numeric
+\item long - Longitude coordinate of house - Numeric
+\item sqft\textunderscore living15 - living room area in 2015 (may or may not have been affected the lot size area) - Numeric
+\item sqft\textunderscore lot15 - lot size area in 2015 - Numeric
+\end{itemize}
+
+```{r}
+sum(is.na(kchouse$yr_renovated))
+```
+
+Before we fit any models, we need to make some adjustments to how the data is being treated by R.
+
 ```{r}
@@
 
+# create a histogram
+gf_dhistogram(~ bedrooms, data = kchouse) %>%
+  gf_labs(title = "Histogram of Prices")
+
 kchouse <- kchouse %>%
-  mutate(date = lubridate::mdy(date))
+  mutate(date = lubridate::mdy(date),
+         waterfront = as.factor(waterfront),
+  #       view = as.factor(view),
+  #       condition = as.factor(condition),
+  #       grade = as.factor(grade),
+         zipcode = as.numeric(as.factor(zipcode)))
+kchouse <- kchouse %>%
+  mutate_at(c('yr_renovated', 'sqft_basement'), ~na_if(.,0))
 
+sum(is.na(kchouse$yr_renovated))/nrow(kchouse)
+
+```
+
+```{r}
 # create a histogram
@@
 favstats(~ price, data = kchouse)
+
+ggplot(data = kchouse, aes(x = lat, y = long)) +
+  geom_point()
+
+ggplot(data = kchouse, aes(x = lat, y = long)) +
+  geom_point()
+
+kchouse1 <- mutate(kchouse, price = ifelse(price > 500000, 1, 0))
+
+kchouse1 <- kchouse1 %>%
+  filter(id != 2402100895) %>%
+  select(-c(id,zipcode, yr_renovated,date, sqft_basement))
 
@@
 set.seed(1)
-n <- nrow(kchouse)
+n <- nrow(kchouse1)
 train_index <- sample(1:n, 3/4 * n)
@@
 
-train <- kchouse[train_index, ]
-test <- kchouse[test_index, ]
+train <- kchouse1[train_index, ]
+test <- kchouse1[test_index, ]
 
@@
 ```{r}
-# creating a poisson GLM 
-poismod <- glm(price ~ ., data = train, family = poisson(link = log))
-msummary(poismod)
+
+logmod <- glm(price ~ ., data = train, family = "binomial")
+msummary(logmod)
+lrtest(logmod)
 ```
@@
 ```{r}
-# likelihood ratio test
-lrtest(poismod)
+augprice1 <- augment(logmod, type.predict = "response")
+favstats(~ .fitted, data = augprice1)
+
 ```
 
-Using the Likelihood Ratio Test, it appears that the overall model is significant.
+```{r}
+augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = augprice1)
+9787/(9787+6410)
+```
+
+```{r}
+tally(~ price, data = augprice1)
+9415/(9415+6782)
+with(augprice1, quantile(.fitted, 0.58128))
+```
+
+```{r}
+augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
+tally(~ binprediction2, data = augprice1)
+```
+
+```{r}
+with(augprice1, table(price, binprediction2))
+```
+
+```{r}
+(8131+5498)/(8131+5498+1284+1284)
+```
 
@@
 # get MSE of training set
-augprice1 <- augment(poismod, type.predict = "response")
+augprice1 <- augment(logmod, type.predict = "response")
 mean((augprice1$.fitted - augprice1$price)^2)
@@
 #get MSE of test set
-test4 <- mutate(test, fitted = predict(poismod, newdata = test, type = "response"))
+test4 <- mutate(test, fitted = predict(logmod, newdata = test, type = "response"))
 test4 <-filter(test4, fitted != "NA")
@@
 ```
-The MSE for the training set is 53,394,691,617 and the MSE for the test set is 49,118,687,275.
 
-Next, we are going to use a Gamma Regression to predict `price`.
+*******************************
+```{r}
+xPrice <- model.matrix(price ~ ., kchouse1)[, -1]
+yPrice <- kchouse1$price
 
-```{r}
-# fit the gamma regression
-gammamod <- glm(price ~ ., data = train, family = Gamma(link = log))
-msummary(gammamod)
-```
-```{r}
-# likelihood ratio test
-lrtest(gammamod)
-```
+x_train <- model.matrix(price ~ ., train)[, -1]
+x_test <- model.matrix(price ~ ., test)[, -1]
 
-It appears the the overall model is significant as well.
+y_train <- train %>%
+  select(price) %>%
+  unlist() %>%
+  as.numeric()
 
-```{r, warning=FALSE}
-# get MSE of training set
-augprice2 <- augment(gammamod, type.predict = "response")
-mean((augprice2$.fitted - augprice2$price)^2)
+y_test <- test %>%
+  select(price) %>%
+  unlist() %>%
+  as.numeric()
 
-#get MSE of test set
-test5 <- mutate(test, fitted = predict(gammamod, newdata = test, type = "response"))
-test5 <-filter(test5, fitted != "NA")
-mean((test5$fitted - test5$price)^2)
+grid <- 10^seq(10, -2, length = 100)
+
+ridge_mod <- glmnet(x_train, y_train, family = "binomial", alpha = 0, lambda = grid)
+
+plot(ridge_mod, label = TRUE)
+#ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
+#mean((ridge_pred - y_test)^2)
+
+set.seed(1)
+
+cv.out <- cv.glmnet(x_train, y_train, alpha = 0)
+bestlam <- cv.out$lambda.min
+bestlam
+
+plot(cv.out)
+
+predict(cv.out, type = "coefficients", s = bestlam)
+
+ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test)
+mean((ridge_pred - y_test)^2)
+
+#augprice2 <- augment(ridge_mod, type.predict = "response")
+#favstats(~ .fitted, data = augprice2)
 
 ```
-
-The MSE for the training set is 55,085,101,906 and the MSE for the test set is 49,965,056,470 which are both higher than the respective values for the Poisson Regression so that model is better at predicting `price`.
 
@@
 ```{r}
-# create the regression tree
-price.rpart1 <- rpart(price ~ ., data = train, method = "anova")
+price.rpart1 <- rpart(price ~ ., data = train, method = "class")
 printcp(price.rpart1)
 
-# print tree to pdf
-pdf("price1.pdf", width = 14, height = 14)
-plot(as.party(price.rpart1))
-dev.off()
+# find the MSE of the training set for default tree
+train1 <- mutate(train, predprice = predict(price.rpart1, type = "class"))
+tally(predprice ~ price, data = train1)
+tally(~ price, data = train1)
 
+#find the MSE of the test set for default tree
+test1 <- mutate(test, predprice = predict(price.rpart1, type = "class", newdata = test))
+tally(predprice ~ price, data = test1)
+tally(~ price, data = test1)
 ```
 ```{r}
-# plot the cp of the regression tree
-plotcp(price.rpart1)
+(8283+5728)/(8283+5728+1132+1054)
 
-# prune the tree
-price.prune <- prune(price.rpart1, cp = 0.02)
-printcp(price.prune)
-```
-After plotting the complexity parameter of the regression tree, we attempted to prune the tree.
-
-```{r}
-# find the MSE of the training set for default tree
-train1 <- mutate(train, fittedtreetrain = predict(price.rpart1))
-mean((train1$fittedtreetrain - train1$price)^2)
-
-#find the MSE of the test set for default tree
-test1 <- mutate(test, fittedtreetest = predict(price.rpart1, newdata = test))
-mean((test1$fittedtreetest - test1$price)^2)
-```
-
-From the Regression Tree with default stopping criteria, we calculated the training set MSE to be 66,750,249,627 and the test set MSE to be 67,376,761,596 which are worse than the MSE's we calculated for the Generalized Linear Models.
-
-```{r}
-# find the MSE of the training set for the pruned tree
-train1 <- mutate(train, fittedtreetrain = predict(price.prune))
-mean((train1$fittedtreetrain - train1$price)^2)
-
-# find the MSE of the test set for the pruned tree
-test1 <- mutate(test, fittedtreetest = predict(price.prune, newdata = test))
-mean((test1$fittedtreetest - test1$price)^2)
-```
-The MSE for the training set and test set from the pruned tree were 77,345,573,675 and 78,691,909,765, respectively.
-It appears that the pruned tree is worse at predicting price than the default tree we created so we'll stick with the default one.
-
-Next, we tried taking the log of `price` and creating a new regression tree.
-
-```{r}
-# create the tree using log of price
-price.rpart2 <- rpart(log(price) ~ ., data = train, method = "anova")
-printcp(price.rpart2)
-
-pdf("price2.pdf", width = 14, height = 14)
-plot(as.party(price.rpart2))
-dev.off()
+(2754+1881)/(2754+1881+377+387)
+(3131)/(3131+2268)
 ```
@@
 ```{r}
-# calculate the MSE of the traning set using log price
-train2 <- mutate(train, fittedtreetrain2 = predict(price.rpart2),
-  traintree2pred = exp(fittedtreetrain2))
+# perhaps make a less complicated one
+# see how much you lose
+plotcp(price.rpart1)
 
-mean((train2$traintree2pred - train2$price)^2)
-```
-However, it appears that the MSE found from predicting the training set is much worse (83,573,000,000), so we will stick with the untransformed `price`.
+price.control <- rpart.control(minsplit = 10, cp = 0.017)
+price.rpart2 <- rpart(price ~ ., data = train, method = "class", control = price.control)
+printcp(price.rpart2)
 
-Next, we will use some stopping critera.
+# find the MSE of the training set for default tree
+train1 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
+tally(predprice ~ price, data = train1)
+tally(~ price, data = train1)
 
-```{r}
-# create a regression tree using stopping criteria
-price.control <- rpart.control(minbucket = 200, xval = 20, cp = 0.02)
-price.rpart3 <- rpart(price ~ ., data = train, method = "anova", control = price.control)
-printcp(price.rpart3)
-
-pdf("price3.pdf", width = 14, height = 14)
-plot(as.party(price.rpart3))
-dev.off()
+#find the MSE of the test set for default tree
+test1 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
+tally(predprice ~ price, data = test1)
+tally(~ price, data = test1)
 ```
@@
 ```{r}
-# get the MSE of the training set
-train3 <- mutate(train, fittedtreetrain = predict(price.rpart3))
-mean((train3$fittedtreetrain - train3$price)^2)
 
-# get the MSE of the test set
-test3 <- mutate(test, fittedtreetest = predict(price.rpart3, newdata = test))
-mean((test3$fittedtreetest - test3$price)^2)
 ```
-The MSE of training set was 101,123,300,000 and the MSE of the test set was 96,700,246,800 which are both worse than the corresponding MSE values of the default regression tree so we would use that tree rather than this one.
 

### 2022-10-17 homework/hmk5/hmk5Stat495F22.Rmd
Work on Hmk5 and push lab for chapter 17

--- 2022-10-09 homework/hmk4/hmk4Stat495F22.Rmd
@@
 ---
-title: "Homework 4 - Stat 495"
-author: "Justin Papagelis"
-date: "Due Wednesday, Oct. 5th by midnight"
+title: "Homework 5 - Stat 495"
+author: "YourNameGoesHere"
+date: "Due Wednesday, October 19th by midnight"
 output:
@@
 options(digits = 6)
-library(rpart)
-library(partykit)
-library(GGally)
-library(broom)
-library(lmtest) # for likelihood ratio tests
 ```
@@
 
-# Homework 4 and 5 Purpose
-
-Homework 4 allows you to practice the two new methods from class recently - GLMs and regression/classification trees. Homework 5 serves as a way to practice our write-up of analyses.
-
-In short, you will be performing some analysis in Homework 4 and then writing it up formally for Homework 5.
-You will receive some general feedback on Homework 4 as a class, and can use it to refine your models for the write-up in Homework 5.
-In other words, you may change your models between the two assignments, particularly if you find an issue as you review your work from Homework 4.
-However, you must submit Homework 4 with potential models for the write-up for both a GLM and tree as discussed below.
-
-# Homework 4 - Analysis
-
-For our analysis, we will use the King County, Washington (State) house sales data set, which I am re-hosting from Kaggle.
-The Kaggle reference is: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1
+# Homework 5 - Prompt - Write-up for Homework 4
 
@@
 ```
-
-A data dictionary taken from Kaggle is provided for your use (separate file).
 
@@
 
-## Instructions for your Homework 4 submission
+## Write-up Purpose and some Guidance
 
-The outline for Homework 4 is next, but I want to include information here for you about what you'll need in Homework 5 so that you can include extra information for yourself in your Homework 4 submission, as desired.
-Look at the end of the assignment for this, and be sure to read it!
+We want to practice reporting our analyses.
+You have been contracted to do an analysis, and you prepared some potential models in Homework 4, and now need to report your process and subsequent findings to the client.
 
-Homework 4 requires the following pieces:
+Things to think about:
 
-* Exploratory Analysis
-* GLM - at least 2 models fit with output and assessment
-* Tree - at least 2 models fit with output and assessment
+* Your report should be well-organized and proofread.
+* Your code should be readable and not run off pages. Employ good commenting practices.
+* The entire process must be reproducible.
+* Review the class feedback on Homework 4 and adjust your models/thinking as necessary before diving in to the write-up. 
+* Think carefully about the organization of the report. Is it useful to have pages of output and THEN a description of what to look for in that output?
+* Should you assume the reader knows where values in the R output are?
+* If you compute a number, and then write a sentence that says, the MSE is small, will the reader associate that number with being the MSE? What would a better sentence look like? 
+* Thinking back to the Tibshirani Writing activity may help you think about ways to improve as well. (Does each of your sections have a purpose? Do you have appropriate signposts, etc.)
 
-It doesn't matter which you tackle first, the GLMs or the trees.
+## Instructions for your submission
 
-Be sure you understand how to read output for both GLMs and trees, as this is material covered on the midterm.
-
-\newpage
-
-# Exploratory Analysis
-
-```{r}
-# explore the data 
-# you need to do this before fitting anything!
-
-# submission should demonstrate you explored the data somewhat before 
-# fitting the models below
-
-# If there is anything else you should do before fitting models,
-# do it here
-
-# change date to a 
-# date format
-
-kchouse <- kchouse %>%
-  mutate(date = lubridate::mdy(date))
-
-# create a histogram
-gf_dhistogram(~ price, data = kchouse) %>%
-  gf_labs(title = "Histogram of Prices")
-
-gf_boxplot(~ price, data = kchouse)%>%
-  gf_labs(title = "Boxplot of Prices")
-
-favstats(~ price, data = kchouse)
-
-```
-
-```{r}
-645000-322000
-```
-
-The distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
-There appears to be many outliers on the high end for `price`.
-The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
-Since the distribution is right-skewed, a log-transformation could be useful.
-
-```{r}
-# create the training and test set for price
-set.seed(1)
-n <- nrow(kchouse)
-train_index <- sample(1:n, 3/4 * n)
-test_index <- setdiff(1:n, train_index)
-
-train <- kchouse[train_index, ]
-test <- kchouse[test_index, ]
-
-```
-
-\newpage
-
-# GLM Model Fitting
-
-```{r}
-# choose and fit at least 2 different models for your GLM
-# include appropriate output and assessment of their performance
-
-# think ahead: what does a reader need to know to follow your model fitting process?
-# you may want to jot down notes for yourself that you'll need later!
-```
-
-We are going to first use Poisson Regression to predict `price`.
-
-```{r}
-# creating a poisson GLM 
-poismod <- glm(price ~ ., data = train, family = poisson(link = log))
-msummary(poismod)
-```
-
-```{r}
-# likelihood ratio test
-lrtest(poismod)
-```
-
-Using the Likelihood Ratio Test, it appears that the overall model is significant.
-
-```{r, warning=FALSE}
-# get MSE of training set
-augprice1 <- augment(poismod, type.predict = "response")
-mean((augprice1$.fitted - augprice1$price)^2)
-
-#get MSE of test set
-test4 <- mutate(test, fitted = predict(poismod, newdata = test, type = "response"))
-test4 <-filter(test4, fitted != "NA")
-mean((test4$fitted - test4$price)^2)
-
-```
-The MSE for the training set is 53,394,691,617 and the MSE for the test set is 49,118,687,275.
-
-Next, we are going to use a Gamma Regression to predict `price`.
-
-```{r}
-# fit the gamma regression
-gammamod <- glm(price ~ ., data = train, family = Gamma(link = log))
-msummary(gammamod)
-```
-```{r}
-# likelihood ratio test
-lrtest(gammamod)
-```
-
-It appears the the overall model is significant as well.
-
-```{r, warning=FALSE}
-# get MSE of training set
-augprice2 <- augment(gammamod, type.predict = "response")
-mean((augprice2$.fitted - augprice2$price)^2)
-
-#get MSE of test set
-test5 <- mutate(test, fitted = predict(gammamod, newdata = test, type = "response"))
-test5 <-filter(test5, fitted != "NA")
-mean((test5$fitted - test5$price)^2)
-
-```
-
-The MSE for the training set is 55,085,101,906 and the MSE for the test set is 49,965,056,470 which are both higher than the respective values for the Poisson Regression so that model is better at predicting `price`.
-
-\newpage
-
-# Tree Fitting
-
-```{r}
-# choose and fit at least 2 different models for your tree
-# include appropriate output and assessment of their performance
-
-# think ahead: what does a reader need to know to follow your model fitting process?
-# you may want to jot down notes for yourself that you'll need later!
-```
-
-```{r}
-# create the regression tree
-price.rpart1 <- rpart(price ~ ., data = train, method = "anova")
-printcp(price.rpart1)
-
-# print tree to pdf
-pdf("price1.pdf", width = 14, height = 14)
-plot(as.party(price.rpart1))
-dev.off()
-
-```
-```{r}
-# plot the cp of the regression tree
-plotcp(price.rpart1)
-
-# prune the tree
-price.prune <- prune(price.rpart1, cp = 0.02)
-printcp(price.prune)
-```
-After plotting the complexity parameter of the regression tree, we attempted to prune the tree.
-
-```{r}
-# find the MSE of the training set for default tree
-train1 <- mutate(train, fittedtreetrain = predict(price.rpart1))
-mean((train1$fittedtreetrain - train1$price)^2)
-
-#find the MSE of the test set for default tree
-test1 <- mutate(test, fittedtreetest = predict(price.rpart1, newdata = test))
-mean((test1$fittedtreetest - test1$price)^2)
-```
-
-From the Regression Tree with default stopping criteria, we calculated the training set MSE to be 66,750,249,627 and the test set MSE to be 67,376,761,596 which are worse than the MSE's we calculated for the Generalized Linear Models.
-
-```{r}
-# find the MSE of the training set for the pruned tree
-train1 <- mutate(train, fittedtreetrain = predict(price.prune))
-mean((train1$fittedtreetrain - train1$price)^2)
-
-# find the MSE of the test set for the pruned tree
-test1 <- mutate(test, fittedtreetest = predict(price.prune, newdata = test))
-mean((test1$fittedtreetest - test1$price)^2)
-```
-The MSE for the training set and test set from the pruned tree were 77,345,573,675 and 78,691,909,765, respectively.
-It appears that the pruned tree is worse at predicting price than the default tree we created so we'll stick with the default one.
-
-Next, we tried taking the log of `price` and creating a new regression tree.
-
-```{r}
-# create the tree using log of price
-price.rpart2 <- rpart(log(price) ~ ., data = train, method = "anova")
-printcp(price.rpart2)
-
-pdf("price2.pdf", width = 14, height = 14)
-plot(as.party(price.rpart2))
-dev.off()
-```
-
-```{r}
-# calculate the MSE of the traning set using log price
-train2 <- mutate(train, fittedtreetrain2 = predict(price.rpart2),
-  traintree2pred = exp(fittedtreetrain2))
-
-mean((train2$traintree2pred - train2$price)^2)
-```
-However, it appears that the MSE found from predicting the training set is much worse (83,573,000,000), so we will stick with the untransformed `price`.
-
-Next, we will use some stopping critera.
-
-```{r}
-# create a regression tree using stopping criteria
-price.control <- rpart.control(minbucket = 200, xval = 20, cp = 0.02)
-price.rpart3 <- rpart(price ~ ., data = train, method = "anova", control = price.control)
-printcp(price.rpart3)
-
-pdf("price3.pdf", width = 14, height = 14)
-plot(as.party(price.rpart3))
-dev.off()
-```
-
-```{r}
-# get the MSE of the training set
-train3 <- mutate(train, fittedtreetrain = predict(price.rpart3))
-mean((train3$fittedtreetrain - train3$price)^2)
-
-# get the MSE of the test set
-test3 <- mutate(test, fittedtreetest = predict(price.rpart3, newdata = test))
-mean((test3$fittedtreetest - test3$price)^2)
-```
-The MSE of training set was 101,123,300,000 and the MSE of the test set was 96,700,246,800 which are both worse than the corresponding MSE values of the default regression tree so we would use that tree rather than this one.
-
-\newpage
-
-# Thinking about Homework 5
-
-The eventual Homework 5 submission will include the following sections (along with all code necessary to reproduce your results):
+Your submission should include the following sections (along with all code necessary to reproduce your results):
 
@@
 
-Descriptions of the purpose for each section follow. The idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.
+Descriptions of the purpose for each section follow.
+Do not use this as a set of check boxes for the assignment.
+Instead, the idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.
 
@@
 * Exploratory Data Analysis - You are the analyst here.
-That means you can use variable re-expressions, subsets of observations, and employ other analytic practices (e.g.
+That means you can use variable transformations, subsets of observations, and employ other analytic practices (e.g.
 training/testing data sets) at your discretion to aid in your analysis, so long as you explain your rationale for them.
@@
 By having each in their own section, you can focus on your explanation for them one at a time.
-The reader doesn't know when to use these methods or what they do.
+The developer does not know what these are - you need to explain them at least enough they can follow your discussion.
 You have options that you need to pick for the different techniques (various tuning parameters) - for example, are you using a classification or a regression tree?
@@
 You also want these sections to show off your ability to build models.
-It is not appropriate to just fit kitchen sink models (as your only model) or accept all default settings without exploring to see if that is really what is best for the task at hand.
+It is not appropriate to only fit kitchen sink models or accept all default settings without exploring to see if that is really what is best for the task at hand.
 Your write-up should make it clear what you explored, but you don't have to show every model you considered.
+You can do a lot in sentences discussing your process.
 
@@
 * Model Comparison - There are several ways to compare the models - performance, interpretability, variables involved, etc.
-Remember you are trying to address the real estate developer's questions of interest, so you probably need to focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree.
+Remember you are trying to address the real estate developer's questions of interest.
+You may do that with a focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree.
 The idea for this section is that you need to convey the process used to pick a final model(s) to use to answer those questions, with justification for your choices.
@@
 It is where you get to state your final model and a quick summary of the process used to get there.
-You also need to address the developer's questions, and this is your last place to do that!
+You also need to address the developer's questions (if not done before), and this is your last place to do that!
 Remember to flush out the details here.
@@
 Please do show your code though (so no echo = FALSE), and remember that your work should be reproducible.
+The chapter 8 lab solution shows alternatives to *partykit* to make the trees look nice.
+You can try out *rpart.plot* yourself to see.
+
+* Length - Your submission should be as long as it needs to be, but not unnecessarily long.
+Plots, etc.
+are encouraged to help illustrate points, but don't include output that isn't needed.
+For example, a histogram or densityplot and favstats for each variable is something good to explore, but you shouldn't put that in your submission for every variable.
+You might need plots to point out outliers you are removing, or maybe you show one plot and then say others were similar.
+I encourage you to do any additional work in a separate .Rmd from your submission (like, back in your Homework 4 .Rmd).
 
@@
 They didn't hand it over to you.
+
+You may remove these instructions if desired for your submission, but must leave the page on Academic Integrity.
+
+\newpage
+
+# Introduction
+
+\newpage
+
+# Exploratory Data Analysis
+
+```{r, include = FALSE}
+# Can be included with the introduction
+```
+
+\newpage
+
+# GLM and Results
+
+\newpage
+
+# Tree and Results
+
+```{r, include = FALSE}
+# Can be before or after your GLM
+```
+
+\newpage
+
+# Model Comparison
+
+```{r, include = FALSE}
+# Can be woven in above
+```
+
+\newpage
+
+# Conclusion

### 2022-10-17 labs/Chapter 17 Lab.Rmd
Work on Hmk5 and push lab for chapter 17

---
title: "Chapter 17 Lab - Random Forests and Boosting"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(tree) #may need to install
library(ISLR)
library(dplyr)
library(ggplot2)
library(gbm)
library(randomForest)
```

This lab is an edited version of an abbreviated version of p. 324-331 of "Introduction to Statistical Learning with Applications in R" by Gareth James, Daniela Witten, Trevor Hastie and Robert Tibshirani. It was re-implemented in Fall 2016 in `tidyverse` format by Amelia McNamara and R. Jordan Crouser at Smith College, and further edited by Amy Wagaman at Amherst College in Fall 2018, Fall 2019, and Fall 2022.

The lab reviews classification trees (as in CASI Chapter 8's classification trees)  but uses a different package to fit them called *tree*. You can use either tree or rpart. Rpart gives a bit better control, but tree has a few other options you might want. After that, it covers random forests, bagging, and boosting. The code is provided in this until the open-ended problem at the end. Be sure you are comfortable with the output, etc. Remember you can use these for regression or classification.

# Fitting Trees - Review with new R Package

The `tree` library is useful for constructing classification and regression trees:

We'll start by using **classification trees** to analyze the `Carseats` data set. In these
data, `Sales` is a continuous variable, we want to consider a binary classification problem, so we begin by converting it to a binary variable. We use the `ifelse()` function to create a variable, called `High`, which takes on a value of `Yes` if the `Sales` variable exceeds 8, and takes on a value of `No` otherwise:

```{r}
Carseats <- Carseats %>%
  mutate(High = as.factor(ifelse(Sales <= 8, "No", "Yes")))
```

In order to properly evaluate the performance of a classification tree on
the data, we must estimate the test error rather than simply computing
the training error. We first split the observations into a training set and a test
set:

```{r}
set.seed(495)

n <- nrow(Carseats)
train_index <- sample(1:n, 0.5 * n)
test_index <- setdiff(1:n, train_index)

train <- Carseats[train_index, ] 
test <- Carseats[test_index, ]
```

We now use the `tree()` function to fit a classification tree in order to predict
`High` using all variables but `Sales` (that would be a little silly...). The syntax of the `tree()` function is quite similar to that of the `lm()` function:

```{r}
tree_carseats <- tree(High ~ . - Sales, train)
```

The `summary()` function lists the variables that are used as internal nodes (forming decision points)
in the tree, the number of terminal nodes, and the (training) error rate:

```{r}
summary(tree_carseats)
```

One of the most attractive properties of trees is that they can be
graphically displayed. We use the `plot()` function to display the tree structure,
and the `text()` function to display the node labels. The argument
`pretty = 0` instructs `R` to include the category names for any qualitative predictors,
rather than simply displaying a letter for each category:

```{r}
plot(tree_carseats)
text(tree_carseats, pretty = 0)
```

Again, you've seen nicer plots are possible with rpart.plot for rpart objects.

The most important indicator of `High` sales appears to be shelving location,
since the first branch differentiates `Good` locations from `Bad` and `Medium`
locations.

If we just type the name of the tree object, `R` prints output corresponding
to each branch of the tree. `R` displays the split criterion (e.g. $Price < 142$), the
number of observations in that branch, the deviance, the overall prediction
for the branch (`Yes` or `No`), and the fraction of observations in that branch
that take on values of `Yes` and `No`. Branches that lead to terminal nodes are
indicated using asterisks:

```{r}
tree_carseats
```

Finally, let's evaluate the tree's performance on
the test data. The `predict()` function can be used for this purpose. In the
case of a classification tree, the argument `type="class"` instructs `R` to return
the actual class prediction.

```{r}
tree_pred <- predict(tree_carseats, test, type = "class")
table(tree_pred, test$High)
```

# Pruning

Next, we consider whether pruning the tree might lead to improved
results. The function `cv.tree()` performs cross-validation in order to
determine the optimal level of tree complexity; cost complexity pruning
is used in order to select a sequence of trees for consideration. We use
the argument `FUN = prune.misclass` in order to indicate that we want the
classification error rate as our cost function to guide the cross-validation and pruning process,
rather than the default for the `cv.tree()` function, which is `deviance`. The
`cv.tree()` function reports the number of terminal nodes of each tree considered
(size) as well as the corresponding error rate and the value of the
cost-complexity parameter used.

```{r}
set.seed(495)
cv_carseats <- cv.tree(tree_carseats, FUN = prune.misclass)
```

Note that, despite the name, the `dev` field corresponds to the cross-validation error
rate in this instance. Let's plot the error rate as a function of size:

```{r}
plot(cv_carseats$size, cv_carseats$dev, type = "b")
```

We see from this plot that the tree with 12 terminal nodes results in the lowest
cross-validation error rate.

We now apply the `prune.misclass()` function in order to prune the tree to
obtain the ten-node tree by setting the parameter `best = 12`:

```{r}
prune_carseats <- prune.misclass(tree_carseats, best = 12)
plot(prune_carseats)
text(prune_carseats, pretty = 0)
```

How well does this pruned tree perform on the test data set? Once again,
we can apply the `predict()` function top find out:

```{r}
tree_pred <- predict(prune_carseats, test, type = "class")
table(tree_pred, test$High)
```

We can check to see what percent of the test observations are correctly classified, and use that to determine if  
the pruning process resulted in a large or small change in classification accuracy. There can be a tradeoff between an interpretable tree versus prediction accuracy.

Note that setting different seeds can lead to different trees and different CV pruning results. This is part of the instability of trees on different data sets.

# Regression Trees

Now let's try fitting a **regression tree** to the `Boston` data set from the `MASS` library. First, we create a
training set, and fit the tree to the training data using `medv` (median home value) as our response:

```{r}
set.seed(495)
n <- nrow(MASS::Boston)
train_index <- sample(1:n, 0.5 * n)
test_index <- setdiff(1:n, train_index)

boston_train <- MASS::Boston[train_index, ] 
boston_test <- MASS::Boston[test_index, ]

tree_boston <- tree(medv ~ ., boston_train)

summary(tree_boston)
```

Notice that the output of `summary()` indicates that only a few of the variables
have been used in constructing the tree. In the context of a regression
tree, the `deviance` is simply the sum of squared errors for the tree. Let's
plot the tree:

```{r}
plot(tree_boston)
text(tree_boston, pretty = 0)
```

The variable `lstat` measures the percentage of individuals with lower
socioeconomic status. The tree indicates that lower values of `lstat` correspond
to more expensive houses.

Now we use the `cv.tree()` function to see whether pruning the tree will
improve performance:

```{r}
cv_boston <- cv.tree(tree_boston)
plot(cv_boston$size, cv_boston$dev, type = 'b')
```

It looks like the full tree (or near to it) has the lowest error, but to practice with pruning, we can see the plot levels off at around size 7.

So, let's prune to the 7-node tree. We can prune the tree using the
`prune.tree()` function as before:

```{r}
prune_boston <- prune.tree(tree_boston, best = 7)
plot(prune_boston)
text(prune_boston, pretty = 0)
```

Now we'll use the pruned tree to make predictions on the test set:

```{r}
single_tree_estimate <- predict(prune_boston, 
                               newdata = boston_test)
ggplot() + 
    geom_point(aes(x = boston_test$medv, y = single_tree_estimate)) +
    geom_abline()

mean((single_tree_estimate - boston_test$medv)^2)
```

In other words, the test set MSE associated with the regression tree is
21.127. The square root of the MSE is therefore around 4.596, indicating
that this model leads to test predictions that are within around $4,596 of
the true median home value for the suburb.

# Bagging and Random Forests

Let's see if we can improve on this result using bagging and random forests. Recall that bagging is simply a special case of a random forest with $m = p$. The `randomForest()` function can
be used to perform both random forests and bagging. By default, 500 trees are "grown". You can change this and other options. Let's start with bagging:

```{r}
set.seed(495)
bag_boston <- randomForest(medv ~ ., 
                          data = boston_train, 
                          mtry = 13, 
                          importance = TRUE)
bag_boston
```

The argument `mtry = 13` indicates that all 13 predictors should be considered
for each split of the tree -- in other words, that bagging should be done. How
well does this bagged model perform on the test set?

```{r}
bagged_estimate <- predict(bag_boston, 
                          newdata = boston_test)

ggplot() + 
    geom_point(aes(x = boston_test$medv, y = bagged_estimate)) +
    geom_abline()

mean((bagged_estimate - boston_test$medv)^2)
```

The test set MSE associated with the bagged regression tree is dramatically smaller than that obtained using an optimally-pruned single tree! We can change
the number of trees grown by `randomForest()` using the `ntree` argument:

```{r}
bag_boston_25_trees <- randomForest(medv ~ ., data =  boston_train, mtry = 13, ntree = 25)
bagged_estimate_25_trees <- predict(bag_boston_25_trees, newdata = boston_test)
mean((bagged_estimate_25_trees - boston_test$medv)^2)
```

We can grow a random forest in exactly the same way, except that
we'll use a smaller value of the `mtry` argument. By default, `randomForest()`
uses $p/3$ variables when building a random forest of regression trees, and
$\sqrt{p}$ variables when building a random forest of classification trees. Here we'll
use `mtry = 6`:

```{r}
set.seed(495)
rf_boston <- randomForest(medv ~ ., 
                         data = boston_train, 
                         mtry = 6, 
                         importance = TRUE)

random_forest_estimate <- predict(rf_boston, 
                                 newdata = boston_test)

mean((random_forest_estimate - boston_test$medv)^2)
```

The test set MSE is quite low, although bagging seems slightly better in this case (at least for the seed I set).

Using the `importance()` function, we can view the importance of each variable:

```{r}
importance(rf_boston)
```

Two measures of variable importance are reported. The former is based
upon the mean decrease of accuracy in predictions on the out-of-bag samples
when a given variable is excluded from the model. The latter is a measure
of the total decrease in node impurity that results from splits over that
variable, averaged over all tree. In the case of regression trees, the node impurity is measured by the training RSS, and for classification trees by the deviance. Plots of these importance
measures can be produced using the `varImpPlot()` function:

```{r}
varImpPlot(rf_boston)
```

The results indicate that across all of the trees considered in the random
forest, the wealth level of the community (`lstat`) and the house size (`rm`)
are by far the two most important variables.

# Boosting

Now we'll use the `gbm` package, and within it the `gbm()` function, to fit boosted
regression trees to the `Boston` data set. We run `gbm()` with the option
`distribution = "gaussian"` since this is a regression problem; if it were a binary
classification problem, we would use `distribution = "bernoulli"`. The
argument `n.trees = 5000` indicates that we want 5000 trees, and the option
`interaction.depth = 4`limits the depth of each tree. A depth of 4 is actually pretty common here, you don't want to go much bigger. Using a depth of 1 is just stumps.

```{r}
set.seed(495)
boost_boston <- gbm(medv ~ ., 
                   data = boston_train, 
                   distribution = "gaussian", 
                   n.trees = 5000, 
                   interaction.depth = 4)
```

The `summary()` function produces a relative influence plot and also outputs
the relative influence statistics:

```{r}
summary(boost_boston)
```

We see that `lstat` and `rm` are again the most important variables by far. We can
also produce partial dependence plots for these two variables. These plots
illustrate the marginal effect of the selected variables on the response after
integrating out the other variables. In this case, as we might expect, median
house prices are increasing with `rm` and decreasing with `lstat`:

```{r}
plot(boost_boston, i = "rm")
plot(boost_boston, i = "lstat")
```

Now let's use the boosted model to predict `medv` on the test set:

```{r}
boost_estimate <- predict(boost_boston, 
                         newdata = boston_test, 
                         n.trees = 5000)

mean((boost_estimate - boston_test$medv)^2)
```

The test MSE obtained is higher than the test MSE for random forests and bagging. If we want to, we can perform boosting with a different value of the shrinkage parameter $\lambda$, which is $\epsilon$ in the CASI textbook. The default value is 0.001, but this is easily modified. Here we take $\lambda = 0.1$:

```{r}
boost_boston2 <- gbm(medv ~ ., data = boston_train, 
                    distribution = "gaussian", 
                    n.trees = 5000, 
                    interaction.depth = 4, 
                    shrinkage = 0.01, 
                    verbose = F)

boost_estimate2 <- predict(boost_boston2, newdata = boston_test, n.trees = 5000)
mean((boost_estimate2-boston_test$medv)^2)
```

In this case, using $\lambda = 0.1$ leads to a slightly lower test MSE than $\lambda = 0.001$.

# Practice

We use a data set that we previously examined when learning about ridge regression that we are returning to for practice.

```{r}
data(Hitters)
# ?Hitters # MLB data from 1986 and 1987; 322 obs on 20 variables
```

We want to predict Salary, which is missing for 59 players.

```{r}
Hitters <- na.omit(Hitters) #263 obs now
```

Use bagging, random forests, and boosting to explore models for predicting salary. Be sure to explore model options and the various parameter settings. (You can fit a single tree for comparison as well, if you want.)

> SOLUTION

```{r}

```

### 2022-10-17 labs/Chapter 17 Lab.Rmd
Finish lab

@@
 ```{r}
+set.seed(495)
+n <- nrow(Hitters)
+train_index <- sample(1:n, 0.5 * n)
+test_index <- setdiff(1:n, train_index)
+
+hitters_train <- Hitters[train_index, ] 
+hitters_test <- Hitters[test_index, ]
 
 ```
+```{r}
+tree_hitters <- tree(Salary ~ ., hitters_train)
+
+summary(tree_hitters)
+
+single_tree_estimate <- predict(tree_hitters, 
+                               newdata = hitters_test)
+ggplot() + 
+    geom_point(aes(x = hitters_test$Salary, y = single_tree_estimate)) +
+    geom_abline()
+
+mean((single_tree_estimate - hitters_test$Salary)^2)
+```
+The MSE for a single tree is 142,426.9.
+
+```{r}
+# bagging
+
+set.seed(495)
+bag_hitters <- randomForest(Salary ~ ., 
+                          data = hitters_train, 
+                          mtry = 13, 
+                          importance = TRUE)
+bag_hitters
+
+bagged_estimate <- predict(bag_hitters, 
+                          newdata = hitters_test)
+
+ggplot() + 
+    geom_point(aes(x = hitters_test$Salary, y = bagged_estimate)) +
+    geom_abline()
+
+mean((bagged_estimate - hitters_test$Salary)^2)
+
+```
+Once we fit a model with bagging, the MSE decreased to 102,961.4 which is much lower than the single tree.
+
+```{r}
+# random forest
+
+set.seed(495)
+rf_hitters <- randomForest(Salary ~ ., 
+                         data = hitters_train, 
+                         mtry = 6, 
+                         importance = TRUE)
+
+random_forest_estimate <- predict(rf_hitters, 
+                                 newdata = hitters_test)
+
+mean((random_forest_estimate - hitters_test$Salary)^2)
+
+varImpPlot(rf_hitters)
+```
+The MSE of the random forest model with `mtry` = 6 is 105,432.7 which is a bit higher than the bagging model.
+
+```{r}
+# boosting
+
+set.seed(495)
+boost_hitters <- gbm(Salary ~ ., 
+                   data = hitters_train, 
+                   distribution = "gaussian", 
+                   n.trees = 5000, 
+                   interaction.depth = 4)
+
+summary(boost_hitters)
+
+boost_estimate <- predict(boost_hitters, 
+                         newdata = hitters_test, 
+                         n.trees = 5000)
+
+mean((boost_estimate - hitters_test$Salary)^2)
+```
+```{r}
+set.seed(495)
+boost_hitters2 <- gbm(Salary ~ ., 
+                   data = hitters_train, 
+                   distribution = "gaussian", 
+                   n.trees = 5000, 
+                   interaction.depth = 4,
+                   shrinkage = 0.01, 
+                   verbose = F)
+
+summary(boost_hitters2)
+
+boost_estimate2 <- predict(boost_hitters2, 
+                         newdata = hitters_test, 
+                         n.trees = 5000)
+
+mean((boost_estimate2 - hitters_test$Salary)^2)
+
+```
+The boosting model has an MSE of 107,212.3 which is a bit higher than the other models

### 2022-10-18 homework/hmk4/hmk4Stat495F22.Rmd
Finish EDA on Hmk 5

@@
 
-```{r}
-sum(is.na(kchouse$yr_renovated))
-```
-
 Before we fit any models, we need to make some adjustments to how the data is being treated by R.
+For example, we need to change the `date` to a date format and change `waterfront` and `zipcode` to be treated as categorical variables instead of numeric variables.
+We also changed the missing values from `yr_renovated` and `sqft_basement` to be "na" instead of 0.
 
 ```{r}
-# explore the data 
-# you need to do this before fitting anything!
-
-# submission should demonstrate you explored the data somewhat before 
-# fitting the models below
-
-# If there is anything else you should do before fitting models,
-# do it here
-
-# change date to a 
-# date format
-
-# create a histogram
-gf_dhistogram(~ bedrooms, data = kchouse) %>%
-  gf_labs(title = "Histogram of Prices")
-
 kchouse <- kchouse %>%
@@
          waterfront = as.factor(waterfront),
-  #       view = as.factor(view),
-  #       condition = as.factor(condition),
-  #       grade = as.factor(grade),
          zipcode = as.numeric(as.factor(zipcode)))
@@
   mutate_at(c('yr_renovated', 'sqft_basement'), ~na_if(.,0))
+```
 
+After examining `yr_renovated` and `sqft_basement`, it appears that 95.8% and 60.7% of the values, respectively, are missing.
+From the scatterplots below, there does not seem to be any clear relationship between `yr_renovated` and `price` as well as `sqft_basement` and `price`.
+Therefore, we will drop these predictors when creating our models.
+
+```{r}
 sum(is.na(kchouse$yr_renovated))/nrow(kchouse)
+sum(is.na(kchouse$sqft_basement))/nrow(kchouse)
+```
+
+```{r, warning = FALSE}
+ggplot(data = kchouse, aes(x = yr_renovated, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Year Renovated and Price", x = "Year Renovated",
+       y = "Price")
+ggplot(data = kchouse, aes(x = sqft_basement, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Sq Ft Basement and Price", 
+       x = "Square Feet Basement", y = "Price")
+```
+Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
+
+```{r}
+ggplot(data = kchouse, aes(x = bedrooms, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Bedrooms and Price", 
+       x = "Bedrooms", y = "Price")
+```
+Since there are a couple variables such as `date`, `id` that do not have a relationship with `price` as seen in the scatterplots below, we will remove those predictors as well.
+
+```{r}
+ggplot(data = kchouse, aes(x = date, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Date and Price", 
+       x = "Date", y = "Price")
+```
+
+```{r}
+ggplot(data = kchouse, aes(x = id, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of ID and Price", 
+       x = "ID", y = "Price")
+```
+Additionally, it appears that there are some concerns with multicollinearity between `sqft_living` and other variables such as `sqft_living15` and `sqft_above` so we are going to remove `sqft_living` as well.
+
+```{r}
+
+ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of SqFt Living and SqFt Above", 
+       x = "Sq Ft Living", y = "SqFt Living in 2015")
 
@@
 ```{r}
-# create a histogram
+ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of SqFt Living and SqFt Living in 2015", 
+       x = "Sq Ft Living", y = "SqFt Living in 2015")
+```
+```{r}
+kchouse1 <- kchouse %>%
+  filter(id != 2402100895) %>%
+  select(-c(id,zipcode, yr_renovated, date, sqft_basement, sqft_living))
+```
+
+From the scatterplot below of the latitude and the longitude, it seems like the houses are all bunched together in near each other (near Seattle) so the results of this analysis can only be generalized to that region of the state.
+
+```{r}
+ggplot(data = kchouse, aes(x = lat, y = long)) +
+  geom_point()
+```
+
+From the histogram below, the distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
+There appears to be many outliers on the high end for `price`.
+The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
+Since the distribution is right-skewed, if we were predicting price, a log-transformation could be useful.
+
+```{r}
 gf_dhistogram(~ price, data = kchouse) %>%
@@
 
-gf_boxplot(~ price, data = kchouse)%>%
-  gf_labs(title = "Boxplot of Prices")
-
 favstats(~ price, data = kchouse)
-
-ggplot(data = kchouse, aes(x = lat, y = long)) +
-  geom_point()
-
-ggplot(data = kchouse, aes(x = lat, y = long)) +
-  geom_point()
-
-kchouse1 <- mutate(kchouse, price = ifelse(price > 500000, 1, 0))
-
-kchouse1 <- kchouse1 %>%
-  filter(id != 2402100895) %>%
-  select(-c(id,zipcode, yr_renovated,date, sqft_basement))
-
 ```
 
+Next, since we want to know if the price of the house is greater or less than \$500,000, we will transform the price variable so that it is an binary predictor that is `1` if the price of the house is greater than \$500,000 and `0` if the price of the house is less than \$500,000.
+
 ```{r}
-645000-322000
+kchouse1 <- mutate(kchouse1, price = ifelse(price > 500000, 1, 0))
 ```
 
-The distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
-There appears to be many outliers on the high end for `price`.
-The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
-Since the distribution is right-skewed, a log-transformation could be useful.
+The last thing that we will do before creating the models is create a training and test set.
+The training set is used to create a model and then the test set is used to see how the model performs in making predictions.
+We will randomly create a 75%/25% split for the training/test set.
 
@@
 test <- kchouse1[test_index, ]
-
 ```

### 2022-10-18 homework/hmk5/hmk5Stat495F22.Rmd
Finish EDA on Hmk 5

@@
 
+For this analysis, we used the King County, Washington (State) house sales data set (`kchouse`).
+Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1.
+There is no information on the source of the data.
+The data set contains the following variables:
+\begin{itemize}
+\item id - notation for a specific house - Numeric
+\item date - date the house was sold - String
+\item price - price the house sold for in dollars - Numeric
+\item bedrooms - number of bedrooms in house - Numeric
+\item bathrooms- number of bathrooms per bedroom - Numeric
+\item sqft\textunderscore living - square footage of the home - Numeric
+\item sqft\textunderscore lot - square footage of the lot - Numeric
+\item floors - total floors (levels) in house - Numeric
+\item waterfront - house has a waterfront view - Y/N
+\item view - house has been viewed - Numeric
+\item condition - How good the condition is (overall) - Numeric
+\item grade - overall grade given to housing unit (based on King County grading system: 1 poor, 13 excellent) - Numeric
+\item sqft\textunderscore above - square footage of house apart from basement - Numeric
+\item yr\textunderscore built - the year the house was built - Numeric
+\item yr\textunderscore renovated - the year when the house was generated
+\item zipcode - the zipcode the house is in - Numeric
+\item lat - Latitude coordinate of house - Numeric
+\item long - Longitude coordinate of house - Numeric
+\item sqft\textunderscore living15 - living room area in 2015 (may or may not have been affected the lot size area) - Numeric
+\item sqft\textunderscore lot15 - lot size area in 2015 - Numeric
+\end{itemize}
+
+Before we fit any models, we need to make some adjustments to how the data is being treated by R.
+For example, we need to change the `date` to a date format and change `waterfront` and `zipcode` to be treated as categorical variables instead of numeric variables.
+We also changed the missing values from `yr_renovated` and `sqft_basement` to be "na" instead of 0.
+
+```{r}
+kchouse <- kchouse %>%
+  mutate(date = lubridate::mdy(date),
+         waterfront = as.factor(waterfront),
+         zipcode = as.numeric(as.factor(zipcode)))
+kchouse <- kchouse %>%
+  mutate_at(c('yr_renovated', 'sqft_basement'), ~na_if(.,0))
+```
+
+After examining `yr_renovated` and `sqft_basement`, it appears that 95.8% and 60.7% of the values, respectively, are missing.
+From the scatterplots below, there does not seem to be any clear relationship between `yr_renovated` and `price` as well as `sqft_basement` and `price`.
+Therefore, we will drop these predictors when creating our models.
+
+```{r}
+sum(is.na(kchouse$yr_renovated))/nrow(kchouse)
+sum(is.na(kchouse$sqft_basement))/nrow(kchouse)
+```
+
+```{r, warning = FALSE}
+ggplot(data = kchouse, aes(x = yr_renovated, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Year Renovated and Price", x = "Year Renovated",
+       y = "Price")
+ggplot(data = kchouse, aes(x = sqft_basement, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Sq Ft Basement and Price", 
+       x = "Square Feet Basement", y = "Price")
+```
+Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
+
+```{r}
+ggplot(data = kchouse, aes(x = bedrooms, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Bedrooms and Price", 
+       x = "Bedrooms", y = "Price")
+```
+Since there are a couple variables such as `date`, `id` that do not have a relationship with `price` as seen in the scatterplots below, we will remove those predictors as well.
+
+```{r}
+ggplot(data = kchouse, aes(x = date, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Date and Price", 
+       x = "Date", y = "Price")
+```
+
+```{r}
+ggplot(data = kchouse, aes(x = id, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of ID and Price", 
+       x = "ID", y = "Price")
+```
+Additionally, it appears that there are some concerns with multicollinearity between `sqft_living` and other variables such as `sqft_living15` and `sqft_above` so we are going to remove `sqft_living` as well.
+
+```{r}
+
+ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of SqFt Living and SqFt Above", 
+       x = "Sq Ft Living", y = "SqFt Living in 2015")
+
+```
+
+```{r}
+ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of SqFt Living and SqFt Living in 2015", 
+       x = "Sq Ft Living", y = "SqFt Living in 2015")
+```
+```{r}
+kchouse1 <- kchouse %>%
+  filter(id != 2402100895) %>%
+  select(-c(id,zipcode, yr_renovated, date, sqft_basement, sqft_living))
+```
+
+From the scatterplot below of the latitude and the longitude, it seems like the houses are all bunched together in near each other (near Seattle) so the results of this analysis can only be generalized to that region of the state.
+
+```{r}
+ggplot(data = kchouse, aes(x = lat, y = long)) +
+  geom_point()
+```
+
+From the histogram below, the distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
+There appears to be many outliers on the high end for `price`.
+The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
+Since the distribution is right-skewed, if we were predicting price, a log-transformation could be useful.
+
+```{r}
+gf_dhistogram(~ price, data = kchouse) %>%
+  gf_labs(title = "Histogram of Prices")
+
+favstats(~ price, data = kchouse)
+```
+
+Next, since we want to know if the price of the house is greater or less than \$500,000, we will transform the price variable so that it is an binary predictor that is `1` if the price of the house is greater than \$500,000 and `0` if the price of the house is less than \$500,000.
+
+```{r}
+kchouse1 <- mutate(kchouse1, price = ifelse(price > 500000, 1, 0))
+```
+
+The last thing that we will do before creating the models is create a training and test set.
+The training set is used to create a model and then the test set is used to see how the model performs in making predictions.
+We will randomly create a 75%/25% split for the training/test set.
+
+```{r}
+# create the training and test set for price
+set.seed(1)
+n <- nrow(kchouse1)
+train_index <- sample(1:n, 3/4 * n)
+test_index <- setdiff(1:n, train_index)
+
+train <- kchouse1[train_index, ]
+test <- kchouse1[test_index, ]
+```
+
 \newpage

### 2022-10-18 homework/hmk4/hmk4Stat495F22.Rmd
Finished GLM section

@@
 library(lmtest) # for likelihood ratio tests
+
+require(gridExtra)
 
@@
 ```{r, warning = FALSE}
-ggplot(data = kchouse, aes(x = yr_renovated, y = price)) + 
+fig1 <- ggplot(data = kchouse, aes(x = yr_renovated, y = price)) + 
   geom_point() + 
@@
        y = "Price")
-ggplot(data = kchouse, aes(x = sqft_basement, y = price)) + 
+fig2 <- ggplot(data = kchouse, aes(x = sqft_basement, y = price)) + 
   geom_point() + 
@@
        x = "Square Feet Basement", y = "Price")
+
 ```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+grid.arrange(fig1, fig2, ncol = 2)
+```
+
 Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
@@
 ```
+
 Since there are a couple variables such as `date`, `id` that do not have a relationship with `price` as seen in the scatterplots below, we will remove those predictors as well.
@@
 ```{r}
-ggplot(data = kchouse, aes(x = date, y = price)) + 
+fig3 <- ggplot(data = kchouse, aes(x = date, y = price)) + 
   geom_point() + 
@@
        x = "Date", y = "Price")
-```
 
-```{r}
-ggplot(data = kchouse, aes(x = id, y = price)) + 
+fig4 <- ggplot(data = kchouse, aes(x = id, y = price)) + 
   geom_point() + 
@@
 ```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+grid.arrange(fig3, fig4, ncol = 2)
+```
+
 Additionally, it appears that there are some concerns with multicollinearity between `sqft_living` and other variables such as `sqft_living15` and `sqft_above` so we are going to remove `sqft_living` as well.
@@
 
-ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
+fig5 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) +
   geom_point() + 
@@
 
-```
-
-```{r}
-ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
+fig6 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
   geom_point() + 
@@
 ```
+```{r, include = TRUE, fig.width=9, fig.height=8, message=FALSE}
+grid.arrange(fig5, fig6, ncol = 2)
+```
+
 ```{r}
@@
   geom_point()
+```
+
+It also appears that many of the predictors are right-skewed which means that a log transformation could be helpful for a model.
+For example, as seen below, `sqft_living15` and `sqft_lot15` before and after a  log transformation.
+This is the same for additional variables as well.
+
+```{r}
+fig7 <- gf_dhistogram(~ sqft_living15, data = kchouse) %>%
+  gf_labs(title = "Histogram of SqFt Living in 2015")
+
+fig8 <- gf_dhistogram(~ sqft_lot, data = kchouse) %>%
+  gf_labs(title = "Histogram of SqFt Lot in 2015")
+
+fig9 <- gf_dhistogram(~ log(sqft_living15), data = kchouse) %>%
+  gf_labs(title = "Histogram of SqFt Living in 2015")
+
+fig10 <- gf_dhistogram(~ log(sqft_lot), data = kchouse) %>%
+  gf_labs(title = "Histogram of SqFt Lot in 2015")
+
+```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+grid.arrange(fig7, fig8, fig9, fig10, ncol = 2)
 ```
@@
 The training set is used to create a model and then the test set is used to see how the model performs in making predictions.
-We will randomly create a 75%/25% split for the training/test set.
+We will randomly create a 75/25 split for the training/test set.
 
@@
 
+The first models that we are going to be fitting are GLMs (or Generalized Linear Models) which are extensions of ordinary linear regression (fitting a least-squares curve) to cases where the response variables are in an exponential family form.
+This can be response variables that are binomial, Poisson, gamma, or beta.
+Since we transformed `price` into a binary variable, it can now be modeled as a binomial distribution.
+
+First, we are going to fit a logistic model using all of the variables that we have not removed from the data set. We use the training set to create the model.
+
 ```{r}
-# choose and fit at least 2 different models for your GLM
-# include appropriate output and assessment of their performance
-
-# think ahead: what does a reader need to know to follow your model fitting process?
-# you may want to jot down notes for yourself that you'll need later!
+logmod <- glm(price ~ ., data = train, family = "binomial")
+msummary(logmod)
 ```
 
-We are going to first use Poisson Regression to predict `price`.
+It appears from the model that we have 9 significant predictors and we can perform a likelihood ratio test to determine if the overall model is significant.
 
 ```{r}
-
-logmod <- glm(price ~ ., data = train, family = "binomial")
-msummary(logmod)
 lrtest(logmod)
@@
 
+Since we have a significant p-value, it appears that the overall model is significant. Now in order to make predictions using this model, we need to bin the fitted values which we will do below.
+
 ```{r}
 augprice1 <- augment(logmod, type.predict = "response")
-favstats(~ .fitted, data = augprice1)
+augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = augprice1)
+9826/(9826+6371)
 
@@
 
+After using 0.5 as a default cutoff, the model classifies 60.7% of the prices as below \$500,000.
+This is close to the actual percentage of the training data that is classified as below \$500,000 which is 58.1% of the observations.
+We can try to match this a little better by adjusting the cutoff to which we round the numbers.
+Finding, the appropriate quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.4% which is much closer than before.
+
 ```{r}
-augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
-tally(~ binprediction, data = augprice1)
-9787/(9787+6410)
+# find out the actual percentage in training set
+tally(~ price, data = augprice1)
+9415/(9415+6782)
+
+# find the appropriate quantile
+with(augprice1, quantile(.fitted, 0.58128))
+
+# re-bin the values and find out the percentage
+augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
+tally(~ binprediction2, data = augprice1)
+9455/(9455+6742)
 ```
 
-```{r}
-tally(~ price, data = augprice1)
-9415/(9415+6782)
-with(augprice1, quantile(.fitted, 0.58128))
-```
-
-```{r}
-augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
-tally(~ binprediction2, data = augprice1)
-```
+Next, we can create a confusion matrix and determine how many of the predictions were correct.
+From the matrix and calculation below, it appears that 84.0% of the predictions for the training set were correct.
 
@@
 with(augprice1, table(price, binprediction2))
+(8138+5465)/(8138+5465+1277+1317)
 ```
 
+We will do the same on the test set to see how the model performs.
+We follow the same process as above to calculate the predicted values and then bin them using our previous cutoff.
+The model classifies 58.9% of the prices below \$500,000.
+
 ```{r}
-(8131+5498)/(8131+5498+1284+1284)
+augprice2 <- mutate(test, fitted = predict(logmod, newdata = test, type = "response"))
+augprice2 <- mutate(augprice2, binprediction = as.numeric(fitted > 0.454465))
+tally(~ binprediction, data = augprice2)
+(3181)/(3181+2218)
+```
+
+Next, we generate a confusion matrix and it appears that 83.8% of the predictions were correct.
+
+```{r}
+with(augprice2, table(price, binprediction))
+(2719+1806)/(2719+1806+462+412)
 ```
@@
 ```{r, warning=FALSE}
+
+# dDELETE I THINK
 # get MSE of training set
@@
 
-*******************************
+Next, we will try creating a smaller model by removing some of the predictors that were not significant in our previous model.
+We are going to remove `bedrooms`, `long`, and `sqft_lot15`.
+After creating this model, we then repeated the process and removed other variables that were significant, but did not seem to have much of an impact on the predictions because the other variables were much more influential.
+The other variables we removed were `sqft_lot`, `floors`, `waterfront`, `view`, `condition`, and  `sqft_above`.
+
 ```{r}
-xPrice <- model.matrix(price ~ ., kchouse1)[, -1]
-yPrice <- kchouse1$price
+logmod2 <- glm(price ~ bathrooms + grade + yr_built + lat + sqft_living15, 
+  data = train, family = "binomial")
+msummary(logmod2)
+lrtest(logmod2)
+```
 
-x_train <- model.matrix(price ~ ., train)[, -1]
-x_test <- model.matrix(price ~ ., test)[, -1]
+All of the variables in our reduced model are significant and the model overall is significant as well. Now, we can create some predictions following the same process as above.
 
-y_train <- train %>%
-  select(price) %>%
-  unlist() %>%
-  as.numeric()
-
-y_test <- test %>%
-  select(price) %>%
-  unlist() %>%
-  as.numeric()
-
-grid <- 10^seq(10, -2, length = 100)
-
-ridge_mod <- glmnet(x_train, y_train, family = "binomial", alpha = 0, lambda = grid)
-
-plot(ridge_mod, label = TRUE)
-#ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
-#mean((ridge_pred - y_test)^2)
-
-set.seed(1)
-
-cv.out <- cv.glmnet(x_train, y_train, alpha = 0)
-bestlam <- cv.out$lambda.min
-bestlam
-
-plot(cv.out)
-
-predict(cv.out, type = "coefficients", s = bestlam)
-
-ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test)
-mean((ridge_pred - y_test)^2)
-
-#augprice2 <- augment(ridge_mod, type.predict = "response")
-#favstats(~ .fitted, data = augprice2)
+```{r}
+augprice3 <- augment(logmod2, type.predict = "response")
+augprice3 <- mutate(augprice3, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = augprice3)
+9829/(9829+6386)
 
 ```
+
+After using 0.5 as a default cutoff, the model classifies 60.6% of the prices as below \$500,000.
+After adjusting the quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.1% which is much closer than before.
+
+```{r}
+# find the appropriate quantile
+with(augprice3, quantile(.fitted, 0.58128))
+
+# re-bin the values and find out the percentage
+augprice3 <- mutate(augprice3, binprediction2 = as.numeric(.fitted > 0.451563))
+tally(~ binprediction2, data = augprice3)
+9414/(9414+6783)
+```
+
+Next, we can create a confusion matrix and determine how many of the predictions were correct.
+From the matrix and calculation below, it appears that 84.0% of the predictions for the training set were correct.
+
+```{r}
+with(augprice3, table(price, binprediction2))
+(8119+5486)/(8119+5486+1296+1296)
+```
+
+We will do the same on the test set to see how the model performs.
+We follow the same process as above to calculate the predicted values and then bin them using our previous cutoff.
+The model classifies 58.6% of the prices below \$500,000.
+
+```{r}
+augprice4 <- mutate(test, fitted = predict(logmod2, newdata = test, type = "response"))
+augprice4 <- mutate(augprice4, binprediction3 = as.numeric(fitted > 0.451563))
+tally(~ binprediction3, data = augprice4)
+(3164)/(3164+2235)
+```
+
+Next, we generate a confusion matrix and it appears that 83.1% of the predictions were correct.
+
+```{r}
+with(augprice4, table(price, binprediction3))
+(2690+1794)/(2690+1794+474+441)
+```
+
+Although this model has a slightly lower correct prediction percentage, this model is much simpler than the first model and has many less predictors.
 

### 2022-10-18 homework/hmk5/hmk5Stat495F22.Rmd
Finished GLM section

@@
 options(digits = 6)
+library(rpart)
+library(partykit)
+library(GGally)
+library(broom)
+library(ggplot2)
+library(lmtest) # for likelihood ratio tests
+
+require(gridExtra)
+
+library(ISLR)
+library(glmnet)
+
+library(lars)    # you may need to install some of these (one time only)
+library(leaps)   # to use variable selection methods if desired
 ```
@@
        x = "Square Feet Basement", y = "Price")
+
 ```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, warning=FALSE}
+grid.arrange(fig1, fig2, ncol = 2)
+```
+
 Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
@@
 
-ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
+fig5 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
   geom_point() + 
@@
 ```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+grid.arrange(fig5, fig6, ncol = 2)
+```
+
 ```{r}

### 2022-10-19 homework/hmk4/hmk4Stat495F22.Rmd
Finish glm and tree and model comparisons section

@@
 library(glmnet)
-
+library(rpart.plot)
 library(lars)    # you may need to install some of these (one time only)
@@
 
-Although this model has a slightly lower correct prediction percentage, this model is much simpler than the first model and has many less predictors.
+Overall, from the two logistic regression models that were created, they both performed very similar to each other with the second one having a slightly lower correct prediction rate.
+However, for the second model, we removed many predictors that were not influential to the model and therefore were not helping make the predictions.
+After those variables were removed, the logistic model became much more simple with less predictors.
+The real estate developer's questions of interest is to find the variables that are indicative of houses that sell for over \$500,000 and by keeping a similar performance of the model, but removing extraneous predictors, we are able to find the predictors that are the most important.
+The second model contained the predictors: `bathrooms`, `grade`, `yr_built`, `lat`, and `sqft_living15`.
 
@@
 
+The second method that we are going to be using to fit models is through classification trees.
+Classification trees are a nonparametric method of prediction and are easy to interpret.
+Classification trees are used when the response variable is binary so it is appropriate to use them in order to predict if the price is over or under \$500,000.
+They are created through recursive partitioning to create "splits" between observations with similar qualities.
+
+We will first create a tree with the default stopping criteria.
+
 ```{r}
@@
 printcp(price.rpart1)
+rpart.plot(price.rpart1)
+```
 
-# find the MSE of the training set for default tree
+The classification tree above uses the predictors, `grade`, `lat`, `sqft_above`, `sqft_living15`, `sqft_lot15`, and `yr_built`.
+The error from this classification tree is 0.8589 which is calculated from the root node error and the relative error in the output above.
+
+```{r}
+1 - 0.3368*0.4187
+```
+
+Next, we will using the classification tree that we created to see how well it predicts the training set.
+From the confusion matrix below, it appears that the classification tree predicts correctly for 85.9% of the observations.
+
+```{r}
 train1 <- mutate(train, predprice = predict(price.rpart1, type = "class"))
 tally(predprice ~ price, data = train1)
-tally(~ price, data = train1)
+(8227+5696)/(8227+5696+1188+1096)
 
-#find the MSE of the test set for default tree
+```
+
+And doing the same thing for the test we, it appears that the model predicts correctly 85.5% of the observations.
+
+```{r}
 test1 <- mutate(test, predprice = predict(price.rpart1, type = "class", newdata = test))
 tally(predprice ~ price, data = test1)
-tally(~ price, data = test1)
-```
-```{r}
-(8283+5728)/(8283+5728+1132+1054)
-
-(2754+1881)/(2754+1881+377+387)
-(3131)/(3131+2268)
+(2748+1870)/(2748+1870+398+383)
 ```
 
+Before we create the second model, we examine the cross -validation process that was used in creating the previous model.
+The default cross-validation is a 10-fold cross-validation.
+Below we can see that as the complexity parameter reaches 0.16, the relative error calculated from the cross-validation decreases only a small amount as the complexity parameter increases.
+Therefore, we are going to use a complexity parameter of 0.016 for our next tree.
+
 ```{r}
-# perhaps make a less complicated one
-# see how much you lose
 plotcp(price.rpart1)
+```
 
-price.control <- rpart.control(minsplit = 10, cp = 0.017)
+We are also going to control `minsplit = 500` which means that there needs to be 500 observations in a node before a split is attempted.
+This is reasonable for a tree created from our training data with a size of 16197.
+We also set `minbucket = 300` which means that the minimum number of observations in any terminal node is 300 observations.
+There controls are to try and attempt to build a smaller tree while keeping the same effectiveness of the first model.
+
+```{r}
+price.control <- rpart.control(minsplit = 500, minbucket = 300, cp = 0.016)
 price.rpart2 <- rpart(price ~ ., data = train, method = "class", control = price.control)
 printcp(price.rpart2)
+```
 
-# find the MSE of the training set for default tree
-train1 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
-tally(predprice ~ price, data = train1)
-tally(~ price, data = train1)
+The classification tree above uses the predictors, `grade`, `lat`, and `sqft_living15`.
+The error from this classification tree is 0.8303 which is calculated from the root node error and the relative error in the output above.
 
-#find the MSE of the test set for default tree
-test1 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
-tally(predprice ~ price, data = test1)
-tally(~ price, data = test1)
+```{r}
+1 - 0.4053*0.4187
 ```
+
+From the output below, the classification tree we created is much more simple.
+
+```{r}
+rpart.plot(price.rpart2)
+```
+
+We will now see how the model performs in classifying observations.
 
@@
 
+train2 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
+tally(predprice ~ price, data = train2)
+(8054+5394)/(8054+5394+1361+1388)
 ```
+
+It appears the the model classifies observations 83.0% correctly in the training set. We will do the same for the test set.
+
+```{r}
+
+test2 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
+tally(predprice ~ price, data = test2)
+(2710+1772)/(2710+1772+421+496)
+```
+
+It appears the the model classifies observations 83.0% correctly in the test set as well.
+
+From these two models, the first one is more complex and predicts correctly about 2.5-3% better than the second model.
+However, this means that the first classification tree is less interpretable than the second one.
+The first tree has 11 splits whereas the second one only has 5.
+Because of this reason, we would choose the second model over the first one.
+The slight decrease in correct predictions matters less than the increase in interpretability for the model.
+Additionally, the error of the second classification tree is slightly less than that of the first tree.
+Also, since we are determining which of the variables are the best predictors if a house is above \$500,000, the second model only uses 3 predictors whereas the first model uses 6.
+The predictors used in the second model are `grade`, `lat`, and `sqft_living15`.
 

### 2022-10-19 homework/hmk5/hmk5Stat495F22.Rmd
Finish glm and tree and model comparisons section

@@
 
+The first models that we are going to be fitting are GLMs (or Generalized Linear Models) which are extensions of ordinary linear regression (fitting a least-squares curve) to cases where the response variables are in an exponential family form.
+This can be response variables that are binomial, Poisson, gamma, or beta.
+Since we transformed `price` into a binary variable, it can now be modeled as a binomial distribution.
+
+First, we are going to fit a logistic model using all of the variables that we have not removed from the data set. We use the training set to create the model.
+
+```{r}
+logmod <- glm(price ~ ., data = train, family = "binomial")
+msummary(logmod)
+```
+
+It appears from the model that we have 9 significant predictors and we can perform a likelihood ratio test to determine if the overall model is significant.
+
+```{r}
+lrtest(logmod)
+```
+
+Since we have a significant p-value, it appears that the overall model is significant. Now in order to make predictions using this model, we need to bin the fitted values which we will do below.
+
+```{r}
+augprice1 <- augment(logmod, type.predict = "response")
+augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = augprice1)
+9826/(9826+6371)
+
+```
+
+After using 0.5 as a default cutoff, the model classifies 60.7% of the prices as below \$500,000.
+This is close to the actual percentage of the training data that is classified as below \$500,000 which is 58.1% of the observations.
+We can try to match this a little better by adjusting the cutoff to which we round the numbers.
+Finding, the appropriate quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.4% which is much closer than before.
+
+```{r}
+# find out the actual percentage in training set
+tally(~ price, data = augprice1)
+9415/(9415+6782)
+
+# find the appropriate quantile
+with(augprice1, quantile(.fitted, 0.58128))
+
+# re-bin the values and find out the percentage
+augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
+tally(~ binprediction2, data = augprice1)
+9455/(9455+6742)
+```
+
+Next, we can create a confusion matrix and determine how many of the predictions were correct.
+From the matrix and calculation below, it appears that 84.0% of the predictions for the training set were correct.
+
+```{r}
+with(augprice1, table(price, binprediction2))
+(8138+5465)/(8138+5465+1277+1317)
+```
+
+We will do the same on the test set to see how the model performs.
+We follow the same process as above to calculate the predicted values and then bin them using our previous cutoff.
+The model classifies 58.9% of the prices below \$500,000.
+
+```{r}
+augprice2 <- mutate(test, fitted = predict(logmod, newdata = test, type = "response"))
+augprice2 <- mutate(augprice2, binprediction = as.numeric(fitted > 0.454465))
+tally(~ binprediction, data = augprice2)
+(3181)/(3181+2218)
+```
+
+Next, we generate a confusion matrix and it appears that 83.8% of the predictions were correct.
+
+```{r}
+with(augprice2, table(price, binprediction))
+(2719+1806)/(2719+1806+462+412)
+```
+
+Next, we will try creating a smaller model by removing some of the predictors that were not significant in our previous model.
+We are going to remove `bedrooms`, `long`, and `sqft_lot15`.
+After creating this model, we then repeated the process and removed other variables that were significant, but did not seem to have much of an impact on the predictions because the other variables were much more influential.
+The other variables we removed were `sqft_lot`, `floors`, `waterfront`, `view`, `condition`, and  `sqft_above`.
+
+```{r}
+logmod2 <- glm(price ~ bathrooms + grade + yr_built + lat + sqft_living15, 
+  data = train, family = "binomial")
+msummary(logmod2)
+lrtest(logmod2)
+```
+
+All of the variables in our reduced model are significant and the model overall is significant as well. Now, we can create some predictions following the same process as above.
+
+```{r}
+augprice3 <- augment(logmod2, type.predict = "response")
+augprice3 <- mutate(augprice3, binprediction = round(.fitted, 0))
+tally(~ binprediction, data = augprice3)
+9829/(9829+6386)
+
+```
+
+After using 0.5 as a default cutoff, the model classifies 60.6% of the prices as below \$500,000.
+After adjusting the quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.1% which is much closer than before.
+
+```{r}
+# find the appropriate quantile
+with(augprice3, quantile(.fitted, 0.58128))
+
+# re-bin the values and find out the percentage
+augprice3 <- mutate(augprice3, binprediction2 = as.numeric(.fitted > 0.451563))
+tally(~ binprediction2, data = augprice3)
+9414/(9414+6783)
+```
+
+Next, we can create a confusion matrix and determine how many of the predictions were correct.
+From the matrix and calculation below, it appears that 84.0% of the predictions for the training set were correct.
+
+```{r}
+with(augprice3, table(price, binprediction2))
+(8119+5486)/(8119+5486+1296+1296)
+```
+
+We will do the same on the test set to see how the model performs.
+We follow the same process as above to calculate the predicted values and then bin them using our previous cutoff.
+The model classifies 58.6% of the prices below \$500,000.
+
+```{r}
+augprice4 <- mutate(test, fitted = predict(logmod2, newdata = test, type = "response"))
+augprice4 <- mutate(augprice4, binprediction3 = as.numeric(fitted > 0.451563))
+tally(~ binprediction3, data = augprice4)
+(3164)/(3164+2235)
+```
+
+Next, we generate a confusion matrix and it appears that 83.1% of the predictions were correct.
+
+```{r}
+with(augprice4, table(price, binprediction3))
+(2690+1794)/(2690+1794+474+441)
+```
+
+Overall, from the two logistic regression models that were created, they both performed very similar to each other with the second one having a slightly lower correct prediction rate.
+However, for the second model, we removed many predictors that were not influential to the model and therefore were not helping make the predictions.
+After those variables were removed, the logistic model became much more simple with less predictors.
+The real estate developer's questions of interest is to find the variables that are indicative of houses that sell for over \$500,000 and by keeping a similar performance of the model, but removing extraneous predictors, we are able to find the predictors that are the most important.
+The second model contained the predictors: `bathrooms`, `grade`, `yr_built`, `lat`, and `sqft_living15`.
+
 \newpage
@@
 # Tree and Results
+The second method that we are going to be using to fit models is through classification trees.
+Classification trees are a nonparametric method of prediction and are easy to interpret.
+Classification trees are used when the response variable is binary so it is appropriate to use them in order to predict if the price is over or under \$500,000.
+They are created through recursive partitioning to create "splits" between observations with similar qualities.
 
-```{r, include = FALSE}
-# Can be before or after your GLM
+We will first create a tree with the default stopping criteria.
+
+```{r}
+price.rpart1 <- rpart(price ~ ., data = train, method = "class")
+printcp(price.rpart1)
+rpart.plot(price.rpart1)
 ```
 
-\newpage
+The classification tree above uses the predictors, `grade`, `lat`, `sqft_above`, `sqft_living15`, `sqft_lot15`, and `yr_built`.
+The error from this classification tree is 0.8589 which is calculated from the root node error and the relative error in the output above.
 
-# Model Comparison
+```{r}
+1 - 0.3368*0.4187
+```
 
-```{r, include = FALSE}
-# Can be woven in above
+Next, we will using the classification tree that we created to see how well it predicts the training set.
+From the confusion matrix below, it appears that the classification tree predicts correctly for 85.9% of the observations.
+
+```{r}
+train1 <- mutate(train, predprice = predict(price.rpart1, type = "class"))
+tally(predprice ~ price, data = train1)
+(8227+5696)/(8227+5696+1188+1096)
+
 ```
+
+And doing the same thing for the test we, it appears that the model predicts correctly 85.5% of the observations.
+
+```{r}
+test1 <- mutate(test, predprice = predict(price.rpart1, type = "class", newdata = test))
+tally(predprice ~ price, data = test1)
+(2748+1870)/(2748+1870+398+383)
+```
+
+Before we create the second model, we examine the cross -validation process that was used in creating the previous model.
+The default cross-validation is a 10-fold cross-validation.
+Below we can see that as the complexity parameter reaches 0.16, the relative error calculated from the cross-validation decreases only a small amount as the complexity parameter increases.
+Therefore, we are going to use a complexity parameter of 0.016 for our next tree.
+
+```{r}
+plotcp(price.rpart1)
+```
+
+We are also going to control `minsplit = 500` which means that there needs to be 500 observations in a node before a split is attempted.
+This is reasonable for a tree created from our training data with a size of 16197.
+We also set `minbucket = 300` which means that the minimum number of observations in any terminal node is 300 observations.
+There controls are to try and attempt to build a smaller tree while keeping the same effectiveness of the first model.
+
+```{r}
+price.control <- rpart.control(minsplit = 500, minbucket = 300, cp = 0.016)
+price.rpart2 <- rpart(price ~ ., data = train, method = "class", control = price.control)
+printcp(price.rpart2)
+```
+
+The classification tree above uses the predictors, `grade`, `lat`, and `sqft_living15`.
+The error from this classification tree is 0.8303 which is calculated from the root node error and the relative error in the output above.
+
+```{r}
+1 - 0.4053*0.4187
+```
+
+From the output below, the classification tree we created is much more simple.
+
+```{r}
+rpart.plot(price.rpart2)
+```
+
+We will now see how the model performs in classifying observations.
+
+```{r}
+
+train2 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
+tally(predprice ~ price, data = train2)
+(8054+5394)/(8054+5394+1361+1388)
+```
+
+It appears the the model classifies observations 83.0% correctly in the training set. We will do the same for the test set.
+
+```{r}
+
+test2 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
+tally(predprice ~ price, data = test2)
+(2710+1772)/(2710+1772+421+496)
+```
+
+It appears the the model classifies observations 83.0% correctly in the test set as well.
+
+From these two models, the first one is more complex and predicts correctly about 2.5-3% better than the second model.
+However, this means that the first classification tree is less interpretable than the second one.
+The first tree has 11 splits whereas the second one only has 5.
+Because of this reason, we would choose the second model over the first one.
+The slight decrease in correct predictions matters less than the increase in interpretability for the model.
+Additionally, the error of the second classification tree is slightly less than that of the first tree.
+Also, since we are determining which of the variables are the best predictors if a house is above \$500,000, the second model only uses 3 predictors whereas the first model uses 6.
+The predictors used in the second model are `grade`, `lat`, and `sqft_living15`.
 

### 2022-10-19 homework/hmk5/hmk5Stat495F22.Rmd
Added intro and conclusion. Just need to edit

@@
 require(gridExtra) 
-
+library(rpart.plot)
 library(ISLR)
@@
 # Introduction 
+We are interested in determining the features that are predictive of homes that are selling for more than half a million dollars.
+We are only interested in whether the price is over or under \$500,000, so will transform the price into a binary response variable where the the price is either over \$500,000 or it isn't.
+Then because the response variable is binary, we will use logistic regression to create the best model that we can.
+We will also perform a non-parametric analysis using classification trees in order to help visualize what predictors are best indicators of a house selling for greater than \$500,000.
+Finally, we will be able to compare the models to help answer the real estate developer's questions.
 
@@
 
-Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
+Additionally, from the Scatterplot of Bedrooms and Price below, there appears to be an outlier so we will remove that observation.
 
@@
   geom_point() + 
-  labs(title = "Scatterplot of SqFt Living and SqFt Living in 2015", 
+  labs(title = "Scatterplot of SqFt Living and SqFt Living 2015", 
        x = "Sq Ft Living", y = "SqFt Living in 2015")
@@
 
-From the scatterplot below of the latitude and the longitude, it seems like the houses are all bunched together in near each other (near Seattle) so the results of this analysis can only be generalized to that region of the state.
+From the scatterplot below of the latitude and the longitude, it seems like the houses are all bunched together near each other (close to Seattle) so the results of this analysis can only be generalized to that region of the state.
 
@@
 ggplot(data = kchouse, aes(x = lat, y = long)) +
-  geom_point()
+  geom_point() + 
+  labs(title = "Scatterplot of Latitude and Longitude", 
+       x = "Latitude", y = "Longitude")
 ```
@@
 Next, since we want to know if the price of the house is greater or less than \$500,000, we will transform the price variable so that it is an binary predictor that is `1` if the price of the house is greater than \$500,000 and `0` if the price of the house is less than \$500,000.
+It appears that there are 12,546 houses with price below \$500,000 and 9,050 houses with a price above \$500,000.
 
@@
 kchouse1 <- mutate(kchouse1, price = ifelse(price > 500000, 1, 0))
+tally(~price, data = kchouse1)
 ```
@@
 Since we transformed `price` into a binary variable, it can now be modeled as a binomial distribution.
+The model that we use for a binary response variable is a logistic regession model.
 
-First, we are going to fit a logistic model using all of the variables that we have not removed from the data set. We use the training set to create the model.
+First, we are going to fit the logistic model using all of the variables that we have not removed from the data set. We use the training set to create the model.
 
@@
 
-```{r}
+```{r, fig.width = 6, fig.height = 5}
 price.rpart1 <- rpart(price ~ ., data = train, method = "class")
@@
 # Conclusion
+The goal of this analysis was to determine the variables that are most indicative of a house's price being greater than \$500,000.
+To accomplish this, we first created two logistic regression models and decided that the one with less predictors was better of the two due to its comparable prediction accuracy and simplicity.
+This model contained the predictors `bathrooms`, `grade`, `yr_built`, `lat`, and `sqft_living15` which means that for the logistic regression model, these variables contributed the most to determining if a house had a price greater than half a million dollars.
+Secondly, we created two classification trees which we used to predict if a price was greater than \$500,000 or not.
+Again, we chose the model that had a similar prediction accuracy and less predictors.
+This tree was also much smaller, and thus easier to interpret.
+The predictors used in this model are `grade`, `lat`, and `sqft_living15`.
+The classification tree models performed slightly better than the logistic regression trees, but they were all within a small range so they are comparable.
+Combining information from both of our final models, `grade`, `lat`, and `sqft_living15` appeared as significant predictors in both models so these varaibles especially, are the ones that are most predictive of a house with a price over \$500,000.

### 2022-10-19 homework/hmk5/hmk5Stat495F22.Rmd
Edited the writing of hmk 5

--- 2022-10-19 homework/hmk5/hmk5Stat495F22.Rmd
@@
 
-*
+* https://www.kaggle.com/datasets/swathiachath/kc-housesales-data
+* https://statisticsglobe.com/count-number-of-na-values-in-vector-and-column-in-r
+* https://cran.r-project.org/web/packages/rpart/vignettes/longintro.pdf
 
@@
 # Homework 5 - Prompt - Write-up for Homework 4
-
-```{r}
-kchouse <- read.csv("https://awagaman.people.amherst.edu/stat495/kc_house_data.csv", header = T)
-```
 
@@
 
-# Introduction
+# Introduction and Exploratory Data Analysis 
+We are interested in determining the features predictive of homes selling for more than half a million dollars.
+We are only interested in whether the price is over or under \$500,000, so we will transform it into a binary response variable where the price is either over \$500,000 or is not.
+Then because the response variable is binary, we will use logistic regression to create the best model we can.
+We will also perform a non-parametric analysis using classification trees to help visualize what predictors are best indicators of a house selling for greater than \$500,000.
+Finally, we can compare the models to help answer the real estate developer's questions.
 
-\newpage
+We used the King County, Washington (State) house sales data set (`kchouse`) for this analysis.
+Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1.
+There is no information on the source of the data.
 
-# Exploratory Data Analysis
-
-```{r, include = FALSE}
-# Can be included with the introduction
+```{r}
+kchouse <- read.csv("https://awagaman.people.amherst.edu/stat495/kc_house_data.csv", header = T)
 ```
 
-For this analysis, we used the King County, Washington (State) house sales data set (`kchouse`).
-Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1.
-There is no information on the source of the data.
 The data set contains the following variables:
@@
 
-Before we fit any models, we need to make some adjustments to how the data is being treated by R.
-For example, we need to change the `date` to a date format and change `waterfront` and `zipcode` to be treated as categorical variables instead of numeric variables.
-We also changed the missing values from `yr_renovated` and `sqft_basement` to be "na" instead of 0.
+Before we fit any models, we need to adjust how R treats the data.
+For example, we need to change the `date` to a date format and treat `waterfront` and `zipcode` as categorical variables instead of numeric variables.
+We also changed the missing values from `yr_renovated` and `sqft_basement` to "na" values instead of 0.
 
@@
 After examining `yr_renovated` and `sqft_basement`, it appears that 95.8% and 60.7% of the values, respectively, are missing.
-From the scatterplots below, there does not seem to be any clear relationship between `yr_renovated` and `price` as well as `sqft_basement` and `price`.
-Therefore, we will drop these predictors when creating our models.
+From Figure 1, there are weak relationships between `yr_renovated` and `price` as well as `sqft_basement` and `price`.
+Therefore, we will drop these predictors when creating our models because they will not be as helpful as other predictors.
 
@@
 
-```{r, include = TRUE, fig.width=9, fig.height=4, warning=FALSE}
+```{r, include = TRUE, fig.width=9, fig.height=4, warning=FALSE, fig.cap="Scatter plots showing relationship between yr_renovated and price as well as sqft_basement and price."}
 grid.arrange(fig1, fig2, ncol = 2)
@@
 
-Additionally, from the Scatterplot of Bedrooms and Price, there appears to be an outlier so we will remove that observation.
+Additionally, from Figure 2, there appears to be an outlier (with 33 bedrooms) so we will remove that observation.
 
-```{r}
+```{r, fig.cap="scatter plot between bedrooms and price. An outlier is visible."}
 ggplot(data = kchouse, aes(x = bedrooms, y = price)) + 
@@
 
-Since there are a couple variables such as `date`, `id` that do not have a relationship with `price` as seen in the scatterplots below, we will remove those predictors as well.
+Since a couple of variables, such as `date` and `id` do not have a relationship with `price` as seen in Figure 3, we will remove those predictors as well.
 
@@
 
-```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="Scatter plots showing there is no relationship between date and price as well as id and price."}
 grid.arrange(fig3, fig4, ncol = 2)
@@
 
-Additionally, it appears that there are some concerns with multicollinearity between `sqft_living` and other variables such as `sqft_living15` and `sqft_above` so we are going to remove `sqft_living` as well.
+Additionally, there are concerns with multicollinearity between `sqft_living` and other variables, including `sqft_living15` and `sqft_above` (Figure 4), so we are going to remove `sqft_living` as well.
 
 ```{r}
-
 fig5 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
@@
 
-```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE}
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="scatter plots showing multicollinearity concerns with sqft_living"}
 grid.arrange(fig5, fig6, ncol = 2)
@@
 
-From the scatterplot below of the latitude and the longitude, it seems like the houses are all bunched together in near each other (near Seattle) so the results of this analysis can only be generalized to that region of the state.
+Referencing Figure 5, the houses are bunched near each other (close to Seattle), so the results of this analysis can only be generalized to that region of the state.
 
-```{r}
+```{r, fig.cap="Scatter plot of latitude and longitude. Clearly the houses are not dispersed."}
 ggplot(data = kchouse, aes(x = lat, y = long)) +
-  geom_point()
+  geom_point() + 
+  labs(title = "Scatterplot of Latitude and Longitude", 
+       x = "Latitude", y = "Longitude")
 ```
 
-From the histogram below, the distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
-There appears to be many outliers on the high end for `price`.
-The minimum of `price` is \$78,000 and the maximum is \$7,700,000.
-Since the distribution is right-skewed, if we were predicting price, a log-transformation could be useful.
+From Figure 6, the distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
+There appear to be many outliers on the high end for `price`.
+The minimum `price` is \$78,000, and the maximum is \$7,700,000.
+Since the distribution is right-skewed, a log transformation could be helpful if we were predicting price.
 
-```{r}
+```{r, fig.cap="Histogram of Price"}
 gf_dhistogram(~ price, data = kchouse) %>%
@@
 
-Next, since we want to know if the price of the house is greater or less than \$500,000, we will transform the price variable so that it is an binary predictor that is `1` if the price of the house is greater than \$500,000 and `0` if the price of the house is less than \$500,000.
+Next, since we want to know if the price of the house is greater or less than \$500,000, we will transform the price variable so that it is a binary predictor that is `1` if the price of the house is greater than \$500,000 and `0` if the price of the house is less than \$500,000.
+There are 12,546 houses with a price below \$500,000 and 9,050 houses with a price above \$500,000.
 
@@
 kchouse1 <- mutate(kchouse1, price = ifelse(price > 500000, 1, 0))
+tally(~price, data = kchouse1)
 ```
 
-The last thing that we will do before creating the models is create a training and test set.
-The training set is used to create a model and then the test set is used to see how the model performs in making predictions.
-We will randomly create a 75%/25% split for the training/test set.
+The last thing we will do before creating the models is creating a training and test set.
+We use the training set to create a model, and then the test set is used to see how the model performs in making predictions.
+We will randomly create a 75/25 split for the training/test set.
 
@@
 
-The first models that we are going to be fitting are GLMs (or Generalized Linear Models) which are extensions of ordinary linear regression (fitting a least-squares curve) to cases where the response variables are in an exponential family form.
-This can be response variables that are binomial, Poisson, gamma, or beta.
+The first models we will be fitting are GLMs (or Generalized Linear Models), extensions of ordinary linear regression (fitting a least-squares curve) to cases where the response variables are in an exponential family form.
+These cases can be response variables that are binomial, Poisson, gamma, or beta.
 Since we transformed `price` into a binary variable, it can now be modeled as a binomial distribution.
+The model for a binary response variable is a logistic regression model.
 
-First, we are going to fit a logistic model using all of the variables that we have not removed from the data set. We use the training set to create the model.
+First, we will fit the logistic model using all of the variables we have not removed from the data set. We use the training set to create the model.
 
@@
 
-It appears from the model that we have 9 significant predictors and we can perform a likelihood ratio test to determine if the overall model is significant.
+The model shows that we have 9 significant predictors, and we can perform a likelihood ratio test to determine if the overall model is significant.
 
@@
 
-Since we have a significant p-value, it appears that the overall model is significant. Now in order to make predictions using this model, we need to bin the fitted values which we will do below.
+Since we have a significant p-value, the overall model appears significant. Now, to make predictions using this model, we need to bin the fitted values, which we will do below.
 
@@
 After using 0.5 as a default cutoff, the model classifies 60.7% of the prices as below \$500,000.
-This is close to the actual percentage of the training data that is classified as below \$500,000 which is 58.1% of the observations.
-We can try to match this a little better by adjusting the cutoff to which we round the numbers.
-Finding, the appropriate quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.4% which is much closer than before.
+This is close to the actual percentage of the training data that is classified as below \$500,000, which is 58.1% of the observations.
+We can try to match this better by adjusting the cutoff to which we round the numbers.
+Finding the appropriate quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.4%, much closer than before.
 
@@
 
-Next, we can create a confusion matrix and determine how many of the predictions were correct.
+Next, we can create a confusion matrix and determine how many predictions were correct.
 From the matrix and calculation below, it appears that 84.0% of the predictions for the training set were correct.
@@
 
-Next, we generate a confusion matrix and it appears that 83.8% of the predictions were correct.
+Next, we generate a confusion matrix, and 83.8% of the predictions were correct.
 
@@
 Next, we will try creating a smaller model by removing some of the predictors that were not significant in our previous model.
-We are going to remove `bedrooms`, `long`, and `sqft_lot15`.
-After creating this model, we then repeated the process and removed other variables that were significant, but did not seem to have much of an impact on the predictions because the other variables were much more influential.
+We will remove `bedrooms`, `long`, and `sqft_lot15`.
+After creating this model, we then repeated the process.
+We removed other variables that were significant but did not seem to have much of an impact on the predictions because the other variables were much more influential.
 The other variables we removed were `sqft_lot`, `floors`, `waterfront`, `view`, `condition`, and  `sqft_above`.
@@
 
-All of the variables in our reduced model are significant and the model overall is significant as well. Now, we can create some predictions following the same process as above.
+All of the variables in our reduced model are significant, and the overall model is significant. Now, we can create some predictions following the same process as above.
 
@@
 After using 0.5 as a default cutoff, the model classifies 60.6% of the prices as below \$500,000.
-After adjusting the quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.1% which is much closer than before.
+After adjusting the quantile, we now see that the percentage of the binned fitted values for prices below \$500,000 is 58.1%, much closer than before.
 
@@
 
-Next, we generate a confusion matrix and it appears that 83.1% of the predictions were correct.
+Next, we generate a confusion matrix, and it appears that 83.1% of the predictions were correct.
 
@@
 
-Overall, from the two logistic regression models that were created, they both performed very similar to each other with the second one having a slightly lower correct prediction rate.
+Overall, We created two logistic regression models that performed very similarly, with the second one having a slightly lower correct prediction rate.
 However, for the second model, we removed many predictors that were not influential to the model and therefore were not helping make the predictions.
-After those variables were removed, the logistic model became much more simple with less predictors.
-The real estate developer's questions of interest is to find the variables that are indicative of houses that sell for over \$500,000 and by keeping a similar performance of the model, but removing extraneous predictors, we are able to find the predictors that are the most important.
+After those variables were removed, the logistic model became simpler with fewer predictors.
+The real estate developer's question of interest is to find the variables indicative of houses that sell for over \$500,000.
+We can find the most important predictors by keeping a similar performance of the model but removing extraneous predictors.
 The second model contained the predictors: `bathrooms`, `grade`, `yr_built`, `lat`, and `sqft_living15`.
@@
 # Tree and Results
-The second method that we are going to be using to fit models is through classification trees.
+The second method that we are going to be using to fit models is classification trees.
 Classification trees are a nonparametric method of prediction and are easy to interpret.
-Classification trees are used when the response variable is binary so it is appropriate to use them in order to predict if the price is over or under \$500,000.
+Classification trees are used when the response variable is binary, so it is appropriate to use them to predict if the price is over or under \$500,000.
 They are created through recursive partitioning to create "splits" between observations with similar qualities.
@@
 The classification tree above uses the predictors, `grade`, `lat`, `sqft_above`, `sqft_living15`, `sqft_lot15`, and `yr_built`.
-The error from this classification tree is 0.8589 which is calculated from the root node error and the relative error in the output above.
+The error from this classification tree is 0.8589, which is calculated from the root node error and the relative error in the output above.
 
@@
 
-Next, we will using the classification tree that we created to see how well it predicts the training set.
-From the confusion matrix below, it appears that the classification tree predicts correctly for 85.9% of the observations.
+Next, we will use the classification tree we created to see how well it predicts the training set.
+From the confusion matrix below, the classification tree correctly predicts 85.9% of the observations.
 
@@
 
-And doing the same thing for the test we, it appears that the model predicts correctly 85.5% of the observations.
+Furthermore, doing the same thing for the test set, it appears that the model predicts correctly 85.5% of the observations.
 
@@
 
-Before we create the second model, we examine the cross -validation process that was used in creating the previous model.
-The default cross-validation is a 10-fold cross-validation.
-Below we can see that as the complexity parameter reaches 0.16, the relative error calculated from the cross-validation decreases only a small amount as the complexity parameter increases.
-Therefore, we are going to use a complexity parameter of 0.016 for our next tree.
+Before we create the second model, we examine the cross-validation process that was used in creating the previous model.
+The default cross-validation is 10-fold cross-validation.
+Below we can see that as the complexity parameter reaches 0.16, the relative error calculated from the cross-validation decreases slightly as the complexity parameter increases.
+Therefore, our next tree will use a complexity parameter of 0.016.
 
@@
 
-We are also going to control `minsplit = 500` which means that there needs to be 500 observations in a node before a split is attempted.
+We are also going to control `minsplit = 500`, which means that there needs to be 500 observations in a node before a split is attempted.
 This is reasonable for a tree created from our training data with a size of 16197.
-We also set `minbucket = 300` which means that the minimum number of observations in any terminal node is 300 observations.
-There controls are to try and attempt to build a smaller tree while keeping the same effectiveness of the first model.
+We also set `minbucket = 300`, which means that the minimum number of observations in any terminal node is 300 observations.
+These controls are to try and attempt to build a smaller tree while keeping the same effectiveness of the first model.
 
@@
 
-The classification tree above uses the predictors, `grade`, `lat`, and `sqft_living15`.
-The error from this classification tree is 0.8303 which is calculated from the root node error and the relative error in the output above.
+The classification tree above uses the predictors `grade`, `lat`, and `sqft_living15`.
+The error from this classification tree is 0.8303, which is calculated from the root node error and the relative error in the output above.
 
@@
 
-From the output below, the classification tree we created is much more simple.
+From the output below, the classification tree we created is much simpler.
 
@@
 
-It appears the the model classifies observations 83.0% correctly in the training set. We will do the same for the test set.
+It appears the model classifies observations 83.0% correctly in the training set. We will do the same for the test set.
 
@@
 
-It appears the the model classifies observations 83.0% correctly in the test set as well.
+It appears that the model classifies observations 83.0% correctly in the test set as well.
 
-From these two models, the first one is more complex and predicts correctly about 2.5-3% better than the second model.
+The first one is more complex from these two models and correctly predicts about 2.5-3% better than the second model.
 However, this means that the first classification tree is less interpretable than the second one.
-The first tree has 11 splits whereas the second one only has 5.
+The first tree has 11 splits, whereas the second one only has 5.
 Because of this reason, we would choose the second model over the first one.
@@
 Additionally, the error of the second classification tree is slightly less than that of the first tree.
-Also, since we are determining which of the variables are the best predictors if a house is above \$500,000, the second model only uses 3 predictors whereas the first model uses 6.
+Also, since we are determining which variables are the best predictors if a house is above \$500,000, the second model only uses 3 predictors, whereas the first model uses 6.
 The predictors used in the second model are `grade`, `lat`, and `sqft_living15`.
@@
 # Conclusion
+This analysis aimed to determine the variables that are most indicative of a house's price being greater than \$500,000.
+To accomplish this, we first created two logistic regression models.
+We decided that the one with fewer predictors was better due to its comparable prediction accuracy and simplicity.
+This model contained the predictors `bathrooms`, `grade`, `yr_built`, `lat`, and `sqft_living15`, which means that for the logistic regression model, these variables contributed the most to determine if a house had a price greater than half a million dollars.
+Secondly, we created two classification trees which we used to predict if a price was greater than \$500,000 or not.
+Again, we chose the model with a similar prediction accuracy and fewer predictors.
+This tree was also much smaller and thus easier to interpret.
+The predictors used in this model are `grade`, `lat`, and `sqft_living15`.
+The classification tree models performed slightly better than the logistic regression trees, but they were all within a small range so they are comparable.
+Combining information from both of our final models, `grade`, `lat`, and `sqft_living15` appeared as significant predictors in both models, so these variables, especially, are the ones that are most predictive of a house with a price over \$500,000.

### 2022-10-20 homework/hmk5/hmk5Stat495F22.Rmd
Finished Hmk5 and created pdf

@@
 title: "Homework 5 - Stat 495"
-author: "YourNameGoesHere"
+author: "Justin Papagelis"
 date: "Due Wednesday, October 19th by midnight"
@@
 
-# Homework 5 - Prompt - Write-up for Homework 4
-
-## Motivation to predict when Price is greater than $500,000
-
-A real estate developer is interested in understanding the features that are predictive of homes selling for more than half a million dollars, and has turned to you, a statistical consultant for help.
-He wants a model that can be applied to make predictions in this setting and wants to understand how the variables in the model are impacting it.
-
-To practice new techniques from class, in your analysis, you are required to use both an appropriate generalized linear model and tree to address the developer's questions of interest, including a model comparison.
-
-## Write-up Purpose and some Guidance
-
-We want to practice reporting our analyses.
-You have been contracted to do an analysis, and you prepared some potential models in Homework 4, and now need to report your process and subsequent findings to the client.
-
-Things to think about:
-
-* Your report should be well-organized and proofread.
-* Your code should be readable and not run off pages. Employ good commenting practices.
-* The entire process must be reproducible.
-* Review the class feedback on Homework 4 and adjust your models/thinking as necessary before diving in to the write-up. 
-* Think carefully about the organization of the report. Is it useful to have pages of output and THEN a description of what to look for in that output?
-* Should you assume the reader knows where values in the R output are?
-* If you compute a number, and then write a sentence that says, the MSE is small, will the reader associate that number with being the MSE? What would a better sentence look like? 
-* Thinking back to the Tibshirani Writing activity may help you think about ways to improve as well. (Does each of your sections have a purpose? Do you have appropriate signposts, etc.)
-
-## Instructions for your submission
-
-Your submission should include the following sections (along with all code necessary to reproduce your results):
-
-* Introduction and Exploratory Data Analysis - could be two separate sections
-* Your GLM and relevant details
-* Your Tree and relevant details (can be before or after your GLM)
-* Your Model Comparison (can be woven in sections above)
-* Your Conclusion
-
-Descriptions of the purpose for each section follow.
-Do not use this as a set of check boxes for the assignment.
-Instead, the idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.
-
-* Introduction - The real estate developer has interests, but will you be able to address them?
-How do you understand the tasks you are presented with?
-It's important to state what you will be doing in the analysis, so the reader can make sure their understanding lines up with what you will be doing.
-The reader also needs an introduction to your data, either in this section, or below.
-They need enough detail to be able to determine if your actions later in the analysis are reasonable.
-
-* Exploratory Data Analysis - You are the analyst here.
-That means you can use variable transformations, subsets of observations, and employ other analytic practices (e.g.
-training/testing data sets) at your discretion to aid in your analysis, so long as you explain your rationale for them.
-The reader needs to know what you found and what you decided to do about it, because this has impacts on the rest of your analysis.
-Remember our lessons from the first classes - be sure you look at the data!
-Here's your chance to share what you found based on how it impacts your analysis.
-
-* GLM and Tree sections - These are new techniques.
-By having each in their own section, you can focus on your explanation for them one at a time.
-The developer does not know what these are - you need to explain them at least enough they can follow your discussion.
-You have options that you need to pick for the different techniques (various tuning parameters) - for example, are you using a classification or a regression tree?
-What tree stopping options are being used?
-What input variables are you using and why?
-What type of GLM are you using?
-How will you be measuring performance?
-Be sure you discuss what options you are selecting and what made you choose those values.
-Helping explain this shows your understanding of the techniques (remember the class example that minbucket of 30 was nonsensical for the iris data).
-
-You also want these sections to show off your ability to build models.
-It is not appropriate to only fit kitchen sink models or accept all default settings without exploring to see if that is really what is best for the task at hand.
-Your write-up should make it clear what you explored, but you don't have to show every model you considered.
-You can do a lot in sentences discussing your process.
-
-Finally, remember to check out your "best" model for each technique.
-Did you check reasonable diagnostics?
-Does the model make sense?
-Are variables behaving as you expect?
-If you focus solely on model performance, that's missing the point.
-For example, you might find a model has very little error because a variant of the response was accidentally included as a predictor.
-You are responsible for checking over the model before reporting it.
-Your write-up should convey that you've done this (the reader can't read your mind to know you did it).
-
-* Model Comparison - There are several ways to compare the models - performance, interpretability, variables involved, etc.
-Remember you are trying to address the real estate developer's questions of interest.
-You may do that with a focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree.
-The idea for this section is that you need to convey the process used to pick a final model(s) to use to answer those questions, with justification for your choices.
-
-* Conclusion - This section should be a stand alone summary of your analysis.
-It is where you get to state your final model and a quick summary of the process used to get there.
-You also need to address the developer's questions (if not done before), and this is your last place to do that!
-Remember to flush out the details here.
-If your final sentence is "Model 5 is the model I choose and it answers your questions", does it?
-Are you doing your job as the analyst to leave things at that?
-For that matter, what is Model 5?
-
-* Printing Trees - It is fine to print your trees out to separate .pdfs (just be sure to include them in your submission!).
-Remember if you want to include the .pdf as an image, you have example code for that.
-Please do show your code though (so no echo = FALSE), and remember that your work should be reproducible.
-The chapter 8 lab solution shows alternatives to *partykit* to make the trees look nice.
-You can try out *rpart.plot* yourself to see.
-
-* Length - Your submission should be as long as it needs to be, but not unnecessarily long.
-Plots, etc.
-are encouraged to help illustrate points, but don't include output that isn't needed.
-For example, a histogram or densityplot and favstats for each variable is something good to explore, but you shouldn't put that in your submission for every variable.
-You might need plots to point out outliers you are removing, or maybe you show one plot and then say others were similar.
-I encourage you to do any additional work in a separate .Rmd from your submission (like, back in your Homework 4 .Rmd).
-
-* Audience - For purposes of this submission, remember that the audience is the real estate developer, so you'll probably need to include some explanations that you'd leave out of a normal homework.
-For example, the developer isn't going to know what a GLM is, or what type you are using, or why you'd use it.
-You should think about where that information should go, and do your best to explain what you need in order to report your findings.
-Similarly, assume that you found this data to assist the developer and they need basic details about it to understand the variables.
-They didn't hand it over to you.
-
-You may remove these instructions if desired for your submission, but must leave the page on Academic Integrity.
-
-\newpage
-
 # Introduction and Exploratory Data Analysis 
@@
 ```{r}
+# change how variables are treated by R
 kchouse <- kchouse %>%
@@
          zipcode = as.numeric(as.factor(zipcode)))
+# change the values that are 0 to na which is more appropriate
 kchouse <- kchouse %>%
@@
 ```{r}
+# calculate the percentage of missing observations in yr_renovated
 sum(is.na(kchouse$yr_renovated))/nrow(kchouse)
+
+# calculate the percentage of missing observations in sqft_basement
 sum(is.na(kchouse$sqft_basement))/nrow(kchouse)
@@
 ```{r, warning = FALSE}
+# generate plot of yr_renovated and price
 fig1 <- ggplot(data = kchouse, aes(x = yr_renovated, y = price)) + 
@@
        y = "Price")
+
+# generate plot of ysqft_basement and price
 fig2 <- ggplot(data = kchouse, aes(x = sqft_basement, y = price)) + 
@@
        x = "Square Feet Basement", y = "Price")
-
 ```
@@
 
-Additionally, from Figure 2, there appears to be an outlier (with 33 bedrooms) so we will remove that observation.
+Additionally, from Figure 2, there appears to be an outlier (with 33 bedrooms) so we will remove that observation and show the relationship once the outlier is removed.
 
 ```{r, fig.cap="scatter plot between bedrooms and price. An outlier is visible."}
-ggplot(data = kchouse, aes(x = bedrooms, y = price)) + 
+# generate plot of bedrooms and price
+fig3 <- ggplot(data = kchouse, aes(x = bedrooms, y = price)) + 
   geom_point() + 
@@
        x = "Bedrooms", y = "Price")
+
+# remove observation
+kchouse1 <- kchouse %>%
+  filter(id != 2402100895)
+
+# generate plot of bedrooms and price w/o outlier
+fig4 <- ggplot(data = kchouse1, aes(x = bedrooms, y = price)) + 
+  geom_point() + 
+  labs(title = "Scatterplot of Bedrooms and Price (no outlier)", 
+       x = "Bedrooms", y = "Price")
+```
+
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="Scatter plots showing Bedrooms and Price before and after the removal of an outlier"}
+grid.arrange(fig3, fig4, ncol = 2)
 ```
@@
 ```{r}
-fig3 <- ggplot(data = kchouse, aes(x = date, y = price)) + 
+fig5 <- ggplot(data = kchouse, aes(x = date, y = price)) + 
   geom_point() + 
@@
 
-fig4 <- ggplot(data = kchouse, aes(x = id, y = price)) + 
+fig6 <- ggplot(data = kchouse, aes(x = id, y = price)) + 
   geom_point() + 
@@
 
-```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="Scatter plots showing there is no relationship between date and price as well as id and price."}
-grid.arrange(fig3, fig4, ncol = 2)
+```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="Scatter plots showing there is no relationship between date and price as well as ID and price."}
+grid.arrange(fig5, fig6, ncol = 2)
 ```
@@
 ```{r}
-fig5 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
+fig7 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_above)) + 
   geom_point() + 
   labs(title = "Scatterplot of SqFt Living and SqFt Above", 
-       x = "Sq Ft Living", y = "SqFt Living in 2015")
+       x = "Sq Ft Living", y = "SqFt Above")
 
-fig6 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
+fig8 <- ggplot(data = kchouse, aes(x = sqft_living, y = sqft_living15)) + 
   geom_point() + 
@@
 ```{r, include = TRUE, fig.width=9, fig.height=4, message=FALSE, fig.cap="scatter plots showing multicollinearity concerns with sqft_living"}
-grid.arrange(fig5, fig6, ncol = 2)
+grid.arrange(fig7, fig8, ncol = 2)
 ```
@@
 ```{r}
-kchouse1 <- kchouse %>%
-  filter(id != 2402100895) %>%
+kchouse1 <- kchouse1 %>%
   select(-c(id,zipcode, yr_renovated, date, sqft_basement, sqft_living))
@@
 
+```{r, fig.cap="Histogram of Price"}
+gf_dhistogram(~ price, data = kchouse) %>%
+  gf_labs(title = "Histogram of Price", x = "Price")
+
+favstats(~ price, data = kchouse)
+```
+
 From Figure 6, the distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000.
@@
 Since the distribution is right-skewed, a log transformation could be helpful if we were predicting price.
-
-```{r, fig.cap="Histogram of Price"}
-gf_dhistogram(~ price, data = kchouse) %>%
-  gf_labs(title = "Histogram of Prices")
-
-favstats(~ price, data = kchouse)
-```
 
@@
 
-```{r, fig.width = 6, fig.height = 5}
+```{r, fig.width = 6, fig.height = 5, fig.cap= "Classification Tree 1"}
 price.rpart1 <- rpart(price ~ ., data = train, method = "class")
@@
 
-```{r}
+```{r, fig.cap="Graph of Relative Error from Cross-Validation as Complexity Parameter (cp) increses"}
 plotcp(price.rpart1)
@@
 
-```{r}
+```{r, fig.cap= "Classification Tree 2"}
 rpart.plot(price.rpart2)
@@
 ```{r}
-
 train2 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
@@
 ```{r}
-
 test2 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))

### 2022-10-22 homework/hmk6/hmk6Stat495F22.Rmd
Finish hw6

---
title: "Homework 6 - Stat 495"
author: "Justin Papagelis"
date: "Due Friday, October 21st by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
```

# Homework 6 - Idea Brainstorm for Project

This homework counts towards the project as a project component (not a homework).

The idea here is to list several potential statistical topics for your project, as well as your motivation for choosing them. This can include where you've heard about the topic, why you want to learn about each topic, etc. Remember that the topics you are brainstorming should be relatively new to you. You should brainstorm at least 3 topics - feel free to add more following the outline below.

Some of you may have datasets that you'd like to perform analysis on. That's fine, and you can choose topics that align with the data set analysis. Feel free to list such connections below. However, the statistical topic must be the focus here. This allows the project to align with our learning goals for the statistics major.

The feedback provided to you from this brainstorm will help you to prepare a proposal for the project.

## Topic Idea 1

<!-- Note: These are comments for instructions and will not show up in your pdf.  -->
<!-- List your potential topic idea, motivation, and where you have encountered the topic before.  -->
My first idea is to do something with Time Series, but I'm not sure if the topic is too broad. Over this summer, I was doing computer science research and we talked about doing statistical/data analysis that involved time series once we had results, but we didn't get to the point where we had results so I didn't have to learn about them. I feel like Time Series are applicable to many ideas.

## Topic Idea 2

<!-- List your potential topic idea, motivation, and where you have encountered the topic before.  -->
I'm interested in doing something with survival analysis, but again, this might be broad of subject. I don't have much experience with other statistic electives, so I was just doing some googling about statistical methods and I read a little about survival analysis and it seems pretty interesting. But it does seem like there are many different types of applications (like in biology, economics, etc) so perhaps I could focus on one of those applications.

## Topic Idea 3

<!-- List your potential topic idea, motivation, and where you have encountered the topic before.  -->
I really enjoyed doing the bootstrap and other simulations, so I was thinking I could do something connected to that. There seems to be a lot of different types of cross-validation methods and cases where different ones are used. We have done a little with cross-validation in class, but I feel like I only briefly understand it so it could possibly be something that I could do more research about.

### 2022-11-01 homework/hmk7/hmk7Stat495F22.Rmd
Add hw7

---
title: "Homework 7 - Stat 495"
author: "Justin Papagelis"
date: "Due Friday, Nov. 4th by midnight (11:59 pm)"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
library(QSARdata) #will need to install for data
library(randomForest)
library(nnet)
library(gbm)
library(e1071)
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle/Git repo, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

*

\newpage

# PROBLEMS TO TURN IN:  Add 1, Add 2, Add 3, Add 4

The first three problems use the bbb2 data set from the QSARdata package. The final problem covers some concepts from the methods in Chapters 17, 18, and 19, without a data set / application.

For the applied problems, the response variable of interest is bbb2_Class, which can be found in the bbb2_Outcome data set. We have joined the outcome variable to the QuickProp data set that we want to focus on below. You can read the associated help file in R to learn more about the data set.

```{r}
data(bbb2)
#?bbb2 # for variable reference and information
mybbb2 <- left_join(bbb2_QuickProp, bbb2_Outcome) %>% select(- Molecule)
tally(~ bbb2_Class, data = mybbb2)
```

Our goal for the applied problems below is to use the recent methods from class (Chapter 17, 18, and 19) to predict the response variable, whether each compound "crosses" the blood-brain barrier or "does not" cross. You should use the *mybbb2* data set going forward. Note that there are 51 variables at the moment, and the last variable "Class" is the target, but if you open the data set to view, it will only show 50 variables by default. Class is there, but you have to use the arrows to see it.

```{r}
# We loaded a lot of data sets we don't need anymore
# remove them to clean up your workspace
remove(bbb2_AtomPair, bbb2_Daylight_FP, bbb2_Dragon, bbb2_Lcalc, bbb2_moe2D,
       bbb2_moe2D_FP, bbb2_moe3D, bbb2_Outcome, bbb2_PipelinePilot_FP,
       bbb2_QuickProp)
```

To avoid issues with reproducibility, you should set a seed in EACH chunk below where you do a random process, whether that is setting up the train/test split or fitting a model that has some random process involved.

\newpage

## Add 1

Your task for this problem is to fit the models described in parts c, d and e, and then compare them in part f. Use all available predictor variables (except what is removed in part a), with no re-expressions. The same training/test split will be used in Add 2 and Add 3 as well (i.e. you only make this once).

> part a. One variable in the data set, QikProp_.amidine causes issues with some of these methods. We will remove it here, but can you see why it is problematic? Why is this variable not very useful for this analysis?

SOLUTION: This variable is not very useful for this analysis because from the histogram below, there are significantly more observations with a value of 0 than a value of 1. Additionally, there are no observations with a value of 1 for `QikProp_.amidine` that "do not cross" the blood-brain barrier and only 1 observation of `QikProp_.amidine` value 1 that "crosses" the blood-brain barrier.

```{r}
tally(bbb2_Class ~ QikProp_.amidine, data = mybbb2)
```

```{r}
# run once you are ready to remove the variable to proceed
# this variable is not used anywhere below, so overwrite the data set
mybbb2 <- select(mybbb2, -QikProp_.amidine)
```

> part b. Create an appropriate training/test split from mybbb2 with a ratio of 70/30 to use throughout the problem. As always, be sure your split is reproducible.

SOLUTION:

```{r}
set.seed(495)

n <- nrow(mybbb2)
train_index <- sample(1:n, 0.7 * n)
test_index <- setdiff(1:n, train_index)

train <- mybbb2[train_index, ] 
test <- mybbb2[test_index, ]
```

> part c. Create an appropriate model to predict Class with the training set using bagging with 1000 trees and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}
set.seed(495)

# for bagging, mtry = 49 so all the variables are used
class.bag <- randomForest(Class ~ ., data = train, ntree = 1000, mtry = 49)

class.bag

table(train$Class, predict(class.bag, train))

```

> part d. Create an appropriate model to predict Class with the training set using a random forest with 1000 trees and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}
set.seed(495)

# no mtry value so it is defualt random forest
class.rf <- randomForest(Class ~ ., data = train, ntree = 1000)

class.rf
table(train$Class, predict(class.rf, train))

```

> part e.  Create an appropriate model to predict Class with the training set using boosting with 500 trees and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}
set.seed(495)

# set 1 to be "crosses" and 0 to be "does not cross"
train2 <- mutate(train, Class = ifelse(Class == "Crosses", 1, 0))

class.boost <- gbm(Class ~ ., data = train2, distribution = "bernoulli", 
                   n.trees = 500)

class.boost

boost_estimate <- predict(class.boost, newdata = train2, n.trees = 500, 
                          type = "response")

pred_class <- boost_estimate > 0.5
tally(~ pred_class)

table(train2$Class, pred_class)

```

> part f. Parts c, d, and e only required you to fit models. Now we want to compare their performance. Use an appropriate measure to compare the three models in terms of their model performance based on the test set.  Be sure your choice of measure is clear. Summarize your findings. Then discuss which model you would choose for predicting Class. Explain your choice.

SOLUTION: In order to compare the performance, we will see how accurate the model can predict the test set.

```{r}
# for the bagging model
table(test$Class, predict(class.bag, newdata = test))
(10+8)/(10+8+2+4)

# for random forest model
table(test$Class, predict(class.rf, newdata = test))
(8+8)/(8+8+2+6)

```

\newpage

## Add 2

Your task for this problem is to fit the models described in parts a, b, and c, and then compare them in part d. Use all available predictor variables, with no re-expressions. Use the same training/test data as above.

> part a. Create an appropriate model to predict Class with the training set using a neural net with a single hidden layer of 15 nodes, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part b. Create an appropriate model to predict Class with the training set using a neural net with a single hidden layer of 15 nodes, and a decay parameter of 5e-4, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part c. Create an appropriate model to predict Class with the training set using a neural net with a single hidden layer of 15 nodes, a decay parameter of 5e-4, and a value for maxit that allows for convergence, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part d. Parts a, b, and c only required you to fit models. Now we want to compare their performance. Use an appropriate measure to compare the three models in terms of their model performance based on the test set.  Be sure your choice of measure is clear. Summarize your findings. Then discuss which model you would choose for predicting Class. Explain your choice.

SOLUTION:

```{r}

```

\newpage

## Add 3

Your task for this problem is to fit the models described in parts a, b, and c, and then compare them in part d. Use all available predictor variables, with no re-expressions. Use the same training/test data as above. Finally, part e will have you compare the best models from Add 1, Add 2, and Add 3.

> part a. Create an appropriate model to predict Class with the training set using an SVM with a radial kernel and a gamma of 0.75, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part b. Create an appropriate model to predict Class with the training set using an SVM with a polynomial kernel and a gamma of 0.5, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part c. Create an appropriate model to predict Class with the training set using an SVM with a polynomial kernel and a gamma of 0.0001, and otherwise with default settings for tuning parameter values.

SOLUTION:

```{r}

```

> part d. Parts a, b, and c only required you to fit models. Now we want to compare their performance. Use an appropriate measure to compare the three models in terms of model performance based on the test set.  Be sure your choice of measure is clear. Summarize your findings. Then discuss which model you would choose for predicting Class. Explain your choice.

SOLUTION:

```{r}

```

> part e. Look over your responses to Add 1, Add 2, and Add 3 in terms of your final model from each method/problem. Compare these three models, and explain which you would choose as an overarching final model to predict Class. Explain your choice. Your final choice may be determined by performance in conjunction with any factors you think are relevant.

SOLUTION:

```{r}

```

\newpage

## Add 4

> part a. Neural nets and SVMs are both discussed as nonlinear models for prediction. Discuss where the "nonlinearity" is in both of these models.

SOLUTION:

> part b. Compare and contrast random forests and boosting in a few sentences. How are they similar? How are they different?

SOLUTION:

> part c. The concepts of backpropagation and the kernel trick are related, even though they are for neural nets and SVMs, respectively. What do these concepts have in common?

Hint: It has to do with what they help with in their respective methods.

SOLUTION:

> part d. Write your own short answer question relating to a concept from Chapter 17, 18, or 19, and then answer it.

Questions should require at least two sentences to answer reasonably well. True/false questions are not short answer questions.

The motivation here is for you to pick something you are still unclear on and ask a question about it. This will make you review the concept in order to answer your question well.

SOLUTION:

Q:

A:

### 2022-11-01 labs/Chapter 18 and 19 Lab.Rmd
Add hw7

---
title: "Chapter 18 and 19 Lab - Neural Nets and SVMs"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic) 
library(tidyverse)
library(ISLR) # for data
library(nnet) # may need to install
library(NeuralNetTools) # may need to install
library(e1071) # may need to install
#install.packages("neuralnet")
library(neuralnet)
```

This lab will practice the code and discuss concepts from Chapters 18 and 19 on Neural Nets and Support Vector Machines.

# A Cautionary Tale

As mentioned in class, there are over 80 packages in R for neural nets. Not all are equal in how well they work, though. If you really want to fit neural nets, you should investigate the *keras* package.

The example here will show you why we can't just use functions blindly. It uses the Boston housing data set we've seen before, and tries to predict medv, the same response variable we had in our Chapter 17 lab. So this is a regression problem.

The code below loads the data, fits the model with only 2 hidden nodes in a single hidden layer on the whole data set, gets the MSE, and plots the predicted values versus the actual values in the data set. (The picture of the net itself is turned off.)

Run the code once and look at your plot of the predicted versus actual values.

```{r}
BostonHousing <- MASS::Boston
nnet.fit <- nnet(medv/50 ~ ., data=BostonHousing, size = 2) 
 # multiply by 50 to restore original scale
nnet.predict <- predict(nnet.fit)*50

# plotnet(nnet.fit)

# mean squared error: claimed to be 16.40581 from blog
mean((nnet.predict - BostonHousing$medv)^2)

plot(BostonHousing$medv, nnet.predict,
    main="Neural network predictions vs actual",
    xlab="Actual")
```

For some of you, this likely will run "fine", meaning you will see a scatterplot that shows the actual versus predicted values have a fairly strong positive linear relationship. Others of you will get something very different. If you got the fairly strong positive linear relationship, try running the code again.  Everyone should run the code chunk several times. What is happening to your predictions / the plot?

Why is this happening?

There is no seed set, and clearly, the results are not reproducible without a seed set. Sometimes we get completely (or almost completely) nonsense predictions that are constant. Even if we set a seed, the different performance we are obtaining indicates there is something off with the function and/or our understanding of the parameters we need to be setting in order for this neural net to run appropriately. Setting a seed allows us to get reproducible results, but we don't want reproducible results that don't make sense! The blog I was following for this doesn't set a seed and doesn't recognize there are these issues with the solution. I tried scaling, changing other tuning parameters, etc. and wasn't able to get a consistent behavior for the solution (for regression).

If you want to really get into neural nets (especially for regression), go use *keras* (or python). *keras* still doesn't have the best documentation, but there is more out there, and it is more stable (it still can take a while to install though!).

For our neural nets below, to keep using the *nnet* package, we'll stick with classification where the behavior seems to be stable. (From what I can tell, anyway.)

# Neural Nets for classification

In the Chapter 17 lab, for classification, we looked at the Carseats data, so let's return to that. In these data, `Sales` is a continuous variable, we want to consider a binary classification problem, so we begin by converting it to a binary variable. We use the `ifelse()` function to create a variable, called `High`, which takes on a value of `Yes` if the `Sales` variable exceeds 8, and takes on a value of `No` otherwise:

```{r}
Carseats <- Carseats %>%
  mutate(High = as.factor(ifelse(Sales <= 8, "No", "Yes")))
```

We again split the observations into a training set and a test set:

```{r}
set.seed(495)

n <- nrow(Carseats)
train_index <- sample(1:n, 0.5 * n)
test_index <- setdiff(1:n, train_index)

train <- Carseats[train_index, ] 
test <- Carseats[test_index, ]
```

We now use the `nnet` function to fit a neural net in order to predict
`High` using all variables but `Sales` (that would be a little silly...).  Besides the model formula, we have to specify the number of nodes in the hidden layer. *nnet* only allows a single hidden layer.

```{r}
set.seed(495)
nnet_carseats <- nnet(High ~ . - Sales, train, size = 4)
```

This neural net had 4 hidden nodes in the single hidden layer, and with this seed, it converged in less than 100 iterations (for me).
Did yours converge?

Let's try increasing the number of nodes in the hidden layer. Does this neural net converge?

No, this neural net does not converge.

```{r}
set.seed(495)
nnet_carseats2 <- nnet(High ~ . - Sales, train, size = 8, maxit = 830)
```

Try adding the *maxit* parameter to the net with 8 hidden nodes and see if you can find a value for which it converges.

It appears that the net converges after 155 iterations.

Let's see how we did with the simpler net with 4 hidden nodes (easier to view, etc.)

Here's how to plot the neural net:

```{r}
plotnet(nnet_carseats)
```

To look at variable importance, because there are only 2 levels to the response here, we can just run:

```{r}
olden(nnet_carseats)
```

Look at the help page for the *olden* function. Why is this method considered superior to Garson's algorithm?

This method is considered superior to Garson's algorithm because it maintains the relative contributions of each connection weight (in sign and magnitude) whereas Garson's only preserves the absolute magnitude.

Finally, let's evaluate the performance of the neural nets. We can check how they do on both the training and the test data sets. Here is code to get predictions for the training and test data using the network with 4 hidden nodes.

```{r}
trainpred <- predict(nnet_carseats, type = "class")
pred <- predict(nnet_carseats, newdata = test, type = "class")
```

Now let's get the confusion matrices for both train and test.

```{r}
tally(High ~ trainpred, data = train)
tally(High ~ pred, data = test)

(113+31)/(113+31+51+5)
(106+19)/(106+19+63+12)
```

Get predictions for the model with 8 hidden nodes and enough iterations to converge on both the training and test sets. How well does this model do compared to the model with 4 hidden nodes?

```{r}
trainpred2 <- predict(nnet_carseats2, type = "class")
pred2 <- predict(nnet_carseats2, newdata = test, type = "class")
```

```{r}
tally(High ~ trainpred2, data = train)
tally(High ~ pred2, data = test)

(118+7)/(118+7+75+0)
(115+5)/(115+5+77+3)
```

This model performs worse on both the training set and the test set than the first model with 4 hidden nodes.

Try one more model with parameters of your choice for at least one new option. How does it do?

```{r}
set.seed(495)
nnet_carseats3 <- nnet(High ~ . - Sales, train, size = 3)
```

```{r}
trainpred3 <- predict(nnet_carseats3, type = "class")
pred3 <- predict(nnet_carseats3, newdata = test, type = "class")
```

```{r}
tally(High ~ trainpred3, data = train)
tally(High ~ pred3, data = test)

(118+31)/(118+31+51+0)
(113+25)/(113+25+57+5)
```

Which neural net model do you prefer overall?

The last model with 3 hidden nodes appears to have the best prediction rates for the training set and for the test set so we would use that one.

# SVMs for Classification

The *e1071* package and the *svm* function allows for SVMs to be fit in R.

What else does it say it can do via the help menu?

The *svm* function can also be used to perform general regression and classification as well as density estimation.

Fitting a model is easy with the usual formula interface.

```{r}
svm1 <- svm(High ~ . - Sales, data = train, gamma = 0.75, kernel = "radial")
summary(svm1)
```

The help menu lists the other possible kernels, and there are options that need to be specified for each.

Fit a model called *svm2* using a polynomial kernel of degree 4 with a gamma of your choice. (To have something to compare to the provided svm1.)

```{r}
svm2 <- svm(High ~ . - Sales, data = train, gamma = 0.75, kernel = "polynomial", degree = 4)
summary(svm2)
```

Getting predictions is pretty easy using predict, as expected. We can then get confusion matrices to see how well the method is doing.

```{r}
svm1predtrain <- predict(svm1, train)
svm1predtest <- predict(svm1, test)
tally(High ~ svm1predtrain, data = train)
tally(High ~ svm1predtest, data = test)

(111+18)/(111+18+64+7)
```

What do you notice about the performance of svm1?

svm1 has all correct predictions for the training set and is 64.5% correct for the test set.

How does your svm2 compare?

```{r}
svm2predtrain <- predict(svm2, train)
svm2predtest <- predict(svm2, test)
tally(High ~ svm2predtrain, data = train)
tally(High ~ svm2predtest, data = test)

(94+58)/(94+58+24+24)
```

svm2 also has all correct predictions for the training set, but does a little better at on the test set at around 76% correct.

Fit another svm to try to improve on the performance on the test set. Can you find a better model than either svm1 or svm2?

```{r}
svm3 <- svm(High ~ . - Sales, data = train, gamma = 0.75, kernel = "polynomial", degree = 2)
summary(svm3)
```

```{r}
svm3predtrain <- predict(svm3, train)
svm3predtest <- predict(svm3, test)
tally(High ~ svm3predtrain, data = train)
tally(High ~ svm3predtest, data = test)

(105+65)/(105+65+17+13)
```

svm3 does a little worse on the training set, but is better than the other two models on the test set at about 85% correct.

# Practice - Regression

We use a data set that we previously examined when learning about ridge regression that we are returning to for practice.

```{r}
data(Hitters)
# ?Hitters # MLB data from 1986 and 1987; 322 obs on 20 variables
```

We want to predict Salary, which is missing for 59 players.

```{r}
Hitters <- na.omit(Hitters) #263 obs now
```

Unfortunately, since the *nnet* package doesn't seem to be reliable for regression, we don't want to fit those models here, and instead will just fit some SVMs after checking out options for neural nets.

Do a brief google search. What other packages do you find out there for neural nets in R? Can you find blog entries about regression with neural nets? Do they use any of these packages?

> SOLUTION

There is the *neuralnet* package. Some of the blog entries use this package. Others use other languages and packages.

Use SVMs to explore models for predicting salary. Be sure to explore the SVM model options and the various parameter settings.

> SOLUTION

```{r}
nn <- 
```

### 2022-11-01 homework/hmk7/hmk7Stat495F22.Rmd
Just have Add 4 left

@@
 
-SOLUTION: This variable is not very useful for this analysis because from the histogram below, there are significantly more observations with a value of 0 than a value of 1.
+SOLUTION: This variable is not very useful for this analysis because there are significantly more observations with a value of 0 than a value of 1.
 Additionally, there are no observations with a value of 1 for `QikProp_.amidine` that "do not cross" the blood-brain barrier and only 1 observation of `QikProp_.amidine` value 1 that "crosses" the blood-brain barrier.
@@
 train2 <- mutate(train, Class = ifelse(Class == "Crosses", 1, 0))
+test2 <- mutate(test, Class = ifelse(Class == "Crosses", 1, 0))
 
@@
 
-boost_estimate <- predict(class.boost, newdata = train2, n.trees = 500, 
+boost_estimate_train <- predict(class.boost, newdata = train2, n.trees = 500, 
                           type = "response")
 
-pred_class <- boost_estimate > 0.5
-tally(~ pred_class)
+pred_class_train <- ifelse(boost_estimate_train > 0.5, 1, 0)
+tally(~ pred_class_train)
 
-table(train2$Class, pred_class)
+table(train2$Class, pred_class_train)
 
@@
 
+# for boosting model
+test2 <- mutate(test, Class = ifelse(Class == "Crosses", 1, 0))
+boost_estimate_test <- predict(class.boost, newdata = test2, n.trees = 500, 
+                          type = "response")
+pred_class_test <- ifelse(boost_estimate_test > 0.5, 1, 0)
+table(test2$Class, pred_class_test)
+(8+7)/(8+7+7+2)
+
 ```
+ The Bagging model appears to have an accuracy of 75% on the test set.
+The Random Forest model appears to have an accuracy of 66.7% on the test set and the Boosting model appears to have an accuracy of 62.5% on the test set.
+Therefore, we would choose the Bagging model for predicting Class because the model had the higest accuracy.
 
@@
 ```{r}
+set.seed(1)
+nnet_class <- nnet(Class ~ ., train, size = 15)
 
+trainpred <- predict(nnet_class, type = "class")
+tally(Class ~ trainpred, data = train)
 ```
@@
 ```{r}
+set.seed(1)
+nnet_class2 <- nnet(Class ~ ., train, size = 15, decay = 5e-4)
+
+trainpred2 <- predict(nnet_class2, type = "class")
+tally(Class ~ trainpred2, data = train)
 
@@
 ```{r}
+set.seed(1)
+nnet_class3 <- nnet(Class ~ ., train, size = 15, decay = 5e-4, maxit = 1030)
+
+trainpred3 <- predict(nnet_class3, type = "class")
+tally(Class ~ trainpred3, data = train)
 
@@
 
-SOLUTION:
+SOLUTION: We will do the same as we did before and compare models based on their accuracy in predicting the test set.
 
 ```{r}
+# neural net 1
+pred <- predict(nnet_class, newdata = test, type = "class")
+tally(Class ~ pred, data = test)
+(8+8)/(8+8+6+2)
 
+# neural net 2
+pred2 <- predict(nnet_class2, newdata = test, type = "class")
+tally(Class ~ pred2, data = test)
+(9+8)/(9+8+1+6)
+
+# neural net 3
+pred3 <- predict(nnet_class3, newdata = test, type = "class")
+tally(Class ~ pred3, data = test)
+(8+8)/(8+8+6+2)
 ```
+
+From the confusion matrices above, it appears the the accuracy in predicting the test set from our first and third neural network model is 66.7% and the accuracy in predicting the test set from the second model is 70.8%.
+This means that we would choose the second neural network for predicting the test set.
+However, it is important to note that the difference between the accuracy in all of these models is only one more correct observation which could could change depending on the seed.
 
@@
 ```{r}
-
+set.seed(1)
+svm1 <- svm(Class ~ ., data = train, gamma = 0.75, kernel = "radial")
+summary(svm1)
 ```
@@
 ```{r}
-
+set.seed(1)
+svm2 <- svm(Class ~ ., data = train, gamma = 0.5, kernel = "poly")
+summary(svm2)
 ```
@@
 ```{r}
-
+set.seed(1)
+svm3 <- svm(Class ~ ., data = train, gamma = 0.0001, kernel = "poly")
+summary(svm2)
 ```
@@
 
-SOLUTION:
+SOLUTION: Again, we will use the confusion matrices to determine how accurate each model is at predicting the test set.
 
 ```{r}
+# for svm1
+svm1predtest <- predict(svm1, test)
+tally(Class ~ svm1predtest, data = test)
+(14+0)/(14+10)
 
+# for svm2
+svm2predtest <- predict(svm2, test)
+tally(Class ~ svm2predtest, data = test)
+(9+8)/(9+8+5+2)
+
+# for svm2
+svm3predtest <- predict(svm3, test)
+tally(Class ~ svm3predtest, data = test)
+(14+0)/(14+10)
 ```
+
+It appears the that first and third SVM model predict the test set with an accuracy of 58.3% while the second model predicts the test set with a 70.8% accuracy.
 
@@
 
-SOLUTION:
+SOLUTION: Between the three models that we picked as the best for each section, the Bagging model was the most accurate at predicting the test set at 75%.
+However, this corresponds to 6 mistakes and best models for the Neural Net and SVM sections only had 7 mistakes.
+Due to the test set being so small, it is difficult to determine which model is the best because even a change of the seed value could cause a different model to have a higher accuracy rate.
+This means that we would choose the Bagging model as our final model to predict Class with these concerns in mind.
 

### 2022-11-03 homework/hmk7/hmk7Stat495F22.Rmd
Finish hw 7

@@
 
-SOLUTION:
+SOLUTION: For Neural Nets, the non-linearity of the model comes from the the non-linear threshold activation functions that creates a non-linear output from the activation values.
+These activation functions can include a sigmoid function or a hyperbolic tangent function, as well as others.
+For SVMs, the non-linearity comes up when the feature space is enlarged to look to optimal separating hyperplanes.
+The feature space can be grown by using kernals (and the "kernal trick") which map a lower dimensional linear model in the enlarged space to a non-linear model in higher dimensional space.
 
@@
 
-SOLUTION:
+SOLUTION: Random forest and boosting are similar that they both use decision trees to create models.
+They are also similar in the way that they lose interpretability due to the complexity of the models.
+Both methods utilize trees which automatically select variables.
+They differ because random forests build a number of larger and more bushy trees while boosting builds a large number of small trees in which the depth is fixed.
+The aim of random forests is variance reduction by averaging because each of the large trees has a high variance, but by averaging, the variance is brought down.
+On the other hand, boosting aims to reduce bias.
 
@@
 
-SOLUTION:
+SOLUTION: The concepts of backpropagation and the kernel trick are related in the ways that they help make the computation of the model more feasible.
+Backpropagation uses gradient descent to optimize the calculation and fixing the weights to minimize error.
+Backpropagation computes the gradient one layer at a time, by starting from the last layer and working backwards to minimize the number of redundant computations.
+The kernel trick is used when creating the enlarged feature space to perform the computations of inner products quicker.
+The kernel allows us to do this in a much lower dimension space which causes the computations to be easier.
+By doing this, it makes the computations for an SVM model more feasible.
 
@@
 
-Q:
+Q: How are Out-Of-Bag Error estimates used in random forests?
 
-A:
+A: The Out-Of-Bag (OOB) Error is used to measure the prediction error of a random forest.
+The Out-Of-Bag set is the set of all the observations that are not chosen in the bootstrap sampling process to be used in a creating a tree in the random-forest.
+The OOB Error is calculated by taking the average of each random-forest tree that the observation pair was left out of the bootstrap sample.
+This is similar to the leave-one-out cross validation error.

### 2022-11-06 homework/hmk7/hmk7Stat495F22.Rmd
Minor changes

@@
 table(train$Class, predict(class.rf, train))
-
 ```
@@
 ```
+
 The Bagging model appears to have an accuracy of 75% on the test set.
 The Random Forest model appears to have an accuracy of 66.7% on the test set and the Boosting model appears to have an accuracy of 62.5% on the test set.
-Therefore, we would choose the Bagging model for predicting Class because the model had the higest accuracy.
+Therefore, we would choose the Bagging model for predicting Class because this model had the highest accuracy.
 
@@
 set.seed(1)
-nnet_class3 <- nnet(Class ~ ., train, size = 15, decay = 5e-4, maxit = 1030)
+nnet_class3 <- nnet(Class ~ ., train, size = 15, decay = 5e-4, maxit = 1170)
 
@@
 tally(Class ~ pred3, data = test)
-(8+8)/(8+8+6+2)
+(7+7)/(7+7+7+3)
 ```
 
-From the confusion matrices above, it appears the the accuracy in predicting the test set from our first and third neural network model is 66.7% and the accuracy in predicting the test set from the second model is 70.8%.
+From the confusion matrices above, it appears the the accuracy in predicting the test set from our first neural network model is 66.7% and the accuracy in predicting the test set from the second model is 70.8% while the accuracy of predicting the test set from the third model was 58.3%.
 This means that we would choose the second neural network for predicting the test set.
-However, it is important to note that the difference between the accuracy in all of these models is only one more correct observation which could could change depending on the seed.
+However, it is important to note that the difference between the accuracy in the first and second model is only one more correct observation which could change depending on the seed.
 
@@
 However, this corresponds to 6 mistakes and best models for the Neural Net and SVM sections only had 7 mistakes.
-Due to the test set being so small, it is difficult to determine which model is the best because even a change of the seed value could cause a different model to have a higher accuracy rate.
-This means that we would choose the Bagging model as our final model to predict Class with these concerns in mind.
-
-```{r}
-
-```
+Due to the test set being so small, it is difficult to determine which model is the best because even a change in the seed value could cause a different model to have a higher accuracy rate.
+This means that we would choose the Bagging model as our final model to predict Class keeping these concerns in mind.
 
@@
 
-SOLUTION: For Neural Nets, the non-linearity of the model comes from the the non-linear threshold activation functions that creates a non-linear output from the activation values.
+SOLUTION: For Neural Nets, the non-linearity of the model comes from the non-linear threshold activation functions that creates a non-linear output from the activation values.
 These activation functions can include a sigmoid function or a hyperbolic tangent function, as well as others.
-For SVMs, the non-linearity comes up when the feature space is enlarged to look to optimal separating hyperplanes.
-The feature space can be grown by using kernals (and the "kernal trick") which map a lower dimensional linear model in the enlarged space to a non-linear model in higher dimensional space.
+For SVMs, the non-linearity comes up when the feature space is enlarged to look for optimal separating hyperplanes.
+The feature space can be grown by using kernels (and the "kernel trick") which maps a lower dimensional linear model in the enlarged space to a non-linear model in higher dimensional space.
 
@@
 They differ because random forests build a number of larger and more bushy trees while boosting builds a large number of small trees in which the depth is fixed.
-The aim of random forests is variance reduction by averaging because each of the large trees has a high variance, but by averaging, the variance is brought down.
+The aim of random forests is variance reduction because each of the large trees has a high variance, but by averaging, the variance is brought down.
 On the other hand, boosting aims to reduce bias.

### 2022-11-09 labs/Chapter 15 Lab.Rmd
Add annotated bib docx and add some literature

---
title: "Stat 495 - Chapter 15 Lab"
author: "A.S. Wagaman"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(DescTools)
```

# ANOVA Example

We will use the current population survey data to do one example with One-Way ANOVA.

```{r}
data(CPS85)
```

We will look for differences in average log wage by sector.

```{r}
favstats(log(wage) ~ sector, data = CPS85)
gf_boxplot(log(wage) ~ sector, data = CPS85)
```

The log re-expression helps with satisfying appropriate conditions.

```{r}
CPS85 <- mutate(CPS85, logwage = log(wage))
mymod <- lm(logwage ~ sector, data = CPS85)
msummary(mymod)
```

What do we learn from the ANOVA output?

> SOLUTION: 
The linear model is not the best because the $R^2$ value is 0.1821 which means that the model is not very strong.

To perform multiple comparisons, several functions can be used, but two common ones for this setting are pairwise.t.test and PostHocTest (in DescTools).

```{r}
with(CPS85, pairwise.t.test(log(wage), sector, p.adjust = "bonf"))
PostHocTest(aov(log(wage)~ sector, data = CPS85), method = "bonf")
```

Compare the output between the methods for Bonferroni's approach. Which method do you prefer? Why?

> SOLUTION
Both inputs have the same values for the comparisons. It is easier to use the first method to find a comparison between two of the predictors because the table makes it helpful to helpful to look at all of the relationships that one predictor has with other ones. However, it is nice that the second method shows significance.

Implement "none", "holm", and "fdr" methods for these comparisons using pairwise.t.test. What differences do you note in the results? (PostHocTests doesn't have all of these implemented for aov.)

> SOLUTION

```{r}
with(CPS85, pairwise.t.test(log(wage), sector, p.adjust = "none"))
```

```{r}
with(CPS85, pairwise.t.test(log(wage), sector, p.adjust = "holm"))
```

```{r}
with(CPS85, pairwise.t.test(log(wage), sector, p.adjust = "fdr"))
```

# p.adjust methods

A suite of p.adjust methods exist - you've been calling them up above. All you need though is just a vector of p-values that can then be adjusted by these methods. As an example, consider:

```{r}
set.seed(495)
pvals <- sort(c(runif(100, 0, 0.01), runif(100, 0.01, 0.20))) #random potential p-values
adjpvals <- p.adjust(pvals, method = "bonf")
head(pvals)
head(adjpvals)
```

Here is the example from the help file:

```{r}
set.seed(123)
x <- rnorm(50, mean = c(rep(0, 25), rep(3, 25)))
p <- 2*pnorm(sort(-abs(x)))

round(p, 3)
round(p.adjust(p), 3)
round(p.adjust(p, "BH"), 3)
```

PostHocTest has some additional description of the methods used there in its help file.

```{r}
?PostHocTest
```

# Prostate Microarray example

The textbook uses the prostate microarray data example throughout the chapter.

The data set is provided on their website, but they also provide the already computed z-scores, from which p-values can be computed.

```{r}
prostz <- read.table("http://web.stanford.edu/~hastie/CASI_files/DATA/prostz.txt", header = FALSE)
```

Examine the distribution of the z-scores.

> SOLUTION 
Unimodal, symmetric, centered at 0 and relatively Normal.

```{r}
gf_histogram(~V1, data = prostz)
```

The textbook examines one-sided POSITIVE results, though in general you might care about just any non-null case.

Consider two-sided hypotheses. How many null hypotheses would be rejected (out of the 6033) if the p-values were unadjusted and $\alpha = 0.05$?

> SOLUTION 
296 of the NULL hypotheses would be rejected

```{r}
prosPvals0 <- 2*pnorm(sort(-abs(prostz$V1)))
count(abs(prosPvals0) < 0.025)
```

What would you do differently if you wanted to apply Bonferroni's procedure to two-sided hypotheses?

> SOLUTION 
We would have to adjust the p-values

Perform your two-sided Bonferroni adjustment on the prostate z-scores by hand. How many null hypotheses are rejected at $\alpha = 0.05$?

> SOLUTION
2 of the null hypotheses would be rejected.

```{r}

prosPvals <- 2*pnorm(sort(-abs(prostz$V1)))
#BonRejectP <- prostz

adjustedPs = p.adjust(prosPvals, method = "bonf")

#adjustedPs = abs(adjustedPs) < 0.05

#adjustedPs

count(abs(adjustedPs) < 0.025)

```

Obtain the two-sided p-values (if you didn't up above - it can be done based on critical values).

> SOLUTION

```{r}
#adjustedPs
```

Apply p.adjust using bonferroni to your p-values. Do you obtain the same results as you did by hand? How many null hypotheses are rejected at $\alpha = 0.05$?

> SOLUTION
Yes, 3. it was done above.

```{r}

```

Apply Holm's method using p.adjust. How many null hypotheses are rejected at $\alpha = 0.05$?

> SOLUTION There are 2 that are rejected

```{r}
adjustedPs2 = p.adjust(prosPvals, method = "holm")

count(abs(adjustedPs2) < 0.025)
```

Apply FDR using p.adjust. How many results are declared interesting at $q=\alpha=0.05$? At $q=0.1$?

> SOLUTION There are 13 that are rejected

```{r}
adjustedPs3 = p.adjust(prosPvals, method = "fdr")

count(abs(adjustedPs3) < 0.025)
```

How do the methods compare?

> SOLUTION The third one is much less conservative.

# Khan Data

The Khan dataset contains 2308 rows (genes) x 64 column (observations). Khan et al., 2001 used cDNA microarrays containing 6567 clones of which 3789 were known genes and 2778 were ESTs to study the expression of genes in of four types of small round blue cell tumours of childhood (SRBCT). These were neuroblastoma (NB),rhabdomyosarcoma (RMS), Burkitt lymphoma, a subset of non-Hodgkin lymphoma (BL), and the Ewing family of tumours (EWS). Gene expression profiles from both tumour biopsy and cell line samples were obtained and are contained in this dataset. The dataset downloaded from the website contained the filtered dataset of 2308 gene expression profiles as described by Khan et al., 2001.

```{r}
khan <- read.csv("https://awagaman.people.amherst.edu/stat495/khan_train.csv", header = T)
khan <- khan[, -1] #remove row indices
khant <- data.frame(t(khan)) #transpose so rows become columns
```

We want to identify the top genes that allow us to significantly distinguish between tumor types, appropriately adjusting for simultaneous testing. Each ROW in the initial data set should be used as the response in ANOVA (which is why we flipped it above), where the class labels are:

```{r}
labels <- c(rep("EWS", 23), rep("BL", 8), rep("NB", 12), rep("RMS", 21))
```

Perform appropriate ANOVA analyses, adjusting for simultaneous testing. An example way to extract the p-value for the *first* gene is shown below to help get you started.

```{r}
anova(lm(khant[, 1]~labels))$"Pr(>F)"[1]
```

> SOLUTION

### 2022-11-09 project/PaperTemplate/test.Rmd
Added paper template and paper discussion

---
title: Title here

# to produce blinded version set to 1
blinded: 0

authors: 
- name: XX YOUR NAME HERE XX
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of Mathematics and Statistics, Amherst College

keywords:
- 3 to 6 keywords
- that do not appear in the title

abstract: |
  The text of your abstract.  200 or fewer words. It is intended to provide an overview of your paper and may be similar to your synopsis. Note that an abstract can only include one paragraph in this format. You may want to put your synopsis here as you work to refer to it easily.

bibliography: bibliography.bib
output:
  rticles::asa_article:
  keep_tex: yes
---

```{r setup, include = FALSE}
library(tidyverse)
library(mosaic)
library(mdsr)
library(knitr)
library(kableExtra)
```

# Introduction

This template will be used for you to submit your final project. You'll need to install the *rticles* package, make sure you have the agsm.bst file and bibliography.bib file, and the gfx folder and figure file in order to compile. If you make your own bibliography.bib file later, that's fine - change the name above to match your file name. You'll want the setup for the file to look the same in your repo as in the class repo, and then compile to asa_article when you knit. You should change the name of the file to something other than "test" though. Remember that if something goes wrong with the file, you can always look back at the class repo for the original files and their structure.

This template was adapted from the template Prof. Horton provided Stat 495 in Fall 2021, used with permission.

# More on the template 
\label{sec:template}

This template demonstrates some of the basic LaTeX commands and syntax you'll need to know to use the `rticles` package to generate a readable report using R Markdown. Markdown allows various formatting and you can find formatting cheatsheets or guides online to assist as well. Here's an example with bullets and some advice:

* I would encourage you to look closely at this file and explore the various parts and pieces.
* I would suggest that you format your Rmd file so that you have only one sentence per line.
* It makes it *much* easier to see changes in your GitHub commits.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of text looks like, for margins and spacing.

Note that we can refer to sections (e.g., this is section \ref{sec:verify}, while the previous section was section \ref{sec:template}).

Note that we should refer to work using the BibTeX system. Here we can reference papers by @Campbell02 and @Schubert13 through inline citations (see the `bibliography.bib` file for the reference database).

More work that is relevant can also be cited in a traditional fashion [@Chi81,@Galyardt14mmm,@Galyardt12dis].

Note that you can capitalize proper nouns in citations [@Campbell02] (again, see `bibliography.bib`).

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
__With this spacing we have 30 lines per page.__

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

# Examples

Lots of things can be done in this template.

```{r sample-table1}
Violations %>%
  select(dba, boro) %>%
  unique() %>%
  group_by(boro) %>%
  summarize(count = n(), .groups = "drop") %>%
  knitr::kable(
    caption = "This is a sample table caption that should interpret the table!")
```

Table \ref{tab:sample-table1} displays the number of dba's per borough.

```{r sample-fig1, fig.height = 3, fig.cap = "\\label{fig:sample-fig1}This is a sample figure caption that should interpret the figure!"}
Violations %>%
  select(dba, boro, inspection_date, score) %>%
  unique() %>%
  group_by(boro) %>%
  summarize(
    count = n(),
    averagescore = mean(score, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = boro, y = averagescore)) +
  geom_boxplot()
```

Figure \ref{fig:sample-fig1} displays the average inspection score by borough.

Figure \ref{fig:sample-fig2} displays a campus map.

```{r sample-fig2, echo=FALSE, out.width = "80%", fig.show='hold', fig.cap="XX another sample figure caption"}
knitr::include_graphics("gfx/campus_map.png")
```

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

# Your Choice of Structure

You are responsible for choosing the structure you want for the report, i.e. what sections and their names. Here are some examples that you could adapt, as appropriate. These are just examples - the first has more sections, some of which may make more sense as sub-sections of others. I'm just trying to give you examples. You don't have to have a conclusion or an introduction, etc. You'll need to find what works for you.

## Example 1

* Introduction
* Background
* Topic X (Main exposition section)
* Applications in Literature
* Application to Data (your data)
* Conclusion

## Example 2

* Introduction (including any relevant Background)
* Topic X (exposition and examples)
* Simulation

### 2022-11-09 project/PaperTemplate/test.tex
Added paper template and paper discussion

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

%% load any required packages here

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Title here}

  \author{
        XX YOUR NAME HERE XX \thanks{The authors gratefully acknowledge
\ldots{}} \\
    Department of Mathematics and Statistics, Amherst College\\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title here}
  \end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
The text of your abstract. 200 or fewer words. It is intended to provide
an overview of your paper and may be similar to your synopsis. Note that
an abstract can only include one paragraph in this format. You may want
to put your synopsis here as you work to refer to it easily.
\end{abstract}

\noindent%
{\it Keywords:} 3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

This template will be used for you to submit your final project. You'll
need to install the \emph{rticles} package, make sure you have the
agsm.bst file and bibliography.bib file, and the gfx folder and figure
file in order to compile. If you make your own bibliography.bib file
later, that's fine - change the name above to match your file name.
You'll want the setup for the file to look the same in your repo as in
the class repo, and then compile to asa\_article when you knit. You
should change the name of the file to something other than ``test''
though. Remember that if something goes wrong with the file, you can
always look back at the class repo for the original files and their
structure.

This template was adapted from the template Prof.~Horton provided Stat
495 in Fall 2021, used with permission.

\hypertarget{more-on-the-template}{%
\section{More on the template}\label{more-on-the-template}}

\label{sec:template}

This template demonstrates some of the basic LaTeX commands and syntax
you'll need to know to use the \texttt{rticles} package to generate a
readable report using R Markdown. Markdown allows various formatting and
you can find formatting cheatsheets or guides online to assist as well.
Here's an example with bullets and some advice:

\begin{itemize}
\tightlist
\item
  I would encourage you to look closely at this file and explore the
  various parts and pieces.
\item
  I would suggest that you format your Rmd file so that you have only
  one sentence per line.
\item
  It makes it \emph{much} easier to see changes in your GitHub commits.
\end{itemize}

\section{Verifications}
\label{sec:verify}

This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

Note that we can refer to sections (e.g., this is section
\ref{sec:verify}, while the previous section was section
\ref{sec:template}).

Note that we should refer to work using the BibTeX system. Here we can
reference papers by \citet{Campbell02} and \citet{Schubert13} through
inline citations (see the \texttt{bibliography.bib} file for the
reference database).

More work that is relevant can also be cited in a traditional fashion
\citep[\citet{Galyardt14mmm},\citet{Galyardt12dis}]{Chi81}.

Note that you can capitalize proper nouns in citations
\citep{Campbell02} (again, see \texttt{bibliography.bib}).

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. \textbf{With this spacing we
have 30 lines per page.}

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

\hypertarget{examples}{%
\section{Examples}\label{examples}}

Lots of things can be done in this template.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Violations }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(dba, boro) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{unique}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(boro) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{(), }\AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
    \AttributeTok{caption =} \StringTok{"This is a sample table caption that should interpret the table!"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:sample-table1}This is a sample table caption that should interpret the table!}
\centering
\begin{tabular}[t]{l|r}
\hline
boro & count\\
\hline
BRONX & 1903\\
\hline
BROOKLYN & 5294\\
\hline
MANHATTAN & 8340\\
\hline
Missing & 6\\
\hline
QUEENS & 4789\\
\hline
STATEN ISLAND & 802\\
\hline
\end{tabular}
\end{table}

Table \ref{tab:sample-table1} displays the number of dba's per borough.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Violations }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(dba, boro, inspection\_date, score) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{unique}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(boro) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{count =} \FunctionTok{n}\NormalTok{(),}
    \AttributeTok{averagescore =} \FunctionTok{mean}\NormalTok{(score, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{),}
    \AttributeTok{.groups =} \StringTok{"drop"}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ boro, }\AttributeTok{y =}\NormalTok{ averagescore)) }\SpecialCharTok{+}
  \FunctionTok{geom\_boxplot}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{test_files/figure-latex/sample-fig1-1.pdf}
\caption{\label{fig:sample-fig1}This is a sample figure caption that
should interpret the figure!}
\end{figure}

Figure \ref{fig:sample-fig1} displays the average inspection score by
borough.

Figure \ref{fig:sample-fig2} displays a campus map.

\begin{figure}
\includegraphics[width=0.8\linewidth]{gfx/campus_map} \caption{XX another sample figure caption}\label{fig:sample-fig2}
\end{figure}

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

\hypertarget{your-choice-of-structure}{%
\section{Your Choice of Structure}\label{your-choice-of-structure}}

You are responsible for choosing the structure you want for the report,
i.e.~what sections and their names. Here are some examples that you
could adapt, as appropriate. These are just examples - the first has
more sections, some of which may make more sense as sub-sections of
others. I'm just trying to give you examples. You don't have to have a
conclusion or an introduction, etc. You'll need to find what works for
you.

\hypertarget{example-1}{%
\subsection{Example 1}\label{example-1}}

\begin{itemize}
\tightlist
\item
  Introduction
\item
  Background
\item
  Topic X (Main exposition section)
\item
  Applications in Literature
\item
  Application to Data (your data)
\item
  Conclusion
\end{itemize}

\hypertarget{example-2}{%
\subsection{Example 2}\label{example-2}}

\begin{itemize}
\tightlist
\item
  Introduction (including any relevant Background)
\item
  Topic X (exposition and examples)
\item
  Simulation
\end{itemize}

\bibliographystyle{agsm}
\bibliography{bibliography.bib}

\end{document}

### 2022-11-14 labs/Coding and Simulations - Lab.Rmd
Add some files

---
title: "Coding and Simulations - Lab"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
library(knitr)
require(BSDA) #may need to install; used for Sign Test
options(digits = 6)
```

This lab is designed to have you practice writing simulations, and explore commenting code and other best practices for writing R code (the lessons apply to most other coding languages).

# Best Practices for Coding in R

Basically, I've just assembled some resources for you to examine at your leisure. There are many other similar pages out there.

[https://www.r-bloggers.com/r-code-best-practices/](https://www.r-bloggers.com/r-code-best-practices/)

This first link has lots of links to other resources at the bottom of it's page.

[Example Best Practices](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/)

[Google's Style Guide](https://google.github.io/styleguide/Rguide.xml)

In regards to commenting, you don't need to comment EVERY line, but the idea is to comment chunks, functions, etc. with their use/purpose. This helps both you and your readers. You also want to keep chunks relatively small - they become hard to parse when they get large (like paragraphs). Don't try to do too much in each chunk.

I strongly recommend the following when it comes to your course projects (and other future work) in terms of coding, especially if you are running a simulation.

* Compile early and often. Don't wait till the last minute to compile.
* Write code in small chunks to check that it works. A large chunk that doesn't run is harder to debug.
* Intentionally break code INTO small chunks. You can always put it into a larger chunk later if needed. 
* Caching is useful, but be careful about pushing/committing said pieces. The limit is 100MB. 
* Learn RMarkdown formatting and use it. There's a cheatsheet from RStudio and an associated DataCamp course. 
* Don't submit at the last minute. If it's late, it's late. Git gives us a time record! Submit EARLY.
* Make sure you set seeds. You need a reproducible submission for the project.

# Simulations (and Toy Examples)

Don't underestimate the importance of a simulation and what it can show. In fact, simple simulation studies and toy examples (simple data sets) can be a great way to demonstrate your understanding of a method. If you can simulate to demonstrate a result, it makes you think more about the underlying setting. Toy examples can help a reader understand the output and should be easy for you to explain. Since I'm confident you can all use toy examples (we have lots of simple data sets in R!), I would like to focus more on simulations today. I'm going to show you several examples of simulations, then ask you to write one of your own.

## Simulation 1

First, we examine a common misconception in linear regression. In this simulation, a SINGLE case of a setting is constructed to demonstrate a point. This is reproduced from a presentation I made for my Stat 230 class. (Normally, you'd imagine repeating the process to collect multiple results.)

There is a normality condition in regression, but there are often misconceptions about "what" has to be normal. Does the response need to be normal? The predictors? The errors?

The condition is that the errors need to be normally distributed, which we then check by using the residuals (our best guesses of the errors).

The simulated examples below are designed to show you that:

* predictors do not need to be normally distributed for regression to be appropriate
* predictors can be normally distributed and regression NOT be appropriate

Re-expressing predictors may prove useful for helping to satisfy conditions, but the idea is to note that you do not need to re-express all predictors to have normal distributions before even starting the regression. If normality of predictors was a requirement, after all, we'd never be able to have categorical predictors.

The examples below are simulated. The code is generating random values to use. I've tried to explain the process with comments and appropriate illustrations.

## Simulating a Regression

Before you see how I accomplish this, discuss with those around you how you would set up a simulation involving a regression model. How would you generate the data? The model?

## Normal Errors - Non-normal Predictors - Regression Works!

In this example, we will use two quantitative predictors with non-normal distributions and a binary (categorical) predictor to construct a response and then build a regression model. We will use normally distributed errors.

```{r}
set.seed(29540) # for reproducibility
x1 <- rgamma(300, 500, rate = 3) #x1 has a gamma distribution; right-skewed
x2 <- runif(300, 30, 40) #x2 has a uniform distribution
x3bin <- factor(c(rep("Low",100), rep("High", 200))) #x3 is a factor Low/High
x3num <- as.numeric(x3bin)-1 #makes High = 0, Low = 1 to construct model
```

We want to look at the distributions of these predictors to verify that they are all non-normal.

```{r}
gf_histogram(~ x1) %>% gf_labs(title = "Histogram of X1")
gf_histogram(~ x2) %>% gf_labs(title = "Histogram of X2")
gf_histogram(~ x3num) %>% gf_labs(title = "Histogram of X3 as Numeric")
tally(~x3bin)
```

None of the predictors are normally distributed.

Next we construct the TRUE regression model for the mean of the response $\mu_Y = 15 + x1 - 3*x2 + 25*x3num$.

```{r}
mu_y <- 15 + x1 - 3*x2 + 25*x3num
```

Now, we add in the error inherent in the process. We use a normal distribution for the errors, with mean 0.

```{r}
set.seed(230)
Y <- mu_y + rnorm(300, 0, 5)
gf_histogram(~ Y) %>% gf_labs(title = "Histogram of Response Y")
```

Remember that we don't really know the truth as presented above. We would start from the data set with a response Y and the three predictors.

First, we would check to see if we think a linear model is appropriate. We make scatterplots for x1 and x2 each versus Y, and a boxplot of Y by x3bin to check the linearity condition.

```{r}
gf_point(Y ~ x1) %>% gf_lm() %>% gf_labs(title = "Y vs. X1")
gf_point(Y ~ x2) %>% gf_lm() %>% gf_labs(title = "Y vs. X2")
gf_boxplot(Y ~ x3bin) %>% gf_lm() %>% gf_labs(title = "Y vs. X3bin")
```

Both scatterplots show linear relationships and the boxplot shows a clear difference between the values of Y for the levels of X3. Thus, it is appropriate to use all variables in the linear model (with NO re-expressions needed).

Now, we see if we can recover the regression coefficients, and check our model conditions.

```{r}
mymod <- lm(Y ~ x1 + x2 + x3bin)
msummary(mymod)
```

Looks like we have recovered the coefficients fairly well. But what about the conditions on the errors for normality and constant variance?

```{r}
mplot(mymod, which = 1)
mplot(mymod, which = 2)
```

The conditions for normality and constant variance of errors check out. The residuals versus fitted plot shows a random scatter of points in a horizontal band about the same width above and below 0. For the normality plot, the points follow the line very closely with only slight deviations in the tails.

In summary, for this example, linear regression was appropriate even though our predictors were NOT normally distributed because we had normally distributed errors (and that's what the condition is about!).

Note that this was only ONE simulation involving this model. You could imagine settings where you want to do more - such as record the slopes over many models to check the estimation. You should be able to think about how to do that with this code as a base.

## Normal Predictors - Non-normal Errors - Regression is NOT appropriate

Here, we take the opposite approach to above. We will use two normally distributed predictors (no categorical predictor can be included if we are forcing normality on the predictors). But, we will NOT use normal errors (which is a condition violation). The goal is to see what happens when we try to recover the model. In this example, I'm going to make the violation fairly egregious, to illustrate the point.

```{r}
set.seed(29582) # for reproducibility
x1 <- rnorm(300, 50, 3) 
x2 <- rnorm(300, 30, 5) 
```

We want to look at the distributions of these predictors to verify that they are both normally distributed.

```{r}
gf_histogram(~ x1) %>% gf_labs(title = "Histogram of X1")
gf_histogram(~ x2) %>% gf_labs(title = "Histogram of X2")
```

Both of the predictors have unimodal bell-shaped distributions. We could check qq-plots to more precisely check to see if they are normally distributed.

```{r}
gf_qq(~ x1) %>% gf_qqline() %>% gf_labs(title = "QQ-Plot for X1")
gf_qq(~ x2) %>% gf_qqline() %>% gf_labs(title = "QQ-Plot for X2")
```

Both of the predictors appear to be normally distributed.

Next we construct the TRUE regression model for the mean of the response $\mu_Y = 15 + 6*x1 - 4*x2$.

```{r}
mu_y <- 15 + 6*x1 - 4*x2 
```

Now, we add in the error inherent in the process. We use a combination of cauchy and normal errors, so this is the condition violation.

```{r}
set.seed(230)
Y <- mu_y + rcauchy(300, location = 0, scale = 6) + rnorm(300, 0, 5)
gf_histogram(~ Y) %>% gf_labs(title = "Histogram of Response Y")
```

Again, in reality, we don't know the true model as presented above. We'd just start from Y and the two predictors in the data set.

First, we would check to see if we think a linear model is appropriate. We make scatterplots for x1 and x2 each versus Y check the linearity condition.

```{r}
gf_point(Y ~ x1) %>% gf_lm() %>% gf_labs(title = "Y vs. X1")
gf_point(Y ~ x2) %>% gf_lm() %>% gf_labs(title = "Y vs. X2")
```

Both scatterplots show linear relationships, Thus, it is appropriate to use all variables in the linear model (with NO re-expressions needed). You might notice another property of both scatterplots - some outliers. This is due to the distributions I choose for the errors.

Now, we see if we can recover the regression coefficients, and check our model conditions.

```{r}
mymod <- lm(Y ~ x1 + x2)
msummary(mymod)
```

Hmm. Our intercept is clearly not the 15 we set. The 5.655 is nearly the 6 we set for the slope of x1, but negative 3 is not negative 4 (what we set) for the slope of x2.

What about the conditions on the errors for normality and constant variance?

```{r}
mplot(mymod, which = 1)
mplot(mymod, which = 2)
```

The conditions for normality and constant variance of errors show extreme outliers, so as it stands, these conditions are not met. For the normality plot, the deviations in the tails are fairly extreme, as we see an S shape. Granted, n = 300 is relatively large, so things aren't too horrible here, but it would be better if we had just normally distributed errors.

In summary, linear regression was NOT appropriate even though our predictors were normally distributed because we had NON-normally distributed errors (and that's what the condition is about!).

Yes, you can argue here that removing the outliers will fix the problem. That's because that would be making the distribution of residuals more normally distributed, which is why we learned about unusual points. The key is to realize the distribution of the predictors doesn't have anything to with the issues encountered here.

## Simulation 2

Rather than simulating a single case, you may want to simulate MANY cases to check things like Type I error, power, or confidence interval coverage. This simulation below is an example from my Stat 225 course - Nonparametric statistics. It compares three test procedures in the one-sample setting examining measures of center. The presentation below is from one of the labs from the class.

In this lab, we want to investigate the efficiencies described in the book in the last section of Chapter 3 (Nonparametric Statistical Methods by Hollander, Wolfe, and Chicken), and see if we can verify that there are situations where the t-test does not perform well compared to the Sign Test or Signed Rank test, and vice versa. To investigate, we'll be setting up a simulation study, and walking through the steps associated with that below.

## Running the three tests

First, let's just see how to run all three test procedures on a set of observations. You can imagine these are the differences or just a set of values (i.e. paired setting or just one-sample setting). All these are run as two-sided examples. That could be changed with the *alternative* option, but we'll run everything here two-sided.

```{r}
fakedata <- c(1:50) #1:50 as our data
t.test(~ fakedata, mu = 25) #parametric t-test
SIGN.test(fakedata, md = 25) #sign test
wilcox.test(fakedata, mu = 25) #signed rank test
```

Now, to do our simulation study, we're going to need to *SAVE* some values from the output of the tests. What might be useful values to save?

> SOLUTION:

It would probably be useful to save the test statistics and p-values (primarily p-values). Let's consider how that can be done. We can rerun the tests and SAVE the output in order to see what pieces are actually computed by R when the test is run. These pieces can be extracted separately.

```{r}
tresult <- t.test(~ fakedata, mu = 25) #parametric t-test
names(tresult)
signresult <- SIGN.test(fakedata, md = 25) #sign test
names(signresult)
srresult <- wilcox.test(fakedata, mu = 25) #signed rank test
names(srresult)
```

So, this means that I could extract all three p-values from the saved tests like this:

```{r}
tresult$p.value
signresult$p.value
srresult$p.value
```

(You should be able to do this for similar pieces of similar objects.)

Even better, I don't have to SAVE the test output to get the p-values. I can get them like this:

```{r}
t.test(~ fakedata, mu = 25)$p.value 
SIGN.test(fakedata, md = 25)$p.value 
wilcox.test(fakedata, mu = 25)$p.value 
```

Ok. So now we have a way to extract p-values quickly from a test. We want to combine this with simulating MANY data sets, using different distributions for the data to see how the different tests behave. (There's a bit more to this, including understanding effect size, but we should be able to have some fun with just this understanding.)

## Simulating Data from a Normal Distribution

Here, we look at an example simulating data from the normal distribution. The code below samples 10 observations from a normal distribution with mean 20 and sd 2, and saves them as x.

```{r}
x <- rnorm(10, 20, 2); x
```

We could feed x into our different tests, along with a hypothesized mean, get the p-values, and compare the results. Better yet, we could simulate MANY different but similar x's and repeat this process to better understand the behavior of the tests.

Here's an example:

```{r}
# Set Useful Values
reps <- 1000 #number of repetitions
truemu <- 40 
truesd <- 3
testcenter <- 37 #center to test for
n <- 25 #sample size
set.seed(1001) #for reproducibility

#Initialize storage vectors
tpvals <- rep(0, reps)
spvals <- rep(0, reps)
srpvals <- rep(0, reps)

#Generate random data, do tests, save p-values
for(i in 1:reps){
  x<-rnorm(n, truemu, truesd)
  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
}
```

What does this give us? Well, we get a set of 1000 p-values each from the three different tests (1000 data sets all run through the three tests). We can figure out how often each test rejected the null, and see which test is performing better. Here, we know the true mean is 40, and we were testing a two-sided alternative with a mean of 37. So, we'd like to think the tests would reject the null.

```{r}
sum(tpvals <= 0.05)/reps
sum(spvals <= 0.05)/reps
sum(srpvals <= 0.05)/reps
```

We see that 99.9% of t-tests and Signed rank tests rejected the null, but only 95.6% of sign tests did. The output is the fraction of p-values less than or equal to 0.05.

Now you try. Here is the same code (pieces combined), and turned into a function. You run the main chunk once to create the function, and then you can run it quickly with different inputs in chunks after it.

```{r}
simnormal <- function(locationinput, scaleinput, testcenterinput, ninput, repsinput = 1000){
# Set Useful Values
reps <- repsinput #number of repetitions
location <- locationinput 
scale <- scaleinput
testcenter <- testcenterinput #center to test for
n <- ninput #sample size

#Initialize storage vectors
tpvals <- rep(0,reps)
spvals <- rep(0,reps)
srpvals <- rep(0,reps)

#Generate random data, do tests, save p-values
for(i in 1:reps){
  x <- rnorm(n, location, scale)
  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
}

output <- c(sum(tpvals <= 0.05)/reps, sum(spvals <= 0.05)/reps, sum(srpvals <= 0.05)/reps)
names(output) <- c("Ttest", "Sign", "SignedRank")
output
}
```

In the code chunk below, change the inputs a few times and see what sorts of results you get. The output is in the order of t-test, sign test, and lastly, signed rank test fractions of p-values less than or equal to 0.05. Some short labels were added to help with keeping the order straight. You could envision fancier functions that took in optional alphas to compare to instead of just 0.05. But this works for our purposes.

```{r}
set.seed(1001)
simnormal(40, 3, 39, 25) #mean, sd, testcenter, n are the inputs
#simnormal()
#simnormal() #add more lines for more settings
```

What tests seem to be performing best based on your simulations?

> SOLUTION

In this setting, the data we generated followed a normal distribution, so we expected the t-test to do well, but signed rank should have been nearly comparable. Let's try some different distributions.

## Your Turn

Write a simulation either in the regression setting to examine the impact of unequal variance of the errors on the solution, or continue in the nonparametric comparison setting but change the distribution to something like cauchy or uniform instead of normal to see how the tests perform.

```{r}
simcauchy <- function(locationinput, scaleinput, testcenterinput, ninput, repsinput = 1000){
# Set Useful Values
reps <- repsinput #number of repetitions
location <- locationinput 
scale <- scaleinput
testcenter <- testcenterinput #center to test for
n <- ninput #sample size

#Initialize storage vectors
tpvals <- rep(0,reps)
spvals <- rep(0,reps)
srpvals <- rep(0,reps)

#Generate random data, do tests, save p-values
for(i in 1:reps){
  x <- rcauchy(n, location, scale)
  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
}

output <- c(sum(tpvals <= 0.05)/reps, sum(spvals <= 0.05)/reps, sum(srpvals <= 0.05)/reps)
names(output) <- c("Ttest", "Sign", "SignedRank")
output
}
```

```{r}
set.seed(1001)
simcauchy(40, 3, 37, 25) #mean, sd, testcenter, n are the inputs
#simnormal()
#simnormal() #add more lines for more settings
```

## Writing up a simulation

Typically, when doing a simulation, you will simulate many data sets and their corresponding sets of results for whatever procedure you are doing, under a host of different parameter settings. You then
need to convey your results. This usually means making a table (or several) or figure (or several) to display results, which you then have to discuss. Figuring out the best layout of tables is often tricky, and I encourage you to sketch it (by hand!) to figure out what makes the best sense for your setting.

```{r}
for(i in 1:100){
  results <- simnormal(40, 3, 37, 25)
}
```

### 2022-11-14 homework/hmk8/hmk8Stat495F22.Rmd
Finish hw8. Need to clean up

---
title: "Homework 8 - Stat 495"
author: "Justin Papagelis"
date: "Due Wednesday, Nov. 16th by midnight (11:59 pm)"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(LaplacesDemon) #move up to normal package chunk in submission
library(mvtnorm)
options(digits = 6)
```

# Practicing Academic Integrity

If you worked with others or used resources outside of provided course material (anything besides our textbook(s), course materials in Moodle/Git repo, R help menu) to complete this assignment, please acknowledge them below using a bulleted list.

<!-- ~~~~~~~~~~~~~~~~ YOU MAY BEGIN EDITING BELOW THIS LINE ~~~~~~~~~~~~~~~~ -->

*I acknowledge the following individuals with whom I worked on this assignment:*

Name(s) and corresponding problem(s)

*

*I used the following sources to help complete this assignment:*

Source(s) and corresponding problem(s)

*

\newpage

# PROBLEMS TO TURN IN:  Add 1

# Additional 1

The goal for this problem is to practice using simulation to explore a potentially unfamiliar setting, and to then communicate your results and overall process.

We are all familiar with the usual Pearson correlation coefficient, $r$, which is computed pairwise between quantitative variables as a measure of the strength of their linear relationship. Other correlation type statistics exist - two nonparametric ones that are notable are Kendall's Tau, $\tau$ and Spearman's rho. We will focus on Kendall's tau and Pearson's $r$ here. An example of how to obtain test output checking to see if the population parameters estimated by these values are statistically significantly different from 0 is shown below.

```{r}
data(iris)
with(iris, cor.test(Sepal.Length, Sepal.Width))
with(iris, cor.test(Sepal.Length, Sepal.Width, method = "kendall"))
```

Your task is to compare how the two procedures perform in terms of identifying significant relationships (significantly non-zero correlations) between the two variables by writing simulations for the following three settings:

* independent observations from two different distributions (your choice, but not say, two normals with different means; two different distributions, like a beta and a normal (pick another pair!))
* bivariate normal observations with a moderate correlation (say something between 0.3 < $\rho$ < 0.5)
* double exponentially distributed observations with a moderate correlation (covariance between 0.3 and 0.5)

In each setting, you should use 15 observations for a run (as one setting). You should use variances of 1 for the bivariate normal and double exponential. An example of generating from the double exponential is shown below. It requires a package that you may need to install.

```{r, message = FALSE, warning = FALSE}
X <- rmvl(15, c(0,1), matrix(c(1, 0.2, 0.2, 1), nrow = 2)) #look at the help file!
joint.density.plot(X[, 1], X[, 2], color = TRUE)
```

If you want to adjust either $n$ or the variances, feel free to do that after completing the requested case. This is not required, but some of you get curious and might want to check out other behaviors.

An outline for the solution is provided below for you to fill in. Please write in complete sentences. Note that you can understand what is going on here with 10,000 or fewer runs in each setting. Referring to the lab on Coding and Simulation may be useful, and remember that your submission should be reproducible. You can delete these instructions and prompts below in your submission, or keep for your reference.

For the sections below, these are potential outlines / suggestions of questions to answer you could follow. But be sure you craft the responses into sentences and paragraphs. Short answers to the bullet-points don't demonstrate your communication skills.

\newpage

## Simulation Comparing Kendall's tau and Pearson's $r$

### Intro and Simulation Overview

* What is the task, as you understand it?
* What do you plan to do for your simulation (generally speaking) to compare the performance of the methods?
* Some questions to consider answering: Are you storing correlation values? p-values? Storing nothing? How many runs are you doing? Is a single run sufficient? What seems reasonable? What will you compare to assess the performance of the methods? 
* You should aim to convey the general structure of your simulation in a paragraph or two, so that a reader can follow along, and could think about pseudocode steps based on your description. 
* What do you expect to happen in the simulations? There are three settings. Describe what you expect to happen in each setting. You can check this with your simulations, but you should be able to make some predictions based on your statistical background knowledge.

The task of the simulation is to compare how Kendall's tau and Pearson's $r$ perform in terms of identifying significant relationships between two variables from varying distributions. For the simulation, we will generate two variables, each from a specified distribution and then once we have that, we will store the p-value that shows if the population parameters estimated by these values are statistically significantly different than 0 for each method. Once we run this about 10,000 and get a large number of p-values, we can see how many of the p-values from each method are significant. A small proportion of significant p-values would tell us that most of the correlation tests failed to reject the null that the true correlation between the two distributions is 0.

We expect that for the independent variables from two different distributions, most of the correlation tests will fail to reject the null because the variables were independently chosen from two different distributions. For the variables from the bivariate normal distribution with a moderate correlation, we expect there to be a larger amount of tests that reject the null because the variables have a moderate correlation. The same goes for the variables from the double exponential distribution with moderate correlation. We would expect to see a larger amount of tests reject the null because the two variables are moderately correlated.

### Independent Variables from Two Different Distributions

* independent observations from two different distributions (your choice, but not say, two normals with different means; two different distributions, like a beta and a normal (pick another pair!))

* What distributions did you choose? Report appropriate parameters.
* Simulation (R code)
* Summarize your results. How do the methods compare?
* How do your findings match your expectations?

We chose to use a Normal distribution and Gamma distribution. The Normal distribution has a mean of 40 and a standard deviation of 3. The Gamma distribution has a shape of 8 and a rate of 2.

```{r}
set.seed(1)

reps <- 10000
n <- 15

r_pvals <- rep(0, reps)
tau_pvals <- rep(0, reps)

for(i in 1: reps) {
  x <- rnorm(n, 40, 3)
  y <- rgamma(n, 8, 2)

  values <- data.frame(x,y)

  r_pvals[i] <- with(values, cor.test(x, y))$p.value
  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
}

sum(r_pvals <= 0.05)/reps
sum(tau_pvals <= 0.05)/reps

```

It appears that Pearson's $r$ rejects the null in 4.63% of the correlation tests and Kendall's tau rejects the null in 4.36% of the correlation tests. These are similar rejection rates which means that both of the methods perform in similar manners for independent observations from two different distributions. The findings match our expectations because we expected both of the methods to fail to reject a large number of the null hypotheses and that's what occurred.

### Bivariate Normal with Moderate Correlation

* What correlation did you choose? (i.e. Report appropriate parameters)
* Simulation (R code)
* Summarize your results. How do the methods compare?
* How do your findings match your expectations?

Since we used a covariance matrix of $\begin{bmatrix}
1&0.4\\
0.4&1
\end{bmatrix}$ we have a moderate correlation of 0.4.

```{r}
set.seed(1)

reps <- 10000
n <- 15

r_pvals <- rep(0, reps)
tau_pvals <- rep(0, reps)

for(i in 1: reps) {

  b <- rmvnorm(n, mean = c(0,1), sigma = matrix(c(1, 0.4, 0.4, 1), nrow = 2)) #correlation of 0.4
  values <- data.frame(b)

  r_pvals[i] <- with(values, cor.test(X1, X2))$p.value
  tau_pvals[i] <- with(values, cor.test(X1, X2, method = "kendall"))$p.value
}

sum(r_pvals <= 0.05)/reps
sum(tau_pvals <= 0.05)/reps

```

It appears that the Pearson's $r$ rejects the null hypotheses in 33.18% of the correlation tests while Kendall's tau rejects the null in 26.8% of the cases. Pearson's $r$ performs better because we know that there is a moderate correlation between the two variables.. It seems that Pearson's $r$ performs better than Kendall's tau with this distribution. This matches what our prediction was for this distribution. A larger amount of tests rejected the null hypothesis that the true correlation is 0.

### Double Exponential with Moderate Correlation

* What correlation (or covariance) did you choose? (i.e. Report appropriate parameters)
* Simulation (R code)
* Summarize your results. How do the methods compare?
* How do your findings match your expectations?

Since we used a covariance matrix of $\begin{bmatrix}
1&0.4\\
0.4&1
\end{bmatrix}$ we have a moderate correlation of 0.4.

```{r}
set.seed(1)

reps <- 10000
n <- 15

r_pvals <- rep(0, reps)
tau_pvals <- rep(0, reps)

for(i in 1: reps) {

  b <- rmvl(15, c(0,1), matrix(c(1, 0.4, 0.4, 1), nrow = 2)) #correlation of 0.4
  values <- data.frame(b)

  r_pvals[i] <- with(values, cor.test(X1, X2))$p.value
  tau_pvals[i] <- with(values, cor.test(X1, X2, method = "kendall"))$p.value
}

sum(r_pvals <= 0.05)/reps
sum(tau_pvals <= 0.05)/reps

```

The Pearson's $r$ rejects the null in 37.78% of the correlation tests while Kendall's tau rejects the null in 29.1% of the cases. Pearson's $r$ performs better because we know there is a moderate correlation between the two variables. As well as before, Pearson's $r$ performs better than Kendall's tau. This matches what our prediction was for this distribution.

### Conclusion

* Sum up what you found.
* What takeaway would you want a reader to get from your submission?

Overall, in the simulation of variables from independent distributions, Pearson's $p$ and Kendall's tau performed similarly in rejecting the null hypothesis, however for the next two simulations where there was a known moderate correlation, Pearson's $p$ outperformed Kendall's tau in rejecting the null hypothesis that the true correlation between the variables is 0.

### 2022-11-17 homework/hmk8/hmk8Stat495F22.Rmd
Finish hw 8

@@
 ### Intro and Simulation Overview
-
-* What is the task, as you understand it?
-* What do you plan to do for your simulation (generally speaking) to compare the performance of the methods?
-* Some questions to consider answering: Are you storing correlation values?
-p-values?
-Storing nothing?
-How many runs are you doing?
-Is a single run sufficient?
-What seems reasonable?
-What will you compare to assess the performance of the methods?
-* You should aim to convey the general structure of your simulation in a paragraph or two, so that a reader can follow along, and could think about pseudocode steps based on your description. 
-* What do you expect to happen in the simulations?
-There are three settings.
-Describe what you expect to happen in each setting.
-You can check this with your simulations, but you should be able to make some predictions based on your statistical background knowledge.
-
 The task of the simulation is to compare how Kendall's tau and Pearson's $r$ perform in terms of identifying significant relationships between two variables from varying distributions.
@@
 ### Independent Variables from Two Different Distributions
-
-* independent observations from two different distributions (your choice, but not say, two normals with different means; two different distributions, like a beta and a normal (pick another pair!))
-
-* What distributions did you choose? Report appropriate parameters.
-* Simulation (R code)
-* Summarize your results. How do the methods compare?
-* How do your findings match your expectations?
-
 We chose to use a Normal distribution and Gamma distribution. The Normal distribution has a mean of 40 and a standard deviation of 3. The Gamma distribution has a shape of 8 and a rate of 2.
@@
 The findings match our expectations because we expected both of the methods to fail to reject a large number of the null hypotheses and that's what occurred.
+The ~4% of tests that were rejected are due to the randomness of selecting from the distributions.
 
 ### Bivariate Normal with Moderate Correlation
-
-* What correlation did you choose? (i.e. Report appropriate parameters)
-* Simulation (R code)
-* Summarize your results. How do the methods compare?
-* How do your findings match your expectations?
-
 Since we used a covariance matrix of $\begin{bmatrix}
@@
 
-  b <- rmvnorm(n, mean = c(0,1), sigma = matrix(c(1, 0.4, 0.4, 1), nrow = 2)) #correlation of 0.4
+  b <- rmvnorm(n, mean = c(0,0), sigma = matrix(c(1, 0.4, 0.4, 1), nrow = 2)) #correlation of 0.4
   values <- data.frame(b)
@@
 ### Double Exponential with Moderate Correlation
-
-* What correlation (or covariance) did you choose? (i.e. Report appropriate parameters)
-* Simulation (R code)
-* Summarize your results. How do the methods compare?
-* How do your findings match your expectations?
-
 Since we used a covariance matrix of $\begin{bmatrix}
@@
 ### Conclusion
-
-* Sum up what you found.
-* What takeaway would you want a reader to get from your submission?
-
 Overall, in the simulation of variables from independent distributions, Pearson's $p$ and Kendall's tau performed similarly in rejecting the null hypothesis, however for the next two simulations where there was a known moderate correlation, Pearson's $p$ outperformed Kendall's tau in rejecting the null hypothesis that the true correlation between the variables is 0.
+This means that Pearson's $r$ is more useful in determining the correlation in distributions that have a known correlation (such as bivariate and double exponential).

### 2022-11-17 project/PaperTemplate/paper.Rmd
Add some files
Edit on paper

--- 2022-11-09 project/PaperTemplate/test.Rmd
@@
 authors: 
-- name: XX YOUR NAME HERE XX
+- name: Justin Papagelis
   thanks: The authors gratefully acknowledge ...
@@
 abstract: |
-  The text of your abstract.
-200 or fewer words.
-It is intended to provide an overview of your paper and may be similar to your synopsis.
-Note that an abstract can only include one paragraph in this format.
-You may want to put your synopsis here as you work to refer to it easily.
+  For my project, I plan to explore different bootstrap methods for creating confidence intervals and then perform comparisons between a couple of the methods.
+My paper will re-introduce the idea of bootstrap to my peers and give some background on constructing confidence intervals.
+We will also go deeper into the theory behind the construction of confidence intervals from bootstrapped data.
+These various methods to create a confidence interval from a bootstrap can include the percentile method, bias-corrected method, accelerated method, and the studentized method, as well as others.
+I will demonstrate how these bootstrap methods work using “toy examples,” which will be datasets in which a specific bootstrap method is appropriate.
+To demonstrate my understanding of the methods, I will write a simulation to compare a few of them and determine how they perform against each other.
+I will show my understanding of the different methods of creating confidence intervals from bootstrapped data by communicating the statistical theory in a concise and accessible way to my peers.
+Writing the simulation and sharing conclusions will demonstrate my ability to implement statistical methods in practice as well as my ability to analyze the results of the simulation.
 
@@
 This template was adapted from the template Prof. Horton provided Stat 495 in Fall 2021, used with permission.
+
+# Exposition
+
+The portion of the paper where you describe the new technique as though you were teaching it to a classmate (with whatever name you want to give it - Literature, Background, or Exposition) will be based on your annotated bibliography.
+You can add sources to what you already have in the annotated bibliography (especially if my feedback says you need to!).
+To be sure that you are on track with the exposition, a full draft of this portion of the paper is due before Thanksgiving break.
+This will also help with incorporating proper citation early in the writing process, as you’ll have a bibliography that we can implement for this portion of the paper at a minimum.
+
+Exposition
+-> what is a bootstrap
+--> parametric
+--> non-parametric
+--> briefly: what is jackknife
+--> SE and bias?
+-> what is a bootstrapped confidence interval
+--> what can it do
+-> how do we create them
+-> different types of bootstrapped CI
+--> standard t interval, approx classical, swapped SE, percentile, Bias-corrected, BCa
+---> for sample mean or corr (check example sheet)
+
+Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution.
+Supposing we have a random sample $X = (x_1,x_2,\dots,x_n)$, then the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$.
+From this bootstrap sample, a bootstrap replication of the test statistic can be computed.
 

### 2022-11-17 project/PaperTemplate/paper.tex
Created copy of test paper
Edit on paper

--- 2022-11-09 project/PaperTemplate/test.tex
@@
   \author{
-        XX YOUR NAME HERE XX \thanks{The authors gratefully acknowledge
+        Justin Papagelis \thanks{The authors gratefully acknowledge
 \ldots{}} \\
@@
 \begin{abstract}
-The text of your abstract. 200 or fewer words. It is intended to provide
-an overview of your paper and may be similar to your synopsis. Note that
-an abstract can only include one paragraph in this format. You may want
-to put your synopsis here as you work to refer to it easily.
+For my project, I plan to explore different bootstrap methods for
+creating confidence intervals and then perform comparisons between a
+couple of the methods. My paper will re-introduce the idea of bootstrap
+to my peers and give some background on constructing confidence
+intervals. We will also go deeper into the theory behind the
+construction of confidence intervals from bootstrapped data. These
+various methods to create a confidence interval from a bootstrap can
+include the percentile method, bias-corrected method, accelerated
+method, and the studentized method, as well as others. I will
+demonstrate how these bootstrap methods work using ``toy examples,''
+which will be datasets in which a specific bootstrap method is
+appropriate. To demonstrate my understanding of the methods, I will
+write a simulation to compare a few of them and determine how they
+perform against each other. I will show my understanding of the
+different methods of creating confidence intervals from bootstrapped
+data by communicating the statistical theory in a concise and accessible
+way to my peers. Writing the simulation and sharing conclusions will
+demonstrate my ability to implement statistical methods in practice as
+well as my ability to analyze the results of the simulation.
 \end{abstract}
@@
 \centering
-\includegraphics{test_files/figure-latex/sample-fig1-1.pdf}
+\includegraphics{paper_files/figure-latex/sample-fig1-1.pdf}
 \caption{\label{fig:sample-fig1}This is a sample figure caption that

### 2022-11-17 project/PaperTemplate/paper.Rmd
Almost done w percentile method

@@
 --> non-parametric
---> briefly: what is jackknife
+--> briefly: what is jackknife nah
 --> SE and bias?
@@
 Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution.
-Supposing we have a random sample $X = (x_1,x_2,\dots,x_n)$, then the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$.
-From this bootstrap sample, a bootstrap replication of the test statistic can be computed.
+In particular, bootstrapping is a computational heavy method which is useful for many different situations.
+
+First, we will introduce the non-parametric bootstrap.
+Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$.
+Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$.
+However $F$ is unknown so this is not possible.
+The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample $X$ without making any parametric assumptions (such as distribution).
+Therefore, the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$.
+From this bootstrap sample, a bootstrap replication of the test statistic can be computed using $\hat{\theta}^* = \hat{\theta}(X^*)$.
+A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated.
+$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$.
+The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications.
+As $B$ increases, $\hat{F}$ approaches $F$ which means that the tests statistic of interest approaches its true value as well.
+
+SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP
+
+Confidence intervals are tools that are used to estimate a parameter.
+Specifically, a confidence interval gives a range in which the true value of the parameter may lie.
+An $\alpha$-level standard confidence interval is given by $$\hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation.
+We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.
+
+The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal.
+This means that for an unknown distribution, the standard confidence interval could present an unmeaningful range.
+However, the same process can be used with bootstrap sampling to form the bootstrap percentile method.
 

### 2022-11-17 project/PaperTemplate/paper.tex
Almost done w percentile method

@@
 495 in Fall 2021, used with permission.
+
+\hypertarget{exposition}{%
+\section{Exposition}\label{exposition}}
+
+The portion of the paper where you describe the new technique as though
+you were teaching it to a classmate (with whatever name you want to give
+it - Literature, Background, or Exposition) will be based on your
+annotated bibliography. You can add sources to what you already have in
+the annotated bibliography (especially if my feedback says you need
+to!). To be sure that you are on track with the exposition, a full draft
+of this portion of the paper is due before Thanksgiving break. This will
+also help with incorporating proper citation early in the writing
+process, as you'll have a bibliography that we can implement for this
+portion of the paper at a minimum.
+
+Exposition -\textgreater{} what is a bootstrap --\textgreater{}
+parametric --\textgreater{} non-parametric --\textgreater{} briefly:
+what is jackknife nah --\textgreater{} SE and bias? -\textgreater{} what
+is a bootstrapped confidence interval --\textgreater{} what can it do
+-\textgreater{} how do we create them -\textgreater{} different types of
+bootstrapped CI --\textgreater{} standard t interval, approx classical,
+swapped SE, percentile, Bias-corrected, BCa ---\textgreater{} for sample
+mean or corr (check example sheet)
+
+Bootstrapping is a statistical method of resampling that allows the
+estimation of a test statistic from an unknown distribution. In
+particular, bootstrapping is a computational heavy method which is
+useful for many different situations.
+
+First, we will introduce the non-parametric bootstrap. Suppose we have a
+random sample \(X = (x_1,x_2,\dots,x_n)\) from our unknown distribution,
+\(F\) and a statistic of interest \(\hat{\theta} = \hat{\theta}(X)\).
+Ideally, the desired test statistic could be found by repeatedly
+sampling new reproductions of \(X\) from \(F\). However \(F\) is unknown
+so this is not possible. The non-parametric bootstrap creates an
+estimate \(\hat{F}\) from \(F\) using our sample \(X\) without making
+any parametric assumptions (such as distribution). Therefore, the
+bootstrap sample could be represented as
+\(X^* = (x^*_1, x^*_2, \dots, x^*_n)\) where each \(x^*_i\) is sampled
+randomly with equal probability and with replacement from
+\(\{x_1,x_2,\dots,x_n\}\). From this bootstrap sample, a bootstrap
+replication of the test statistic can be computed using
+\(\hat{\theta}^* = \hat{\theta}(X^*)\). A large number, \(B\), of
+bootstrap samples are drawn independently and the corresponding
+bootstrap replication of the test statistic is calculated.
+\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B\].
+The bootstrap estimate of the test statistic is the empirical value of
+the test statistic from all of the \(\hat{\theta}^{*b}\) replications.
+As \(B\) increases, \(\hat{F}\) approaches \(F\) which means that the
+tests statistic of interest approaches its true value as well.
+
+SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP
+
+Confidence intervals are tools that are used to estimate a parameter.
+Specifically, a confidence interval gives a range in which the true
+value of the parameter may lie. An \(\alpha\)-level standard confidence
+interval is given by \[\hat{\theta} \pm z_{\alpha}\hat{\sigma}\] where
+\(\hat{\theta}\) is a point estimate of the parameter of interest
+\(\theta\), \(\hat{\sigma}\) is the estimate of the standard deviation
+of \(\hat{\theta}\) and \(z_{\alpha}\) is the \((100 *\alpha)\)th
+percentile of the normal deviation. We say that the confidence interval
+constructed in this manner has a chance of capturing the true parameter
+with a probability of \(\alpha\).
+
+The standard confidence interval is built based on the assumption that
+the distribution from which we are sampling is Normal. This means that
+for an unknown distribution, the standard confidence interval could
+present an unmeaningful range. However, the same process can be used
+with bootstrap sampling to form the bootstrap percentile method.
 

### 2022-11-17 project/PaperTemplate/paper.Rmd
Finished percentile method section.

@@
 The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal.
-This means that for an unknown distribution, the standard confidence interval could present an unmeaningful range.
+This means that for an unknown distribution, the standard confidence interval could present an incorrect range.
 However, the same process can be used with bootstrap sampling to form the bootstrap percentile method.
+This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created.
+
+The percentile method interval is defined as the interval between the $100 * \alpha$ and the $100(1 - \alpha)$ percentiles of the bootstrap distribution of $\hat{\theta}$.
+That is, the $(1 - 2\alpha)$ coverage interval can be defined as $$[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].$$ In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval.
+However, this is not usually the case.
+When the bootstrap distribution is non-normal, we can suppose that there exists, for all $\theta$, $$\hat{\phi} \sim N(\phi, \tau^2),$$ for some monotone transformation $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$, and $\tau$ is a constant.
+In other words, this transformation perfectly normalizes the distribution of $\hat{\theta}$.
+This transformation invariant can be applied to the bootstrap replications such that $$\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.$$ The corresponding percentiles of the distribution transform similarly, $\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )$.
+Or we can say that the $(1 - 2\alpha)$ percentile interval is $\hat{\phi} \pm \tau z_\alpha$ which can also be represented as  $[\hat{\phi}^*_\alpha,\hat{\phi}^*_{1-\alpha}]$.
+This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ Or $\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]$.
+Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$.
+This method assumes the existence of some monotone normalizing mapping $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$ and relies on that to create a correct interval.
+Since the process is automatic, we do not need to know the transformation itself, only that it exists.
+However, in some cases, no monotone normalizing mapping will exist.
 

### 2022-11-17 project/PaperTemplate/paper.tex
Finished percentile method section.

@@
 for an unknown distribution, the standard confidence interval could
-present an unmeaningful range. However, the same process can be used
-with bootstrap sampling to form the bootstrap percentile method.
+present an incorrect range. However, the same process can be used with
+bootstrap sampling to form the bootstrap percentile method. This means
+that an approximate bootstrap confidence interval will be created in the
+same automatic way that the standard confidence interval was created.
+
+The percentile method interval is defined as the interval between the
+\(100 * \alpha\) and the \(100(1 - \alpha)\) percentiles of the
+bootstrap distribution of \(\hat{\theta}\). That is, the
+\((1 - 2\alpha)\) coverage interval can be defined as
+\[[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].\] In the case that
+the bootstrap distribution of
+\(\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)\), the
+corresponding percentile interval would be equivalent to the standard
+interval. However, this is not usually the case. When the bootstrap
+distribution is non-normal, we can suppose that there exists, for all
+\(\theta\), \[\hat{\phi} \sim N(\phi, \tau^2),\] for some monotone
+transformation \(\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)\), and
+\(\tau\) is a constant. In other words, this transformation perfectly
+normalizes the distribution of \(\hat{\theta}\). This transformation
+invariant can be applied to the bootstrap replications such that
+\[\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.\]
+The corresponding percentiles of the distribution transform similarly,
+\(\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )\). Or
+we can say that the \((1 - 2\alpha)\) percentile interval is
+\(\hat{\phi} \pm \tau z_\alpha\) which can also be represented as
+\([\hat{\phi}^*_\alpha,\hat{\phi}^*_{1-\alpha}]\). This means that the
+interval on the \(\theta\) scale can be defined as
+\[\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).\] Or
+\(\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]\).
+Therefore, the percentile method produces a correct interval for
+\(\phi\) and due to the transformation invariance, also produces a
+correct percentile interval for \(\theta\). This method assumes the
+existence of some monotone normalizing mapping
+\(\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)\) and relies on that to
+create a correct interval. Since the process is automatic, we do not
+need to know the transformation itself, only that it exists. However, in
+some cases, no monotone normalizing mapping will exist.
 

### 2022-11-18 project/PaperTemplate/paper.Rmd
added BC and BCa

@@
 
-# Exposition
-
+what is exposition
 The portion of the paper where you describe the new technique as though you were teaching it to a classmate (with whatever name you want to give it - Literature, Background, or Exposition) will be based on your annotated bibliography.
@@
 
+\newpage
+# Exposition
 Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution.
@@
 A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated.
-$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$.
-The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications.
+$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B.$$ The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications.
 As $B$ increases, $\hat{F}$ approaches $F$ which means that the tests statistic of interest approaches its true value as well.
@@
 Specifically, a confidence interval gives a range in which the true value of the parameter may lie.
-An $\alpha$-level standard confidence interval is given by $$\hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation.
+An $\alpha$-level standard confidence interval is given by $$\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation.
 We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.
@@
 This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created.
+For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy.
 
 The percentile method interval is defined as the interval between the $100 * \alpha$ and the $100(1 - \alpha)$ percentiles of the bootstrap distribution of $\hat{\theta}$.
-That is, the $(1 - 2\alpha)$ coverage interval can be defined as $$[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].$$ In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval.
+That is, the $(1 - 2\alpha)$ coverage interval can be defined as $[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].$ To go further, we can say define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$.
+$$\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}$$ Thus the $\alpha$th percentile point of the distribution is given by $$\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).$$
+
+It follows that the percentile interval can be represented as $$\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].$$
+
+In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval.
 However, this is not usually the case.
@@
 However, in some cases, no monotone normalizing mapping will exist.
+
+The next method we will be looking at is the bias-corrected percentile method (BC method) which is an improvement upon the previous percentile method because we now take into account the possibility of bias.
+It can be shown (SHOULD I SHOW LATER?) that $\hat{\theta}$ is biased upwards relative to $\theta$ which means that the confidence intervals should be adjusted downwards.
+From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B}$, define $p_0 = = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}$, and define the bias-correction value $z_0 = \Phi^{-1}(p_0)$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
+Thus we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $\hat{\phi} \sim N(\phi - z_0\tau, \tau^2)$, with $z_0$ and $\tau$ constants.
+This means that we can say the bias corrected method has an $\alpha$-level endpoint can be represented as
+
+$$\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].$$ If $\hat{G} = 0.50$, then half of the bootstrap distribution is less than $\hat{\theta}$ and our bias-correction value $z_0 = 0$.
+In this case, the confidence interval produced by BC would be the same interval produced by the percentile method.
+
+A further modification upon the BC interval is the bias corrected and accelerated method (BCa).
+For this method, we do assume the the standard error, $\tau$ to be constant as we did in the BC interval.
+Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2)$ where $\tau_\phi = 1+ a\phi$.
+The $a$ in known as the acceleration value and is a constant that describes how the standard deviation of $\hat{\phi}$ varies with $\phi$.
+In other words, $a$ is proportional to the skewness of the bootstrap distribution.
+For example, for one-parameter exponential families, $a=z_0$, however, there are many different algorithms to compute and estimate $a$.
+Now, our $\alpha$-level endpoint from BCa is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ If $a = 0$, then $\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].$ When calculating a BCa interval, the acceleration value $a$ is not a function of the bootstrap distribution and must be calculated separate, however the process is algorithmic and can be calculated without too much work.
+Each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, however computation increases as we loosen assumptions.
 

### 2022-11-18 project/PaperTemplate/paper.tex
added BC and BCa

@@
 same automatic way that the standard confidence interval was created.
+For bootstrapped confidence intervals, the number of bootstrap
+replications \(B\) must be large (around 2000) due to the nature of
+confidence intervals requiring greater accuracy.
 
@@
 \((1 - 2\alpha)\) coverage interval can be defined as
-\[[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].\] In the case that
-the bootstrap distribution of
+\([\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].\) To go further, we
+can say define \(\hat{G}(t)\) as the bootstrap cdf, or the proportion of
+bootstrap samples less than \(t\).
+\[\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}\] Thus the
+\(\alpha\)th percentile point of the distribution is given by
+\[\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).\]
+
+It follows that the percentile interval can be represented as
+\[\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].\]
+
+In the case that the bootstrap distribution of
 \(\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)\), the
@@
 some cases, no monotone normalizing mapping will exist.
+
+The next method we will be looking at is the bias-corrected percentile
+method (BC method) which is an improvement upon the previous percentile
+method because we now take into account the possibility of bias. It can
+be shown (SHOULD I SHOW LATER?) that \(\hat{\theta}\) is biased upwards
+relative to \(\theta\) which means that the confidence intervals should
+be adjusted downwards. From our simulated bootstrap replications
+\(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B}\),
+define \(p_0 = = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}\), and
+define the bias-correction value \(z_0 = \Phi^{-1}(p_0)\) where
+\(\Phi^{-1}\) is the inverse function of the standard normal cdf. Thus
+we define a transformation
+\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
+any \(\theta\), \(\hat{\phi} \sim N(\phi - z_0\tau, \tau^2)\), with
+\(z_0\) and \(\tau\) constants. This means that we can say the bias
+corrected method has an \(\alpha\)-level endpoint can be represented as
+
+\[\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].\]
+If \(\hat{G} = 0.50\), then half of the bootstrap distribution is less
+than \(\hat{\theta}\) and our bias-correction value \(z_0 = 0\). In this
+case, the confidence interval produced by BC would be the same interval
+produced by the percentile method.
+
+A further modification upon the BC interval is the bias corrected and
+accelerated method (BCa). For this method, we do assume the the standard
+error, \(\tau\) to be constant as we did in the BC interval. Rather, we
+assume the existence of a monotone transformation
+\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
+any \(\theta\), \(\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2)\)
+where \(\tau_\phi = 1+ a\phi\). The \(a\) in known as the acceleration
+value and is a constant that describes how the standard deviation of
+\(\hat{\phi}\) varies with \(\phi\). In other words, \(a\) is
+proportional to the skewness of the bootstrap distribution. For example,
+for one-parameter exponential families, \(a=z_0\), however, there are
+many different algorithms to compute and estimate \(a\). Now, our
+\(\alpha\)-level endpoint from BCa is
+\[\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].\]
+If \(a = 0\), then
+\(\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].\) When
+calculating a BCa interval, the acceleration value \(a\) is not a
+function of the bootstrap distribution and must be calculated separate,
+however the process is algorithmic and can be calculated without too
+much work. Each of the three previous methods (percentile, BC, and BCa)
+all build upon each other and have less restrictive assumptions, however
+computation increases as we loosen assumptions.
 

### 2022-11-19 project/PaperTemplate/paper.Rmd
Finished first draft of exposition

--- 2022-11-17 project/PaperTemplate/paper.Rmd
@@
 ---
-title: Title here
+title: A Comparision of Bootstrap Methods
 
@@
 # Introduction
-
-This template will be used for you to submit your final project.
-You'll need to install the *rticles* package, make sure you have the agsm.bst file and bibliography.bib file, and the gfx folder and figure file in order to compile.
-If you make your own bibliography.bib file later, that's fine - change the name above to match your file name.
-You'll want the setup for the file to look the same in your repo as in the class repo, and then compile to asa_article when you knit.
-You should change the name of the file to something other than "test" though.
-Remember that if something goes wrong with the file, you can always look back at the class repo for the original files and their structure.
-
-This template was adapted from the template Prof. Horton provided Stat 495 in Fall 2021, used with permission.
+To be added later
 
 # Exposition
-
-The portion of the paper where you describe the new technique as though you were teaching it to a classmate (with whatever name you want to give it - Literature, Background, or Exposition) will be based on your annotated bibliography.
-You can add sources to what you already have in the annotated bibliography (especially if my feedback says you need to!).
-To be sure that you are on track with the exposition, a full draft of this portion of the paper is due before Thanksgiving break.
-This will also help with incorporating proper citation early in the writing process, as you’ll have a bibliography that we can implement for this portion of the paper at a minimum.
-
-Exposition
--> what is a bootstrap
---> parametric
---> non-parametric
---> briefly: what is jackknife nah
---> SE and bias?
--> what is a bootstrapped confidence interval
---> what can it do
--> how do we create them
--> different types of bootstrapped CI
---> standard t interval, approx classical, swapped SE, percentile, Bias-corrected, BCa
----> for sample mean or corr (check example sheet)
-
+## The Non-Parametric Bootstrap
 Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution. 
@@
 First, we will introduce the non-parametric bootstrap.
-Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$.
+Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$ [@EfronCasi]. 
 Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$.
@@
 A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated. 
-$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$.
+$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$ 
 The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications. 
@@
 
-SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP
+## Standard Confidence Interval
 
@@
 Specifically, a confidence interval gives a range in which the true value of the parameter may lie. 
-An $\alpha$-level standard confidence interval is given by $$\hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation.
+An $\alpha$-level standard confidence interval is given by $$\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation [@Efron86].
 We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.
@@
 This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created. 
+For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy.
+
+## The Percentile Method
 
 The percentile method interval is defined as the interval between the $100 * \alpha$ and the $100(1 - \alpha)$ percentiles of the bootstrap distribution of $\hat{\theta}$.
-That is, the $(1 - 2\alpha)$ coverage interval can be defined as $$[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].$$ In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval.
+That is, the $(1 - 2\alpha)$ coverage interval can be defined as $[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}]$ [@Efron86,@EfronCasi]. 
+To go further, we can say define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$. $$\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.$$ 
+Thus the $\alpha$th percentile point of the distribution is given by $$\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).$$ It follows that the percentile interval can be represented as $$\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].$$
+In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval. 
 However, this is not usually the case. 
@@
 In other words, this transformation perfectly normalizes the distribution of $\hat{\theta}$. 
-This transformation invariant can be applied to the bootstrap replications such that $$\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.$$ The corresponding percentiles of the distribution transform similarly, $\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )$.
+This transformation invariant can be applied to the bootstrap replications such that $$\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.$$
+The corresponding percentiles of the distribution transform similarly, $\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )$. 
 Or we can say that the $(1 - 2\alpha)$ percentile interval is $\hat{\phi} \pm \tau z_\alpha$ which can also be represented as $[\hat{\phi}^*_\alpha,\hat{\phi}^*_{1-\alpha}]$. 
-This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ Or $\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]$.
+This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ 
+This also can be represented as an interval, $$\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]$$. 
 Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$. 
@@
 
-# More on the template 
-\label{sec:template}
+## The Bias-Corrected (BC) Method
 
-This template demonstrates some of the basic LaTeX commands and syntax you'll need to know to use the `rticles` package to generate a readable report using R Markdown.
-Markdown allows various formatting and you can find formatting cheatsheets or guides online to assist as well.
-Here's an example with bullets and some advice:
+The next method we will be looking at is the bias-corrected percentile method (BC method) which is an improvement upon the previous percentile method because we now take into account the possibility of bias.
+It can be shown that $\hat{\theta}$ is biased upwards relative to $\theta$ which means that the confidence intervals should be adjusted downwards [@Efron86,@EfronCasi]. 
+From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}$$, and define the bias-correction value $$z_0 = \Phi^{-1}(p_0)$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
+Thus we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),$$ with $z_0$ and $\tau$ constants. 
+This means that we can say the bias corrected method has an $\alpha$-level endpoint can be represented as $$\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].$$ If $\hat{G} = 0.50$, then half of the bootstrap distribution is less than $\hat{\theta}$ and our bias-correction value $z_0 = 0$.
+In this case, the confidence interval produced by BC would be the same interval produced by the percentile method.
 
-* I would encourage you to look closely at this file and explore the various parts and pieces.
-* I would suggest that you format your Rmd file so that you have only one sentence per line.
-* It makes it *much* easier to see changes in your GitHub commits.
+## The Bias-Corrected and Accelerated (BCa) Method
 
-\section{Verifications}
-\label{sec:verify}
-This section will be just long enough to illustrate what a full page of text looks like, for margins and spacing.
+A further modification upon the BC interval is the bias corrected and accelerated method (BCa). 
+For this method, we do assume the the standard error, $\tau$ to be constant as we did in the BC interval [@Efron86,@EfronCasi]. 
+Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.$$
+The $a$ in known as the acceleration and is a constant that describes how the standard deviation of $\hat{\phi}$ varies with $\phi$. 
+In other words, $a$ is proportional to the skewness of the bootstrap distribution. 
+For example, for one-parameter exponential families, $a=z_0$, however, there are many different algorithms to compute and estimate $a$ [@Flowers18]. 
+Now, our $\alpha$-level endpoint from BCa is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ If $a = 0$, then $\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].$
+When calculating a BCa interval, the acceleration value $a$ is not a function of the bootstrap distribution and must be calculated separate, however the process is algorithmic and can be calculated without too much work.
+Each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, however computation increases as we loosen assumptions.
 
-Note that we can refer to sections (e.g., this is section \ref{sec:verify}, while the previous section was section \ref{sec:template}).
+## The Bootstrap-t (Studentized) Method
 
-Note that we should refer to work using the BibTeX system.
-Here we can reference papers by @Campbell02 and @Schubert13 through inline citations (see the `bibliography.bib` file for the reference database).
-
-More work that is relevant can also be cited in a traditional fashion [@Chi81,@Galyardt14mmm,@Galyardt12dis].
-
-Note that you can capitalize proper nouns in citations [@Campbell02] (again, see `bibliography.bib`).
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-__With this spacing we have 30 lines per page.__
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-# Examples
-
-Lots of things can be done in this template.
-
-```{r sample-table1}
-Violations %>%
-  select(dba, boro) %>%
-  unique() %>%
-  group_by(boro) %>%
-  summarize(count = n(), .groups = "drop") %>%
-  knitr::kable(
-    caption = "This is a sample table caption that should interpret the table!")
-```
-
-Table \ref{tab:sample-table1} displays the number of dba's per borough.
-
-```{r sample-fig1, fig.height = 3, fig.cap = "\\label{fig:sample-fig1}This is a sample figure caption that should interpret the figure!"}
-Violations %>%
-  select(dba, boro, inspection_date, score) %>%
-  unique() %>%
-  group_by(boro) %>%
-  summarize(
-    count = n(),
-    averagescore = mean(score, na.rm = TRUE),
-    .groups = "drop"
-  ) %>%
-  ggplot(aes(x = boro, y = averagescore)) +
-  geom_boxplot()
-```
-
-Figure \ref{fig:sample-fig1} displays the average inspection score by borough.
-
-Figure \ref{fig:sample-fig2} displays a campus map.
-
-```{r sample-fig2, echo=FALSE, out.width = "80%", fig.show='hold', fig.cap="XX another sample figure caption"}
-knitr::include_graphics("gfx/campus_map.png")
-```
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-The quick brown fox jumped over the lazy dog.
-
-# Your Choice of Structure
-
-You are responsible for choosing the structure you want for the report, i.e.
-what sections and their names.
-Here are some examples that you could adapt, as appropriate.
-These are just examples - the first has more sections, some of which may make more sense as sub-sections of others.
-I'm just trying to give you examples.
-You don't have to have a conclusion or an introduction, etc.
-You'll need to find what works for you.
-
-## Example 1
-
-* Introduction
-* Background
-* Topic X (Main exposition section)
-* Applications in Literature
-* Application to Data (your data)
-* Conclusion
-
-## Example 2
-
-* Introduction (including any relevant Background)
-* Topic X (exposition and examples)
-* Simulation
+The next method is the bootstrap-t interval (or the studentized method). 
+Recalling from earlier, our sample, $X$ from which we can calculate an estimate, $\hat{\theta}(X)$ of the parameter of interest $\theta$ [@Efron86,@Puth15]. 
+We can also estimate $\hat{\sigma}(X)$ for the standard error of $\theta$. 
+We can use these parameters to find the Student's $t$-statistic defined as $$T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.$$ 
+As such, the $\alpha$th percentile point of a confidence interval of $\theta$ would be $\hat{\theta} - \hat{\sigma}T_{(\alpha)}$ where $T_{(\alpha)}$ represents the $\alpha$th percentile of the $t$-distribution, $T$.
+Unfortunately, the percentiles of the t-distribution are unknown in most cases, but we can use bootstrapping to estimate these percentiles. 
+To do this, we perform a large number, $B$, of bootstrap samples, from which we can find the bootstrap replications of the parameter of interest, $\hat{\theta^*} = \hat{\theta}(X^*)$, and the standard error, $\hat{\sigma^*} = \hat{\sigma}(X^*)$.
+From these we can calculate a $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}$$ for each bootstrap sample.
+Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
+This means that for $B = 2000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
+It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)}$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
+Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistic.

### 2022-11-19 project/PaperTemplate/paper.tex
Finished first draft of exposition

@@
 %% load any required packages here
-
-% Pandoc syntax highlighting
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
@@
 {
-  \title{\bf Title here}
+  \title{\bf A Comparision of Bootstrap Methods}
 
@@
   \begin{center}
-    {\LARGE\bf Title here}
+    {\LARGE\bf A Comparision of Bootstrap Methods}
   \end{center}
@@
 
-This template will be used for you to submit your final project. You'll
-need to install the \emph{rticles} package, make sure you have the
-agsm.bst file and bibliography.bib file, and the gfx folder and figure
-file in order to compile. If you make your own bibliography.bib file
-later, that's fine - change the name above to match your file name.
-You'll want the setup for the file to look the same in your repo as in
-the class repo, and then compile to asa\_article when you knit. You
-should change the name of the file to something other than ``test''
-though. Remember that if something goes wrong with the file, you can
-always look back at the class repo for the original files and their
-structure.
-
-This template was adapted from the template Prof.~Horton provided Stat
-495 in Fall 2021, used with permission.
+To be added later
 
@@
 
-The portion of the paper where you describe the new technique as though
-you were teaching it to a classmate (with whatever name you want to give
-it - Literature, Background, or Exposition) will be based on your
-annotated bibliography. You can add sources to what you already have in
-the annotated bibliography (especially if my feedback says you need
-to!). To be sure that you are on track with the exposition, a full draft
-of this portion of the paper is due before Thanksgiving break. This will
-also help with incorporating proper citation early in the writing
-process, as you'll have a bibliography that we can implement for this
-portion of the paper at a minimum.
-
-Exposition -\textgreater{} what is a bootstrap --\textgreater{}
-parametric --\textgreater{} non-parametric --\textgreater{} briefly:
-what is jackknife nah --\textgreater{} SE and bias? -\textgreater{} what
-is a bootstrapped confidence interval --\textgreater{} what can it do
--\textgreater{} how do we create them -\textgreater{} different types of
-bootstrapped CI --\textgreater{} standard t interval, approx classical,
-swapped SE, percentile, Bias-corrected, BCa ---\textgreater{} for sample
-mean or corr (check example sheet)
+\hypertarget{the-non-parametric-bootstrap}{%
+\subsection{The Non-Parametric
+Bootstrap}\label{the-non-parametric-bootstrap}}
 
@@
 random sample \(X = (x_1,x_2,\dots,x_n)\) from our unknown distribution,
-\(F\) and a statistic of interest \(\hat{\theta} = \hat{\theta}(X)\).
-Ideally, the desired test statistic could be found by repeatedly
-sampling new reproductions of \(X\) from \(F\). However \(F\) is unknown
-so this is not possible. The non-parametric bootstrap creates an
-estimate \(\hat{F}\) from \(F\) using our sample \(X\) without making
+\(F\) and a statistic of interest \(\hat{\theta} = \hat{\theta}(X)\)
+\citep{EfronCasi}. Ideally, the desired test statistic could be found by
+repeatedly sampling new reproductions of \(X\) from \(F\). However \(F\)
+is unknown so this is not possible. The non-parametric bootstrap creates
+an estimate \(\hat{F}\) from \(F\) using our sample \(X\) without making
 any parametric assumptions (such as distribution). Therefore, the
@@
 bootstrap replication of the test statistic is calculated.
-\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B\].
+\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B\]
 The bootstrap estimate of the test statistic is the empirical value of
@@
 
-SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP
+\hypertarget{standard-confidence-interval}{%
+\subsection{Standard Confidence
+Interval}\label{standard-confidence-interval}}
 
@@
 value of the parameter may lie. An \(\alpha\)-level standard confidence
-interval is given by \[\hat{\theta} \pm z_{\alpha}\hat{\sigma}\] where
-\(\hat{\theta}\) is a point estimate of the parameter of interest
+interval is given by
+\[\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma}\]
+where \(\hat{\theta}\) is a point estimate of the parameter of interest
 \(\theta\), \(\hat{\sigma}\) is the estimate of the standard deviation
 of \(\hat{\theta}\) and \(z_{\alpha}\) is the \((100 *\alpha)\)th
-percentile of the normal deviation. We say that the confidence interval
-constructed in this manner has a chance of capturing the true parameter
-with a probability of \(\alpha\).
+percentile of the normal deviation \citep{Efron86}. We say that the
+confidence interval constructed in this manner has a chance of capturing
+the true parameter with a probability of \(\alpha\).
 
@@
 
+\hypertarget{the-percentile-method}{%
+\subsection{The Percentile Method}\label{the-percentile-method}}
+
 The percentile method interval is defined as the interval between the
@@
 \((1 - 2\alpha)\) coverage interval can be defined as
-\([\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].\) To go further, we
-can say define \(\hat{G}(t)\) as the bootstrap cdf, or the proportion of
-bootstrap samples less than \(t\).
-\[\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}\] Thus the
+\([\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}]\)
+\citep[\citet{EfronCasi}]{Efron86}. To go further, we can say define
+\(\hat{G}(t)\) as the bootstrap cdf, or the proportion of bootstrap
+samples less than \(t\).
+\[\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.\] Thus the
 \(\alpha\)th percentile point of the distribution is given by
 \[\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).\]
-
 It follows that the percentile interval can be represented as
-\[\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].\]
-
-In the case that the bootstrap distribution of
+\[\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].\] In the
+case that the bootstrap distribution of
 \(\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)\), the
@@
 interval on the \(\theta\) scale can be defined as
-\[\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).\] Or
-\(\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]\).
+\[\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).\] This
+also can be represented as an interval,
+\[\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]\].
 Therefore, the percentile method produces a correct interval for
@@
 
+\hypertarget{the-bias-corrected-bc-method}{%
+\subsection{The Bias-Corrected (BC)
+Method}\label{the-bias-corrected-bc-method}}
+
 The next method we will be looking at is the bias-corrected percentile
@@
 method because we now take into account the possibility of bias. It can
-be shown (SHOULD I SHOW LATER?) that \(\hat{\theta}\) is biased upwards
-relative to \(\theta\) which means that the confidence intervals should
-be adjusted downwards. From our simulated bootstrap replications
-\(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B}\),
-define \(p_0 = = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}\), and
-define the bias-correction value \(z_0 = \Phi^{-1}(p_0)\) where
+be shown that \(\hat{\theta}\) is biased upwards relative to \(\theta\)
+which means that the confidence intervals should be adjusted downwards
+\citep[\citet{EfronCasi}]{Efron86}. From our simulated bootstrap
+replications
+\(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},\)
+define \[p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}\], and
+define the bias-correction value \[z_0 = \Phi^{-1}(p_0)\] where
 \(\Phi^{-1}\) is the inverse function of the standard normal cdf. Thus
@@
 \(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
-any \(\theta\), \(\hat{\phi} \sim N(\phi - z_0\tau, \tau^2)\), with
+any \(\theta\), \[\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),\] with
 \(z_0\) and \(\tau\) constants. This means that we can say the bias
 corrected method has an \(\alpha\)-level endpoint can be represented as
-
 \[\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].\]
@@
 
+\hypertarget{the-bias-corrected-and-accelerated-bca-method}{%
+\subsection{The Bias-Corrected and Accelerated (BCa)
+Method}\label{the-bias-corrected-and-accelerated-bca-method}}
+
 A further modification upon the BC interval is the bias corrected and
 accelerated method (BCa). For this method, we do assume the the standard
-error, \(\tau\) to be constant as we did in the BC interval. Rather, we
-assume the existence of a monotone transformation
+error, \(\tau\) to be constant as we did in the BC interval
+\citep[\citet{EfronCasi}]{Efron86}. Rather, we assume the existence of a
+monotone transformation
 \(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
-any \(\theta\), \(\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2)\)
-where \(\tau_\phi = 1+ a\phi\). The \(a\) in known as the acceleration
-value and is a constant that describes how the standard deviation of
-\(\hat{\phi}\) varies with \(\phi\). In other words, \(a\) is
-proportional to the skewness of the bootstrap distribution. For example,
-for one-parameter exponential families, \(a=z_0\), however, there are
-many different algorithms to compute and estimate \(a\). Now, our
-\(\alpha\)-level endpoint from BCa is
+any \(\theta\),
+\[\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.\]
+The \(a\) in known as the acceleration and is a constant that describes
+how the standard deviation of \(\hat{\phi}\) varies with \(\phi\). In
+other words, \(a\) is proportional to the skewness of the bootstrap
+distribution. For example, for one-parameter exponential families,
+\(a=z_0\), however, there are many different algorithms to compute and
+estimate \(a\) \citep{Flowers18}. Now, our \(\alpha\)-level endpoint
+from BCa is
 \[\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].\]
@@
 
-\hypertarget{more-on-the-template}{%
-\section{More on the template}\label{more-on-the-template}}
+\hypertarget{the-bootstrap-t-studentized-method}{%
+\subsection{The Bootstrap-t (Studentized)
+Method}\label{the-bootstrap-t-studentized-method}}
 
-\label{sec:template}
-
-This template demonstrates some of the basic LaTeX commands and syntax
-you'll need to know to use the \texttt{rticles} package to generate a
-readable report using R Markdown. Markdown allows various formatting and
-you can find formatting cheatsheets or guides online to assist as well.
-Here's an example with bullets and some advice:
-
-\begin{itemize}
-\tightlist
-\item
-  I would encourage you to look closely at this file and explore the
-  various parts and pieces.
-\item
-  I would suggest that you format your Rmd file so that you have only
-  one sentence per line.
-\item
-  It makes it \emph{much} easier to see changes in your GitHub commits.
-\end{itemize}
-
-\section{Verifications}
-\label{sec:verify}
-
-This section will be just long enough to illustrate what a full page of
-text looks like, for margins and spacing.
-
-Note that we can refer to sections (e.g., this is section
-\ref{sec:verify}, while the previous section was section
-\ref{sec:template}).
-
-Note that we should refer to work using the BibTeX system. Here we can
-reference papers by \citet{Campbell02} and \citet{Schubert13} through
-inline citations (see the \texttt{bibliography.bib} file for the
-reference database).
-
-More work that is relevant can also be cited in a traditional fashion
-\citep[\citet{Galyardt14mmm},\citet{Galyardt12dis}]{Chi81}.
-
-Note that you can capitalize proper nouns in citations
-\citep{Campbell02} (again, see \texttt{bibliography.bib}).
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. \textbf{With this spacing we
-have 30 lines per page.}
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-\hypertarget{examples}{%
-\section{Examples}\label{examples}}
-
-Lots of things can be done in this template.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{Violations }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{select}\NormalTok{(dba, boro) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{unique}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(boro) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{(), }\AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-\NormalTok{  knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}
-    \AttributeTok{caption =} \StringTok{"This is a sample table caption that should interpret the table!"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}
-
-\caption{\label{tab:sample-table1}This is a sample table caption that should interpret the table!}
-\centering
-\begin{tabular}[t]{l|r}
-\hline
-boro & count\\
-\hline
-BRONX & 1903\\
-\hline
-BROOKLYN & 5294\\
-\hline
-MANHATTAN & 8340\\
-\hline
-Missing & 6\\
-\hline
-QUEENS & 4789\\
-\hline
-STATEN ISLAND & 802\\
-\hline
-\end{tabular}
-\end{table}
-
-Table \ref{tab:sample-table1} displays the number of dba's per borough.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{Violations }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{select}\NormalTok{(dba, boro, inspection\_date, score) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{unique}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(boro) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}
-    \AttributeTok{count =} \FunctionTok{n}\NormalTok{(),}
-    \AttributeTok{averagescore =} \FunctionTok{mean}\NormalTok{(score, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{),}
-    \AttributeTok{.groups =} \StringTok{"drop"}
-\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ boro, }\AttributeTok{y =}\NormalTok{ averagescore)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_boxplot}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/sample-fig1-1.pdf}
-\caption{\label{fig:sample-fig1}This is a sample figure caption that
-should interpret the figure!}
-\end{figure}
-
-Figure \ref{fig:sample-fig1} displays the average inspection score by
-borough.
-
-Figure \ref{fig:sample-fig2} displays a campus map.
-
-\begin{figure}
-\includegraphics[width=0.8\linewidth]{gfx/campus_map} \caption{XX another sample figure caption}\label{fig:sample-fig2}
-\end{figure}
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped
-over the lazy dog. The quick brown fox jumped over the lazy dog. The
-quick brown fox jumped over the lazy dog.
-
-\hypertarget{your-choice-of-structure}{%
-\section{Your Choice of Structure}\label{your-choice-of-structure}}
-
-You are responsible for choosing the structure you want for the report,
-i.e.~what sections and their names. Here are some examples that you
-could adapt, as appropriate. These are just examples - the first has
-more sections, some of which may make more sense as sub-sections of
-others. I'm just trying to give you examples. You don't have to have a
-conclusion or an introduction, etc. You'll need to find what works for
-you.
-
-\hypertarget{example-1}{%
-\subsection{Example 1}\label{example-1}}
-
-\begin{itemize}
-\tightlist
-\item
-  Introduction
-\item
-  Background
-\item
-  Topic X (Main exposition section)
-\item
-  Applications in Literature
-\item
-  Application to Data (your data)
-\item
-  Conclusion
-\end{itemize}
-
-\hypertarget{example-2}{%
-\subsection{Example 2}\label{example-2}}
-
-\begin{itemize}
-\tightlist
-\item
-  Introduction (including any relevant Background)
-\item
-  Topic X (exposition and examples)
-\item
-  Simulation
-\end{itemize}
+The next method is the bootstrap-t interval (or the studentized method).
+Recalling from earlier, our sample, \(X\) from which we can calculate an
+estimate, \(\hat{\theta}(X)\) of the parameter of interest \(\theta\)
+\citep[\citet{Puth15}]{Efron86}. We can also estimate
+\(\hat{\sigma}(X)\) for the standard error of \(\theta\). We can use
+these parameters to find the Student's \(t\)-statistic defined as
+\[T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.\] As such, the
+\(\alpha\)th percentile point of a confidence interval of \(\theta\)
+would be \(\hat{\theta} - \hat{\sigma}T_{(\alpha)}\) where
+\(T_{(\alpha)}\) represents the \(\alpha\)th percentile of the
+\(t\)-distribution, \(T\). Unfortunately, the percentiles of the
+t-distribution are unknown in most cases, but we can use bootstrapping
+to estimate these percentiles. To do this, we perform a large number,
+\(B\), of bootstrap samples, from which we can find the bootstrap
+replications of the parameter of interest,
+\(\hat{\theta^*} = \hat{\theta}(X^*)\), and the standard error,
+\(\hat{\sigma^*} = \hat{\sigma}(X^*)\). From these we can calculate a
+\[T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}\] for each
+bootstrap sample. Using a large number of these bootstrap samples, we
+can estimate the percentiles of the \(t\)-distribution such that
+\[\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.\]
+This means that for \(B = 2000\) and \(\alpha = 0.90\), then
+\(\hat{T}_{(\alpha)}\) is the 1,800th ordered point of all of the
+bootstrap replications of \(T^*\). It follows that the \(\alpha\)th
+studentized confidence interval endpoint can be given with
+\[\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)}\]
+where we can estimate the standard error using
+\[\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.\] One of the main
+factors why the studentized method is so popular is because we assume
+that our bootstrapped statistic is pivotal which means that the
+confidence interval does not depend on any other parameters. Instead, we
+can calculate the appropriate confidence interval for the parameter of
+interest specifically from the bootstrapped statistic.
 

### 2022-11-29 project/PaperTemplate/paper.Rmd
Modifications to exposition and starting simulation

@@
 
-First, we will introduce the non-parametric bootstrap.
+First, we introduce the non-parametric bootstrap.
 Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$ [@EfronCasi]. 
 Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$.
-However $F$ is unknown so this is not possible. 
-The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample $X$ without making any parametric assumptions (such as distribution). 
+However $F$ is unknown, so this is not possible. 
+The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample $X$ without making any parametric assumptions about $F$ (such as its distribution type). 
 Therefore, the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$.
@@
 A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated. 
-$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$ 
+$$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B.$$ 
 The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications. 
-As $B$ increases, $\hat{F}$ approaches $F$ which means that the tests statistic of interest approaches its true value as well.
+As $B$ increases, $\hat{F}$ approaches $F$ which means that the test statistic of interest approaches its true value as well.
 
@@
 Confidence intervals are tools that are used to estimate a parameter. 
-Specifically, a confidence interval gives a range in which the true value of the parameter may lie. 
-An $\alpha$-level standard confidence interval is given by $$\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation [@Efron86].
+Specifically, a confidence interval gives a range of values in which the true value of the parameter may lie. 
+An $\alpha$-level standard confidence interval is given by $$\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma},$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation [@Efron86].
 We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.
@@
 This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created. 
-For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy.
+For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy [@Efron86].
 
@@
 That is, the $(1 - 2\alpha)$ coverage interval can be defined as $[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}]$ [@Efron86,@EfronCasi]. 
-To go further, we can say define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$. $$\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.$$ 
+To go further, we can define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$: $$\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.$$ 
 Thus the $\alpha$th percentile point of the distribution is given by $$\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).$$ It follows that the percentile interval can be represented as $$\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].$$
@@
 This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ 
-This also can be represented as an interval, $$\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]$$. 
-Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$. 
+This also can be represented as an interval, $$\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ].$$ Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$.
 This method assumes the existence of some monotone normalizing mapping $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$ and relies on that to create a correct interval.
 Since the process is automatic, we do not need to know the transformation itself, only that it exists. 
-However, in some cases, no monotone normalizing mapping will exist.
+However, in some cases, no monotone normalizing mapping will exist [@Efron86].
 
@@
 It can be shown that $\hat{\theta}$ is biased upwards relative to $\theta$ which means that the confidence intervals should be adjusted downwards [@Efron86,@EfronCasi]. 
-From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}$$, and define the bias-correction value $$z_0 = \Phi^{-1}(p_0)$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
-Thus we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),$$ with $z_0$ and $\tau$ constants. 
+From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B},$$ and define the bias-correction value $$z_0 = \Phi^{-1}(p_0),$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
+Thus we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),$$ with $z_0$ and $\tau$ constants. 
 This means that we can say the bias corrected method has an $\alpha$-level endpoint can be represented as $$\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].$$ If $\hat{G} = 0.50$, then half of the bootstrap distribution is less than $\hat{\theta}$ and our bias-correction value $z_0 = 0$.
@@
 A further modification upon the BC interval is the bias corrected and accelerated method (BCa). 
-For this method, we do assume the the standard error, $\tau$ to be constant as we did in the BC interval [@Efron86,@EfronCasi]. 
-Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.$$
-The $a$ in known as the acceleration and is a constant that describes how the standard deviation of $\hat{\phi}$ varies with $\phi$. 
+For this method, we do not assume the the standard error, $\tau$ is constant as we did in the BC interval [@Efron86,@EfronCasi]. 
+Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.$$
+The $a$ is known as the acceleration and is a constant that describes how the standard deviation of $\hat{\phi}$ varies with $\phi$. 
 In other words, $a$ is proportional to the skewness of the bootstrap distribution. 
@@
 Now, our $\alpha$-level endpoint from BCa is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ If $a = 0$, then $\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].$
-When calculating a BCa interval, the acceleration value $a$ is not a function of the bootstrap distribution and must be calculated separate, however the process is algorithmic and can be calculated without too much work.
+When calculating a BCa interval, the acceleration value $a$ is not a function of the bootstrap distribution and must be calculated separately, however the process is algorithmic and can be calculated without too much work.
 Each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, however computation increases as we loosen assumptions.
@@
 
-The next method is the bootstrap-t interval (or the studentized method). 
-Recalling from earlier, our sample, $X$ from which we can calculate an estimate, $\hat{\theta}(X)$ of the parameter of interest $\theta$ [@Efron86,@Puth15]. 
+The final method we explain is the bootstrap-t interval (or the studentized method). 
+Recall from earlier, our sample, $X$ from which we can calculate an estimate, $\hat{\theta}(X)$ of the parameter of interest $\theta$ [@Efron86,@Puth15]. 
 We can also estimate $\hat{\sigma}(X)$ for the standard error of $\theta$. 
@@
 To do this, we perform a large number, $B$, of bootstrap samples, from which we can find the bootstrap replications of the parameter of interest, $\hat{\theta^*} = \hat{\theta}(X^*)$, and the standard error, $\hat{\sigma^*} = \hat{\sigma}(X^*)$.
-From these we can calculate a $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}$$ for each bootstrap sample.
-Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
+From these we can calculate a t-statistic for each bootstrap sample: $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.$$ for each bootstrap sample.
+Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
 This means that for $B = 2000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
-It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)}$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
-Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistic.
+It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
+Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistic [@Efron86,@Puth15].
+
+# Simulation
+
+Justin,
+
+An example before a simulation could be useful if your simulation is assessing their performance (i.e.
+if your simulation is like Hmk 8, where you do a lot of reps to check performance).
+You could run anything on an existing data set (the one we have from Hmk 4/5), for example, that you want.
+I think you have enough without worrying about the parametric bootstrap.
+
+```{r}
+
+library(boot)
+set.seed(495)
+
+reps <- 2000
+n <- 50
+
+X <- rnorm(n, 0, 1)
+values <- data.frame(X)
+
+mean.fun <- function(d, i) {
+  d <- X[i]
+  return (mean(d))
+}
+
+results <- boot(data = values, statistic = mean.fun, R = reps)
+
+results
+
+plot(results)
+
+ci <- boot.ci(results, type = "all")
+
+```
+
+```{r}
+set.seed(1)
+
+reps <- 10000
+n <- 15
+
+r_pvals <- rep(0, reps)
+tau_pvals <- rep(0, reps)
+
+for(i in 1: reps) {
+  x <- rnorm(n, 40, 3)
+  y <- rgamma(n, 8, 2)
+
+  values <- data.frame(x,y)
+
+  r_pvals[i] <- with(values, cor.test(x, y))$p.value
+  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
+}
+
+sum(r_pvals <= 0.05)/reps
+sum(tau_pvals <= 0.05)/reps
+
+```
+
+```{r}
+simbootstraps <- function(dataset, trueparameter) {
+
+  # use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)
+  # like 2000 times
+
+  #use that bootstrap distribution as follows to test for the intervals
+
+  # see how many times the true value lies inside the interval --> first do one and then show the actual intervals
+
+}
+
+simnormal <- function(locationinput, scaleinput, testcenterinput, ninput, repsinput = 1000){
+# Set Useful Values
+reps <- repsinput #number of repetitions
+location <- locationinput 
+scale <- scaleinput
+testcenter <- testcenterinput #center to test for
+n <- ninput #sample size
+
+#Initialize storage vectors
+tpvals <- rep(0,reps)
+spvals <- rep(0,reps)
+srpvals <- rep(0,reps)
+
+#Generate random data, do tests, save p-values
+for(i in 1:reps){
+  x <- rnorm(n, location, scale)
+  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
+  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
+  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
+}
+
+output <- c(sum(tpvals <= 0.05)/reps, sum(spvals <= 0.05)/reps, sum(srpvals <= 0.05)/reps)
+names(output) <- c("Ttest", "Sign", "SignedRank")
+output
+}
+```
+
+```{r}
+set.seed(495)
+
+reps <- 10000
+n <- 15
+
+r_pvals <- rep(0, reps)
+tau_pvals <- rep(0, reps)
+
+for(i in 1: reps) {
+  y <- rgamma(n, 8, 2)
+
+  values <- data.frame(x,y)
+
+  r_pvals[i] <- with(values, cor.test(x, y))$p.value
+  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
+}
+
+sum(r_pvals <= 0.05)/reps
+sum(tau_pvals <= 0.05)/reps
+
+```

### 2022-11-30 project/PaperTemplate/paper.Rmd
Added the examples

@@
 library(kableExtra)
+library(boot)
 ```
@@
 
+We demonstrate performing a non-parametric bootstrap below using `SnowGR` which gives the official snowfall dataset by month for Grand Rapids, MI, starting in 1893.
+We will be using the `Dec` variable which gives the number of inches of snow that fell in December of each year.
+In particular, we are interested in the sample mean and later finding confidence intervals for population mean of `Dec`.
+The distribution is below.
+
+```{r}
+data(SnowGR)
+favstats(~ Dec, data = SnowGR)
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count")
+```
+
+Next, we will perform the non-parametric bootstrap using 10,000 replications.
+
+```{r}
+
+orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
+
+set.seed(495)
+nboot <- 10000
+
+mean <- rep(0,nboot)
+sd <- rep(0,nboot)
+se <- rep(0,nboot)
+t_stat <- rep(0,nboot)
+
+for (i in 1:nboot) {
+  resampled <- as.data.frame(mosaic::resample(SnowGR, replace = TRUE))
+  mean[i] <- mean(~Dec, data = resampled)
+  sd[i] <- sd(~Dec, data = resampled)
+ # se[i] <- sd[i]/nrow(resampled)
+#  t_stat[i] <- (mean[i] - orig_mean)/se[i]
+}
+
+dec_means <- as.data.frame(mean)
+#dec_t_stat <- as.data.frame(t_stat)
+
+```
+
+```{r}
+
+#set.seed(495)
+#dec_means <- do(10000)*mean(~ Dec, data = mosaic::resample(SnowGR, replace = TRUE))
+
+gf_dhistogram(~ mean, data = dec_means) %>%
+  gf_dens() %>%
+  gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values")
+```
+
 ## Standard Confidence Interval
@@
 For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy [@Efron86].
+
+Using our example, to find a 95% confidence interval for the population mean of `Dec`, we would get the following:
+
+```{r}
+mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
+```
+
+```{r}
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  geom_vline(aes(xintercept= 13.85639)) +
+  geom_vline(aes(xintercept= 17.65957))
+```
 
@@
 
+Finding a 95% confidence interval for the true population mean of `Dec` using the percentile method, we get:
+
+```{r}
+qdata(~ mean, c(0.025, 0.975), data = dec_means)
+```
+
+```{r}
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  geom_vline(aes(xintercept= 13.91170)) +
+  geom_vline(aes(xintercept= 17.72353))
+```
+This interval is similar to the one created using the Standard method, but shifted slightly to the right.
+
 ## The Bias-Corrected (BC) Method
@@
 In this case, the confidence interval produced by BC would be the same interval produced by the percentile method.
+
+Using this method to create a 95% confidence interval has a couple more steps because we need to find the bias-correction value. First we calculate the sample mean.
+
+```{r}
+sample_mean <- mean(~Dec, data = SnowGR); sample_mean
+```
+
+Then we find the proportion of bootstrap replications that have a sample mean less than the original sample mean.
+```{r}
+less_than_sample_mean <- sum(ifelse(dec_means <= sample_mean, 1, 0))/10000
+less_than_sample_mean
+```
+
+From this, we can calculate the bias-correction value, $z_0$:
+```{r}
+z0 <- qnorm(less_than_sample_mean); z0
+```
+
+Then we can find the modified percentiles:
+
+```{r}
+alphalow <- 0.025; alphahigh <- 0.975
+
+newlow <- pnorm(2*z0 + qnorm(alphalow)); #newlow
+newhigh <- pnorm(2*z0 + qnorm(alphahigh)); #newhigh
+
+qdata(~ mean, c(newlow, newhigh), data = dec_means)
+```
+
+```{r}
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  geom_vline(aes(xintercept= 14.01172)) +
+  geom_vline(aes(xintercept= 17.82017))
+
+```
 
@@
 Each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, however computation increases as we loosen assumptions.
+
+In practice, we can use the jackknife procedure to estimate the acceleration value for this method. Thus, we will run the jackknife procedure:
+
+```{r}
+theta <- function(x){mean(x)}
+jackknife_results <- bootstrap::jackknife(SnowGR$Dec, theta) 
+```
+
+We find the mean of the jackknife values below:
+
+```{r}
+jackmean <- mean(~ jackknife_results$jack.values); jackmean
+```
+
+Then we can compute $a$.
+
+```{r}
+estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
+  (sum((jackknife_results$jack.values - jackmean)^2))^(1.5); estimated_a
+```
+
+Now, we can find the adjust percentiles and the bias-corrected with acceleration confidence interval.
+
+```{r}
+a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
+a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
+qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
+```
+
+```{r}
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  geom_vline(aes(xintercept= 13.91591)) +
+  geom_vline(aes(xintercept= 17.72353))
+
+```
 
@@
 Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistic [@Efron86,@Puth15].
+
+We can use the following to get our studentized confidence interval:
+```{r}
+mean(~ Dec, data = SnowGR) + qt(c(0.025, 0.975), df = (nrow(SnowGR-1))) * 
+  sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
+```
+
+```{r}
+set.seed(495)
+
+orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
+orig_se <- sd(~ Dec, data = SnowGR)/sqrt(nrow(SnowGR))
+
+nboot <- 10000
+
+se <- rep(0,nboot)
+t_stat <- rep(0,nboot)
+
+for (i in 1:nboot) {
+  se[i] <- sd[i]/sqrt(nrow(SnowGR))
+  t_stat[i] <- (mean[i] - orig_mean)/se[i]
+}
+
+dec_t_stat <- as.data.frame(t_stat)
+
+q <- unname(quantile(dec_t_stat$t_stat, c(0.025, 0.975)))
+lower <- q[1]
+upper <- q[2]
+
+c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
+
+```
 

### 2022-11-30 project/PaperTemplate/paper.tex

@@
 %% load any required packages here
+
+% Pandoc syntax highlighting
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
@@
 
-First, we will introduce the non-parametric bootstrap. Suppose we have a
+First, we introduce the non-parametric bootstrap. Suppose we have a
 random sample \(X = (x_1,x_2,\dots,x_n)\) from our unknown distribution,
@@
 repeatedly sampling new reproductions of \(X\) from \(F\). However \(F\)
-is unknown so this is not possible. The non-parametric bootstrap creates
-an estimate \(\hat{F}\) from \(F\) using our sample \(X\) without making
-any parametric assumptions (such as distribution). Therefore, the
-bootstrap sample could be represented as
-\(X^* = (x^*_1, x^*_2, \dots, x^*_n)\) where each \(x^*_i\) is sampled
-randomly with equal probability and with replacement from
+is unknown, so this is not possible. The non-parametric bootstrap
+creates an estimate \(\hat{F}\) from \(F\) using our sample \(X\)
+without making any parametric assumptions about \(F\) (such as its
+distribution type). Therefore, the bootstrap sample could be represented
+as \(X^* = (x^*_1, x^*_2, \dots, x^*_n)\) where each \(x^*_i\) is
+sampled randomly with equal probability and with replacement from
 \(\{x_1,x_2,\dots,x_n\}\). From this bootstrap sample, a bootstrap
@@
 bootstrap replication of the test statistic is calculated.
-\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B\]
+\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B.\]
 The bootstrap estimate of the test statistic is the empirical value of
@@
 As \(B\) increases, \(\hat{F}\) approaches \(F\) which means that the
-tests statistic of interest approaches its true value as well.
+test statistic of interest approaches its true value as well.
+
+We demonstrate performing a non-parametric bootstrap below using
+\texttt{SnowGR} which gives the official snowfall dataset by month for
+Grand Rapids, MI, starting in 1893. We will be using the \texttt{Dec}
+variable which gives the number of inches of snow that fell in December
+of each year. In particular, we are interested in the sample mean. The
+distribution is below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{data}\NormalTok{(SnowGR)}
+\FunctionTok{favstats}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##  min   Q1 median    Q3  max     mean       sd   n missing
+##  0.8 8.35   13.8 18.65 59.2 15.75798 10.58382 119       0
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
 
@@
 Confidence intervals are tools that are used to estimate a parameter.
-Specifically, a confidence interval gives a range in which the true
-value of the parameter may lie. An \(\alpha\)-level standard confidence
-interval is given by
-\[\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma}\]
+Specifically, a confidence interval gives a range of values in which the
+true value of the parameter may lie. An \(\alpha\)-level standard
+confidence interval is given by
+\[\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma},\]
 where \(\hat{\theta}\) is a point estimate of the parameter of interest
@@
 replications \(B\) must be large (around 2000) due to the nature of
-confidence intervals requiring greater accuracy.
+confidence intervals requiring greater accuracy \citep{Efron86}.
 
@@
 \([\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}]\)
-\citep[\citet{EfronCasi}]{Efron86}. To go further, we can say define
+\citep[\citet{EfronCasi}]{Efron86}. To go further, we can define
 \(\hat{G}(t)\) as the bootstrap cdf, or the proportion of bootstrap
-samples less than \(t\).
+samples less than \(t\):
 \[\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.\] Thus the
@@
 also can be represented as an interval,
-\[\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]\].
+\[\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ].\]
 Therefore, the percentile method produces a correct interval for
@@
 need to know the transformation itself, only that it exists. However, in
-some cases, no monotone normalizing mapping will exist.
+some cases, no monotone normalizing mapping will exist \citep{Efron86}.
 
@@
 \(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},\)
-define \[p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B}\], and
-define the bias-correction value \[z_0 = \Phi^{-1}(p_0)\] where
+define \[p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B},\] and
+define the bias-correction value \[z_0 = \Phi^{-1}(p_0),\] where
 \(\Phi^{-1}\) is the inverse function of the standard normal cdf. Thus
 we define a transformation
-\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
-any \(\theta\), \[\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),\] with
-\(z_0\) and \(\tau\) constants. This means that we can say the bias
-corrected method has an \(\alpha\)-level endpoint can be represented as
+\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)\) such that for any
+\(\theta\), \[\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),\] with \(z_0\)
+and \(\tau\) constants. This means that we can say the bias corrected
+method has an \(\alpha\)-level endpoint can be represented as
 \[\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].\]
@@
 A further modification upon the BC interval is the bias corrected and
-accelerated method (BCa). For this method, we do assume the the standard
-error, \(\tau\) to be constant as we did in the BC interval
+accelerated method (BCa). For this method, we do not assume the the
+standard error, \(\tau\) is constant as we did in the BC interval
 \citep[\citet{EfronCasi}]{Efron86}. Rather, we assume the existence of a
 monotone transformation
-\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\hat{\theta)}\) such that for
-any \(\theta\),
+\(\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)\) such that for any
+\(\theta\),
 \[\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.\]
-The \(a\) in known as the acceleration and is a constant that describes
+The \(a\) is known as the acceleration and is a constant that describes
 how the standard deviation of \(\hat{\phi}\) varies with \(\phi\). In
@@
 calculating a BCa interval, the acceleration value \(a\) is not a
-function of the bootstrap distribution and must be calculated separate,
-however the process is algorithmic and can be calculated without too
-much work. Each of the three previous methods (percentile, BC, and BCa)
-all build upon each other and have less restrictive assumptions, however
-computation increases as we loosen assumptions.
+function of the bootstrap distribution and must be calculated
+separately, however the process is algorithmic and can be calculated
+without too much work. Each of the three previous methods (percentile,
+BC, and BCa) all build upon each other and have less restrictive
+assumptions, however computation increases as we loosen assumptions.
 
@@
 
-The next method is the bootstrap-t interval (or the studentized method).
-Recalling from earlier, our sample, \(X\) from which we can calculate an
-estimate, \(\hat{\theta}(X)\) of the parameter of interest \(\theta\)
-\citep[\citet{Puth15}]{Efron86}. We can also estimate
-\(\hat{\sigma}(X)\) for the standard error of \(\theta\). We can use
-these parameters to find the Student's \(t\)-statistic defined as
-\[T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.\] As such, the
+The final method we explain is the bootstrap-t interval (or the
+studentized method). Recall from earlier, our sample, \(X\) from which
+we can calculate an estimate, \(\hat{\theta}(X)\) of the parameter of
+interest \(\theta\) \citep[\citet{Puth15}]{Efron86}. We can also
+estimate \(\hat{\sigma}(X)\) for the standard error of \(\theta\). We
+can use these parameters to find the Student's \(t\)-statistic defined
+as \[T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.\] As such, the
 \(\alpha\)th percentile point of a confidence interval of \(\theta\)
@@
 \(\hat{\sigma^*} = \hat{\sigma}(X^*)\). From these we can calculate a
-\[T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}\] for each
+t-statistic for each bootstrap sample:
+\[T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.\] for each
 bootstrap sample. Using a large number of these bootstrap samples, we
-can estimate the percentiles of the \(t\)-distribution such that
+can estimate the percentiles of the \(t\)-distribution such that:
 \[\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.\]
@@
 studentized confidence interval endpoint can be given with
-\[\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)}\]
+\[\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},\]
 where we can estimate the standard error using
@@
 can calculate the appropriate confidence interval for the parameter of
-interest specifically from the bootstrapped statistic.
+interest specifically from the bootstrapped statistic
+\citep[\citet{Puth15}]{Efron86}.
+
+\hypertarget{simulation}{%
+\section{Simulation}\label{simulation}}
+
+Justin,
+
+An example before a simulation could be useful if your simulation is
+assessing their performance (i.e.~if your simulation is like Hmk 8,
+where you do a lot of reps to check performance). You could run anything
+on an existing data set (the one we have from Hmk 4/5), for example,
+that you want. I think you have enough without worrying about the
+parametric bootstrap.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(boot)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Attaching package: 'boot'
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:mosaic':
+## 
+##     logit
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:lattice':
+## 
+##     melanoma
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+
+\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{50}
+
+\NormalTok{X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
+\NormalTok{values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+
+\NormalTok{mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{  d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+  \FunctionTok{return}\NormalTok{ (}\FunctionTok{mean}\NormalTok{(d))}
+\NormalTok{\}}
+
+\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ reps)}
+
+\NormalTok{results}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## ORDINARY NONPARAMETRIC BOOTSTRAP
+## 
+## 
+## Call:
+## boot(data = values, statistic = mean.fun, R = reps)
+## 
+## 
+## Bootstrap Statistics :
+##        original       bias    std. error
+## t1* 0.008974394 -0.003054148   0.1320787
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(results)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning in boot.ci(results, type = "all"): bootstrap variances needed for
+## studentized intervals
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+
+\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
+\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{15}
+
+\NormalTok{r\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
+\NormalTok{tau\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
+
+\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{ reps) \{}
+\NormalTok{  x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{40}\NormalTok{, }\DecValTok{3}\NormalTok{)}
+\NormalTok{  y }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(n, }\DecValTok{8}\NormalTok{, }\DecValTok{2}\NormalTok{)}
+
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x,y)}
+
+\NormalTok{  r\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y))}\SpecialCharTok{$}\NormalTok{p.value}
+\NormalTok{  tau\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y, }\AttributeTok{method =} \StringTok{"kendall"}\NormalTok{))}\SpecialCharTok{$}\NormalTok{p.value}
+\NormalTok{\}}
+
+\FunctionTok{sum}\NormalTok{(r\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.0463
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{sum}\NormalTok{(tau\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.0436
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{simbootstraps }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(dataset, trueparameter) \{}
+
+  \CommentTok{\# use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)}
+  \CommentTok{\# like 2000 times}
+
+  \CommentTok{\#use that bootstrap distribution as follows to test for the intervals}
+
+  \CommentTok{\# see how many times the true value lies inside the interval {-}{-}\textgreater{} first do one and then show the actual intervals}
+
+\NormalTok{\}}
+
+\NormalTok{simnormal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(locationinput, scaleinput, testcenterinput, ninput, }\AttributeTok{repsinput =} \DecValTok{1000}\NormalTok{)\{}
+\CommentTok{\# Set Useful Values}
+\NormalTok{reps }\OtherTok{\textless{}{-}}\NormalTok{ repsinput }\CommentTok{\#number of repetitions}
+\NormalTok{location }\OtherTok{\textless{}{-}}\NormalTok{ locationinput }
+\NormalTok{scale }\OtherTok{\textless{}{-}}\NormalTok{ scaleinput}
+\NormalTok{testcenter }\OtherTok{\textless{}{-}}\NormalTok{ testcenterinput }\CommentTok{\#center to test for}
+\NormalTok{n }\OtherTok{\textless{}{-}}\NormalTok{ ninput }\CommentTok{\#sample size}
+
+\CommentTok{\#Initialize storage vectors}
+\NormalTok{tpvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
+\NormalTok{spvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
+\NormalTok{srpvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
+
+\CommentTok{\#Generate random data, do tests, save p{-}values}
+\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{reps)\{}
+\NormalTok{  x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, location, scale)}
+\NormalTok{  tpvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{t.test}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{x, }\AttributeTok{mu =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
+\NormalTok{  spvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{SIGN.test}\NormalTok{(x, }\AttributeTok{md =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
+\NormalTok{  srpvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{wilcox.test}\NormalTok{(x, }\AttributeTok{mu =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
+\NormalTok{\}}
+
+\NormalTok{output }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FunctionTok{sum}\NormalTok{(tpvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps, }\FunctionTok{sum}\NormalTok{(spvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps, }\FunctionTok{sum}\NormalTok{(srpvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps)}
+\FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Ttest"}\NormalTok{, }\StringTok{"Sign"}\NormalTok{, }\StringTok{"SignedRank"}\NormalTok{)}
+\NormalTok{output}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+
+\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
+\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{15}
+
+\NormalTok{r\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
+\NormalTok{tau\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
+
+\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{ reps) \{}
+\NormalTok{  y }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(n, }\DecValTok{8}\NormalTok{, }\DecValTok{2}\NormalTok{)}
+
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x,y)}
+
+\NormalTok{  r\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y))}\SpecialCharTok{$}\NormalTok{p.value}
+\NormalTok{  tau\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y, }\AttributeTok{method =} \StringTok{"kendall"}\NormalTok{))}\SpecialCharTok{$}\NormalTok{p.value}
+\NormalTok{\}}
+
+\FunctionTok{sum}\NormalTok{(r\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.0489
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{sum}\NormalTok{(tau\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.0456
+\end{verbatim}
 

### 2022-11-30 project/PaperTemplate/paper.Rmd
Working on simulation

@@
 
-nboot <- 10000
+#nboot <- 10000
 
@@
 
-Justin,
-
-An example before a simulation could be useful if your simulation is assessing their performance (i.e.
-if your simulation is like Hmk 8, where you do a lot of reps to check performance).
-You could run anything on an existing data set (the one we have from Hmk 4/5), for example, that you want.
-I think you have enough without worrying about the parametric bootstrap.
-
 ```{r}
@@
   d <- X[i]
-  return (mean(d))
+  return (c(mean(d), sd(d)))
 }
@@
 ci <- boot.ci(results, type = "all")
+ci
 
@@
 ```{r}
-set.seed(1)
+findCIs <- function(sampleinput, trueparameter, nboot) {
 
-reps <- 10000
-n <- 15
+  sample_mean <- mean(~ Dec, data = sampleinput)
+  sample_sd <- sd(~ Dec, data = sampleinput)
+  sample_n <- nrow(sampleinput)
 
-r_pvals <- rep(0, reps)
-tau_pvals <- rep(0, reps)
+  alphalow <- 0.025
+  alphahigh <- 0.975
 
-for(i in 1: reps) {
-  x <- rnorm(n, 40, 3)
-  y <- rgamma(n, 8, 2)
+  #perform bootstrap
+  mean <- rep(0,nboot)
+  sd <- rep(0,nboot)
+  se <- rep(0,nboot)
+  t_stat <- rep(0,nboot)
 
-  values <- data.frame(x,y)
-
-  r_pvals[i] <- with(values, cor.test(x, y))$p.value
-  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
+  for (i in 1:nboot) {
+    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
+    mean[i] <- mean(~ Dec, data = resampled)
+    sd[i] <- sd(~ Dec, data = resampled)
+    se[i] <- sd[i]/sqrt(nrow(resampled))
+    t_stat[i] <- (mean[i] - orig_mean)/se[i]
   }
 
-sum(r_pvals <= 0.05)/reps
-sum(tau_pvals <= 0.05)/reps
+  boot_means <- as.data.frame(mean)
+  boot_t_stat <- as.data.frame(t_stat)
 
-```
+  # find the standard confidence interval
+  standard_interval <- sample_mean + qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
 
-```{r}
-simbootstraps <- function(dataset, trueparameter) {
+  # find percentile interval
+  percentile_interval <- qdata(~ mean, c(0.025, 0.975), data = boot_means)
+
+  # find BC interval
+  less_than_sample_mean <- sum(ifelse(boot_means <= sample_mean, 1, 0))/nboot
+  z0 <- qnorm(less_than_sample_mean)
+  newlow <- pnorm(2*z0 + qnorm(alphalow))
+  newhigh <- pnorm(2*z0 + qnorm(alphahigh))
+
+  bc_interval <- qdata(~ mean, c(newlow, newhigh), data = boot_means)
+
+  # find BCa interval
+  theta <- function(x){mean(x)}
+  jackknife_results <- bootstrap::jackknife(sampleinput$Dec, theta)
+  jackmean <- mean(~ jackknife_results$jack.values)
+  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
+    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
+  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
+  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
+  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)
+
+  # find studentized
+  q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
+  lower <- q[1]
+  upper <- q[2]
+  t_interval <- c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
+
+  output <- c(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
+  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
+  output
+}
 
@@
 
-}
+```
 
-simnormal <- function(locationinput, scaleinput, testcenterinput, ninput, repsinput = 1000){
-# Set Useful Values
-reps <- repsinput #number of repetitions
-location <- locationinput 
-scale <- scaleinput
-testcenter <- testcenterinput #center to test for
-n <- ninput #sample size
+```{r}
 
-#Initialize storage vectors
-tpvals <- rep(0,reps)
-spvals <- rep(0,reps)
-srpvals <- rep(0,reps)
-
-#Generate random data, do tests, save p-values
-for(i in 1:reps){
-  x <- rnorm(n, location, scale)
-  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
-  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
-  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
-}
-
-output <- c(sum(tpvals <= 0.05)/reps, sum(spvals <= 0.05)/reps, sum(srpvals <= 0.05)/reps)
-names(output) <- c("Ttest", "Sign", "SignedRank")
-output
-}
+OUTPUT1 <- findCIs(SnowGR, 0, 10)
 ```

### 2022-11-30 project/PaperTemplate/paper.Rmd
Updated simulation

@@
 ```{r}
+findCIs <- function(sampleinput, nboot) {
 
+  sample_mean <- mean(~ X, data = sampleinput)
+  sample_sd <- sd(~ X, data = sampleinput)
+  sample_n <- nrow(sampleinput)
+  sample_se <- sample_sd/sqrt(sample_n)
+
+  alphalow <- 0.025
+  alphahigh <- 0.975
+
+  #perform bootstrap
+  mean <- rep(0,nboot)
+  sd <- rep(0,nboot)
+  se <- rep(0,nboot)
+  t_stat <- rep(0,nboot)
+
+  for (i in 1:nboot) {
+    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
+    mean[i] <- mean(~ X, data = resampled)
+    sd[i] <- sd(~ X, data = resampled)
+    se[i] <- sd[i]/sqrt(nrow(resampled))
+    t_stat[i] <- (mean[i] - sample_mean)/se[i]
+  }
+
+  boot_means <- as.data.frame(mean)
+  boot_t_stat <- as.data.frame(t_stat)
+
+  # find the standard confidence interval
+  standard_interval <- sample_mean + qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
+
+  # find percentile interval
+  percentile_interval <- qdata(~ mean, c(0.025, 0.975), data = boot_means)
+
+  # find BC interval
+  less_than_sample_mean <- sum(ifelse(boot_means <= sample_mean, 1, 0))/nboot
+  z0 <- qnorm(less_than_sample_mean)
+  newlow <- pnorm(2*z0 + qnorm(alphalow))
+  newhigh <- pnorm(2*z0 + qnorm(alphahigh))
+
+  bc_interval <- qdata(~ mean, c(newlow, newhigh), data = boot_means)
+
+  # find BCa interval
+  theta <- function(x){mean(x)}
+  jackknife_results <- bootstrap::jackknife(sampleinput$X, theta)
+  jackmean <- mean(~ jackknife_results$jack.values)
+  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
+    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
+  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
+  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
+  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)
+
+  # find studentized
+  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
+  lower_q <- t_q[1]
+  upper_q <- t_q[2]
+  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))
+  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
+  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
+  output
+}
+
+  # use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)
+  # like 2000 times
+
+  #use that bootstrap distribution as follows to test for the intervals
+
+  # see how many times the true value lies inside the interval --> first do one and then show the actual intervals
+
+```
+
+```{r}
+set.seed(495)
+#OUTPUT1 <- findCIs(values, 2000)
+#OUTPUT1
+```
+
+```{r}
+# way with boot library
 library(boot)
@@
 ```
-
-```{r}
-findCIs <- function(sampleinput, trueparameter, nboot) {
-
-  sample_mean <- mean(~ Dec, data = sampleinput)
-  sample_sd <- sd(~ Dec, data = sampleinput)
-  sample_n <- nrow(sampleinput)
-
-  alphalow <- 0.025
-  alphahigh <- 0.975
-
-  #perform bootstrap
-  mean <- rep(0,nboot)
-  sd <- rep(0,nboot)
-  se <- rep(0,nboot)
-  t_stat <- rep(0,nboot)
-
-  for (i in 1:nboot) {
-    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
-    mean[i] <- mean(~ Dec, data = resampled)
-    sd[i] <- sd(~ Dec, data = resampled)
-    se[i] <- sd[i]/sqrt(nrow(resampled))
-    t_stat[i] <- (mean[i] - orig_mean)/se[i]
-  }
-
-  boot_means <- as.data.frame(mean)
-  boot_t_stat <- as.data.frame(t_stat)
-
-  # find the standard confidence interval
-  standard_interval <- sample_mean + qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
-
-  # find percentile interval
-  percentile_interval <- qdata(~ mean, c(0.025, 0.975), data = boot_means)
-
-  # find BC interval
-  less_than_sample_mean <- sum(ifelse(boot_means <= sample_mean, 1, 0))/nboot
-  z0 <- qnorm(less_than_sample_mean)
-  newlow <- pnorm(2*z0 + qnorm(alphalow))
-  newhigh <- pnorm(2*z0 + qnorm(alphahigh))
-
-  bc_interval <- qdata(~ mean, c(newlow, newhigh), data = boot_means)
-
-  # find BCa interval
-  theta <- function(x){mean(x)}
-  jackknife_results <- bootstrap::jackknife(sampleinput$Dec, theta)
-  jackmean <- mean(~ jackknife_results$jack.values)
-  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
-    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
-  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
-  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
-  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)
-
-  # find studentized
-  q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
-  lower <- q[1]
-  upper <- q[2]
-  t_interval <- c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
-
-  output <- c(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
-  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
-  output
-}
-
-  # use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)
-  # like 2000 times
-
-  #use that bootstrap distribution as follows to test for the intervals
-
-  # see how many times the true value lies inside the interval --> first do one and then show the actual intervals
-
-```
-
-```{r}
-
-OUTPUT1 <- findCIs(SnowGR, 0, 10)
-```
-
-```{r}
-set.seed(495)
-
-reps <- 10000
-n <- 15
-
-r_pvals <- rep(0, reps)
-tau_pvals <- rep(0, reps)
-
-for(i in 1: reps) {
-  y <- rgamma(n, 8, 2)
-
-  values <- data.frame(x,y)
-
-  r_pvals[i] <- with(values, cor.test(x, y))$p.value
-  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
-}
-
-sum(r_pvals <= 0.05)/reps
-sum(tau_pvals <= 0.05)/reps
-
-```

### 2022-11-30 project/PaperTemplate/paper.tex
Updated simulation

@@
 variable which gives the number of inches of snow that fell in December
-of each year. In particular, we are interested in the sample mean. The
-distribution is below:
+of each year. In particular, we are interested in the sample mean and
+later finding confidence intervals for population mean of \texttt{Dec}.
+The distribution is below.
 
@@
 \includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+Next, we will perform the non-parametric bootstrap using 10,000
+replications.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
+
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{nboot }\OtherTok{\textless{}{-}} \DecValTok{10000}
+
+\NormalTok{mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
+\NormalTok{  resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(SnowGR, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{  mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
+\NormalTok{  sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
+ \CommentTok{\# se[i] \textless{}{-} sd[i]/nrow(resampled)}
+\CommentTok{\#  t\_stat[i] \textless{}{-} (mean[i] {-} orig\_mean)/se[i]}
+\NormalTok{\}}
+
+\NormalTok{dec\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
+\CommentTok{\#dec\_t\_stat \textless{}{-} as.data.frame(t\_stat)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#set.seed(495)}
+\CommentTok{\#dec\_means \textless{}{-} do(10000)*mean(\textasciitilde{} Dec, data = mosaic::resample(SnowGR, replace = TRUE))}
+
+\FunctionTok{gf\_dhistogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\AttributeTok{data =}\NormalTok{ dec\_means) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{gf\_dens}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
 
@@
 confidence intervals requiring greater accuracy \citep{Efron86}.
+
+Using our example, to find a 95\% confidence interval for the population
+mean of \texttt{Dec}, we would get the following:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{/} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 13.85639 17.65957
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.65957}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
 
@@
 
+Finding a 95\% confidence interval for the true population mean of
+\texttt{Dec} using the percentile method, we get:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{data =}\NormalTok{ dec\_means)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##     2.5%    97.5% 
+## 13.91170 17.72353
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-7-1.pdf} This
+interval is similar to the one created using the Standard method, but
+shifted slightly to the right.
+
 \hypertarget{the-bias-corrected-bc-method}{%
@@
 produced by the percentile method.
+
+Using this method to create a 95\% confidence interval has a couple more
+steps because we need to find the bias-correction value. First we
+calculate the sample mean.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ SnowGR); sample\_mean}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 15.75798
+\end{verbatim}
+
+Then we find the proportion of bootstrap replications that have a sample
+mean less than the original sample mean.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{less\_than\_sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\FunctionTok{ifelse}\NormalTok{(dec\_means }\SpecialCharTok{\textless{}=}\NormalTok{ sample\_mean, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}\SpecialCharTok{/}\DecValTok{10000}
+\NormalTok{less\_than\_sample\_mean}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.5208
+\end{verbatim}
+
+From this, we can calculate the bias-correction value, \(z_0\):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{z0 }\OtherTok{\textless{}{-}} \FunctionTok{qnorm}\NormalTok{(less\_than\_sample\_mean); z0}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 0.05216151
+\end{verbatim}
+
+Then we can find the modified percentiles:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{alphalow }\OtherTok{\textless{}{-}} \FloatTok{0.025}\NormalTok{; alphahigh }\OtherTok{\textless{}{-}} \FloatTok{0.975}
+
+\NormalTok{newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)); }\CommentTok{\#newlow}
+\NormalTok{newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)); }\CommentTok{\#newhigh}
+
+\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(newlow, newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 3.175238% 98.05047% 
+##  14.01172  17.82017
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.82017}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-12-1.pdf}
 
@@
 assumptions, however computation increases as we loosen assumptions.
+
+In practice, we can use the jackknife procedure to estimate the
+acceleration value for this method. Thus, we will run the jackknife
+procedure:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{theta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{mean}\NormalTok{(x)\}}
+\NormalTok{jackknife\_results }\OtherTok{\textless{}{-}}\NormalTok{ bootstrap}\SpecialCharTok{::}\FunctionTok{jackknife}\NormalTok{(SnowGR}\SpecialCharTok{$}\NormalTok{Dec, theta) }
+\end{Highlighting}
+\end{Shaded}
+
+We find the mean of the jackknife values below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{jackmean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values); jackmean}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 15.75798
+\end{verbatim}
+
+Then we can compute \(a\).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
+\NormalTok{  (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{); estimated\_a}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] -0.02674911
+\end{verbatim}
+
+Now, we can find the adjust percentiles and the bias-corrected with
+acceleration confidence interval.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }\CommentTok{\#a\_newlow}
+\NormalTok{a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }\CommentTok{\#a\_newhigh}
+\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 2.510119% 97.50908% 
+##  13.91591  17.72353
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-17-1.pdf}
 
@@
 
-\hypertarget{simulation}{%
-\section{Simulation}\label{simulation}}
-
-Justin,
-
-An example before a simulation could be useful if your simulation is
-assessing their performance (i.e.~if your simulation is like Hmk 8,
-where you do a lot of reps to check performance). You could run anything
-on an existing data set (the one we have from Hmk 4/5), for example,
-that you want. I think you have enough without worrying about the
-parametric bootstrap.
+We can use the following to get our studentized confidence interval:
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(boot)}
+\FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+} \FunctionTok{qt}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{df =}\NormalTok{ (}\FunctionTok{nrow}\NormalTok{(SnowGR}\DecValTok{{-}1}\NormalTok{))) }\SpecialCharTok{*}
+  \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{/} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
 \end{Highlighting}
@@
 \begin{verbatim}
-## 
-## Attaching package: 'boot'
-\end{verbatim}
-
-\begin{verbatim}
-## The following object is masked from 'package:mosaic':
-## 
-##     logit
-\end{verbatim}
-
-\begin{verbatim}
-## The following object is masked from 'package:lattice':
-## 
-##     melanoma
+## [1] 13.83686 17.67911
 \end{verbatim}
@@
 \begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+
+\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
+\NormalTok{orig\_se }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
+
+\CommentTok{\#nboot \textless{}{-} 10000}
+
+\NormalTok{se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
+\NormalTok{  se[i] }\OtherTok{\textless{}{-}}\NormalTok{ sd[i]}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
+\NormalTok{  t\_stat[i] }\OtherTok{\textless{}{-}}\NormalTok{ (mean[i] }\SpecialCharTok{{-}}\NormalTok{ orig\_mean)}\SpecialCharTok{/}\NormalTok{se[i]}
+\NormalTok{\}}
+
+\NormalTok{dec\_t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(t\_stat)}
+
+\NormalTok{q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(dec\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
+\NormalTok{lower }\OtherTok{\textless{}{-}}\NormalTok{ q[}\DecValTok{1}\NormalTok{]}
+\NormalTok{upper }\OtherTok{\textless{}{-}}\NormalTok{ q[}\DecValTok{2}\NormalTok{]}
+
+\FunctionTok{c}\NormalTok{(orig\_mean }\SpecialCharTok{{-}}\NormalTok{ upper}\SpecialCharTok{*}\NormalTok{orig\_se, orig\_mean }\SpecialCharTok{{-}}\NormalTok{ lower}\SpecialCharTok{*}\NormalTok{orig\_se)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 14.03467 18.01709
+\end{verbatim}
+
+\hypertarget{simulation}{%
+\section{Simulation}\label{simulation}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{findCIs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sampleinput, nboot) \{}
+
+\NormalTok{  sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
+\NormalTok{  sample\_sd }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
+\NormalTok{  sample\_n }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(sampleinput)}
+\NormalTok{  sample\_se }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
+
+\NormalTok{  alphalow }\OtherTok{\textless{}{-}} \FloatTok{0.025}
+\NormalTok{  alphahigh }\OtherTok{\textless{}{-}} \FloatTok{0.975}
+
+  \CommentTok{\#perform bootstrap}
+\NormalTok{  mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{  sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{  se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+\NormalTok{  t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
+
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
+\NormalTok{    resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(sampleinput, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{    mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
+\NormalTok{    sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
+\NormalTok{    se[i] }\OtherTok{\textless{}{-}}\NormalTok{ sd[i]}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(resampled))}
+\NormalTok{    t\_stat[i] }\OtherTok{\textless{}{-}}\NormalTok{ (mean[i] }\SpecialCharTok{{-}}\NormalTok{ sample\_mean)}\SpecialCharTok{/}\NormalTok{se[i]}
+\NormalTok{  \}}
+
+\NormalTok{  boot\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
+\NormalTok{  boot\_t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(t\_stat)}
+
+  \CommentTok{\# find the standard confidence interval}
+\NormalTok{  standard\_interval }\OtherTok{\textless{}{-}}\NormalTok{ sample\_mean }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
+
+  \CommentTok{\# find percentile interval}
+\NormalTok{  percentile\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{data =}\NormalTok{ boot\_means)}
+
+  \CommentTok{\# find BC interval}
+\NormalTok{  less\_than\_sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\FunctionTok{ifelse}\NormalTok{(boot\_means }\SpecialCharTok{\textless{}=}\NormalTok{ sample\_mean, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}\SpecialCharTok{/}\NormalTok{nboot}
+\NormalTok{  z0 }\OtherTok{\textless{}{-}} \FunctionTok{qnorm}\NormalTok{(less\_than\_sample\_mean)}
+\NormalTok{  newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}
+\NormalTok{  newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}
+
+\NormalTok{  bc\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(newlow, newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}
+
+  \CommentTok{\# find BCa interval}
+\NormalTok{  theta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{mean}\NormalTok{(x)\}}
+\NormalTok{  jackknife\_results }\OtherTok{\textless{}{-}}\NormalTok{ bootstrap}\SpecialCharTok{::}\FunctionTok{jackknife}\NormalTok{(sampleinput}\SpecialCharTok{$}\NormalTok{X, theta)}
+\NormalTok{  jackmean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values)}
+\NormalTok{  estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
+\NormalTok{    (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{)}
+\NormalTok{  a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))))}
+\NormalTok{  a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))))}
+\NormalTok{  bca\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}
+
+  \CommentTok{\# find studentized}
+\NormalTok{  t\_q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(boot\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
+\NormalTok{  lower\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{1}\NormalTok{]}
+\NormalTok{  upper\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{2}\NormalTok{]}
+\NormalTok{  t\_interval }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (upper\_q}\SpecialCharTok{*}\NormalTok{sample\_se), sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (lower\_q}\SpecialCharTok{*}\NormalTok{sample\_se))}
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(standard\_interval, percentile\_interval, bc\_interval, bca\_interval, t\_interval)}
+  \FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Standard Interval"}\NormalTok{, }\StringTok{"Percentile Interval"}\NormalTok{, }\StringTok{"BC Interval"}\NormalTok{, }\StringTok{"BCa Interval"}\NormalTok{, }\StringTok{"Studentized Interval"}\NormalTok{)}
+\NormalTok{  output}
+\NormalTok{\}}
+
+  \CommentTok{\# use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)}
+  \CommentTok{\# like 2000 times}
+
+  \CommentTok{\#use that bootstrap distribution as follows to test for the intervals}
+
+  \CommentTok{\# see how many times the true value lies inside the interval {-}{-}\textgreater{} first do one and then show the actual intervals}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\CommentTok{\#OUTPUT1 \textless{}{-} findCIs(values, 2000)}
+\CommentTok{\#OUTPUT1}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# way with boot library}
+\FunctionTok{library}\NormalTok{(boot)}
 \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
@@
 \NormalTok{  d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
-  \FunctionTok{return}\NormalTok{ (}\FunctionTok{mean}\NormalTok{(d))}
+  \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
 \NormalTok{\}}
@@
 ##        original       bias    std. error
-## t1* 0.008974394 -0.003054148   0.1320787
+## t1* 0.008974394 -0.003054148  0.13207867
+## t2* 0.942964007 -0.014138705  0.09914509
 \end{verbatim}
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-22-1.pdf}
 
@@
 \NormalTok{ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+\NormalTok{ci}
 \end{Highlighting}
@@
 \begin{verbatim}
-## Warning in boot.ci(results, type = "all"): bootstrap variances needed for
-## studentized intervals
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-
-\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
-\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{15}
-
-\NormalTok{r\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
-\NormalTok{tau\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
-
-\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{ reps) \{}
-\NormalTok{  x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{40}\NormalTok{, }\DecValTok{3}\NormalTok{)}
-\NormalTok{  y }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(n, }\DecValTok{8}\NormalTok{, }\DecValTok{2}\NormalTok{)}
-
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x,y)}
-
-\NormalTok{  r\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y))}\SpecialCharTok{$}\NormalTok{p.value}
-\NormalTok{  tau\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y, }\AttributeTok{method =} \StringTok{"kendall"}\NormalTok{))}\SpecialCharTok{$}\NormalTok{p.value}
-\NormalTok{\}}
-
-\FunctionTok{sum}\NormalTok{(r\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 0.0463
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{sum}\NormalTok{(tau\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 0.0436
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{simbootstraps }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(dataset, trueparameter) \{}
-
-  \CommentTok{\# use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)}
-  \CommentTok{\# like 2000 times}
-
-  \CommentTok{\#use that bootstrap distribution as follows to test for the intervals}
-
-  \CommentTok{\# see how many times the true value lies inside the interval {-}{-}\textgreater{} first do one and then show the actual intervals}
-
-\NormalTok{\}}
-
-\NormalTok{simnormal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(locationinput, scaleinput, testcenterinput, ninput, }\AttributeTok{repsinput =} \DecValTok{1000}\NormalTok{)\{}
-\CommentTok{\# Set Useful Values}
-\NormalTok{reps }\OtherTok{\textless{}{-}}\NormalTok{ repsinput }\CommentTok{\#number of repetitions}
-\NormalTok{location }\OtherTok{\textless{}{-}}\NormalTok{ locationinput }
-\NormalTok{scale }\OtherTok{\textless{}{-}}\NormalTok{ scaleinput}
-\NormalTok{testcenter }\OtherTok{\textless{}{-}}\NormalTok{ testcenterinput }\CommentTok{\#center to test for}
-\NormalTok{n }\OtherTok{\textless{}{-}}\NormalTok{ ninput }\CommentTok{\#sample size}
-
-\CommentTok{\#Initialize storage vectors}
-\NormalTok{tpvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
-\NormalTok{spvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
-\NormalTok{srpvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,reps)}
-
-\CommentTok{\#Generate random data, do tests, save p{-}values}
-\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{reps)\{}
-\NormalTok{  x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, location, scale)}
-\NormalTok{  tpvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{t.test}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{x, }\AttributeTok{mu =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
-\NormalTok{  spvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{SIGN.test}\NormalTok{(x, }\AttributeTok{md =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
-\NormalTok{  srpvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{wilcox.test}\NormalTok{(x, }\AttributeTok{mu =}\NormalTok{ testcenter)}\SpecialCharTok{$}\NormalTok{p.value }
-\NormalTok{\}}
-
-\NormalTok{output }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FunctionTok{sum}\NormalTok{(tpvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps, }\FunctionTok{sum}\NormalTok{(spvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps, }\FunctionTok{sum}\NormalTok{(srpvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps)}
-\FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Ttest"}\NormalTok{, }\StringTok{"Sign"}\NormalTok{, }\StringTok{"SignedRank"}\NormalTok{)}
-\NormalTok{output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-
-\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
-\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{15}
-
-\NormalTok{r\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
-\NormalTok{tau\_pvals }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, reps)}
-
-\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{ reps) \{}
-\NormalTok{  y }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(n, }\DecValTok{8}\NormalTok{, }\DecValTok{2}\NormalTok{)}
-
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x,y)}
-
-\NormalTok{  r\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y))}\SpecialCharTok{$}\NormalTok{p.value}
-\NormalTok{  tau\_pvals[i] }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(values, }\FunctionTok{cor.test}\NormalTok{(x, y, }\AttributeTok{method =} \StringTok{"kendall"}\NormalTok{))}\SpecialCharTok{$}\NormalTok{p.value}
-\NormalTok{\}}
-
-\FunctionTok{sum}\NormalTok{(r\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 0.0489
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{sum}\NormalTok{(tau\_pvals }\SpecialCharTok{\textless{}=} \FloatTok{0.05}\NormalTok{)}\SpecialCharTok{/}\NormalTok{reps}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 0.0456
+## BOOTSTRAP CONFIDENCE INTERVAL CALCULATIONS
+## Based on 2000 bootstrap replicates
+## 
+## CALL : 
+## boot.ci(boot.out = results, type = "all")
+## 
+## Intervals : 
+## Level      Normal              Basic             Studentized     
+## 95%   (-0.2468,  0.2709 )   (-0.2415,  0.2733 )   (-0.2336,  0.2958 )  
+## 
+## Level     Percentile            BCa          
+## 95%   (-0.2554,  0.2594 )   (-0.2411,  0.2807 )  
+## Calculations and Intervals on Original Scale
 \end{verbatim}

### 2022-12-01 project/PaperTemplate/paper.Rmd
Added second part of simulation

@@
   t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))
+
   output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
@@
 set.seed(495)
-#OUTPUT1 <- findCIs(values, 2000)
-#OUTPUT1
+simulation_reps <- 30
+trueparameter <- 4
+n <- 100
+
+ci <- matrix(nrow = simulation_reps, ncol = 5)
+
+for (i in 1:simulation_reps){
+  #X <- rnorm(n, trueparameter, 3)
+  X <- rgamma(n, shape = 1, scale = 4)
+  values <- data.frame(X)
+  output <- findCIs(values, 2000)
+  ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & trueparameter <= output$`Standard Interval`[2]
+  ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & trueparameter <= output$`Percentile Interval`[2]
+  ci[i, 3] <- trueparameter >= output$`BC Interval`[1] & trueparameter <= output$`BC Interval`[2]
+  ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & trueparameter <= output$`BCa Interval`[2]
+  ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & trueparameter <= output$`Studentized Interval`[2]
+
+}
+
+#ci <- as.data.frame(ci) %>%
+#  rename("Standard Interval" = V1, "Percentile Interval" = V2, "BC Interval" = V3, "BCa Interval" = V4, "Studentized Interval" = V5)
+
+output
+
+ci_prop <- colSums(ci)/simulation_reps
+ci_prop
+
+```
+
+```{r}
+Y <- rgamma(5, shape = 8, scale = 2)
+Y
+
 ```

### 2022-12-01 project/PaperTemplate/paper.Rmd
more sim

@@
 }
-
-  # use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)
-  # like 2000 times
-
-  #use that bootstrap distribution as follows to test for the intervals
-
-  # see how many times the true value lies inside the interval --> first do one and then show the actual intervals
-
 ```
@@
 ```{r}
+run_simulation_gamma <- function(num_reps, sample_size){
   set.seed(495)
-simulation_reps <- 30
+  simulation_reps <- num_reps
   trueparameter <- 4
-n <- 100
+  n <- sample_size
 
@@
 
-#ci <- as.data.frame(ci) %>%
-#  rename("Standard Interval" = V1, "Percentile Interval" = V2, "BC Interval" = V3, "BCa Interval" = V4, "Studentized Interval" = V5)
-
-output
-
   ci_prop <- colSums(ci)/simulation_reps
   ci_prop
+}
 
@@
 ```{r}
+#10 100 500 1000
+data2 <- matrix(nrow = 3, ncol = 6)
+
+for (i in 1:3) {
+  output2 <- run_simulation_gamma(10, 10^i)
+  data2[i, 1] <- 10^i
+  data2[i, 2] <- output2[1]
+  data2[i, 3] <- output2[2]
+  data2[i, 4] <- output2[3]
+  data2[i, 5] <- output2[4]
+  data2[i, 6] <- output2[5]
+}
+
+output3 <- as.data.frame(data2) %>% 
+  rename("sample_size" = V1, "standard" = V2, "percentile" = V3, "BC" = V4, "BCa" = V5, "studentized" = V6)
+
+output4 <- output3 %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+ggplot(data = output4, aes(x = sample_size, y = prop, color = method))+
+  geom_point() +
+  geom_line()
+
+```
+
+```{r}
+
 Y <- rgamma(5, shape = 8, scale = 2)

### 2022-12-02 project/PaperTemplate/paper.Rmd
added parallel to speed things up

@@
 keywords:
-- 3 to 6 keywords
-- that do not appear in the title
+- confidence interval
+- simulation
+- percentile
+- bias-corrected
+- acceleration
+- studentized
 
@@
 library(boot)
+library(gridExtra)
 ```
@@
 # Introduction
-To be added later
+Bootstrapping is an important tool in Statistics, even more so, now that there is access to a higher-level of computing power.
+We use bootstrapping to find an estimate of a desired population parameter from a given sample, without making any assumptions about any underlying distributions of the sample.
 
@@
 ```{r}
-
 orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
@@
   sd[i] <- sd(~Dec, data = resampled)
- # se[i] <- sd[i]/nrow(resampled)
-#  t_stat[i] <- (mean[i] - orig_mean)/se[i]
 }
@@
 dec_means <- as.data.frame(mean)
-#dec_t_stat <- as.data.frame(t_stat)
-
 ```
@@
 ```{r}
-
-#set.seed(495)
-#dec_means <- do(10000)*mean(~ Dec, data = mosaic::resample(SnowGR, replace = TRUE))
-
 gf_dhistogram(~ mean, data = dec_means) %>%
@@
   for (i in 1:simulation_reps){
-    #X <- rnorm(n, trueparameter, 3)
     X <- rgamma(n, shape = 1, scale = 4)
@@
     output <- findCIs(values, 2000)
-    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & trueparameter <= output$`Standard Interval`[2]
-    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & trueparameter <= output$`Percentile Interval`[2]
-    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] & trueparameter <= output$`BC Interval`[2]
-    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & trueparameter <= output$`BCa Interval`[2]
-    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & trueparameter <= output$`Studentized Interval`[2]
-
+    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
+      trueparameter <= output$`Standard Interval`[2]
+    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
+      trueparameter <= output$`Percentile Interval`[2]
+    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
+      trueparameter <= output$`BC Interval`[2]
+    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
+      trueparameter <= output$`BCa Interval`[2]
+    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
+      trueparameter <= output$`Studentized Interval`[2]
   }
@@
 ```{r}
-#10 100 500 1000
-data2 <- matrix(nrow = 3, ncol = 6)
+run_simulation_log_normal <- function(num_reps, sample_size){
+  set.seed(495)
+  simulation_reps <- num_reps
+  trueparameter <- exp(1/2)
+  n <- sample_size
 
-for (i in 1:3) {
-  output2 <- run_simulation_gamma(10, 10^i)
-  data2[i, 1] <- 10^i
-  data2[i, 2] <- output2[1]
-  data2[i, 3] <- output2[2]
-  data2[i, 4] <- output2[3]
-  data2[i, 5] <- output2[4]
-  data2[i, 6] <- output2[5]
+  ci <- matrix(nrow = simulation_reps, ncol = 5)
+
+  for (i in 1:simulation_reps){
+    X <- rlnorm(n, meanlog = 0, sdlog = 1)
+    values <- data.frame(X)
+    output <- findCIs(values, 2000)
+    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
+      trueparameter <= output$`Standard Interval`[2]
+    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
+      trueparameter <= output$`Percentile Interval`[2]
+    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
+      trueparameter <= output$`BC Interval`[2]
+    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
+      trueparameter <= output$`BCa Interval`[2]
+    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
+      trueparameter <= output$`Studentized Interval`[2]
   }
-
-output3 <- as.data.frame(data2) %>% 
-  rename("sample_size" = V1, "standard" = V2, "percentile" = V3, "BC" = V4, "BCa" = V5, "studentized" = V6)
-
-output4 <- output3 %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-ggplot(data = output4, aes(x = sample_size, y = prop, color = method))+
-  geom_point() +
-  geom_line()
+  ci_prop <- colSums(ci)/simulation_reps
+  ci_prop
+}
 
@@
 ```{r}
+run_simulation_normal <- function(num_reps, sample_size){
+  set.seed(495)
+  simulation_reps <- num_reps
+  trueparameter <- 0
+  n <- sample_size
 
-Y <- rgamma(5, shape = 8, scale = 2)
-Y
+  ci <- matrix(nrow = simulation_reps, ncol = 5)
+
+  for (i in 1:simulation_reps){
+    X <- rnorm(n, mean = 0, sd = 1)
+    values <- data.frame(X)
+    output <- findCIs(values, 2000)
+    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
+      trueparameter <= output$`Standard Interval`[2]
+    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
+      trueparameter <= output$`Percentile Interval`[2]
+    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
+      trueparameter <= output$`BC Interval`[2]
+    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
+      trueparameter <= output$`BCa Interval`[2]
+    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
+      trueparameter <= output$`Studentized Interval`[2]
+  }
+  ci_prop <- colSums(ci)/simulation_reps
+  ci_prop
+}
+
+```
+
+```{r}
+collect_data_gamma <- function(sim_reps) {
+  data2 <- matrix(nrow = 5, ncol = 6)
+
+  simulation_reps <- sim_reps
+  sample_sizes <- c(10, 25, 50, 100, 250)
+
+  for (i in 1:5) {
+    output2 <- run_simulation_gamma(simulation_reps, sample_sizes[i])
+    data2[i, 1] <- sample_sizes[i]
+    data2[i, 2:6] <- output2
+  }
+
+  gamma_output <- as.data.frame(data2) %>% 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+  gamma_output
+}
+
+```
+
+```{r}
+collect_data_log_normal <- function(sim_reps) {
+  data2 <- matrix(nrow = 5, ncol = 6)
+
+  simulation_reps <- sim_reps
+  sample_sizes <- c(10, 25, 50, 100, 250)
+
+  for (i in 1:5) {
+    output2 <- run_simulation_log_normal(simulation_reps, sample_sizes[i])
+    data2[i, 1] <- sample_sizes[i]
+    data2[i, 2:6] <- output2
+  }
+
+  normal_output <- as.data.frame(data2) %>% 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+  normal_output
+}
+
+```
+
+```{r}
+collect_data_normal <- function(sim_reps) {
+  data2 <- matrix(nrow = 5, ncol = 6)
+
+  simulation_reps <- sim_reps
+  sample_sizes <- c(10, 25, 50, 100, 250)
+
+  for (i in 1:5) {
+    output2 <- run_simulation_normal(simulation_reps, sample_sizes[i])
+    data2[i, 1] <- sample_sizes[i]
+    data2[i, 2:6] <- output2
+  }
+
+  normal_output <- as.data.frame(data2) %>% 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+  normal_output
+}
+
+```
+
+```{r, cache = TRUE}
+set.seed(495)
+gamma_data <- collect_data_gamma(30)
+normal_data <- collect_data_normal(30)
+log_normal_data <- collect_data_log_normal(30)
+```
+
+```{r}
+  gamma_data1 <- gamma_data %>%
+    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+  gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, color = method))+
+    geom_point() +
+    geom_line() + 
+    labs(title = "Proportion of CIs that Contain the True Parameter from Gamma Distibution",
+         x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
+    theme_light()
+
+  gamma_table <- gamma_data %>%
+    kable(booktabs = TRUE, align = "c", caption = "gamma", col.names = gsub("[_]", " ", names(gamma_data)))
+
+  gamma_table
+  gamma_fig
 
@@
 ```
+
+```{r}
+library(parallel)
+numCores <- detectCores()
+#simulation_reps <- 30
+#simulation_rep <- seq(1,simulation_reps)
+#sample_size <- 20
+#  simulation_reps <- num_reps
+
+run_simulation_normal1 <- function(simulation_rep){
+  trueparameter <- 0
+
+  X <- rnorm(sample_sizes, mean = 0, sd = 1)
+  values <- data.frame(X)
+  output <- findCIs(values, 2000)
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
+}
+
+  collect_data_normal1 <- function(sim_reps) {
+  data2 <- matrix(nrow = 5, ncol = 6)
+
+  sample_sizes = 10
+
+  for (i in 1:5) {
+    #output2 <- run_simulation_normal1(simulation_reps)
+    simulation_rep <- seq(1,sim_reps)
+    results <- mclapply(simulation_rep, run_simulation_normal1, mc.cores = detectCores())
+    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
+    ci_prop <- colSums(df)/sim_reps
+
+    data2[i, 1] <- sample_sizes
+    data2[i, 2:6] <- ci_prop
+    sample_sizes <- sample_sizes*2
+  }
+
+  normal_output <- as.data.frame(data2) %>% 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+  normal_output
+  }
+
+    xyzw <- collect_data_normal1(20)
+
+```

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added parallel

@@
 library(gridExtra)
+library(parallel)
 ```
@@
 
-```{r}
+```{r find CIs}
 findCIs <- function(sampleinput, nboot) {
@@
 
-```{r}
-run_simulation_gamma <- function(num_reps, sample_size){
-  set.seed(495)
-  simulation_reps <- num_reps
+```{r run simulation gamma}
+run_simulation_gamma <- function(simulation_rep){
   trueparameter <- 4
-  n <- sample_size
 
-  ci <- matrix(nrow = simulation_reps, ncol = 5)
-
-  for (i in 1:simulation_reps){
-    X <- rgamma(n, shape = 1, scale = 4)
+  X <- rgamma(sample_sizes, shape = 1, scale = 4)
   values <- data.frame(X)
   output <- findCIs(values, 2000)
-    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
-      trueparameter <= output$`Standard Interval`[2]
-    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
-      trueparameter <= output$`Percentile Interval`[2]
-    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
-      trueparameter <= output$`BC Interval`[2]
-    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
-      trueparameter <= output$`BCa Interval`[2]
-    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
-      trueparameter <= output$`Studentized Interval`[2]
-  }
-
-  ci_prop <- colSums(ci)/simulation_reps
-  ci_prop
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
 }
@@
 
-```{r}
-run_simulation_log_normal <- function(num_reps, sample_size){
-  set.seed(495)
-  simulation_reps <- num_reps
+```{r run simulation log normal}
+run_simulation_log_normal <- function(simulation_rep){
   trueparameter <- exp(1/2)
-  n <- sample_size
 
-  ci <- matrix(nrow = simulation_reps, ncol = 5)
-
-  for (i in 1:simulation_reps){
-    X <- rlnorm(n, meanlog = 0, sdlog = 1)
+  X <- rlnorm(sample_sizes, meanlog = 0, sdlog = 1)
   values <- data.frame(X)
   output <- findCIs(values, 2000)
-    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
-      trueparameter <= output$`Standard Interval`[2]
-    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
-      trueparameter <= output$`Percentile Interval`[2]
-    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
-      trueparameter <= output$`BC Interval`[2]
-    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
-      trueparameter <= output$`BCa Interval`[2]
-    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
-      trueparameter <= output$`Studentized Interval`[2]
-  }
-  ci_prop <- colSums(ci)/simulation_reps
-  ci_prop
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
 }
@@
 
-```{r}
-run_simulation_normal <- function(num_reps, sample_size){
-  set.seed(495)
-  simulation_reps <- num_reps
+```{r run simulation normal}
+run_simulation_normal <- function(simulation_rep){
   trueparameter <- 0
-  n <- sample_size
 
-  ci <- matrix(nrow = simulation_reps, ncol = 5)
-
-  for (i in 1:simulation_reps){
-    X <- rnorm(n, mean = 0, sd = 1)
+  X <- rnorm(sample_sizes, mean = 0, sd = 1)
   values <- data.frame(X)
   output <- findCIs(values, 2000)
-    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
-      trueparameter <= output$`Standard Interval`[2]
-    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
-      trueparameter <= output$`Percentile Interval`[2]
-    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
-      trueparameter <= output$`BC Interval`[2]
-    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
-      trueparameter <= output$`BCa Interval`[2]
-    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
-      trueparameter <= output$`Studentized Interval`[2]
-  }
-  ci_prop <- colSums(ci)/simulation_reps
-  ci_prop
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
 }
@@
 
-```{r}
+```{r collect data gamma}
 collect_data_gamma <- function(sim_reps) {
   data2 <- matrix(nrow = 5, ncol = 6)
+  sample_sizes = 10
+ # sim_reps <- 10
+  for (i in 1:5) {
+    simulation_rep <- seq(1,sim_reps)
+    results <- mclapply(simulation_rep, run_simulation_gamma, mc.cores = detectCores())
+    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
+    ci_prop <- unname(colSums(df)/sim_reps)
 
-  simulation_reps <- sim_reps
-  sample_sizes <- c(10, 25, 50, 100, 250)
-
-  for (i in 1:5) {
-    output2 <- run_simulation_gamma(simulation_reps, sample_sizes[i])
-    data2[i, 1] <- sample_sizes[i]
-    data2[i, 2:6] <- output2
+    data2[i, 1] <- sample_sizes
+    data2[i, 2:6] <- ci_prop
+    sample_sizes <- sample_sizes*2
   }
@@
 
-```{r}
+```{r collect data log normal}
 collect_data_log_normal <- function(sim_reps) {
   data2 <- matrix(nrow = 5, ncol = 6)
-
-  simulation_reps <- sim_reps
-  sample_sizes <- c(10, 25, 50, 100, 250)
+  sample_sizes = 10
 
   for (i in 1:5) {
-    output2 <- run_simulation_log_normal(simulation_reps, sample_sizes[i])
-    data2[i, 1] <- sample_sizes[i]
-    data2[i, 2:6] <- output2
+    simulation_rep <- seq(1,sim_reps)
+    results <- mclapply(simulation_rep, run_simulation_log_normal, mc.cores = detectCores())
+    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
+    ci_prop <- unname(colSums(df)/sim_reps)
+
+    data2[i, 1] <- sample_sizes
+    data2[i, 2:6] <- ci_prop
+    sample_sizes <- sample_sizes*2
   }
 
-  normal_output <- as.data.frame(data2) %>% 
+  log_normal_output <- as.data.frame(data2) %>% 
     rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
-  normal_output
+  log_normal_output
 }
@@
 
-```{r}
+```{r collect data normal}
 collect_data_normal <- function(sim_reps) {
   data2 <- matrix(nrow = 5, ncol = 6)
-
-  simulation_reps <- sim_reps
-  sample_sizes <- c(10, 25, 50, 100, 250)
+  sample_sizes = 10
 
   for (i in 1:5) {
-    output2 <- run_simulation_normal(simulation_reps, sample_sizes[i])
-    data2[i, 1] <- sample_sizes[i]
-    data2[i, 2:6] <- output2
+    simulation_rep <- seq(1,sim_reps)
+    results <- mclapply(simulation_rep, run_simulation_normal, mc.cores = detectCores())
+    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
+    ci_prop <- unname(colSums(df)/sim_reps)
+
+    data2[i, 1] <- sample_sizes
+    data2[i, 2:6] <- ci_prop
+    sample_sizes <- sample_sizes*2
   }
@@
 set.seed(495)
-gamma_data <- collect_data_gamma(30)
-normal_data <- collect_data_normal(30)
-log_normal_data <- collect_data_log_normal(30)
+gamma_data <- collect_data_gamma(5000)
+normal_data <- collect_data_normal(5000)
+log_normal_data <- collect_data_log_normal(5000)
 ```
@@
 ```
-
-```{r}
-library(parallel)
-numCores <- detectCores()
-#simulation_reps <- 30
-#simulation_rep <- seq(1,simulation_reps)
-#sample_size <- 20
-#  simulation_reps <- num_reps
-
-run_simulation_normal1 <- function(simulation_rep){
-  trueparameter <- 0
-
-  X <- rnorm(sample_sizes, mean = 0, sd = 1)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-  collect_data_normal1 <- function(sim_reps) {
-  data2 <- matrix(nrow = 5, ncol = 6)
-
-  sample_sizes = 10
-
-  for (i in 1:5) {
-    #output2 <- run_simulation_normal1(simulation_reps)
-    simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_normal1, mc.cores = detectCores())
-    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- colSums(df)/sim_reps
-
-    data2[i, 1] <- sample_sizes
-    data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
-  }
-
-  normal_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
-  normal_output
-  }
-
-    xyzw <- collect_data_normal1(20)
-
-```

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added intro

@@
 # Introduction
-Bootstrapping is an important tool in Statistics, even more so, now that there is access to a higher-level of computing power.
-We use bootstrapping to find an estimate of a desired population parameter from a given sample, without making any assumptions about any underlying distributions of the sample.
+Bootstrapping is an essential tool in Statistics, even more so now that there is access to higher computing power.
+We use bootstrapping to estimate the desired population parameter from a given sample without making assumptions about any underlying distributions of the sample.
+Different bootstrap techniques are developed, but we will focus on the non-parametric bootstrap for our purposes.
+One way to make a statistical inference is through confidence intervals which give a range of estimates for the unknown population parameter at a certain confidence level.
+We can use bootstrapping to create accurate approximate confidence intervals for our population parameter even without its underlying distributions.
+There are many different ways to create intervals, and we will go through a couple of them: The Standard Method, The Percentile Method, The Bias-Corrected (BC) Method, The Bias-Corrected with Acceleration (BCa) Method, and finally, The Studentized Method.
+Additionally, we will go through an example of creating a bootstrapped confidence interval for each method.
+Then, we will perform a simulation to evaluate the performance of the bootstrapped confidence interval methods on different distribution types.
 
@@
 
+```{r run simulation beta}
+run_simulation_beta <- function(simulation_rep){
+  trueparameter <- 0.8
+
+  X <- rbeta(sample_sizes, shape1 = 4, shape2 = 1)
+  values <- data.frame(X)
+  output <- findCIs(values, 2000)
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
+}
+
+```
+
 ```{r collect data gamma}
@@
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  sample_sizes = 50
  # sim_reps <- 10
@@
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  sample_sizes = 50
 
@@
 
+```{r collect data beta}
+collect_data_beta <- function(sim_reps) {
+  data2 <- matrix(nrow = 5, ncol = 6)
+  sample_sizes = 50
+
+  for (i in 1:5) {
+    simulation_rep <- seq(1,sim_reps)
+    results <- mclapply(simulation_rep, run_simulation_beta, mc.cores = detectCores())
+    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
+    ci_prop <- unname(colSums(df)/sim_reps)
+
+    data2[i, 1] <- sample_sizes
+    data2[i, 2:6] <- ci_prop
+    sample_sizes <- sample_sizes*2
+  }
+
+  beta_output <- as.data.frame(data2) %>% 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+  beta_output
+}
+
+```
+
 ```{r, cache = TRUE}
 set.seed(495)
-gamma_data <- collect_data_gamma(5000)
-normal_data <- collect_data_normal(5000)
-log_normal_data <- collect_data_log_normal(5000)
+gamma_data1 <- collect_data_gamma(10000)
+normal_data1 <- collect_data_normal(10000)
+log_normal_data1 <- collect_data_log_normal(10000)
+beta_data1 <- collect_data_beta(10000)
+
+write.csv(gamma_data,"gamma_data1_10000.csv", row.names = FALSE)
+write.csv(normal_data,"normal_data1_10000.csv", row.names = FALSE)
+write.csv(log_normal_data,"log_normal1_data_10000.csv", row.names = FALSE)
+write.csv(beta_data,"beta_data1_10000.csv", row.names = FALSE)
+
 ```
@@
 ```{r}
-  gamma_data1 <- gamma_data %>%
+  gamma_data1 <- gamma_data5 %>%
     pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
@@
 ```{r}
+  gamma_data1 <- log_normal_data7 %>%
+    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+  gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, color = method))+
+    geom_point() +
+    geom_line() + 
+    labs(title = "Proportion of CIs that Contain the True Parameter from Gamma Distibution",
+         x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
+    theme_light()
+
+  gamma_table <- gamma_data %>%
+    kable(booktabs = TRUE, align = "c", caption = "gamma", col.names = gsub("[_]", " ", names(gamma_data)))
+
+  gamma_table
+  gamma_fig
+
+```
+
+```{r, eval = FALSE}
 # way with boot library

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added some text for simualtion

@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count")
+  labs(x = "Annual Snowfall in Decemeber", 
+       title = "Distribution of Annual Snowfall in Decemeber", y = "Count")
 ```
@@
 ```{r}
-mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
+mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * 
+  sd(~ Dec, data = SnowGR)/sqrt(nrow(SnowGR))
 ```
@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in Decemeber", 
+       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
   geom_vline(aes(xintercept= 13.85639)) +
@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in Decemeber", 
+       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
   geom_vline(aes(xintercept= 13.91170)) +
@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in Decemeber", 
+       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
   geom_vline(aes(xintercept= 14.01172)) +
@@
 ```{r}
-a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
-a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
+a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
+                    (1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
+a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
+                     (1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
 qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in Decemeber", 
+       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
   geom_vline(aes(xintercept= 13.91591)) +
@@
 
-We can use the following to get our studentized confidence interval:
-```{r}
-mean(~ Dec, data = SnowGR) + qt(c(0.025, 0.975), df = (nrow(SnowGR-1))) * 
-  sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
-```
+Following the process above, we can use the following to get our studentized confidence interval:
 
@@
 orig_se <- sd(~ Dec, data = SnowGR)/sqrt(nrow(SnowGR))
-
-#nboot <- 10000
 
@@
 # Simulation
+
+For the simulation, we will randomly sample from distributions in which we know the true population mean.
+For example, we will sampling from a Gamma Distribution where we can find the true population mean using the shape and rate parameters of the sample distribution.
+After we sample from a distribution, we will create a bootstrapped confidence interval for each of the methods we described in the exposition.
+Since we know the true population mean of the distribution, we will determine if the true population parameter is contained in the confidence interval for each of the methods.
+We will perform this process a large number of times (10,000) and then average by the number of iterations to determine the average proportion that each bootstrapped confidence interval method contains the true population mean.
+We will do this for a couple different distributions as well as a range of sample sizes show how the intervals perform with skewed distributions and larger sample sizes.
+
+First, we create a function that calculates the bootstrapped confidence intervals from a given sample. To do this, we first bootstrap the sample and then perform each method.
 
@@
   # find the standard confidence interval
-  standard_interval <- sample_mean + qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
+  standard_interval <- sample_mean + 
+    qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
 
@@
     (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
-  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
-  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
+  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
+                      (1-estimated_a*(z0 + qnorm(alphalow))))
+  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
+                       (1-estimated_a*(z0 + qnorm(alphahigh))))
   bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)
 
-  # find studentized
+  # find studentized interval
   t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
@@
 
-  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
-  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
+  output <- list(standard_interval, percentile_interval, bc_interval, 
+                 bca_interval, t_interval)
+  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", 
+                     "BCa Interval", "Studentized Interval")
   output
@@
 ```
+
+Next, we will create the simulation that picks the random sample from a distribution and tests to see if the sample creates bootstrapped confidence intervals that contain the true population parameter.
+First, we have the simulation of selecting from a Normal Distribution.
+Since we have a $N(0,1)$ distribution, out true population mean is 0.
+
+```{r run simulation normal}
+run_simulation_normal <- function(simulation_rep){
+  trueparameter <- 0
+
+  X <- rnorm(sample_sizes, mean = 0, sd = 1)
+  values <- data.frame(X)
+  output <- findCIs(values, 2000)
+  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
+    trueparameter <= output$`Standard Interval`[2],
+    trueparameter >= output$`Percentile Interval`[1] & 
+    trueparameter <= output$`Percentile Interval`[2],
+    trueparameter >= output$`BC Interval`[1] &
+    trueparameter <= output$`BC Interval`[2],
+    trueparameter >= output$`BCa Interval`[1] & 
+    trueparameter <= output$`BCa Interval`[2],
+    trueparameter >= output$`Studentized Interval`[1] & 
+    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
+  res <- rbind(data.frame(), ci)
+  res
+}
+
+```
+
+Second, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4. This means the true population parameter is 4.
 
@@
 
+Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$.
+
 ```{r run simulation log normal}
@@
 
-```{r run simulation normal}
-run_simulation_normal <- function(simulation_rep){
-  trueparameter <- 0
-
-  X <- rnorm(sample_sizes, mean = 0, sd = 1)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-```
+Lastly, we sample from a Beta distribution with shape parameters of 4 and 1 which gives us a true population mean of 0.8.
 
@@
 
+After that, these functions will compile all of the information we have created from the previous methods and run the simulations of each method for a variety of sample sizes.
+
 ```{r collect data gamma}
@@
   sample_sizes = 50
- # sim_reps <- 10
   for (i in 1:5) {
@@
   gamma_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
+           "BCa" = V5, "Studentized" = V6) 
   gamma_output
@@
   log_normal_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
+           "BCa" = V5, "Studentized" = V6) 
   log_normal_output
 }
-
 ```
@@
     simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_normal, mc.cores = detectCores())
+    results <- mclapply(simulation_rep, run_simulation_normal, 
+                        mc.cores = detectCores())
     df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
@@
   normal_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
+           "BCa" = V5, "Studentized" = V6) 
   normal_output
@@
     simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_beta, mc.cores = detectCores())
+    results <- mclapply(simulation_rep, run_simulation_beta, 
+                        mc.cores = detectCores())
     df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
@@
   beta_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
+    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
+           "BCa" = V5, "Studentized" = V6) 
   beta_output
@@
 
-```{r, cache = TRUE}
+```{r, cache = TRUE, eval = FALSE}
 set.seed(495)
 gamma_data1 <- collect_data_gamma(10000)
+write.csv(gamma_data1,"gamma_data1_10000.csv", row.names = FALSE)
+
 normal_data1 <- collect_data_normal(10000)
+write.csv(normal_data1,"normal_data1_10000.csv", row.names = FALSE)
+
 log_normal_data1 <- collect_data_log_normal(10000)
+write.csv(log_normal_data1,"log_normal1_data_10000.csv", row.names = FALSE)
+
 beta_data1 <- collect_data_beta(10000)
-
-write.csv(gamma_data,"gamma_data1_10000.csv", row.names = FALSE)
-write.csv(normal_data,"normal_data1_10000.csv", row.names = FALSE)
-write.csv(log_normal_data,"log_normal1_data_10000.csv", row.names = FALSE)
-write.csv(beta_data,"beta_data1_10000.csv", row.names = FALSE)
+write.csv(beta_data1,"beta_data1_10000.csv", row.names = FALSE)
 
@@
 
-```{r}
+```{r, eval = FALSE}
     gamma_data1 <- gamma_data5 %>%
@@
 
-  gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, color = method))+
+    gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, 
+                                                color = method))+
       geom_point() +
       geom_line() + 
-    labs(title = "Proportion of CIs that Contain the True Parameter from Gamma Distibution",
+      labs(title = "Proportion of CIs that Contain the True Parameter 
+           from Gamma Distibution",
            x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
@@
 ```
-
-```{r}
-  gamma_data1 <- log_normal_data7 %>%
-    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-  gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, color = method))+
-    geom_point() +
-    geom_line() + 
-    labs(title = "Proportion of CIs that Contain the True Parameter from Gamma Distibution",
-         x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
-    theme_light()
-
-  gamma_table <- gamma_data %>%
-    kable(booktabs = TRUE, align = "c", caption = "gamma", col.names = gsub("[_]", " ", names(gamma_data)))
-
-  gamma_table
-  gamma_fig
-
-```
-
-```{r, eval = FALSE}
-# way with boot library
-library(boot)
-set.seed(495)
-
-reps <- 2000
-n <- 50
-
-X <- rnorm(n, 0, 1)
-values <- data.frame(X)
-
-mean.fun <- function(d, i) {
-  d <- X[i]
-  return (c(mean(d), sd(d)))
-}
-
-results <- boot(data = values, statistic = mean.fun, R = reps)
-
-results
-
-plot(results)
-
-ci <- boot.ci(results, type = "all")
-ci
-
-```

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added updated pdf and another paper

@@
 
-Following the process above, we can use the following to get our studentized confidence interval:
+Following the process above, we can use the following to get our studentized confidence interval [@Lau20]:
 
@@
 
-Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$.
+Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$ [@Guillaume21].
 
@@
 
+And here, we run the simulations for each of the distributions and store the results.
+
 ```{r, cache = TRUE, eval = FALSE}
@@
 write.csv(beta_data1,"beta_data1_10000.csv", row.names = FALSE)
-
 ```
@@
       labs(title = "Proportion of CIs that Contain the True Parameter 
-           from Gamma Distibution",
-           x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
+           from Gamma Distibution", x = "Sample Size", 
+           y = "Proportion (of xyz Simulations)", color = "Method") +
       theme_light()
@@
     gamma_table <- gamma_data %>%
-      kable(booktabs = TRUE, align = "c", caption = "gamma", col.names = gsub("[_]", " ", names(gamma_data)))
+      kable(booktabs = TRUE, align = "c", caption = "gamma", 
+            col.names = gsub("[_]", " ", names(gamma_data)))
 

### 2022-12-02 project/PaperTemplate/paper.tex
Added updated pdf and another paper

@@
 \noindent%
-{\it Keywords:} 3 to 6 keywords, that do not appear in the title
+{\it Keywords:} confidence
+interval, simulation, percentile, bias-corrected, acceleration, studentized
 \vfill
@@
 
-To be added later
+Bootstrapping is an essential tool in Statistics, even more so now that
+there is access to higher computing power. We use bootstrapping to
+estimate the desired population parameter from a given sample without
+making assumptions about any underlying distributions of the sample.
+Different bootstrap techniques are developed, but we will focus on the
+non-parametric bootstrap for our purposes. One way to make a statistical
+inference is through confidence intervals which give a range of
+estimates for the unknown population parameter at a certain confidence
+level. We can use bootstrapping to create accurate approximate
+confidence intervals for our population parameter even without its
+underlying distributions. There are many different ways to create
+intervals, and we will go through a couple of them: The Standard Method,
+The Percentile Method, The Bias-Corrected (BC) Method, The
+Bias-Corrected with Acceleration (BCa) Method, and finally, The
+Studentized Method. Additionally, we will go through an example of
+creating a bootstrapped confidence interval for each method. Then, we
+will perform a simulation to evaluate the performance of the
+bootstrapped confidence interval methods on different distribution
+types.
 
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{)}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{)}
 \end{Highlighting}
@@
 \NormalTok{  sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
- \CommentTok{\# se[i] \textless{}{-} sd[i]/nrow(resampled)}
-\CommentTok{\#  t\_stat[i] \textless{}{-} (mean[i] {-} orig\_mean)/se[i]}
 \NormalTok{\}}
@@
 \NormalTok{dec\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
-\CommentTok{\#dec\_t\_stat \textless{}{-} as.data.frame(t\_stat)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\CommentTok{\#set.seed(495)}
-\CommentTok{\#dec\_means \textless{}{-} do(10000)*mean(\textasciitilde{} Dec, data = mosaic::resample(SnowGR, replace = TRUE))}
-
 \FunctionTok{gf\_dhistogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\AttributeTok{data =}\NormalTok{ dec\_means) }\SpecialCharTok{\%\textgreater{}\%}
@@
 \begin{Highlighting}[]
-\FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{/} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
+\FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}
+  \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
 \end{Highlighting}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
@@
 \begin{Highlighting}[]
-\NormalTok{a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }\CommentTok{\#a\_newlow}
-\NormalTok{a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }\CommentTok{\#a\_newhigh}
+\NormalTok{a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
+\NormalTok{                    (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }\CommentTok{\#a\_newlow}
+\NormalTok{a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
+\NormalTok{                     (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }\CommentTok{\#a\_newhigh}
 \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
@@
 
-We can use the following to get our studentized confidence interval:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+} \FunctionTok{qt}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{df =}\NormalTok{ (}\FunctionTok{nrow}\NormalTok{(SnowGR}\DecValTok{{-}1}\NormalTok{))) }\SpecialCharTok{*}
-  \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{/} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 13.83686 17.67911
-\end{verbatim}
+Following the process above, we can use the following to get our
+studentized confidence interval \citep{Lau20}:
 
@@
 \NormalTok{orig\_se }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
-
-\CommentTok{\#nboot \textless{}{-} 10000}
 
@@
 \section{Simulation}\label{simulation}}
+
+For the simulation, we will randomly sample from distributions in which
+we know the true population mean. For example, we will sampling from a
+Gamma Distribution where we can find the true population mean using the
+shape and rate parameters of the sample distribution. After we sample
+from a distribution, we will create a bootstrapped confidence interval
+for each of the methods we described in the exposition. Since we know
+the true population mean of the distribution, we will determine if the
+true population parameter is contained in the confidence interval for
+each of the methods. We will perform this process a large number of
+times (10,000) and then average by the number of iterations to determine
+the average proportion that each bootstrapped confidence interval method
+contains the true population mean. We will do this for a couple
+different distributions as well as a range of sample sizes show how the
+intervals perform with skewed distributions and larger sample sizes.
+
+First, we create a function that calculates the bootstrapped confidence
+intervals from a given sample. To do this, we first bootstrap the sample
+and then perform each method.
 
@@
   \CommentTok{\# find the standard confidence interval}
-\NormalTok{  standard\_interval }\OtherTok{\textless{}{-}}\NormalTok{ sample\_mean }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
+\NormalTok{  standard\_interval }\OtherTok{\textless{}{-}}\NormalTok{ sample\_mean }\SpecialCharTok{+} 
+    \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
 
@@
 \NormalTok{    (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{)}
-\NormalTok{  a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))))}
-\NormalTok{  a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))))}
+\NormalTok{  a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
+\NormalTok{                      (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))))}
+\NormalTok{  a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
+\NormalTok{                       (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))))}
 \NormalTok{  bca\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}
 
-  \CommentTok{\# find studentized}
+  \CommentTok{\# find studentized interval}
 \NormalTok{  t\_q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(boot\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
@@
 \NormalTok{  t\_interval }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (upper\_q}\SpecialCharTok{*}\NormalTok{sample\_se), sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (lower\_q}\SpecialCharTok{*}\NormalTok{sample\_se))}
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(standard\_interval, percentile\_interval, bc\_interval, bca\_interval, t\_interval)}
-  \FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Standard Interval"}\NormalTok{, }\StringTok{"Percentile Interval"}\NormalTok{, }\StringTok{"BC Interval"}\NormalTok{, }\StringTok{"BCa Interval"}\NormalTok{, }\StringTok{"Studentized Interval"}\NormalTok{)}
+
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(standard\_interval, percentile\_interval, bc\_interval, }
+\NormalTok{                 bca\_interval, t\_interval)}
+  \FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Standard Interval"}\NormalTok{, }\StringTok{"Percentile Interval"}\NormalTok{, }\StringTok{"BC Interval"}\NormalTok{, }
+                     \StringTok{"BCa Interval"}\NormalTok{, }\StringTok{"Studentized Interval"}\NormalTok{)}
 \NormalTok{  output}
 \NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
 
-  \CommentTok{\# use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)}
-  \CommentTok{\# like 2000 times}
+Next, we will create the simulation that picks the random sample from a
+distribution and tests to see if the sample creates bootstrapped
+confidence intervals that contain the true population parameter. First,
+we have the simulation of selecting from a Normal Distribution. Since we
+have a \(N(0,1)\) distribution, out true population mean is 0.
 
-  \CommentTok{\#use that bootstrap distribution as follows to test for the intervals}
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_simulation\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
+\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{0}
 
-  \CommentTok{\# see how many times the true value lies inside the interval {-}{-}\textgreater{} first do one and then show the actual intervals}
+\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(sample\_sizes, }\AttributeTok{mean =} \DecValTok{0}\NormalTok{, }\AttributeTok{sd =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
+\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
+\NormalTok{  res}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Second, we select from a Gamma Distribution with a shape parameter of 1
+and a scale parameter of 4. This means the true population parameter is
+4.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_simulation\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
+\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{4}
+
+\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
+\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
+\NormalTok{  res}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Third, we sample from a Log-Normal distribution with mean log of 0 and a
+mean standard deviation of 1. Therefore, the true population mean of
+this distribution is \(e^{\frac{1}{2}}\) \citep{Guillaume21}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_simulation\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
+\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}
+
+\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rlnorm}\NormalTok{(sample\_sizes, }\AttributeTok{meanlog =} \DecValTok{0}\NormalTok{, }\AttributeTok{sdlog =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
+\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
+\NormalTok{  res}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Lastly, we sample from a Beta distribution with shape parameters of 4
+and 1 which gives us a true population mean of 0.8.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_simulation\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
+\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FloatTok{0.8}
+
+\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rbeta}\NormalTok{(sample\_sizes, }\AttributeTok{shape1 =} \DecValTok{4}\NormalTok{, }\AttributeTok{shape2 =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
+\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
+\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
+\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
+\NormalTok{  res}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+After that, these functions will compile all of the information we have
+created from the previous methods and run the simulations of each method
+for a variety of sample sizes.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{collect\_data\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
+\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
+\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
+\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
+
+\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
+\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
+\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
+\NormalTok{  \}}
+
+\NormalTok{  gamma\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
+           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  gamma\_output}
+\NormalTok{\}}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\CommentTok{\#OUTPUT1 \textless{}{-} findCIs(values, 2000)}
-\CommentTok{\#OUTPUT1}
+\NormalTok{collect\_data\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
+
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
+\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
+\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_log\_normal, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
+\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
+
+\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
+\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
+\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
+\NormalTok{  \}}
+
+\NormalTok{  log\_normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
+           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  log\_normal\_output}
+\NormalTok{\}}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\CommentTok{\# way with boot library}
-\FunctionTok{library}\NormalTok{(boot)}
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
 
-\NormalTok{reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
-\NormalTok{n }\OtherTok{\textless{}{-}} \DecValTok{50}
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
+\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
+\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_normal, }
+                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
+\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
 
-\NormalTok{X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
-\NormalTok{values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
+\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
+\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
+\NormalTok{  \}}
 
-\NormalTok{mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
-\NormalTok{  d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
-  \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
+           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  normal\_output}
 \NormalTok{\}}
-
-\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ reps)}
-
-\NormalTok{results}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## 
-## ORDINARY NONPARAMETRIC BOOTSTRAP
-## 
-## 
-## Call:
-## boot(data = values, statistic = mean.fun, R = reps)
-## 
-## 
-## Bootstrap Statistics :
-##        original       bias    std. error
-## t1* 0.008974394 -0.003054148  0.13207867
-## t2* 0.942964007 -0.014138705  0.09914509
-\end{verbatim}
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{collect\_data\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
+
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
+\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
+\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_beta, }
+                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
+\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
+\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
+
+\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
+\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
+\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
+\NormalTok{  \}}
+
+\NormalTok{  beta\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
+    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
+           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  beta\_output}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+And here, we run the simulations for each of the distributions and store
+the results.
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot}\NormalTok{(results)}
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{gamma\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(gamma\_data1,}\StringTok{"gamma\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{normal\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(normal\_data1,}\StringTok{"normal\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{log\_normal\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(log\_normal\_data1,}\StringTok{"log\_normal1\_data\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{beta\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_beta}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(beta\_data1,}\StringTok{"beta\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
 \end{Highlighting}
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-22-1.pdf}
-
 \begin{Shaded}
 \begin{Highlighting}[]
-\NormalTok{ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
-\NormalTok{ci}
+\NormalTok{    gamma\_data1 }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_data5 }\SpecialCharTok{\%\textgreater{}\%}
+      \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+
+\NormalTok{    gamma\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ gamma\_data1, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }
+                                                \AttributeTok{color =}\NormalTok{ method))}\SpecialCharTok{+}
+      \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
+      \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+      \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter }
+\StringTok{           from Gamma Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+           \AttributeTok{y =} \StringTok{"Proportion (of xyz Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{) }\SpecialCharTok{+}
+      \FunctionTok{theme\_light}\NormalTok{()}
+
+\NormalTok{    gamma\_table }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_data }\SpecialCharTok{\%\textgreater{}\%}
+      \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"gamma"}\NormalTok{, }
+            \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_data)))}
+
+\NormalTok{    gamma\_table}
+\NormalTok{    gamma\_fig}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-## BOOTSTRAP CONFIDENCE INTERVAL CALCULATIONS
-## Based on 2000 bootstrap replicates
-## 
-## CALL : 
-## boot.ci(boot.out = results, type = "all")
-## 
-## Intervals : 
-## Level      Normal              Basic             Studentized     
-## 95%   (-0.2468,  0.2709 )   (-0.2415,  0.2733 )   (-0.2336,  0.2958 )  
-## 
-## Level     Percentile            BCa          
-## 95%   (-0.2554,  0.2594 )   (-0.2411,  0.2807 )  
-## Calculations and Intervals on Original Scale
-\end{verbatim}
 

### 2022-12-03 project/PaperTemplate/paper.Rmd
Finish first draft

@@
 ---
-title: A Comparision of Bootstrap Methods
+title: A Comparision of Bootstrap Confidence Interval Methods
 
@@
 keywords:
-- confidence interval
 - simulation
@@
 
-```{r}
+```{r, cache = TRUE}
 data(SnowGR)
@@
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", 
-       title = "Distribution of Annual Snowfall in Decemeber", y = "Count")
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count",
+       caption = "Fig. 1: Histogram with Studentized Interval Shown")
 ```
@@
 
-```{r}
+```{r, cache = TRUE}
+set.seed(495)
 orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
@@
 
-```{r}
+```{r, cache = TRUE}
 gf_dhistogram(~ mean, data = dec_means) %>%
   gf_dens() %>%
-  gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values")
+  gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values",
+          caption = "Fig. 2: Bootstrap Histogram")
 ```
@@
 
-```{r}
+```{r, cache = TRUE}
 mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * 
@@
 
-```{r}
+```{r, cache = TRUE}
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", 
-       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count",
+       caption = "Fig. 3: Histogram with Standard Interval Shown") +
   geom_vline(aes(xintercept= 13.85639)) +
@@
 
-```{r}
+```{r, cache = TRUE}
 qdata(~ mean, c(0.025, 0.975), data = dec_means)
@@
 
-```{r}
+```{r, cache = TRUE}
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", 
-       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count",
+       caption = "Fig. 4: Histogram with Percentile Interval Shown") +
   geom_vline(aes(xintercept= 13.91170)) +
@@
 
-```{r}
+```{r, cache = TRUE}
 sample_mean <- mean(~Dec, data = SnowGR); sample_mean
@@
 Then we find the proportion of bootstrap replications that have a sample mean less than the original sample mean.
-```{r}
+```{r, cache = TRUE}
 less_than_sample_mean <- sum(ifelse(dec_means <= sample_mean, 1, 0))/10000
@@
 From this, we can calculate the bias-correction value, $z_0$:
-```{r}
+```{r, cache = TRUE}
 z0 <- qnorm(less_than_sample_mean); z0
@@
 
-```{r}
+```{r, cache = TRUE}
 alphalow <- 0.025; alphahigh <- 0.975
@@
 
-```{r}
+```{r, cache = TRUE}
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", 
-       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count",
+       caption = "Fig. 5: Histogram with BC Interval Shown") +
   geom_vline(aes(xintercept= 14.01172)) +
@@
 
-```{r}
+```{r, cache = TRUE}
 theta <- function(x){mean(x)}
@@
 
-```{r}
+```{r, cache = TRUE}
 jackmean <- mean(~ jackknife_results$jack.values); jackmean
@@
 
-```{r}
+```{r, cache = TRUE}
 estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
@@
 
-```{r}
+```{r, cache = TRUE}
 a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
@@
 
-```{r}
+```{r, cache = TRUE}
 gf_histogram(~ Dec, data = SnowGR) +
-  labs(x = "Annual Snowfall in Decemeber", 
-       title = "Distribution of Annual Snowfall in Decemeber", y = "Count") +
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count",
+       caption = "Fig. 6: Histogram with BCa Interval Shown") +
   geom_vline(aes(xintercept= 13.91591)) +
@@
 
-```{r}
+```{r, cache = TRUE}
 set.seed(495)
@@
 c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
+
+```
+
+This would give us the following histogram:
+
+```{r, cache = TRUE}
+gf_histogram(~ Dec, data = SnowGR) +
+  labs(x = "Annual Snowfall in December", 
+       title = "Distribution of Annual Snowfall in December", y = "Count", 
+       caption = "Fig. 7: Histogram with Studentized Interval Shown") +
+  geom_vline(aes(xintercept= 14.03467)) +
+  geom_vline(aes(xintercept= 18.01709))
 
@@
 
-Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$ [@Guillaume21].
+```{r run simulation log normal, include = FALSE}
 
-```{r run simulation log normal}
+#Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$ [@Guillaume21].
+
 run_simulation_log_normal <- function(simulation_rep){
@@
 
-Lastly, we sample from a Beta distribution with shape parameters of 4 and 1 which gives us a true population mean of 0.8.
-
-```{r run simulation beta}
+```{r run simulation beta, include = FALSE}
 run_simulation_beta <- function(simulation_rep){
@@
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 50
+  sample_sizes = 10
+
   for (i in 1:5) {
     simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_gamma, mc.cores = detectCores())
+    results <- mclapply(simulation_rep, run_simulation_gamma, 
+                        mc.cores = detectCores())
     df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- unname(colSums(df)/sim_reps)
+    ci_prop <- colSums(df)/sim_reps
 
@@
     data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
+    sample_sizes <- sample_sizes+10
   }
@@
 
-```{r collect data log normal}
+```{r collect data log normal, include = FALSE}
 collect_data_log_normal <- function(sim_reps) {
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 50
+  sample_sizes = 10
 
@@
     simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_log_normal, mc.cores = detectCores())
+    results <- mclapply(simulation_rep, run_simulation_log_normal, 
+                        mc.cores = detectCores())
     df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
@@
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 50
+  sample_sizes = 10
 
@@
 
-```{r collect data beta}
+```{r collect data beta, include = FALSE}
 collect_data_beta <- function(sim_reps) {
   data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 50
+  sample_sizes = 10
 
@@
 set.seed(495)
-gamma_data1 <- collect_data_gamma(10000)
-write.csv(gamma_data1,"gamma_data1_10000.csv", row.names = FALSE)
+sim_reps <- 10000
 
-normal_data1 <- collect_data_normal(10000)
-write.csv(normal_data1,"normal_data1_10000.csv", row.names = FALSE)
+gamma_data <- collect_data_gamma(sim_reps)
+write.csv(gamma_data1,"gamma_data1.csv", row.names = FALSE)
 
-log_normal_data1 <- collect_data_log_normal(10000)
-write.csv(log_normal_data1,"log_normal1_data_10000.csv", row.names = FALSE)
-
-beta_data1 <- collect_data_beta(10000)
-write.csv(beta_data1,"beta_data1_10000.csv", row.names = FALSE)
+normal_data <- collect_data_normal(sim_reps)
+write.csv(normal_data1,"normal_data1.csv", row.names = FALSE)
 ```
 
-```{r, eval = FALSE}
-    gamma_data1 <- gamma_data5 %>%
+```{r, include = FALSE, eval = FALSE}
+#beta_data11 <- collect_data_beta(sim_reps)
+#write.csv(beta_data1,"beta_data1_100002.csv", row.names = FALSE)
+
+log_normal_data <- collect_data_log_normal(sim_reps)
+write.csv(log_normal_data1,"log_normal_data1.csv", row.names = FALSE)
+
+lognormal_df_long <- lognormal_df %>%
   pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
 
-    gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, 
-                                                color = method))+
-      geom_point() +
-      geom_line() + 
-      labs(title = "Proportion of CIs that Contain the True Parameter 
-           from Gamma Distibution", x = "Sample Size", 
-           y = "Proportion (of xyz Simulations)", color = "Method") +
-      theme_light()
+lognormal_fig <- ggplot(data = lognormal_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method") +
+  theme_light() + 
+  theme(legend.position="bottom")
 
-    gamma_table <- gamma_data %>%
-      kable(booktabs = TRUE, align = "c", caption = "gamma", 
-            col.names = gsub("[_]", " ", names(gamma_data)))
+lognormal_table <- lognormal_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "log normal", 
+        col.names = gsub("[_]", " ", names(lognormal_df)))
 
-    gamma_table
-    gamma_fig
+lognormal_df <- read.csv(file = 'log_normal1_data_10000.csv')
 
 ```
+
+Then, we can plot the results and compile the results into tables.
+
+```{r create graphs}
+
+gamma_df <- read.csv(file = 'gamma_data1_10000.csv')
+normal_df <- read.csv(file = 'normal_data1_10000.csv')
+
+gamma_df_long <- gamma_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+gamma_fig <- ggplot(data = gamma_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Gamma 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+gamma_table <- gamma_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled From Gamma Dist.", 
+        col.names = gsub("[_]", " ", names(gamma_df)))
+
+normal_df_long <- normal_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+normal_fig <- ggplot(data = normal_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+normal_table <- normal_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
+        col.names = gsub("[_]", " ", names(normal_df)))
+```
+
+```{r}
+gamma_fig
+gamma_table
+```
+
+When we sample from the Gamma distribution which is a distribution that is heavily skewed, the Studentized Confidence interval performs the best.
+At a large sample size, the Studentized Confidence interval contains the true population parameter about 94.5% of the time.
+The Studentized confidence interval outperforms the rest of the intervals by a bit.
+The rest of the intervals are very similar to each other ranging from a correct interval 92.5% to 93% of the time.
+In general, as the sample size that we are bootstrapping from increases, the higher percentage our confidence intervals predict correctly.
+
+```{r}
+normal_fig
+normal_table
+```
+
+Similar to when we sampled from the Gamma distribution, the Studentized confidence interval performed the best when we sampled from a Normal distribution with around 95% of the confidence intervals containing the true population parameter.
+The next best is the Standard confidence interval with a performance of around 94.5% correct intervals at a high sample size.
+The rest of the intervals performed similarly at around 94.2% accuracy.
+As before, the accuracy increased as the sample size increased.

### 2022-12-06 project/PaperTemplate/paper.Rmd
Added new simulation

@@
 
-```{r run simulation log normal, include = FALSE}
+```{r run simulation log normal}
 
@@
 
-```{r run simulation beta, include = FALSE}
+```{r run simulation beta}
 run_simulation_beta <- function(simulation_rep){
@@
 collect_data_gamma <- function(sim_reps) {
-  data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  data2 <- matrix(nrow = 7, ncol = 6)
+  sample_sizes = 4
 
-  for (i in 1:5) {
+  for (i in 1:7) {
     simulation_rep <- seq(1,sim_reps)
@@
     data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes+10
+    sample_sizes <- sample_sizes*2
   }
@@
 
-```{r collect data log normal, include = FALSE}
+```{r collect data log normal}
 collect_data_log_normal <- function(sim_reps) {
-  data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  data2 <- matrix(nrow = 7, ncol = 6)
+  sample_sizes = 4
 
-  for (i in 1:5) {
+  for (i in 1:7) {
     simulation_rep <- seq(1,sim_reps)
@@
 collect_data_normal <- function(sim_reps) {
-  data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  data2 <- matrix(nrow = 7, ncol = 6)
+  sample_sizes = 4
 
-  for (i in 1:5) {
+  for (i in 1:7) {
     simulation_rep <- seq(1,sim_reps)
@@
 
-```{r collect data beta, include = FALSE}
+```{r collect data beta}
 collect_data_beta <- function(sim_reps) {
-  data2 <- matrix(nrow = 5, ncol = 6)
-  sample_sizes = 10
+  data2 <- matrix(nrow = 7, ncol = 6)
+  sample_sizes = 4
 
-  for (i in 1:5) {
+  for (i in 1:7) {
     simulation_rep <- seq(1,sim_reps)
@@
 
-```{r, cache = TRUE, eval = FALSE}
+```{r, cache = TRUE}
 set.seed(495)
@@
 
-gamma_data <- collect_data_gamma(sim_reps)
-write.csv(gamma_data1,"gamma_data1.csv", row.names = FALSE)
+gamma_data_4_128 <- collect_data_gamma(sim_reps)
+write.csv(gamma_data_4_128,"gamma_data_4_128.csv", row.names = FALSE)
 
-normal_data <- collect_data_normal(sim_reps)
-write.csv(normal_data1,"normal_data1.csv", row.names = FALSE)
+normal_data_4_128 <- collect_data_normal(sim_reps)
+write.csv(normal_data_4_128,"normal_data_4_128.csv", row.names = FALSE)
+
+log_normal_data_4_128 <- collect_data_log_normal(sim_reps)
+write.csv(log_normal_data_4_128,"log_normal_data_4_128.csv", row.names = FALSE)
+
+beta_data_4_128 <- collect_data_beta(sim_reps)
+write.csv(beta_data_4_128,"beta_data_4_128.csv", row.names = FALSE)
 ```
@@
 ```{r, include = FALSE, eval = FALSE}
-#beta_data11 <- collect_data_beta(sim_reps)
-#write.csv(beta_data1,"beta_data1_100002.csv", row.names = FALSE)
-
-log_normal_data <- collect_data_log_normal(sim_reps)
-write.csv(log_normal_data1,"log_normal_data1.csv", row.names = FALSE)
 
@@
 normal_df <- read.csv(file = 'normal_data1_10000.csv')
+log_normal_df <- read.csv(file = 'log_normal1_data_10000.csv')
 
-gamma_df_long <- gamma_df %>%
+gamma_df_long <- log_normal_df %>%
   pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
@@
 As before, the accuracy increased as the sample size increased.
+
+```{r}
+library(boot)
+
+mean.fun <- function(d, i) {
+  d <- X[i]
+  return (c(mean(d), sd(d)))
+}
+
+sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
+num_sample_sizes <- length(sample_sizes)
+master <- matrix(nrow = num_sample_sizes, ncol = 6)
+
+for(i in 1:num_sample_sizes) {
+
+  sim_reps <- 10000
+  norm_contains <- rep(0, sim_reps)
+  basic_contains <- rep(0, sim_reps)
+  student_contains <- rep(0, sim_reps)
+  percentile_contains <- rep(0, sim_reps)
+  bca_contains <- rep(0, sim_reps)
+
+  boot_reps <- 2000
+  n <- sample_sizes[i]
+  true_mean <- exp(1/2)
+
+  set.seed(495)
+  for (j in 1:sim_reps) {
+    X <- rlnorm(n, 0, 1)
+    values <- data.frame(X)
+
+    results <- boot(data = values, statistic = mean.fun, R = boot_reps)
+    results
+    #plot(results)
+    ci <- boot.ci(results, type = "all")
+
+    norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+    basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+    student_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+    percentile_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+    bca_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+
+  }
+
+  master[i, 1] <- sample_sizes[i]
+  master[i, 2] <- sum(norm_contains)/sim_reps
+  master[i, 3] <- sum(basic_contains)/sim_reps
+  master[i, 4] <- sum(student_contains)/sim_reps
+  master[i, 5] <- sum(percentile_contains)/sim_reps
+  master[i, 6] <- sum(bca_contains)/sim_reps
+
+}
+
+```

### 2022-12-06 project/PaperTemplate/paper.Rmd
Redid simulation

@@
 
-```{r, cache = TRUE}
+```{r, cache = TRUE, eval = FALSE}
 set.seed(495)
@@
 
-```{r}
+```{r, warning = FALSE}
 library(boot)
 
+run_sim_log_normal <- function(sim_reps) {
+  set.seed(495)
   mean.fun <- function(d, i) {
@@
 
-  sim_reps <- 10000
     norm_contains <- rep(0, sim_reps)
@@
 
-  set.seed(495)
     for (j in 1:sim_reps) {
@@
       basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-    student_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-    percentile_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-    bca_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
 
@@
     master[i, 6] <- sum(bca_contains)/sim_reps
+  }
+
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
+             "Percentile" = V5, "BCa" = V6) 
+  master_df
+}
+```
+
+```{r}
+master_df_long <- master_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+master_fig <- ggplot(data = master_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+master_fig
+```
+```{r, warning = FALSE}
+library(boot)
+
+run_sim_normal <- function(sim_reps) {
+  set.seed(495)
+  mean.fun <- function(d, i) {
+    d <- X[i]
+    return (c(mean(d), sd(d)))
+  }
+
+  sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
+  num_sample_sizes <- length(sample_sizes)
+  master <- matrix(nrow = num_sample_sizes, ncol = 6)
+
+  for(i in 1:num_sample_sizes) {
+
+    norm_contains <- rep(0, sim_reps)
+    basic_contains <- rep(0, sim_reps)
+    student_contains <- rep(0, sim_reps)
+    percentile_contains <- rep(0, sim_reps)
+    bca_contains <- rep(0, sim_reps)
+
+    boot_reps <- 2000
+    n <- sample_sizes[i]
+    true_mean <- 0
+
+    for (j in 1:sim_reps) {
+      X <- rnorm(n, 0, 1)
+      values <- data.frame(X)
+
+      results <- boot(data = values, statistic = mean.fun, R = boot_reps)
+      results
+      #plot(results)
+      ci <- boot.ci(results, type = "all")
+
+      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
 
@@
 
+    master[i, 1] <- sample_sizes[i]
+    master[i, 2] <- sum(norm_contains)/sim_reps
+    master[i, 3] <- sum(basic_contains)/sim_reps
+    master[i, 4] <- sum(student_contains)/sim_reps
+    master[i, 5] <- sum(percentile_contains)/sim_reps
+    master[i, 6] <- sum(bca_contains)/sim_reps
+  }
+
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
+             "Percentile" = V5, "BCa" = V6) 
+  master_df
+}
+
 ```
+
+```{r, warning = FALSE}
+library(boot)
+
+run_sim_gamma <- function(sim_reps) {
+  set.seed(495)
+  mean.fun <- function(d, i) {
+    d <- X[i]
+    return (c(mean(d), sd(d)))
+  }
+
+  sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
+  num_sample_sizes <- length(sample_sizes)
+  master <- matrix(nrow = num_sample_sizes, ncol = 6)
+
+  for(i in 1:num_sample_sizes) {
+
+    norm_contains <- rep(0, sim_reps)
+    basic_contains <- rep(0, sim_reps)
+    student_contains <- rep(0, sim_reps)
+    percentile_contains <- rep(0, sim_reps)
+    bca_contains <- rep(0, sim_reps)
+
+    boot_reps <- 2000
+    n <- sample_sizes[i]
+    true_mean <- 4
+
+    for (j in 1:sim_reps) {
+      X <- rgamma(sample_sizes, shape = 1, scale = 4)
+      values <- data.frame(X)
+
+      results <- boot(data = values, statistic = mean.fun, R = boot_reps)
+      results
+      #plot(results)
+      ci <- boot.ci(results, type = "all")
+
+      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+
+    }
+
+    master[i, 1] <- sample_sizes[i]
+    master[i, 2] <- sum(norm_contains)/sim_reps
+    master[i, 3] <- sum(basic_contains)/sim_reps
+    master[i, 4] <- sum(student_contains)/sim_reps
+    master[i, 5] <- sum(percentile_contains)/sim_reps
+    master[i, 6] <- sum(bca_contains)/sim_reps
+  }
+
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
+             "Percentile" = V5, "BCa" = V6) 
+  master_df
+}
+
+```
+
+```{r}
+set.seed(495)
+log_normal_df <- run_sim_log_normal(10000)
+write.csv(log_normal_df,"log_normal_df.csv", row.names = FALSE)
+
+normal_df <- run_sim_normal(10000)
+write.csv(normal_df,"normal_data_df.csv", row.names = FALSE)
+
+gamma_df <- run_sim_gamma(10000)
+write.csv(gamma_df,"gamma_data_df.csv", row.names = FALSE)
+
+```

### 2022-12-06 project/PaperTemplate/paper.tex
Redid simulation

@@
 {
-  \title{\bf A Comparision of Bootstrap Methods}
+  \title{\bf A Comparision of Bootstrap Confidence Interval Methods}
 
@@
   \begin{center}
-    {\LARGE\bf A Comparision of Bootstrap Methods}
+    {\LARGE\bf A Comparision of Bootstrap Confidence Interval Methods}
   \end{center}
@@
 \noindent%
-{\it Keywords:} confidence
-interval, simulation, percentile, bias-corrected, acceleration, studentized
+{\it Keywords:} simulation, percentile, bias-corrected, acceleration, studentized
 \vfill
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{)}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 1: Histogram with Studentized Interval Shown"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
 \NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
@@
   \FunctionTok{gf\_dens}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{)}
+  \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{,}
+          \AttributeTok{caption =} \StringTok{"Fig. 2: Bootstrap Histogram"}\NormalTok{)}
 \end{Highlighting}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 3: Histogram with Standard Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 4: Histogram with Percentile Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 5: Histogram with BC Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
@@
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 6: Histogram with BCa Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
@@
 
+This would give us the following histogram:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
+       \AttributeTok{caption =} \StringTok{"Fig. 7: Histogram with Studentized Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.03467}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{18.01709}\NormalTok{)) }
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-19-1.pdf}
+
 \hypertarget{simulation}{%
@@
 
-Third, we sample from a Log-Normal distribution with mean log of 0 and a
-mean standard deviation of 1. Therefore, the true population mean of
-this distribution is \(e^{\frac{1}{2}}\) \citep{Guillaume21}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_simulation\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
-\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}
-
-\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rlnorm}\NormalTok{(sample\_sizes, }\AttributeTok{meanlog =} \DecValTok{0}\NormalTok{, }\AttributeTok{sdlog =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
-\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
-\NormalTok{  res}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-Lastly, we sample from a Beta distribution with shape parameters of 4
-and 1 which gives us a true population mean of 0.8.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_simulation\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
-\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FloatTok{0.8}
-
-\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rbeta}\NormalTok{(sample\_sizes, }\AttributeTok{shape1 =} \DecValTok{4}\NormalTok{, }\AttributeTok{shape2 =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
-\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
-\NormalTok{  res}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 After that, these functions will compile all of the information we have
@@
 \NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}
+
   \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
 \NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
-\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
+\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }
+                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
 \NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
+\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps}
 
@@
 \NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
-\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
+\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
 \NormalTok{  \}}
@@
 \begin{Highlighting}[]
-\NormalTok{collect\_data\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
-
-  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
-\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_log\_normal, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
-\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
-
-\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
-\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
-\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
-\NormalTok{  \}}
-
-\NormalTok{  log\_normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
-           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  log\_normal\_output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
 \NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
+\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{collect\_data\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
-
-  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
-\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_beta, }
-                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
-\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
-
-\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
-\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
-\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
-\NormalTok{  \}}
-
-\NormalTok{  beta\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
-           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  beta\_output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 And here, we run the simulations for each of the distributions and store
@@
 \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{gamma\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(gamma\_data1,}\StringTok{"gamma\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{normal\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(normal\_data1,}\StringTok{"normal\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{log\_normal\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(log\_normal\_data1,}\StringTok{"log\_normal1\_data\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{beta\_data1 }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_beta}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(beta\_data1,}\StringTok{"beta\_data1\_10000.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{    gamma\_data1 }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_data5 }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{sim\_reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
+
+\NormalTok{gamma\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_gamma}\NormalTok{(sim\_reps)}
+\FunctionTok{write.csv}\NormalTok{(gamma\_data1,}\StringTok{"gamma\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{normal\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_normal}\NormalTok{(sim\_reps)}
+\FunctionTok{write.csv}\NormalTok{(normal\_data1,}\StringTok{"normal\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+Then, we can plot the results and compile the results into tables.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}
+
+\NormalTok{gamma\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
   \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
 
-\NormalTok{    gamma\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ gamma\_data1, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }
-                                                \AttributeTok{color =}\NormalTok{ method))}\SpecialCharTok{+}
-      \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
-      \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-      \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter }
-\StringTok{           from Gamma Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
-           \AttributeTok{y =} \StringTok{"Proportion (of xyz Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{) }\SpecialCharTok{+}
-      \FunctionTok{theme\_light}\NormalTok{()}
-
-\NormalTok{    gamma\_table }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_data }\SpecialCharTok{\%\textgreater{}\%}
-      \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"gamma"}\NormalTok{, }
-            \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_data)))}
-
-\NormalTok{    gamma\_table}
-\NormalTok{    gamma\_fig}
-\end{Highlighting}
-\end{Shaded}
+\NormalTok{gamma\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ gamma\_df\_long, }
+                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Gamma }
+\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
+
+\NormalTok{gamma\_table }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled From Gamma Dist."}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_df))) }
+
+\NormalTok{normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+
+\NormalTok{normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ normal\_df\_long, }
+                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Normal }
+\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
+
+\NormalTok{normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-22-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_table}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:create graphs}Sampled From Gamma Dist.}
+\centering
+\begin{tabular}[t]{cccccc}
+\toprule
+Sample Size & Standard & Percentile & BC & BCa & Studentized\\
+\midrule
+100 & 0.9205 & 0.9210 & 0.9226 & 0.9182 & 0.9406\\
+200 & 0.9284 & 0.9286 & 0.9305 & 0.9257 & 0.9463\\
+400 & 0.9298 & 0.9291 & 0.9310 & 0.9273 & 0.9465\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+When we sample from the Gamma distribution which is a distribution that
+is heavily skewed, the Studentized Confidence interval performs the
+best. At a large sample size, the Studentized Confidence interval
+contains the true population parameter about 94.5\% of the time. The
+Studentized confidence interval outperforms the rest of the intervals by
+a bit. The rest of the intervals are very similar to each other ranging
+from a correct interval 92.5\% to 93\% of the time. In general, as the
+sample size that we are bootstrapping from increases, the higher
+percentage our confidence intervals predict correctly.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-23-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_table}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:create graphs}Sampled from Normal Dist.}
+\centering
+\begin{tabular}[t]{cccccc}
+\toprule
+Sample Size & Standard & Percentile & BC & BCa & Studentized\\
+\midrule
+100 & 0.9415 & 0.9394 & 0.9391 & 0.9390 & 0.9483\\
+200 & 0.9448 & 0.9411 & 0.9405 & 0.9404 & 0.9489\\
+400 & 0.9464 & 0.9417 & 0.9421 & 0.9426 & 0.9503\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Similar to when we sampled from the Gamma distribution, the Studentized
+confidence interval performed the best when we sampled from a Normal
+distribution with around 95\% of the confidence intervals containing the
+true population parameter. The next best is the Standard confidence
+interval with a performance of around 94.5\% correct intervals at a high
+sample size. The rest of the intervals performed similarly at around
+94.2\% accuracy. As before, the accuracy increased as the sample size
+increased.
 

### 2022-12-06 project/PaperTemplate/paper.Rmd
Last commit before deleting old simulation
Knitted to pdf

@@
 
-```{r find CIs}
-findCIs <- function(sampleinput, nboot) {
-
-  sample_mean <- mean(~ X, data = sampleinput)
-  sample_sd <- sd(~ X, data = sampleinput)
-  sample_n <- nrow(sampleinput)
-  sample_se <- sample_sd/sqrt(sample_n)
-
-  alphalow <- 0.025
-  alphahigh <- 0.975
-
-  #perform bootstrap
-  mean <- rep(0,nboot)
-  sd <- rep(0,nboot)
-  se <- rep(0,nboot)
-  t_stat <- rep(0,nboot)
-
-  for (i in 1:nboot) {
-    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
-    mean[i] <- mean(~ X, data = resampled)
-    sd[i] <- sd(~ X, data = resampled)
-    se[i] <- sd[i]/sqrt(nrow(resampled))
-    t_stat[i] <- (mean[i] - sample_mean)/se[i]
-  }
-
-  boot_means <- as.data.frame(mean)
-  boot_t_stat <- as.data.frame(t_stat)
-
-  # find the standard confidence interval
-  standard_interval <- sample_mean + 
-    qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)
-
-  # find percentile interval
-  percentile_interval <- qdata(~ mean, c(0.025, 0.975), data = boot_means)
-
-  # find BC interval
-  less_than_sample_mean <- sum(ifelse(boot_means <= sample_mean, 1, 0))/nboot
-  z0 <- qnorm(less_than_sample_mean)
-  newlow <- pnorm(2*z0 + qnorm(alphalow))
-  newhigh <- pnorm(2*z0 + qnorm(alphahigh))
-
-  bc_interval <- qdata(~ mean, c(newlow, newhigh), data = boot_means)
-
-  # find BCa interval
-  theta <- function(x){mean(x)}
-  jackknife_results <- bootstrap::jackknife(sampleinput$X, theta)
-  jackmean <- mean(~ jackknife_results$jack.values)
-  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
-    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
-  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
-                      (1-estimated_a*(z0 + qnorm(alphalow))))
-  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
-                       (1-estimated_a*(z0 + qnorm(alphahigh))))
-  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)
-
-  # find studentized interval
-  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
-  lower_q <- t_q[1]
-  upper_q <- t_q[2]
-  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))
-
-  output <- list(standard_interval, percentile_interval, bc_interval, 
-                 bca_interval, t_interval)
-  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", 
-                     "BCa Interval", "Studentized Interval")
-  output
-}
-```
-
 Next, we will create the simulation that picks the random sample from a distribution and tests to see if the sample creates bootstrapped confidence intervals that contain the true population parameter.
@@
 
-```{r run simulation normal}
-run_simulation_normal <- function(simulation_rep){
-  trueparameter <- 0
-
-  X <- rnorm(sample_sizes, mean = 0, sd = 1)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-```
-
 Second, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4. This means the true population parameter is 4.
-
-```{r run simulation gamma}
-run_simulation_gamma <- function(simulation_rep){
-  trueparameter <- 4
-
-  X <- rgamma(sample_sizes, shape = 1, scale = 4)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-```
-
-```{r run simulation log normal}
-
-#Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$ [@Guillaume21].
-
-run_simulation_log_normal <- function(simulation_rep){
-  trueparameter <- exp(1/2)
-
-  X <- rlnorm(sample_sizes, meanlog = 0, sdlog = 1)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-```
-
-```{r run simulation beta}
-run_simulation_beta <- function(simulation_rep){
-  trueparameter <- 0.8
-
-  X <- rbeta(sample_sizes, shape1 = 4, shape2 = 1)
-  values <- data.frame(X)
-  output <- findCIs(values, 2000)
-  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
-    trueparameter <= output$`Standard Interval`[2],
-    trueparameter >= output$`Percentile Interval`[1] & 
-    trueparameter <= output$`Percentile Interval`[2],
-    trueparameter >= output$`BC Interval`[1] &
-    trueparameter <= output$`BC Interval`[2],
-    trueparameter >= output$`BCa Interval`[1] & 
-    trueparameter <= output$`BCa Interval`[2],
-    trueparameter >= output$`Studentized Interval`[1] & 
-    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
-  res <- rbind(data.frame(), ci)
-  res
-}
-
-```
 
@@
 
-```{r collect data gamma}
-collect_data_gamma <- function(sim_reps) {
-  data2 <- matrix(nrow = 7, ncol = 6)
-  sample_sizes = 4
-
-  for (i in 1:7) {
-    simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_gamma, 
-                        mc.cores = detectCores())
-    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- colSums(df)/sim_reps
-
-    data2[i, 1] <- sample_sizes
-    data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
-  }
-
-  gamma_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
-           "BCa" = V5, "Studentized" = V6) 
-  gamma_output
-}
-
-```
-
-```{r collect data log normal}
-collect_data_log_normal <- function(sim_reps) {
-  data2 <- matrix(nrow = 7, ncol = 6)
-  sample_sizes = 4
-
-  for (i in 1:7) {
-    simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_log_normal, 
-                        mc.cores = detectCores())
-    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- unname(colSums(df)/sim_reps)
-
-    data2[i, 1] <- sample_sizes
-    data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
-  }
-
-  log_normal_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
-           "BCa" = V5, "Studentized" = V6) 
-  log_normal_output
-}
-```
-
-```{r collect data normal}
-collect_data_normal <- function(sim_reps) {
-  data2 <- matrix(nrow = 7, ncol = 6)
-  sample_sizes = 4
-
-  for (i in 1:7) {
-    simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_normal, 
-                        mc.cores = detectCores())
-    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- unname(colSums(df)/sim_reps)
-
-    data2[i, 1] <- sample_sizes
-    data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
-  }
-
-  normal_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
-           "BCa" = V5, "Studentized" = V6) 
-  normal_output
-}
-
-```
-
-```{r collect data beta}
-collect_data_beta <- function(sim_reps) {
-  data2 <- matrix(nrow = 7, ncol = 6)
-  sample_sizes = 4
-
-  for (i in 1:7) {
-    simulation_rep <- seq(1,sim_reps)
-    results <- mclapply(simulation_rep, run_simulation_beta, 
-                        mc.cores = detectCores())
-    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
-    ci_prop <- unname(colSums(df)/sim_reps)
-
-    data2[i, 1] <- sample_sizes
-    data2[i, 2:6] <- ci_prop
-    sample_sizes <- sample_sizes*2
-  }
-
-  beta_output <- as.data.frame(data2) %>% 
-    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
-           "BCa" = V5, "Studentized" = V6) 
-  beta_output
-}
-
-```
-
 And here, we run the simulations for each of the distributions and store the results.
 
-```{r, cache = TRUE, eval = FALSE}
-set.seed(495)
-sim_reps <- 10000
-
-gamma_data_4_128 <- collect_data_gamma(sim_reps)
-write.csv(gamma_data_4_128,"gamma_data_4_128.csv", row.names = FALSE)
-
-normal_data_4_128 <- collect_data_normal(sim_reps)
-write.csv(normal_data_4_128,"normal_data_4_128.csv", row.names = FALSE)
-
-log_normal_data_4_128 <- collect_data_log_normal(sim_reps)
-write.csv(log_normal_data_4_128,"log_normal_data_4_128.csv", row.names = FALSE)
-
-beta_data_4_128 <- collect_data_beta(sim_reps)
-write.csv(beta_data_4_128,"beta_data_4_128.csv", row.names = FALSE)
-```
-
-```{r, include = FALSE, eval = FALSE}
-
-lognormal_df_long <- lognormal_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-lognormal_fig <- ggplot(data = lognormal_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal 
-       Distibution", x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method") +
-  theme_light() + 
-  theme(legend.position="bottom")
-
-lognormal_table <- lognormal_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "log normal", 
-        col.names = gsub("[_]", " ", names(lognormal_df)))
-
-lognormal_df <- read.csv(file = 'log_normal1_data_10000.csv')
-
-```
-
 Then, we can plot the results and compile the results into tables.
-
-```{r create graphs}
-
-gamma_df <- read.csv(file = 'gamma_data1_10000.csv')
-normal_df <- read.csv(file = 'normal_data1_10000.csv')
-log_normal_df <- read.csv(file = 'log_normal1_data_10000.csv')
-
-gamma_df_long <- log_normal_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-gamma_fig <- ggplot(data = gamma_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Gamma 
-       Distibution", x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist.") +
-  theme_light() +
-  theme(legend.position="bottom")
-
-gamma_table <- gamma_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled From Gamma Dist.", 
-        col.names = gsub("[_]", " ", names(gamma_df)))
-
-normal_df_long <- normal_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-normal_fig <- ggplot(data = normal_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
-       Distibution", x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist.") +
-  theme_light() +
-  theme(legend.position="bottom")
-
-normal_table <- normal_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
-        col.names = gsub("[_]", " ", names(normal_df)))
-```
-
-```{r}
-gamma_fig
-gamma_table
-```
 
@@
 In general, as the sample size that we are bootstrapping from increases, the higher percentage our confidence intervals predict correctly.
-
-```{r}
-normal_fig
-normal_table
-```
 
@@
 
-```{r}
-master_df_long <- master_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-master_fig <- ggplot(data = master_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal
-       Distibution", x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
-  theme_light() +
-  theme(legend.position="bottom")
-
-master_fig
-```
 ```{r, warning = FALSE}
@@
 
-```{r}
+```{r, warning = FALSE, eval = FALSE}
 set.seed(495)
@@
 ```
+
+```{r create graphs}
+
+gamma_df <- read.csv(file = 'gamma_data_df.csv')
+normal_df <- read.csv(file = 'normal_data_df.csv')
+log_normal_df <- read.csv(file = 'log_normal_df.csv')
+
+gamma_df_long <- gamma_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+gamma_fig <- ggplot(data = gamma_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Gamma 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+gamma_table <- gamma_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled From Gamma Dist.", 
+        col.names = gsub("[_]", " ", names(gamma_df)))
+
+normal_df_long <- normal_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+normal_fig <- ggplot(data = normal_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+normal_table <- normal_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
+        col.names = gsub("[_]", " ", names(normal_df)))
+
+log_normal_df_long <- log_normal_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+log_normal_fig <- ggplot(data = log_normal_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+log_normal_table <- log_normal_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
+        col.names = gsub("[_]", " ", names(log_normal_df)))
+
+```
+
+```{r}
+log_normal_fig
+log_normal_table
+
+normal_fig
+normal_table
+
+gamma_fig
+gamma_table
+
+```
+
+```{r, eval = FALSE}
+
+normal_df <- read.csv(file = 'normal_data_df.csv')
+
+master_df_long <- master_df %>%
+  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+
+master_fig <- ggplot(data = master_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+master_fig
+```

### 2022-12-06 project/PaperTemplate/paper.tex
Knitted to pdf

@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{findCIs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sampleinput, nboot) \{}
-
-\NormalTok{  sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
-\NormalTok{  sample\_sd }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
-\NormalTok{  sample\_n }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(sampleinput)}
-\NormalTok{  sample\_se }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
-
-\NormalTok{  alphalow }\OtherTok{\textless{}{-}} \FloatTok{0.025}
-\NormalTok{  alphahigh }\OtherTok{\textless{}{-}} \FloatTok{0.975}
-
-  \CommentTok{\#perform bootstrap}
-\NormalTok{  mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-\NormalTok{  sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-\NormalTok{  se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-\NormalTok{  t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-
-  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
-\NormalTok{    resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(sampleinput, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
-\NormalTok{    sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
-\NormalTok{    se[i] }\OtherTok{\textless{}{-}}\NormalTok{ sd[i]}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(resampled))}
-\NormalTok{    t\_stat[i] }\OtherTok{\textless{}{-}}\NormalTok{ (mean[i] }\SpecialCharTok{{-}}\NormalTok{ sample\_mean)}\SpecialCharTok{/}\NormalTok{se[i]}
-\NormalTok{  \}}
-
-\NormalTok{  boot\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
-\NormalTok{  boot\_t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(t\_stat)}
-
-  \CommentTok{\# find the standard confidence interval}
-\NormalTok{  standard\_interval }\OtherTok{\textless{}{-}}\NormalTok{ sample\_mean }\SpecialCharTok{+} 
-    \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}
-
-  \CommentTok{\# find percentile interval}
-\NormalTok{  percentile\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{data =}\NormalTok{ boot\_means)}
-
-  \CommentTok{\# find BC interval}
-\NormalTok{  less\_than\_sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\FunctionTok{ifelse}\NormalTok{(boot\_means }\SpecialCharTok{\textless{}=}\NormalTok{ sample\_mean, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}\SpecialCharTok{/}\NormalTok{nboot}
-\NormalTok{  z0 }\OtherTok{\textless{}{-}} \FunctionTok{qnorm}\NormalTok{(less\_than\_sample\_mean)}
-\NormalTok{  newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}
-\NormalTok{  newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}
-
-\NormalTok{  bc\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(newlow, newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}
-
-  \CommentTok{\# find BCa interval}
-\NormalTok{  theta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{mean}\NormalTok{(x)\}}
-\NormalTok{  jackknife\_results }\OtherTok{\textless{}{-}}\NormalTok{ bootstrap}\SpecialCharTok{::}\FunctionTok{jackknife}\NormalTok{(sampleinput}\SpecialCharTok{$}\NormalTok{X, theta)}
-\NormalTok{  jackmean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values)}
-\NormalTok{  estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
-\NormalTok{    (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{)}
-\NormalTok{  a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
-\NormalTok{                      (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))))}
-\NormalTok{  a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
-\NormalTok{                       (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))))}
-\NormalTok{  bca\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}
-
-  \CommentTok{\# find studentized interval}
-\NormalTok{  t\_q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(boot\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
-\NormalTok{  lower\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{1}\NormalTok{]}
-\NormalTok{  upper\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{2}\NormalTok{]}
-\NormalTok{  t\_interval }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (upper\_q}\SpecialCharTok{*}\NormalTok{sample\_se), sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (lower\_q}\SpecialCharTok{*}\NormalTok{sample\_se))}
-
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(standard\_interval, percentile\_interval, bc\_interval, }
-\NormalTok{                 bca\_interval, t\_interval)}
-  \FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Standard Interval"}\NormalTok{, }\StringTok{"Percentile Interval"}\NormalTok{, }\StringTok{"BC Interval"}\NormalTok{, }
-                     \StringTok{"BCa Interval"}\NormalTok{, }\StringTok{"Studentized Interval"}\NormalTok{)}
-\NormalTok{  output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 Next, we will create the simulation that picks the random sample from a
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_simulation\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
-\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{0}
-
-\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(sample\_sizes, }\AttributeTok{mean =} \DecValTok{0}\NormalTok{, }\AttributeTok{sd =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
-\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
-\NormalTok{  res}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 Second, we select from a Gamma Distribution with a shape parameter of 1
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_simulation\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
-\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{4}
-
-\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
-\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
-\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
-\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
-\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
-\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
-\NormalTok{  res}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 After that, these functions will compile all of the information we have
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{collect\_data\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}
-
-  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
-\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }
-                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
-\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-
-\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
-\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
-\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
-\NormalTok{  \}}
-
-\NormalTok{  gamma\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
-           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  gamma\_output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}
-
-  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
-\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_normal, }
-                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
-\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
-\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}
-
-\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
-\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
-\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
-\NormalTok{  \}}
-
-\NormalTok{  normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
-    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
-           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  normal\_output}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
 And here, we run the simulations for each of the distributions and store
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
+Then, we can plot the results and compile the results into tables.
+
+When we sample from the Gamma distribution which is a distribution that
+is heavily skewed, the Studentized Confidence interval performs the
+best. At a large sample size, the Studentized Confidence interval
+contains the true population parameter about 94.5\% of the time. The
+Studentized confidence interval outperforms the rest of the intervals by
+a bit. The rest of the intervals are very similar to each other ranging
+from a correct interval 92.5\% to 93\% of the time. In general, as the
+sample size that we are bootstrapping from increases, the higher
+percentage our confidence intervals predict correctly.
+
+Similar to when we sampled from the Gamma distribution, the Studentized
+confidence interval performed the best when we sampled from a Normal
+distribution with around 95\% of the confidence intervals containing the
+true population parameter. The next best is the Standard confidence
+interval with a performance of around 94.5\% correct intervals at a high
+sample size. The rest of the intervals performed similarly at around
+94.2\% accuracy. As before, the accuracy increased as the sample size
+increased.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(boot)}
+
+\NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
   \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{sim\_reps }\OtherTok{\textless{}{-}} \DecValTok{10000}
-
-\NormalTok{gamma\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_gamma}\NormalTok{(sim\_reps)}
-\FunctionTok{write.csv}\NormalTok{(gamma\_data1,}\StringTok{"gamma\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{normal\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_normal}\NormalTok{(sim\_reps)}
-\FunctionTok{write.csv}\NormalTok{(normal\_data1,}\StringTok{"normal\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-Then, we can plot the results and compile the results into tables.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}
-\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  \}}
+
+\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
+\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
+
+\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+
+\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}
+
+    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
+\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rlnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
+\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
+\NormalTok{      results}
+      \CommentTok{\#plot(results)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+
+\NormalTok{    \}}
+
+\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{  \}}
+
+\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  master\_df}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(boot)}
+
+\NormalTok{run\_sim\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+  \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  \}}
+
+\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
+\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
+
+\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+
+\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{0}
+
+    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
+\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
+\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
+\NormalTok{      results}
+      \CommentTok{\#plot(results)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+
+\NormalTok{    \}}
+
+\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{  \}}
+
+\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  master\_df}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(boot)}
+
+\NormalTok{run\_sim\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+  \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  \}}
+
+\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
+\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
+
+\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+
+\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{4}
+
+    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
+\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
+\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
+\NormalTok{      results}
+      \CommentTok{\#plot(results)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+
+\NormalTok{    \}}
+
+\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{  \}}
+
+\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
+\NormalTok{  master\_df}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
+\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(log\_normal\_df,}\StringTok{"log\_normal\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(normal\_df,}\StringTok{"normal\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(gamma\_df,}\StringTok{"gamma\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data\_df.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}log\_normal\_df.csv\textquotesingle{}}\NormalTok{)}
 
@@
         \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)))}
-\end{Highlighting}
-\end{Shaded}
+
+\NormalTok{log\_normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+
+\NormalTok{log\_normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ log\_normal\_df\_long, }
+                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal }
+\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
+
+\NormalTok{log\_normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(log\_normal\_df)))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{log\_normal\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-24-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{log\_normal\_table}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:create graphs}Sampled from Normal Dist.}
+\centering
+\begin{tabular}[t]{cccccc}
+\toprule
+Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
+\midrule
+4 & 0.6795 & 0.6542 & 0.8186 & 0.6810 & 0.6814\\
+10 & 0.7911 & 0.7684 & 0.8526 & 0.8019 & 0.8266\\
+15 & 0.8268 & 0.8061 & 0.8705 & 0.8387 & 0.8552\\
+20 & 0.8437 & 0.8236 & 0.8797 & 0.8526 & 0.8725\\
+30 & 0.8639 & 0.8464 & 0.8951 & 0.8734 & 0.8900\\
+\addlinespace
+40 & 0.8789 & 0.8623 & 0.9055 & 0.8881 & 0.9013\\
+60 & 0.8897 & 0.8783 & 0.9100 & 0.8978 & 0.9069\\
+80 & 0.9088 & 0.8969 & 0.9218 & 0.9136 & 0.9181\\
+100 & 0.9103 & 0.8980 & 0.9264 & 0.9162 & 0.9229\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-24-2.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_table}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:create graphs}Sampled from Normal Dist.}
+\centering
+\begin{tabular}[t]{cccccc}
+\toprule
+Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
+\midrule
+4 & 0.8046 & 0.7913 & 0.9058 & 0.7941 & 0.7943\\
+10 & 0.9015 & 0.9005 & 0.9265 & 0.9007 & 0.8994\\
+15 & 0.9187 & 0.9183 & 0.9331 & 0.9184 & 0.9167\\
+20 & 0.9257 & 0.9249 & 0.9357 & 0.9242 & 0.9235\\
+30 & 0.9363 & 0.9372 & 0.9421 & 0.9351 & 0.9323\\
+\addlinespace
+40 & 0.9421 & 0.9421 & 0.9466 & 0.9416 & 0.9416\\
+60 & 0.9381 & 0.9390 & 0.9420 & 0.9389 & 0.9386\\
+80 & 0.9403 & 0.9408 & 0.9430 & 0.9406 & 0.9396\\
+100 & 0.9483 & 0.9478 & 0.9499 & 0.9475 & 0.9480\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-22-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-24-3.pdf}
 
@@
 \toprule
-Sample Size & Standard & Percentile & BC & BCa & Studentized\\
+Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
 \midrule
-100 & 0.9205 & 0.9210 & 0.9226 & 0.9182 & 0.9406\\
-200 & 0.9284 & 0.9286 & 0.9305 & 0.9257 & 0.9463\\
-400 & 0.9298 & 0.9291 & 0.9310 & 0.9273 & 0.9465\\
+4 & 0.8494 & 0.8332 & 0.9039 & 0.8578 & 0.8750\\
+10 & 0.8476 & 0.8291 & 0.9008 & 0.8543 & 0.8708\\
+15 & 0.8510 & 0.8322 & 0.9012 & 0.8563 & 0.8706\\
+20 & 0.8458 & 0.8274 & 0.9030 & 0.8511 & 0.8672\\
+30 & 0.8380 & 0.8218 & 0.8954 & 0.8463 & 0.8642\\
+\addlinespace
+40 & 0.8480 & 0.8313 & 0.8989 & 0.8525 & 0.8664\\
+60 & 0.8466 & 0.8292 & 0.9069 & 0.8571 & 0.8741\\
+80 & 0.8486 & 0.8310 & 0.9016 & 0.8535 & 0.8717\\
+100 & 0.8478 & 0.8308 & 0.8974 & 0.8533 & 0.8660\\
 \bottomrule
@@
 
-When we sample from the Gamma distribution which is a distribution that
-is heavily skewed, the Studentized Confidence interval performs the
-best. At a large sample size, the Studentized Confidence interval
-contains the true population parameter about 94.5\% of the time. The
-Studentized confidence interval outperforms the rest of the intervals by
-a bit. The rest of the intervals are very similar to each other ranging
-from a correct interval 92.5\% to 93\% of the time. In general, as the
-sample size that we are bootstrapping from increases, the higher
-percentage our confidence intervals predict correctly.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_fig}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-23-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_table}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}
-
-\caption{\label{tab:create graphs}Sampled from Normal Dist.}
-\centering
-\begin{tabular}[t]{cccccc}
-\toprule
-Sample Size & Standard & Percentile & BC & BCa & Studentized\\
-\midrule
-100 & 0.9415 & 0.9394 & 0.9391 & 0.9390 & 0.9483\\
-200 & 0.9448 & 0.9411 & 0.9405 & 0.9404 & 0.9489\\
-400 & 0.9464 & 0.9417 & 0.9421 & 0.9426 & 0.9503\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Similar to when we sampled from the Gamma distribution, the Studentized
-confidence interval performed the best when we sampled from a Normal
-distribution with around 95\% of the confidence intervals containing the
-true population parameter. The next best is the Standard confidence
-interval with a performance of around 94.5\% correct intervals at a high
-sample size. The rest of the intervals performed similarly at around
-94.2\% accuracy. As before, the accuracy increased as the sample size
-increased.
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df.csv\textquotesingle{}}\NormalTok{)}
+
+\NormalTok{master\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ master\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+
+\NormalTok{master\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ master\_df\_long, }
+                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal}
+\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
+
+\NormalTok{master\_fig}
+\end{Highlighting}
+\end{Shaded}
 

### 2022-12-07 project/PaperTemplate/paper.Rmd
Rewrote beginning of simulation write-up

@@
 - name: Justin Papagelis
-  thanks: The authors gratefully acknowledge ...
+  thanks: The authors gratefully acknowledge Profossor Wagaman
   affiliation: Department of Mathematics and Statistics, Amherst College
@@
 
+Below is the
+
 ```{r, cache = TRUE}
@@
 The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal.
+As such, the standard confidence interval is sometimes called the normal confidence interval for bootstrapped data.
 This means that for an unknown distribution, the standard confidence interval could present an incorrect range.
@@
 This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created. 
-For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2000) due to the nature of confidence intervals requiring greater accuracy [@Efron86].
+For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2,000) due to the nature of confidence intervals requiring greater accuracy [@Efron86].
 
@@
 Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
-This means that for $B = 2000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
+This means that for $B = 2,000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
 It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
@@
 For example, we will sampling from a Gamma Distribution where we can find the true population mean using the shape and rate parameters of the sample distribution. 
-After we sample from a distribution, we will create a bootstrapped confidence interval for each of the methods we described in the exposition.
-Since we know the true population mean of the distribution, we will determine if the true population parameter is contained in the confidence interval for each of the methods.
-We will perform this process a large number of times (10,000) and then average by the number of iterations to determine the average proportion that each bootstrapped confidence interval method contains the true population mean.
+After we sample from a distribution, we will create a bootstrapped confidence interval for a few of the methods we described in the exposition. 
+Since we know the true population mean of the distribution, we will determine if the true population parameter is contained in the confidence interval for each of the methods we are testing. 
+We will perform this process a large number of times (10,000 simulations) and then average by the number of iterations to determines on average, the proportion that each bootstrapped confidence interval method contains the true population mean for a given distribution.
 We will do this for a couple different distributions as well as a range of sample sizes show how the intervals perform with skewed distributions and larger sample sizes.
 
-First, we create a function that calculates the bootstrapped confidence intervals from a given sample. To do this, we first bootstrap the sample and then perform each method.
+To do this simulation, we will be using the `boot` package [@boot]. 
+This package can compute a bootstrap object which contains the output from a bootstrap calculation of a given sample and then produces confidence intervals from the bootstrap object. 
+In particular, we will use the `boot.ci` function to create four types of confidence intervals: the standard (or normal) confidence interval, the studentized confidence interval, the percentile confidence interval, and the bias-corrected with acceleration confidence interval.
 
-Next, we will create the simulation that picks the random sample from a distribution and tests to see if the sample creates bootstrapped confidence intervals that contain the true population parameter.
-First, we have the simulation of selecting from a Normal Distribution.
-Since we have a $N(0,1)$ distribution, out true population mean is 0.
+Before we create the simulation, we create a helper function to extract the replication statistics we will need from the bootstrapped data. 
+These are the bootstrapped replicated mean and standard deviation of each bootstrapped sample.
+We will also declare some constants here including the sample sizes we will be using and the number of bootstrap replication we are using as well.
 
-Second, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4. This means the true population parameter is 4.
+```{r pre-simulation}
+boot.stat <- function(d, i) {
+  d <- X[i]
+  return (c(mean(d), sd(d)))
+}
+sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
+num_sample_sizes <- length(sample_sizes)
+boot_reps <- 2000
+```
+
+Next, we will create a simulation that randomly selects a sample from a Normal distribution and performs a bootstrap with 2,000 bootstrap replications.
+After, we will create the confidence intervals that we will be testing from this bootstrap and then determine if the true mean, our population parameter, is contained within our interval. 
+Since we are using a $N(0,1)$ distribution, our true population mean is equal to 0. 
+We will repeat this process 10,000 times as specified for each of the sample sizes that we are using. 
+Since we are using originally sampling from a Normal distribution, the assumptions we hold for the standard interval are true and thus we would expect all of the methods to perform comparably to each other at large sample sizes.
+
+```{r normal simulation}
+run_sim_normal <- function(sim_reps) {
+  master <- matrix(nrow = num_sample_sizes, ncol = 5)
+
+  for(i in 1:num_sample_sizes) {
+
+    norm_contains <- rep(0, sim_reps)
+    student_contains <- rep(0, sim_reps)
+    percentile_contains <- rep(0, sim_reps)
+    bca_contains <- rep(0, sim_reps)
+
+    n <- sample_sizes[i]
+    true_mean <- 0
+
+    for (j in 1:sim_reps) {
+      X <- rnorm(n, 0, 1)
+      values <- data.frame(X)
+      results <- boot(data = values, statistic = boot.stat, R = boot_reps)
+      ci <- boot.ci(results, conf = 0.95, type = c("norm", "perc", "bca", "stud"))
+
+      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+    }
+
+    master[i, 1] <- sample_sizes[i]
+    master[i, 2] <- sum(norm_contains)/sim_reps
+    master[i, 3] <- sum(student_contains)/sim_reps
+    master[i, 4] <- sum(percentile_contains)/sim_reps
+    master[i, 5] <- sum(bca_contains)/sim_reps
+  }
+
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Studentized" = V3, 
+             "Percentile" = V4, "BCa" = V5) 
+  master_df
+}
+
+```
+
+Secondly, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4 $Gamma(1,4)$. 
+This means the true population mean is 4 because the true mean is given by the product of the shape and scale parameter. 
+The simulation follows the same process as above where we sampled from the Normal distribution except we are sampling from a Gamma Distribution this time. 
+Since, the Gamma Distribution we are using heavily left-skewed, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
+
+```{r gamma simulation}
+run_sim_gamma <- function(sim_reps) {
+
+  master <- matrix(nrow = num_sample_sizes, ncol = 6)
+
+  for(i in 1:num_sample_sizes) {
+
+    norm_contains <- rep(0, sim_reps)
+    student_contains <- rep(0, sim_reps)
+    percentile_contains <- rep(0, sim_reps)
+    bca_contains <- rep(0, sim_reps)
+
+    n <- sample_sizes[i]
+    true_mean <- 4
+
+    for (j in 1:sim_reps) {
+      X <- rgamma(sample_sizes, shape = 1, scale = 4)
+      values <- data.frame(X)
+
+      results <- boot(data = values, statistic = boot.stat, R = boot_reps)
+      ci <- boot.ci(results, conf = 0.95, type = c("norm", "perc", "bca", "stud"))
+
+      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+    }
+    master[i, 1] <- sample_sizes[i]
+    master[i, 2] <- sum(norm_contains)/sim_reps
+    master[i, 3] <- sum(student_contains)/sim_reps
+    master[i, 4] <- sum(percentile_contains)/sim_reps
+    master[i, 5] <- sum(bca_contains)/sim_reps
+  }
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Studentized" = V3, 
+             "Percentile" = V4, "BCa" = V5) 
+  master_df
+}
+
+```
+
+Lastly, we will be sampling from a Log-Normal Distribution. 
+This means that if we have a random variable $X \sim Lognormal$, then the random variable, $Y = ln(X) \sim N$. 
+Therefore, the distribution is left-skewed, although not as heavily as the Gamma Distribution we previously used.
+The true mean of this distribution can be found using $E(X) = e^{u+\frac{\sigma^2}{2}}$ which means that for a $Lognormal(0,1)$ distribution, we should expect the population mean to be $e^{\frac{1}{2}}$.
+Again, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
+
+```{r log-normal simulation}
+run_sim_log_normal <- function(sim_reps) {
+
+  master <- matrix(nrow = num_sample_sizes, ncol = 6)
+
+  for(i in 1:num_sample_sizes) {
+
+    norm_contains <- rep(0, sim_reps)
+    student_contains <- rep(0, sim_reps)
+    percentile_contains <- rep(0, sim_reps)
+    bca_contains <- rep(0, sim_reps)
+
+    n <- sample_sizes[i]
+    true_mean <- exp(1/2)
+
+    for (j in 1:sim_reps) {
+      X <- rlnorm(n, 0, 1)
+      values <- data.frame(X)
+
+      results <- boot(data = values, statistic = boot.stat, R = boot_reps)
+      ci <- boot.ci(results, conf = 0.95, type = c("norm", "perc", "bca", "stud"))
+
+      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
+      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+    }
+    master[i, 1] <- sample_sizes[i]
+    master[i, 2] <- sum(norm_contains)/sim_reps
+    master[i, 3] <- sum(student_contains)/sim_reps
+    master[i, 4] <- sum(percentile_contains)/sim_reps
+    master[i, 5] <- sum(bca_contains)/sim_reps
+  }
+  master_df <- as.data.frame(master) %>% 
+      rename("Sample_Size" = V1, "Normal" = V2, "Studentized" = V3, 
+             "Percentile" = V4, "BCa" = V5) 
+  master_df
+}
+```
 
@@
 
-```{r, warning = FALSE}
-library(boot)
-
-run_sim_log_normal <- function(sim_reps) {
-  set.seed(495)
-  mean.fun <- function(d, i) {
-    d <- X[i]
-    return (c(mean(d), sd(d)))
-  }
-
-  sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
-  num_sample_sizes <- length(sample_sizes)
-  master <- matrix(nrow = num_sample_sizes, ncol = 6)
-
-  for(i in 1:num_sample_sizes) {
-
-    norm_contains <- rep(0, sim_reps)
-    basic_contains <- rep(0, sim_reps)
-    student_contains <- rep(0, sim_reps)
-    percentile_contains <- rep(0, sim_reps)
-    bca_contains <- rep(0, sim_reps)
-
-    boot_reps <- 2000
-    n <- sample_sizes[i]
-    true_mean <- exp(1/2)
-
-    for (j in 1:sim_reps) {
-      X <- rlnorm(n, 0, 1)
-      values <- data.frame(X)
-
-      results <- boot(data = values, statistic = mean.fun, R = boot_reps)
-      results
-      #plot(results)
-      ci <- boot.ci(results, type = "all")
-
-      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
-      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
-      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
-      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
-
-    }
-
-    master[i, 1] <- sample_sizes[i]
-    master[i, 2] <- sum(norm_contains)/sim_reps
-    master[i, 3] <- sum(basic_contains)/sim_reps
-    master[i, 4] <- sum(student_contains)/sim_reps
-    master[i, 5] <- sum(percentile_contains)/sim_reps
-    master[i, 6] <- sum(bca_contains)/sim_reps
-  }
-
-  master_df <- as.data.frame(master) %>% 
-      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
-             "Percentile" = V5, "BCa" = V6) 
-  master_df
-}
-```
-
-```{r, warning = FALSE}
-library(boot)
-
-run_sim_normal <- function(sim_reps) {
-  set.seed(495)
-  mean.fun <- function(d, i) {
-    d <- X[i]
-    return (c(mean(d), sd(d)))
-  }
-
-  sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
-  num_sample_sizes <- length(sample_sizes)
-  master <- matrix(nrow = num_sample_sizes, ncol = 6)
-
-  for(i in 1:num_sample_sizes) {
-
-    norm_contains <- rep(0, sim_reps)
-    basic_contains <- rep(0, sim_reps)
-    student_contains <- rep(0, sim_reps)
-    percentile_contains <- rep(0, sim_reps)
-    bca_contains <- rep(0, sim_reps)
-
-    boot_reps <- 2000
-    n <- sample_sizes[i]
-    true_mean <- 0
-
-    for (j in 1:sim_reps) {
-      X <- rnorm(n, 0, 1)
-      values <- data.frame(X)
-
-      results <- boot(data = values, statistic = mean.fun, R = boot_reps)
-      results
-      #plot(results)
-      ci <- boot.ci(results, type = "all")
-
-      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
-      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
-      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
-      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
-
-    }
-
-    master[i, 1] <- sample_sizes[i]
-    master[i, 2] <- sum(norm_contains)/sim_reps
-    master[i, 3] <- sum(basic_contains)/sim_reps
-    master[i, 4] <- sum(student_contains)/sim_reps
-    master[i, 5] <- sum(percentile_contains)/sim_reps
-    master[i, 6] <- sum(bca_contains)/sim_reps
-  }
-
-  master_df <- as.data.frame(master) %>% 
-      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
-             "Percentile" = V5, "BCa" = V6) 
-  master_df
-}
-
-```
-
-```{r, warning = FALSE}
-library(boot)
-
-run_sim_gamma <- function(sim_reps) {
-  set.seed(495)
-  mean.fun <- function(d, i) {
-    d <- X[i]
-    return (c(mean(d), sd(d)))
-  }
-
-  sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
-  num_sample_sizes <- length(sample_sizes)
-  master <- matrix(nrow = num_sample_sizes, ncol = 6)
-
-  for(i in 1:num_sample_sizes) {
-
-    norm_contains <- rep(0, sim_reps)
-    basic_contains <- rep(0, sim_reps)
-    student_contains <- rep(0, sim_reps)
-    percentile_contains <- rep(0, sim_reps)
-    bca_contains <- rep(0, sim_reps)
-
-    boot_reps <- 2000
-    n <- sample_sizes[i]
-    true_mean <- 4
-
-    for (j in 1:sim_reps) {
-      X <- rgamma(sample_sizes, shape = 1, scale = 4)
-      values <- data.frame(X)
-
-      results <- boot(data = values, statistic = mean.fun, R = boot_reps)
-      results
-      #plot(results)
-      ci <- boot.ci(results, type = "all")
-
-      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
-      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
-      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
-      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
-      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
-
-    }
-
-    master[i, 1] <- sample_sizes[i]
-    master[i, 2] <- sum(norm_contains)/sim_reps
-    master[i, 3] <- sum(basic_contains)/sim_reps
-    master[i, 4] <- sum(student_contains)/sim_reps
-    master[i, 5] <- sum(percentile_contains)/sim_reps
-    master[i, 6] <- sum(bca_contains)/sim_reps
-  }
-
-  master_df <- as.data.frame(master) %>% 
-      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
-             "Percentile" = V5, "BCa" = V6) 
-  master_df
-}
-
-```
-
-```{r, warning = FALSE, eval = FALSE}
+```{r run simulations, warning = FALSE, eval = FALSE}
 set.seed(495)
@@
 ```{r create graphs}
-
 gamma_df <- read.csv(file = 'gamma_data_df.csv')
@@
 
+# create the figure that shows the gamma output
 gamma_df_long <- gamma_df %>%
@@
 
+# create the table for the gamma output
 gamma_table <- gamma_df %>%
   kable(booktabs = TRUE, align = "c", caption = "Sampled From Gamma Dist.", 
-        col.names = gsub("[_]", " ", names(gamma_df)))
+        col.names = gsub("[_]", " ", names(gamma_df)), digits = 3)
 
+# create the figure that shows the normal output 
 normal_df_long <- normal_df %>%
@@
 
+# create the table for the normal output
 normal_table <- normal_df %>%
@@
 
+# create the figure that shows the log normal output
 log_normal_df_long <- log_normal_df %>%
@@
 
+# create the table for the log normal output
 log_normal_table <- log_normal_df %>%
@@
 
-```{r}
+```{r output the graphs/tables, cache = TRUE}
 log_normal_fig
@@
 
-```{r, eval = FALSE}
-
+```{r delete, eval = FALSE}
 normal_df <- read.csv(file = 'normal_data_df.csv')
@@
   geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal
-       Distibution", x = "Sample Size", 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal Distibution", 
+       x = "Sample Size", 
        y = "Proportion (of 10,000 Simulations)", color = "Method",

### 2022-12-07 project/PaperTemplate/paper.tex
Rewrote beginning of simulation write-up

@@
         Justin Papagelis \thanks{The authors gratefully acknowledge
-\ldots{}} \\
+Profossor Wagaman} \\
     Department of Mathematics and Statistics, Amherst College\\
@@
 
+Below is the
+
 \begin{Shaded}
@@
 The standard confidence interval is built based on the assumption that
-the distribution from which we are sampling is Normal. This means that
-for an unknown distribution, the standard confidence interval could
-present an incorrect range. However, the same process can be used with
-bootstrap sampling to form the bootstrap percentile method. This means
-that an approximate bootstrap confidence interval will be created in the
-same automatic way that the standard confidence interval was created.
-For bootstrapped confidence intervals, the number of bootstrap
-replications \(B\) must be large (around 2000) due to the nature of
-confidence intervals requiring greater accuracy \citep{Efron86}.
+the distribution from which we are sampling is Normal. As such, the
+standard confidence interval is sometimes called the normal confidence
+interval for bootstrapped data. This means that for an unknown
+distribution, the standard confidence interval could present an
+incorrect range. However, the same process can be used with bootstrap
+sampling to form the bootstrap percentile method. This means that an
+approximate bootstrap confidence interval will be created in the same
+automatic way that the standard confidence interval was created. For
+bootstrapped confidence intervals, the number of bootstrap replications
+\(B\) must be large (around 2000) due to the nature of confidence
+intervals requiring greater accuracy \citep{Efron86}.
 
@@
 from a distribution, we will create a bootstrapped confidence interval
-for each of the methods we described in the exposition. Since we know
+for a few of the methods we described in the exposition. Since we know
 the true population mean of the distribution, we will determine if the
 true population parameter is contained in the confidence interval for
-each of the methods. We will perform this process a large number of
-times (10,000) and then average by the number of iterations to determine
-the average proportion that each bootstrapped confidence interval method
-contains the true population mean. We will do this for a couple
-different distributions as well as a range of sample sizes show how the
-intervals perform with skewed distributions and larger sample sizes.
-
-First, we create a function that calculates the bootstrapped confidence
-intervals from a given sample. To do this, we first bootstrap the sample
-and then perform each method.
-
-Next, we will create the simulation that picks the random sample from a
-distribution and tests to see if the sample creates bootstrapped
-confidence intervals that contain the true population parameter. First,
-we have the simulation of selecting from a Normal Distribution. Since we
-have a \(N(0,1)\) distribution, out true population mean is 0.
+each of the methods we are testing. We will perform this process a large
+number of times (10,000 simulations) and then average by the number of
+iterations to determines on average, the proportion that each
+bootstrapped confidence interval method contains the true population
+mean for a given distribution. We will do this for a couple different
+distributions as well as a range of sample sizes show how the intervals
+perform with skewed distributions and larger sample sizes.
+
+To do this simulation, we will be using the \texttt{boot} package
+\citep{boot}. This package can compute a bootstrap object which contains
+the output from a bootstrap calculation of a given sample and then
+produces confidence intervals from the bootstrap object. In particular,
+we will use the \texttt{boot.ci} function to create four types of
+confidence intervals: the standard (or normal) confidence interval, the
+studentized confidence interval, the percentile confidence interval, and
+the bias-corrected with acceleration confidence interval.
+
+First, we will create a simulation that pick a random sample from a
+distribution and performs
+
+and tests to see if the sample creates a bootstrapped confidence
+intervals that contain the true population parameter. First, we have the
+simulation of selecting from a Normal Distribution. Since we have a
+\(N(0,1)\) distribution, out true population mean is 0.
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(boot)}
-
 \NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
@@
       \CommentTok{\#plot(results)}
-\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(boot)}
-
 \NormalTok{run\_sim\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(boot)}
-
 \NormalTok{run\_sim\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
@@
 
+\CommentTok{\# create the figure that shows the gamma output}
 \NormalTok{gamma\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
@@
 
+\CommentTok{\# create the table for the gamma output}
 \NormalTok{gamma\_table }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
   \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled From Gamma Dist."}\NormalTok{, }
-        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_df))) }
-
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_df)), }\AttributeTok{digits =} \DecValTok{3}\NormalTok{) }
+
+\CommentTok{\# create the figure that shows the normal output }
 \NormalTok{normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
@@
 
+\CommentTok{\# create the table for the normal output}
 \NormalTok{normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
@@
 
+\CommentTok{\# create the figure that shows the log normal output}
 \NormalTok{log\_normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
@@
 
+\CommentTok{\# create the table for the log normal output}
 \NormalTok{log\_normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-24-1.pdf}
+\includegraphics{paper_files/figure-latex/output the graphs/tables-1.pdf}
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-24-2.pdf}
+\includegraphics{paper_files/figure-latex/output the graphs/tables-2.pdf}
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-24-3.pdf}
+\includegraphics{paper_files/figure-latex/output the graphs/tables-3.pdf}
 
@@
 \midrule
-4 & 0.8494 & 0.8332 & 0.9039 & 0.8578 & 0.8750\\
-10 & 0.8476 & 0.8291 & 0.9008 & 0.8543 & 0.8708\\
-15 & 0.8510 & 0.8322 & 0.9012 & 0.8563 & 0.8706\\
-20 & 0.8458 & 0.8274 & 0.9030 & 0.8511 & 0.8672\\
-30 & 0.8380 & 0.8218 & 0.8954 & 0.8463 & 0.8642\\
+4 & 0.849 & 0.833 & 0.904 & 0.858 & 0.875\\
+10 & 0.848 & 0.829 & 0.901 & 0.854 & 0.871\\
+15 & 0.851 & 0.832 & 0.901 & 0.856 & 0.871\\
+20 & 0.846 & 0.827 & 0.903 & 0.851 & 0.867\\
+30 & 0.838 & 0.822 & 0.895 & 0.846 & 0.864\\
 \addlinespace
-40 & 0.8480 & 0.8313 & 0.8989 & 0.8525 & 0.8664\\
-60 & 0.8466 & 0.8292 & 0.9069 & 0.8571 & 0.8741\\
-80 & 0.8486 & 0.8310 & 0.9016 & 0.8535 & 0.8717\\
-100 & 0.8478 & 0.8308 & 0.8974 & 0.8533 & 0.8660\\
+40 & 0.848 & 0.831 & 0.899 & 0.853 & 0.866\\
+60 & 0.847 & 0.829 & 0.907 & 0.857 & 0.874\\
+80 & 0.849 & 0.831 & 0.902 & 0.854 & 0.872\\
+100 & 0.848 & 0.831 & 0.897 & 0.853 & 0.866\\
 \bottomrule
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal}
-\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal Distibution"}\NormalTok{, }
+       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}

### 2022-12-08 project/PaperTemplate/paper.Rmd
Finished running simulations and edited once

@@
 - name: Justin Papagelis
-  thanks: The authors gratefully acknowledge Profossor Wagaman
+  thanks: The authors gratefully acknowledge
+
+   '' Profossor Wagaman
   affiliation: Department of Mathematics and Statistics, Amherst College
@@
 abstract: |
-  For my project, I plan to explore different bootstrap methods for creating confidence intervals and then perform comparisons between a couple of the methods.
-My paper will re-introduce the idea of bootstrap to my peers and give some background on constructing confidence intervals.
-We will also go deeper into the theory behind the construction of confidence intervals from bootstrapped data.
-These various methods to create a confidence interval from a bootstrap can include the percentile method, bias-corrected method, accelerated method, and the studentized method, as well as others.
-I will demonstrate how these bootstrap methods work using “toy examples,” which will be datasets in which a specific bootstrap method is appropriate.
-To demonstrate my understanding of the methods, I will write a simulation to compare a few of them and determine how they perform against each other.
-I will show my understanding of the different methods of creating confidence intervals from bootstrapped data by communicating the statistical theory in a concise and accessible way to my peers.
-Writing the simulation and sharing conclusions will demonstrate my ability to implement statistical methods in practice as well as my ability to analyze the results of the simulation.
+  This paper explores different bootstrap methods for creating confidence intervals and tests their performance against each other for different types of distributions.
+This paper will re-introduce the ideas of bootstraps and confidence intervals, as well as the theory behind different methods of bootstrapped confidence intervals.
+Along with the theoretical details of each method, we will provide an example of each bootstrapped confidence interval method with a toy dataset.
+Then, we will run a simulation that evaluates the performance of a couple of the methods we introduced on a variety of sample sizes and types of distributions.
 
@@
 One way to make a statistical inference is through confidence intervals which give a range of estimates for the unknown population parameter at a certain confidence level. 
-We can use bootstrapping to create accurate approximate confidence intervals for our population parameter even without its underlying distributions. 
+We can use bootstrapping to create accurate approximate confidence intervals for our population parameter even without knowing its underlying distributions. 
 There are many different ways to create intervals, and we will go through a couple of them: The Standard Method, The Percentile Method, The Bias-Corrected (BC) Method, The Bias-Corrected with Acceleration (BCa) Method, and finally, The Studentized Method.
 Additionally, we will go through an example of creating a bootstrapped confidence interval for each method.
-Then, we will perform a simulation to evaluate the performance of the bootstrapped confidence interval methods on different distribution types.
+Then, we will perform a simulation to evaluate the performance of some of the bootstrapped confidence interval methods on different types of distributions.
 
@@
 First, we introduce the non-parametric bootstrap.
-Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$ [@EfronCasi]. 
+Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest, $\hat{\theta} = \hat{\theta}(X)$ [@EfronCasi]. 
 Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$.
 However $F$ is unknown, so this is not possible. 
-The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample $X$ without making any parametric assumptions about $F$ (such as its distribution type). 
-Therefore, the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$.
+The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample, $X$, without making any parametric assumptions about $F$ (such as its distribution type). 
+Therefore, the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from our original sample: $\{x_1,x_2,\dots,x_n\}$.
 From this bootstrap sample, a bootstrap replication of the test statistic can be computed using $\hat{\theta}^* = \hat{\theta}(X^*)$. 
@@
 
+### Using the Non-Parametric Bootstrap
+
 We demonstrate performing a non-parametric bootstrap below using `SnowGR` which gives the official snowfall dataset by month for Grand Rapids, MI, starting in 1893. 
-We will be using the `Dec` variable which gives the number of inches of snow that fell in December of each year.
+We will be using the `Dec` variable which is the number of inches of snow that fell in December of each year. 
 In particular, we are interested in the sample mean and later finding confidence intervals for population mean of `Dec`. 
-The distribution is below.
+The distribution is below (Figure 1).
 
-```{r, cache = TRUE}
+```{r SnowGR histogram, cache = TRUE}
 data(SnowGR)
-favstats(~ Dec, data = SnowGR)
 gf_histogram(~ Dec, data = SnowGR) +
@@
        title = "Distribution of Annual Snowfall in December", y = "Count",
-       caption = "Fig. 1: Histogram with Studentized Interval Shown")
+       caption = "Fig. 1: Histogram of SnowGR")
 ```
-
 Next, we will perform the non-parametric bootstrap using 10,000 replications.
 
-```{r, cache = TRUE}
+```{r non-paramteric bootstrap, cache = TRUE}
 set.seed(495)
@@
 ```
-
-Below is the
+Below, in Figure 2, is the histogram of bootstrapped values. Since we performed a large number of bootstrap replications, the bootstrapped distribution appears to be approximately Normal.
 
@@
   gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values",
-          caption = "Fig. 2: Bootstrap Histogram")
+          caption = "Fig. 2: Bootstrap histogram of Dec values")
 ```
@@
 ## Standard Confidence Interval
-
 Confidence intervals are tools that are used to estimate a parameter. 
@@
 The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal.
-As such, the standard confidence interval is sometimes called the normal confidence interval for bootstrapped data.
-This means that for an unknown distribution, the standard confidence interval could present an incorrect range.
+As such, the standard confidence interval is sometimes called the normal confidence interval for a bootstrapped sample.
+This means that for an unknown skewed distribution, the standard confidence interval could present an incorrect range.
 However, the same process can be used with bootstrap sampling to form the bootstrap percentile method. 
@@
 
-Using our example, to find a 95% confidence interval for the population mean of `Dec`, we would get the following:
+### Standard Confidence Interval in Use
+
+Using our previous example to find a 95% confidence interval for the population mean of `Dec`, we would get the following confidence interval:
 
@@
 ```
+This means that we can say we are 95% confident that the true mean number of inches of snow that fall in December is betwwen 13.86 inches and 17.66 inches.
+Our original histogram with the confidence interval is below (Figure 3).
 
@@
 ## The Percentile Method
-
 The percentile method interval is defined as the interval between the $100 * \alpha$ and the $100(1 - \alpha)$ percentiles of the bootstrap distribution of $\hat{\theta}$.
 That is, the $(1 - 2\alpha)$ coverage interval can be defined as $[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}]$ [@Efron86,@EfronCasi]. 
-To go further, we can define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$: $$\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.$$ 
+To go further, we can define $\hat{G}(t)$ as the bootstrap cdf, or the proportion of bootstrap samples less than $t$: $$\hat{G}(t) = \frac{\#\{\hat{\theta}^{*b} \leq t\}}{B}.$$ 
 Thus the $\alpha$th percentile point of the distribution is given by $$\hat{\theta}_p[\alpha] = \hat{\theta^*_\alpha} = \hat{G}^{-1}(\alpha).$$ It follows that the percentile interval can be represented as $$\left [ \hat{G}^{-1}(\alpha),\hat{G}^{-1}(1-\alpha) \right ].$$
@@
 
+### The Percentile Method in Use
+
 Finding a 95% confidence interval for the true population mean of `Dec` using the percentile method, we get:
@@
 ```
-
+Therefore, we can say that we are 95% confident that the true population mean of inches of snow that fall in December is between 13.91 inches and 17.72 inches.
+Our original histogram with the percentile confidence interval is shown below (Figure 4).
 ```{r, cache = TRUE}
@@
 ```
-This interval is similar to the one created using the Standard method, but shifted slightly to the right.
+This interval is similar to the one created using the standard method, but shifted slightly to the right.
 
@@
 It can be shown that $\hat{\theta}$ is biased upwards relative to $\theta$ which means that the confidence intervals should be adjusted downwards [@Efron86,@EfronCasi]. 
-From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B},$$ and define the bias-correction value $$z_0 = \Phi^{-1}(p_0),$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
-Thus we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),$$ with $z_0$ and $\tau$ constants. 
-This means that we can say the bias corrected method has an $\alpha$-level endpoint can be represented as $$\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].$$ If $\hat{G} = 0.50$, then half of the bootstrap distribution is less than $\hat{\theta}$ and our bias-correction value $z_0 = 0$.
-In this case, the confidence interval produced by BC would be the same interval produced by the percentile method.
+From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta}^{*b} \leq \theta\}}{B},$$ and define the bias-correction value $$z_0 = \Phi^{-1}(p_0),$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
+Thus, we define a transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),$$ with $z_0$ and $\tau$ constants. 
+This means that we can say the bias-corrected method has an $\alpha$-level endpoint which can be represented as $$\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].$$ If $\hat{G} = 0.50$, then half of the bootstrap distribution is less than $\hat{\theta}$ and our bias-correction value $z_0 = 0$.
+In this case, the confidence interval produced by BC would be the same interval that was produced by the percentile method.
 
-Using this method to create a 95% confidence interval has a couple more steps because we need to find the bias-correction value. First we calculate the sample mean.
+### The BC Method in Use
+Using this method to create a 95% confidence interval has a couple more steps because we need to find the bias-correction value. First we calculate the sample mean:
 
@@
 ```
+Then we find the proportion of bootstrap replications that have a sample mean less than the original sample mean.
 
-Then we find the proportion of bootstrap replications that have a sample mean less than the original sample mean.
 ```{r, cache = TRUE}
@@
 ```
+From this, we can calculate the bias-correction value, $z_0$:
 
-From this, we can calculate the bias-correction value, $z_0$:
 ```{r, cache = TRUE}
@@
 ```
-
-Then we can find the modified percentiles:
+Then we can find the modified percentiles and get the corresponding confidence interval:
 
@@
 ```
+Therefore, we are 95% confident that the true mean inches of snow that fall in December in Grand Rapids, Michigan is between 14.01 inches and 17.82 inches. Our histogram (Figure 5) is shown below.
 
@@
 ## The Bias-Corrected and Accelerated (BCa) Method
-
-A further modification upon the BC interval is the bias corrected and accelerated method (BCa). 
-For this method, we do not assume the the standard error, $\tau$ is constant as we did in the BC interval [@Efron86,@EfronCasi]. 
+A further modification upon the BC interval is the bias-corrected and accelerated method (BCa). 
+For this method, we do not assume the the standard error, $\tau$, is constant as we did in the BC interval [@Efron86,@EfronCasi]. 
 Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.$$
@@
 In other words, $a$ is proportional to the skewness of the bootstrap distribution. 
-For example, for one-parameter exponential families, $a=z_0$, however, there are many different algorithms to compute and estimate $a$ [@Flowers18]. 
-Now, our $\alpha$-level endpoint from BCa is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ If $a = 0$, then $\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].$
-When calculating a BCa interval, the acceleration value $a$ is not a function of the bootstrap distribution and must be calculated separately, however the process is algorithmic and can be calculated without too much work.
-Each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, however computation increases as we loosen assumptions.
+For example, $a=z_0$ for one-parameter exponential families, however, there are many different algorithms to compute and estimate $a$ [@Flowers18]. 
+Now, our $\alpha$-level endpoint for a BCa confidence interval is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ 
+We can observe that if $a = 0$, then $\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].$ 
+When calculating a BCa confidence interval, the acceleration value, $a$, is not a function of the bootstrap distribution and must be calculated separately.
+However the process is algorithmic and can be calculated without too much work. 
+As we saw, each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, but this means that computation increases as we loosen assumptions.
 
-In practice, we can use the jackknife procedure to estimate the acceleration value for this method. Thus, we will run the jackknife procedure:
+### The BCa Confidence Interval in Use
+In practice, we can use the jackknife procedure to estimate the acceleration value for this method.
+The jackknife procedure is a different resampling technique that is often used to estimate the bias and variance of a large population.
+Thus, we will run the jackknife procedure:
 
@@
 ```
-
 We find the mean of the jackknife values below:
@@
 ```
-
-Then we can compute $a$.
+Then we can compute an approximation for $a$.
 
@@
 ```
-
-Now, we can find the adjust percentiles and the bias-corrected with acceleration confidence interval.
+Now, we can find the adjusted percentiles and the bias-corrected with acceleration confidence interval.
 
@@
 a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
-                    (1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
+                    (1-estimated_a*(z0 + qnorm(alphalow)))); 
 a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
-                     (1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
+                     (1-estimated_a*(z0 + qnorm(alphahigh)))); 
 qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
 ```
+We are 95% confident that the true mean number of inches of snow that fall in December is between 13.92 inches and 17.72 inches. Figure 6 shows our confidence interval.
 
@@
 ## The Bootstrap-t (Studentized) Method
-
 The final method we explain is the bootstrap-t interval (or the studentized method). 
-Recall from earlier, our sample, $X$ from which we can calculate an estimate, $\hat{\theta}(X)$ of the parameter of interest $\theta$ [@Efron86,@Puth15]. 
+Recall from earlier, our sample, $X$ from which we can calculate an estimate ($\hat{\theta}(X)$) of the parameter of interest $\theta$ [@Efron86,@Puth15]. 
 We can also estimate $\hat{\sigma}(X)$ for the standard error of $\theta$. 
-We can use these parameters to find the Student's $t$-statistic defined as $$T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.$$ 
+We can use these parameters to find the Student's $t$-statistic defined as: $$T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.$$ 
 As such, the $\alpha$th percentile point of a confidence interval of $\theta$ would be $\hat{\theta} - \hat{\sigma}T_{(\alpha)}$ where $T_{(\alpha)}$ represents the $\alpha$th percentile of the $t$-distribution, $T$.
-Unfortunately, the percentiles of the t-distribution are unknown in most cases, but we can use bootstrapping to estimate these percentiles. 
+Unfortunately, the percentiles of this $t$-distribution are unknown in most cases, but we can use bootstrapping to estimate these percentiles. 
 To do this, we perform a large number, $B$, of bootstrap samples, from which we can find the bootstrap replications of the parameter of interest, $\hat{\theta^*} = \hat{\theta}(X^*)$, and the standard error, $\hat{\sigma^*} = \hat{\sigma}(X^*)$.
-From these we can calculate a t-statistic for each bootstrap sample: $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.$$ for each bootstrap sample.
-Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
+From these we can calculate a t-statistic for each bootstrap sample: $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.$$ Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
 This means that for $B = 2,000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
 It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
-Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistic [@Efron86,@Puth15].
+Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistics [@Efron86,@Puth15].
+
+### Studentized Confidence Interval in Use
 
@@
 c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
-
 ```
-
-This would give us the following histogram:
+So we are 95% confident that the true mean number of inches of snow that fall in December in Grand Rapids, Michigan is between 14.03 inches and 18.02 inches.
+This would give us the following confidence interval (Figure 7)
 
@@
 
-For the simulation, we will randomly sample from distributions in which we know the true population mean. 
-For example, we will sampling from a Gamma Distribution where we can find the true population mean using the shape and rate parameters of the sample distribution. 
-After we sample from a distribution, we will create a bootstrapped confidence interval for a few of the methods we described in the exposition. 
-Since we know the true population mean of the distribution, we will determine if the true population parameter is contained in the confidence interval for each of the methods we are testing. 
+For our simulation, we will randomly sample from distributions in which we know the true population mean. 
+For example, we will be sampling from a Gamma distribution where we can find the true population mean using the shape and rate parameters of the sample distribution. 
+After we sample from the distribution, we will create a bootstrapped confidence interval for a few of the methods we described in the exposition. 
+Since we know the true population mean of the distribution, we will determine if the true population mean is contained in the confidence interval for each of the methods we are testing. 
 We will perform this process a large number of times (10,000 simulations) and then average by the number of iterations to determines on average, the proportion that each bootstrapped confidence interval method contains the true population mean for a given distribution.
-We will do this for a couple different distributions as well as a range of sample sizes show how the intervals perform with skewed distributions and larger sample sizes.
+We will do this for a couple different distributions as well as a range of sample sizes to show how the intervals perform with skewed distributions and larger sample sizes.
 
@@
 
-Before we create the simulation, we create a helper function to extract the replication statistics we will need from the bootstrapped data. 
-These are the bootstrapped replicated mean and standard deviation of each bootstrapped sample.
-We will also declare some constants here including the sample sizes we will be using and the number of bootstrap replication we are using as well.
+To start, we will declare some constants including the sample sizes and the number of bootstrap replications we are using.
 
-```{r pre-simulation}
+```{r pre-simulation, eval = TRUE}
+
+sample_sizes <- c(5, 10, 15, 20, 30, 40, 60, 100, 150)
+num_sample_sizes <- length(sample_sizes)
+boot_reps <- 2000
+```
+Next, we create a simulation that randomly selects a sample from a Normal distribution and performs a bootstrap with 2,000 bootstrap replications.
+Then, we create the confidence intervals from this bootstrap and determine if the true mean, our population parameter, is contained within our intervals.
+Since we are using a $Normal(0,1)$ distribution, our true population mean is equal to 0. 
+We will repeat this process 10,000 times as specified for each of the sample sizes that we are testing. 
+Since we are originally sampling from a Normal distribution, the assumptions we hold for the standard interval are true and thus, we would expect all of the methods to perform comparably to each other at large sample sizes.
+
+```{r normal simulation}
+run_sim_normal <- function(sim_reps) {
+
   boot.stat <- function(d, i) {
@@
   }
-sample_sizes <- c(4, 10, 15, 20, 30, 40, 60, 80, 100)
-num_sample_sizes <- length(sample_sizes)
-boot_reps <- 2000
-```
 
-Next, we will create a simulation that randomly selects a sample from a Normal distribution and performs a bootstrap with 2,000 bootstrap replications.
-After, we will create the confidence intervals that we will be testing from this bootstrap and then determine if the true mean, our population parameter, is contained within our interval. 
-Since we are using a $N(0,1)$ distribution, our true population mean is equal to 0. 
-We will repeat this process 10,000 times as specified for each of the sample sizes that we are using. 
-Since we are using originally sampling from a Normal distribution, the assumptions we hold for the standard interval are true and thus we would expect all of the methods to perform comparably to each other at large sample sizes.
-
-```{r normal simulation}
-run_sim_normal <- function(sim_reps) {
   master <- matrix(nrow = num_sample_sizes, ncol = 5)
@@
 
-Secondly, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4 $Gamma(1,4)$. 
-This means the true population mean is 4 because the true mean is given by the product of the shape and scale parameter. 
-The simulation follows the same process as above where we sampled from the Normal distribution except we are sampling from a Gamma Distribution this time. 
-Since, the Gamma Distribution we are using heavily left-skewed, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
+Secondly, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4 ($Gamma(1,4)$). 
+Therefore, the true population mean is 4 because the true mean is given by the product of the shape and scale parameter. 
+This simulation follows the same process as above where we sampled from the Normal distribution except we are sampling from a Gamma distribution this time. 
+Since, our Gamma distribution is heavily left-skewed, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
 
@@
 
-  master <- matrix(nrow = num_sample_sizes, ncol = 6)
+  boot.stat <- function(d, i) {
+    d <- X[i]
+    return (c(mean(d), sd(d)))
+  }
+
+  master <- matrix(nrow = num_sample_sizes, ncol = 5)
 
@@
 
-Lastly, we will be sampling from a Log-Normal Distribution. 
-This means that if we have a random variable $X \sim Lognormal$, then the random variable, $Y = ln(X) \sim N$. 
-Therefore, the distribution is left-skewed, although not as heavily as the Gamma Distribution we previously used.
-The true mean of this distribution can be found using $E(X) = e^{u+\frac{\sigma^2}{2}}$ which means that for a $Lognormal(0,1)$ distribution, we should expect the population mean to be $e^{\frac{1}{2}}$.
+Lastly, we will be sampling from a Log-Normal distribution. 
+This means that if we have a random variable, $X \sim Lognormal$, then the random variable, $Y = ln(X) \sim Normal$. 
+Therefore, the distribution is left-skewed, although not as heavily as the Gamma distribution we previously used.
+The true mean of this distribution can be found using $E(X) = e^{u+\frac{\sigma^2}{2}}$ which means that for a $Lognormal(0,1)$ distribution, we expect the population mean to be $e^{\frac{1}{2}}$.
 Again, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
@@
 ```
-
-After that, these functions will compile all of the information we have created from the previous methods and run the simulations of each method for a variety of sample sizes.
-
-And here, we run the simulations for each of the distributions and store the results.
-
-Then, we can plot the results and compile the results into tables.
-
-When we sample from the Gamma distribution which is a distribution that is heavily skewed, the Studentized Confidence interval performs the best.
-At a large sample size, the Studentized Confidence interval contains the true population parameter about 94.5% of the time.
-The Studentized confidence interval outperforms the rest of the intervals by a bit.
-The rest of the intervals are very similar to each other ranging from a correct interval 92.5% to 93% of the time.
-In general, as the sample size that we are bootstrapping from increases, the higher percentage our confidence intervals predict correctly.
-
-Similar to when we sampled from the Gamma distribution, the Studentized confidence interval performed the best when we sampled from a Normal distribution with around 95% of the confidence intervals containing the true population parameter.
-The next best is the Standard confidence interval with a performance of around 94.5% correct intervals at a high sample size.
-The rest of the intervals performed similarly at around 94.2% accuracy.
-As before, the accuracy increased as the sample size increased.
+Once we have all the simulations, we can run them below.
 
@@
 set.seed(495)
-log_normal_df <- run_sim_log_normal(10000)
-write.csv(log_normal_df,"log_normal_df.csv", row.names = FALSE)
+normal_df_trial2 <- run_sim_normal(10000)
+write.csv(normal_df_trial2,"normal_data_df_trial2.csv", row.names = FALSE)
 
-normal_df <- run_sim_normal(10000)
-write.csv(normal_df,"normal_data_df.csv", row.names = FALSE)
+log_normal_df_trial2 <- run_sim_log_normal(10000)
+write.csv(log_normal_df_trial2,"log_normal_df_trial2.csv", row.names = FALSE)
 
-gamma_df <- run_sim_gamma(10000)
-write.csv(gamma_df,"gamma_data_df.csv", row.names = FALSE)
-
+gamma_df_trial2 <- run_sim_gamma(10000)
+write.csv(gamma_df_trial2,"gamma_data_df_trial2.csv", row.names = FALSE)
 ```
@@
 ```{r create graphs}
-gamma_df <- read.csv(file = 'gamma_data_df.csv')
-normal_df <- read.csv(file = 'normal_data_df.csv')
-log_normal_df <- read.csv(file = 'log_normal_df.csv')
+normal_df <- read.csv(file = 'normal_data_df_trial2.csv')
+gamma_df <- read.csv(file = 'gamma_data_df_trial2.csv')
+log_normal_df <- read.csv(file = 'log_normal_df_trial2.csv')
+
+# create the figure that shows the normal output 
+normal_df_long <- normal_df %>%
+  pivot_longer(cols = 2:5, names_to = "method", values_to = "prop")
+
+normal_fig <- ggplot(data = normal_df_long, 
+                    aes(x = Sample_Size, y = prop, color = method)) + 
+  geom_point() + geom_line() + 
+  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
+       Distibution", x = "Sample Size", 
+       y = "Proportion (of 10,000 Simulations)", color = "Method",
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
+       different sample sizes on Normal Dist.") +
+  theme_light() +
+  theme(legend.position="bottom")
+
+# create the table for the normal output
+normal_table <- normal_df %>%
+  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
+        col.names = gsub("[_]", " ", names(normal_df)))
 
@@
 gamma_df_long <- gamma_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+  pivot_longer(cols = 2:5, names_to = "method", values_to = "prop")
 
@@
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist.") +
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
+       different sample sizes on Gamma Dist.") +
   theme_light() +
@@
 
-# create the figure that shows the normal output 
-normal_df_long <- normal_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-normal_fig <- ggplot(data = normal_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
-       Distibution", x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist.") +
-  theme_light() +
-  theme(legend.position="bottom")
-
-# create the table for the normal output
-normal_table <- normal_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
-        col.names = gsub("[_]", " ", names(normal_df)))
-
 # create the figure that shows the log normal output
 log_normal_df_long <- log_normal_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
+  pivot_longer(cols = 2:5, names_to = "method", values_to = "prop")
 
@@
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
+       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
+       different sample sizes on Log-Normal Dist.") +
   theme_light() +
@@
 ```
-
-```{r delete, eval = FALSE}
-normal_df <- read.csv(file = 'normal_data_df.csv')
-
-master_df_long <- master_df %>%
-  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")
-
-master_fig <- ggplot(data = master_df_long, 
-                    aes(x = Sample_Size, y = prop, color = method)) + 
-  geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal Distibution", 
-       x = "Sample Size", 
-       y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
-  theme_light() +
-  theme(legend.position="bottom")
-
-master_fig
-```

### 2022-12-08 project/PaperTemplate/paper.tex
Finished running simulations and edited once

@@
   \author{
-        Justin Papagelis \thanks{The authors gratefully acknowledge
+        Justin Papagelis \thanks{The authors gratefully acknowledge '\,'
 Profossor Wagaman} \\
@@
 \begin{abstract}
-For my project, I plan to explore different bootstrap methods for
-creating confidence intervals and then perform comparisons between a
-couple of the methods. My paper will re-introduce the idea of bootstrap
-to my peers and give some background on constructing confidence
-intervals. We will also go deeper into the theory behind the
-construction of confidence intervals from bootstrapped data. These
-various methods to create a confidence interval from a bootstrap can
-include the percentile method, bias-corrected method, accelerated
-method, and the studentized method, as well as others. I will
-demonstrate how these bootstrap methods work using ``toy examples,''
-which will be datasets in which a specific bootstrap method is
-appropriate. To demonstrate my understanding of the methods, I will
-write a simulation to compare a few of them and determine how they
-perform against each other. I will show my understanding of the
-different methods of creating confidence intervals from bootstrapped
-data by communicating the statistical theory in a concise and accessible
-way to my peers. Writing the simulation and sharing conclusions will
-demonstrate my ability to implement statistical methods in practice as
-well as my ability to analyze the results of the simulation.
+This paper explores different bootstrap methods for creating confidence
+intervals and tests their performance against each other for different
+types of distributions. This paper will re-introduce the ideas of
+bootstraps and confidence intervals, as well as the theory behind
+different methods of bootstrapped confidence intervals. Along with the
+theoretical details of each method, we will provide an example of each
+bootstrapped confidence interval method with a toy dataset. Then, we
+will run a simulation that evaluates the performance of a couple of the
+methods we introduced on a variety of sample sizes and types of
+distributions.
 \end{abstract}
@@
 level. We can use bootstrapping to create accurate approximate
-confidence intervals for our population parameter even without its
-underlying distributions. There are many different ways to create
+confidence intervals for our population parameter even without knowing
+its underlying distributions. There are many different ways to create
 intervals, and we will go through a couple of them: The Standard Method,
@@
 creating a bootstrapped confidence interval for each method. Then, we
-will perform a simulation to evaluate the performance of the
-bootstrapped confidence interval methods on different distribution
-types.
+will perform a simulation to evaluate the performance of some of the
+bootstrapped confidence interval methods on different types of
+distributions.
 
@@
 random sample \(X = (x_1,x_2,\dots,x_n)\) from our unknown distribution,
-\(F\) and a statistic of interest \(\hat{\theta} = \hat{\theta}(X)\)
+\(F\) and a statistic of interest, \(\hat{\theta} = \hat{\theta}(X)\)
 \citep{EfronCasi}. Ideally, the desired test statistic could be found by
@@
 is unknown, so this is not possible. The non-parametric bootstrap
-creates an estimate \(\hat{F}\) from \(F\) using our sample \(X\)
+creates an estimate \(\hat{F}\) from \(F\) using our sample, \(X\),
 without making any parametric assumptions about \(F\) (such as its
@@
 as \(X^* = (x^*_1, x^*_2, \dots, x^*_n)\) where each \(x^*_i\) is
-sampled randomly with equal probability and with replacement from
-\(\{x_1,x_2,\dots,x_n\}\). From this bootstrap sample, a bootstrap
-replication of the test statistic can be computed using
+sampled randomly with equal probability and with replacement from our
+original sample: \(\{x_1,x_2,\dots,x_n\}\). From this bootstrap sample,
+a bootstrap replication of the test statistic can be computed using
 \(\hat{\theta}^* = \hat{\theta}(X^*)\). A large number, \(B\), of
@@
 
+\hypertarget{using-the-non-parametric-bootstrap}{%
+\subsubsection{Using the Non-Parametric
+Bootstrap}\label{using-the-non-parametric-bootstrap}}
+
 We demonstrate performing a non-parametric bootstrap below using
@@
 Grand Rapids, MI, starting in 1893. We will be using the \texttt{Dec}
-variable which gives the number of inches of snow that fell in December
-of each year. In particular, we are interested in the sample mean and
-later finding confidence intervals for population mean of \texttt{Dec}.
-The distribution is below.
+variable which is the number of inches of snow that fell in December of
+each year. In particular, we are interested in the sample mean and later
+finding confidence intervals for population mean of \texttt{Dec}. The
+distribution is below (Figure 1).
 
@@
 \FunctionTok{data}\NormalTok{(SnowGR)}
-\FunctionTok{favstats}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##  min   Q1 median    Q3  max     mean       sd   n missing
-##  0.8 8.35   13.8 18.65 59.2 15.75798 10.58382 119       0
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
@@
        \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 1: Histogram with Studentized Interval Shown"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-Next, we will perform the non-parametric bootstrap using 10,000
-replications.
+       \AttributeTok{caption =} \StringTok{"Fig. 1: Histogram of SnowGR"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/SnowGR histogram-1.pdf} Next,
+we will perform the non-parametric bootstrap using 10,000 replications.
 
@@
 
-Below is the
+Below, in Figure 2, is the histogram of bootstrapped values. Since we
+performed a large number of bootstrap replications, the bootstrapped
+distribution appears to be approximately Normal.
 
@@
   \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{,}
-          \AttributeTok{caption =} \StringTok{"Fig. 2: Bootstrap Histogram"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
+          \AttributeTok{caption =} \StringTok{"Fig. 2: Bootstrap histogram of Dec values"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
 
@@
 standard confidence interval is sometimes called the normal confidence
-interval for bootstrapped data. This means that for an unknown
-distribution, the standard confidence interval could present an
+interval for a bootstrapped sample. This means that for an unknown
+skewed distribution, the standard confidence interval could present an
 incorrect range. However, the same process can be used with bootstrap
@@
 bootstrapped confidence intervals, the number of bootstrap replications
-\(B\) must be large (around 2000) due to the nature of confidence
+\(B\) must be large (around 2,000) due to the nature of confidence
 intervals requiring greater accuracy \citep{Efron86}.
 
-Using our example, to find a 95\% confidence interval for the population
-mean of \texttt{Dec}, we would get the following:
+\hypertarget{standard-confidence-interval-in-use}{%
+\subsubsection{Standard Confidence Interval in
+Use}\label{standard-confidence-interval-in-use}}
+
+Using our previous example to find a 95\% confidence interval for the
+population mean of \texttt{Dec}, we would get the following confidence
+interval:
 
@@
 \end{verbatim}
+
+This means that we can say we are 95\% confident that the true mean
+number of inches of snow that fall in December is betwwen 13.86 inches
+and 17.66 inches. Our original histogram with the confidence interval is
+below (Figure 3).
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
 
@@
 samples less than \(t\):
-\[\hat{G}(t) = \frac{\#\{\hat{\theta^{*b} \leq t}\}}{B}.\] Thus the
+\[\hat{G}(t) = \frac{\#\{\hat{\theta}^{*b} \leq t\}}{B}.\] Thus the
 \(\alpha\)th percentile point of the distribution is given by
@@
 
+\hypertarget{the-percentile-method-in-use}{%
+\subsubsection{The Percentile Method in
+Use}\label{the-percentile-method-in-use}}
+
 Finding a 95\% confidence interval for the true population mean of
@@
 \end{verbatim}
+
+Therefore, we can say that we are 95\% confident that the true
+population mean of inches of snow that fall in December is between 13.91
+inches and 17.72 inches. Our original histogram with the percentile
+confidence interval is shown below (Figure 4).
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-7-1.pdf} This
-interval is similar to the one created using the Standard method, but
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf} This
+interval is similar to the one created using the standard method, but
 shifted slightly to the right.
@@
 \(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},\)
-define \[p_0 = \frac{\#\{\hat{\theta^{*b} \leq \theta}\}}{B},\] and
+define \[p_0 = \frac{\#\{\hat{\theta}^{*b} \leq \theta\}}{B},\] and
 define the bias-correction value \[z_0 = \Phi^{-1}(p_0),\] where
-\(\Phi^{-1}\) is the inverse function of the standard normal cdf. Thus
+\(\Phi^{-1}\) is the inverse function of the standard normal cdf. Thus,
 we define a transformation
@@
 \(\theta\), \[\hat{\phi} \sim N(\phi - z_0\tau, \tau^2),\] with \(z_0\)
-and \(\tau\) constants. This means that we can say the bias corrected
-method has an \(\alpha\)-level endpoint can be represented as
+and \(\tau\) constants. This means that we can say the bias-corrected
+method has an \(\alpha\)-level endpoint which can be represented as
 \[\hat{\theta}_{BC}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( 2z_0 + z_\alpha\right ) \right ].\]
@@
 case, the confidence interval produced by BC would be the same interval
-produced by the percentile method.
+that was produced by the percentile method.
+
+\hypertarget{the-bc-method-in-use}{%
+\subsubsection{The BC Method in Use}\label{the-bc-method-in-use}}
 
@@
 steps because we need to find the bias-correction value. First we
-calculate the sample mean.
+calculate the sample mean:
 
@@
 
-Then we can find the modified percentiles:
+Then we can find the modified percentiles and get the corresponding
+confidence interval:
 
@@
 \end{verbatim}
+
+Therefore, we are 95\% confident that the true mean inches of snow that
+fall in December in Grand Rapids, Michigan is between 14.01 inches and
+17.82 inches. Our histogram (Figure 5) is shown below.
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-10-1.pdf}
 
@@
 
-A further modification upon the BC interval is the bias corrected and
+A further modification upon the BC interval is the bias-corrected and
 accelerated method (BCa). For this method, we do not assume the the
-standard error, \(\tau\) is constant as we did in the BC interval
+standard error, \(\tau\), is constant as we did in the BC interval
 \citep[\citet{EfronCasi}]{Efron86}. Rather, we assume the existence of a
@@
 other words, \(a\) is proportional to the skewness of the bootstrap
-distribution. For example, for one-parameter exponential families,
-\(a=z_0\), however, there are many different algorithms to compute and
-estimate \(a\) \citep{Flowers18}. Now, our \(\alpha\)-level endpoint
-from BCa is
+distribution. For example, \(a=z_0\) for one-parameter exponential
+families, however, there are many different algorithms to compute and
+estimate \(a\) \citep{Flowers18}. Now, our \(\alpha\)-level endpoint for
+a BCa confidence interval is
 \[\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].\]
-If \(a = 0\), then
+We can observe that if \(a = 0\), then
 \(\hat{\theta}_{BCa}[\alpha] = \hat{\theta}_{BC}[\alpha].\) When
-calculating a BCa interval, the acceleration value \(a\) is not a
-function of the bootstrap distribution and must be calculated
-separately, however the process is algorithmic and can be calculated
-without too much work. Each of the three previous methods (percentile,
-BC, and BCa) all build upon each other and have less restrictive
-assumptions, however computation increases as we loosen assumptions.
+calculating a BCa confidence interval, the acceleration value, \(a\), is
+not a function of the bootstrap distribution and must be calculated
+separately. However the process is algorithmic and can be calculated
+without too much work. As we saw, each of the three previous methods
+(percentile, BC, and BCa) all build upon each other and have less
+restrictive assumptions, but this means that computation increases as we
+loosen assumptions.
+
+\hypertarget{the-bca-confidence-interval-in-use}{%
+\subsubsection{The BCa Confidence Interval in
+Use}\label{the-bca-confidence-interval-in-use}}
 
 In practice, we can use the jackknife procedure to estimate the
-acceleration value for this method. Thus, we will run the jackknife
+acceleration value for this method. The jackknife procedure is a
+different resampling technique that is often used to estimate the bias
+and variance of a large population. Thus, we will run the jackknife
 procedure:
@@
 
-Then we can compute \(a\).
+Then we can compute an approximation for \(a\).
 
@@
 
-Now, we can find the adjust percentiles and the bias-corrected with
+Now, we can find the adjusted percentiles and the bias-corrected with
 acceleration confidence interval.
@@
 \NormalTok{a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
-\NormalTok{                    (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }\CommentTok{\#a\_newlow}
+\NormalTok{                    (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }
 \NormalTok{a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
-\NormalTok{                     (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }\CommentTok{\#a\_newhigh}
+\NormalTok{                     (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }
 \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
@@
 \end{verbatim}
+
+We are 95\% confident that the true mean number of inches of snow that
+fall in December is between 13.92 inches and 17.72 inches. Figure 6
+shows our confidence interval.
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-17-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 studentized method). Recall from earlier, our sample, \(X\) from which
-we can calculate an estimate, \(\hat{\theta}(X)\) of the parameter of
+we can calculate an estimate (\(\hat{\theta}(X)\)) of the parameter of
 interest \(\theta\) \citep[\citet{Puth15}]{Efron86}. We can also
@@
 can use these parameters to find the Student's \(t\)-statistic defined
-as \[T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.\] As such, the
+as: \[T = \frac{\hat{\theta} - \theta}{\hat{\sigma}}.\] As such, the
 \(\alpha\)th percentile point of a confidence interval of \(\theta\)
@@
 \(T_{(\alpha)}\) represents the \(\alpha\)th percentile of the
-\(t\)-distribution, \(T\). Unfortunately, the percentiles of the
-t-distribution are unknown in most cases, but we can use bootstrapping
-to estimate these percentiles. To do this, we perform a large number,
-\(B\), of bootstrap samples, from which we can find the bootstrap
-replications of the parameter of interest,
+\(t\)-distribution, \(T\). Unfortunately, the percentiles of this
+\(t\)-distribution are unknown in most cases, but we can use
+bootstrapping to estimate these percentiles. To do this, we perform a
+large number, \(B\), of bootstrap samples, from which we can find the
+bootstrap replications of the parameter of interest,
 \(\hat{\theta^*} = \hat{\theta}(X^*)\), and the standard error,
@@
 t-statistic for each bootstrap sample:
-\[T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.\] for each
-bootstrap sample. Using a large number of these bootstrap samples, we
-can estimate the percentiles of the \(t\)-distribution such that:
+\[T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.\] Using a
+large number of these bootstrap samples, we can estimate the percentiles
+of the \(t\)-distribution such that:
 \[\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.\]
-This means that for \(B = 2000\) and \(\alpha = 0.90\), then
+This means that for \(B = 2,000\) and \(\alpha = 0.90\), then
 \(\hat{T}_{(\alpha)}\) is the 1,800th ordered point of all of the
@@
 can calculate the appropriate confidence interval for the parameter of
-interest specifically from the bootstrapped statistic
+interest specifically from the bootstrapped statistics
 \citep[\citet{Puth15}]{Efron86}.
+
+\hypertarget{studentized-confidence-interval-in-use}{%
+\subsubsection{Studentized Confidence Interval in
+Use}\label{studentized-confidence-interval-in-use}}
 
@@
 
-This would give us the following histogram:
+So we are 95\% confident that the true mean number of inches of snow
+that fall in December in Grand Rapids, Michigan is between 14.03 inches
+and 18.02 inches. This would give us the following confidence interval
+(Figure 7)
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-17-1.pdf}
 
@@
 
-For the simulation, we will randomly sample from distributions in which
-we know the true population mean. For example, we will sampling from a
-Gamma Distribution where we can find the true population mean using the
-shape and rate parameters of the sample distribution. After we sample
-from a distribution, we will create a bootstrapped confidence interval
-for a few of the methods we described in the exposition. Since we know
-the true population mean of the distribution, we will determine if the
-true population parameter is contained in the confidence interval for
+For our simulation, we will randomly sample from distributions in which
+we know the true population mean. For example, we will be sampling from
+a Gamma distribution where we can find the true population mean using
+the shape and rate parameters of the sample distribution. After we
+sample from the distribution, we will create a bootstrapped confidence
+interval for a few of the methods we described in the exposition. Since
+we know the true population mean of the distribution, we will determine
+if the true population mean is contained in the confidence interval for
 each of the methods we are testing. We will perform this process a large
@@
 mean for a given distribution. We will do this for a couple different
-distributions as well as a range of sample sizes show how the intervals
-perform with skewed distributions and larger sample sizes.
+distributions as well as a range of sample sizes to show how the
+intervals perform with skewed distributions and larger sample sizes.
 
@@
 
-First, we will create a simulation that pick a random sample from a
-distribution and performs
-
-and tests to see if the sample creates a bootstrapped confidence
-intervals that contain the true population parameter. First, we have the
-simulation of selecting from a Normal Distribution. Since we have a
-\(N(0,1)\) distribution, out true population mean is 0.
-
-Second, we select from a Gamma Distribution with a shape parameter of 1
-and a scale parameter of 4. This means the true population parameter is
-4.
-
-After that, these functions will compile all of the information we have
-created from the previous methods and run the simulations of each method
-for a variety of sample sizes.
-
-And here, we run the simulations for each of the distributions and store
-the results.
-
-Then, we can plot the results and compile the results into tables.
-
-When we sample from the Gamma distribution which is a distribution that
-is heavily skewed, the Studentized Confidence interval performs the
-best. At a large sample size, the Studentized Confidence interval
-contains the true population parameter about 94.5\% of the time. The
-Studentized confidence interval outperforms the rest of the intervals by
-a bit. The rest of the intervals are very similar to each other ranging
-from a correct interval 92.5\% to 93\% of the time. In general, as the
-sample size that we are bootstrapping from increases, the higher
-percentage our confidence intervals predict correctly.
-
-Similar to when we sampled from the Gamma distribution, the Studentized
-confidence interval performed the best when we sampled from a Normal
-distribution with around 95\% of the confidence intervals containing the
-true population parameter. The next best is the Standard confidence
-interval with a performance of around 94.5\% correct intervals at a high
-sample size. The rest of the intervals performed similarly at around
-94.2\% accuracy. As before, the accuracy increased as the sample size
-increased.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-  \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+To start, we will declare some constants including the sample sizes and
+the number of bootstrap replications we are using.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{5}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{100}\NormalTok{, }\DecValTok{150}\NormalTok{)}
+\NormalTok{num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
+\NormalTok{boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\end{Highlighting}
+\end{Shaded}
+
+Next, we create a simulation that randomly selects a sample from a
+Normal distribution and performs a bootstrap with 2,000 bootstrap
+replications. Then, we create the confidence intervals from this
+bootstrap and determine if the true mean, our population parameter, is
+contained within our intervals. Since we are using a \(Normal(0,1)\)
+distribution, our true population mean is equal to 0. We will repeat
+this process 10,000 times as specified for each of the sample sizes that
+we are testing. Since we are originally sampling from a Normal
+distribution, the assumptions we hold for the standard interval are true
+and thus, we would expect all of the methods to perform comparably to
+each other at large sample sizes.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_sim\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+
+\NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
 \NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
@@
 
-\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
-\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
-\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
 
@@
 \NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
 \NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
@@
 
-\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
+\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{0}
+
+    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
+\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
+\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ boot.stat, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
+
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+\NormalTok{    \}}
+
+\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{  \}}
+
+\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V3, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V4, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5) }
+\NormalTok{  master\_df}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Secondly, we select from a Gamma Distribution with a shape parameter of
+1 and a scale parameter of 4 (\(Gamma(1,4)\)). Therefore, the true
+population mean is 4 because the true mean is given by the product of
+the shape and scale parameter. This simulation follows the same process
+as above where we sampled from the Normal distribution except we are
+sampling from a Gamma distribution this time. Since, our Gamma
+distribution is heavily left-skewed, we would expect the studentized
+confidence interval and the BCa confidence interval to perform the best.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_sim\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+
+\NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  \}}
+
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
+
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
+
+\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+
+\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{4}
+
+    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
+\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
+\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ boot.stat, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
+
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+\NormalTok{    \}}
+\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
+\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{  \}}
+\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V3, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V4, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5) }
+\NormalTok{  master\_df}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Lastly, we will be sampling from a Log-Normal distribution. This means
+that if we have a random variable, \(X \sim Lognormal\), then the random
+variable, \(Y = ln(X) \sim Normal\). Therefore, the distribution is
+left-skewed, although not as heavily as the Gamma distribution we
+previously used. The true mean of this distribution can be found using
+\(E(X) = e^{u+\frac{\sigma^2}{2}}\) which means that for a
+\(Lognormal(0,1)\) distribution, we expect the population mean to be
+\(e^{\frac{1}{2}}\). Again, we would expect the studentized confidence
+interval and the BCa confidence interval to perform the best.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+
+\NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
+\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
+    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
+\NormalTok{  \}}
+
+\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
+
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
+
+\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
+
 \NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
@@
 
-\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
-\NormalTok{      results}
-      \CommentTok{\#plot(results)}
+\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ boot.stat, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
 \NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
@@
 \NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
-\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
 \NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
@@
 \NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
-
 \NormalTok{    \}}
-
 \NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
 \NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
+\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
 \NormalTok{  \}}
-
 \NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
-             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
+      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V3, }
+             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V4, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5) }
 \NormalTok{  master\_df}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_sim\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
+Once we have all the simulations, we can run them below.
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
-\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
-    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
-\NormalTok{  \}}
-
-\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
-\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
-\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
-
-\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-
-\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
-\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
-\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{0}
-
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
-\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
-\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-
-\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
-\NormalTok{      results}
-      \CommentTok{\#plot(results)}
-\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
-
-\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
-\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
-
-\NormalTok{    \}}
-
-\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
-\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{  \}}
-
-\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
-             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  master\_df}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{run\_sim\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-  \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
-\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
-    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
-\NormalTok{  \}}
-
-\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
-\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
-\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
-
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
-
-\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-
-\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
-\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
-\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{4}
-
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
-\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
-\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-
-\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
-\NormalTok{      results}
-      \CommentTok{\#plot(results)}
-\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
-
-\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
-\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
-
-\NormalTok{    \}}
-
-\NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
-\NormalTok{    master[i, }\DecValTok{2}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(norm\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{3}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(basic\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{4}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(student\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{5}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(percentile\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{    master[i, }\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(bca\_contains)}\SpecialCharTok{/}\NormalTok{sim\_reps}
-\NormalTok{  \}}
-
-\NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
-      \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Normal"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Basic"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V4, }
-             \StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"BCa"} \OtherTok{=}\NormalTok{ V6) }
-\NormalTok{  master\_df}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(log\_normal\_df,}\StringTok{"log\_normal\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(normal\_df,}\StringTok{"normal\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(gamma\_df,}\StringTok{"gamma\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data\_df.csv\textquotesingle{}}\NormalTok{)}
-\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df.csv\textquotesingle{}}\NormalTok{)}
-\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}log\_normal\_df.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{normal\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(normal\_df\_trial2,}\StringTok{"normal\_data\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{log\_normal\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(log\_normal\_df\_trial2,}\StringTok{"log\_normal\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{gamma\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(gamma\_df\_trial2,}\StringTok{"gamma\_data\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}log\_normal\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
+
+\CommentTok{\# create the figure that shows the normal output }
+\NormalTok{normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+
+\NormalTok{normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ normal\_df\_long, }
+                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Normal }
+\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
+\StringTok{       different sample sizes on Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
+
+\CommentTok{\# create the table for the normal output}
+\NormalTok{normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)))}
 
@@
 \NormalTok{gamma\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
 
@@
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
+\StringTok{       different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
@@
 
-\CommentTok{\# create the figure that shows the normal output }
-\NormalTok{normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
-
-\NormalTok{normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ normal\_df\_long, }
-                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Normal }
-\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
-       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
-
-\CommentTok{\# create the table for the normal output}
-\NormalTok{normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
-        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)))}
-
 \CommentTok{\# create the figure that shows the log normal output}
 \NormalTok{log\_normal\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
+  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
 
@@
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
+\StringTok{       different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df.csv\textquotesingle{}}\NormalTok{)}
-
-\NormalTok{master\_df\_long }\OtherTok{\textless{}{-}}\NormalTok{ master\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{, }\AttributeTok{names\_to =} \StringTok{"method"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }
-
-\NormalTok{master\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ master\_df\_long, }
-                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal Distibution"}\NormalTok{, }
-       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
-       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
-
-\NormalTok{master\_fig}
-\end{Highlighting}
-\end{Shaded}
-
 \bibliographystyle{agsm}

### 2022-12-09 project/PaperTemplate/paper.Rmd
Finished paper

@@
 - name: Justin Papagelis
-  thanks: The authors gratefully acknowledge
-
-   '' Profossor Wagaman
+  thanks: The authors gratefully acknowledge Profossor Wagaman
   affiliation: Department of Mathematics and Statistics, Amherst College
@@
 Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution. 
-In particular, bootstrapping is a computational heavy method which is useful for many different situations.
+In particular, bootstrapping is a heavy computational method useful for many situations.
 
@@
 Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$.
-However $F$ is unknown, so this is not possible. 
+However, $F$ is unknown, so this is not possible. 
 The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample, $X$, without making any parametric assumptions about $F$ (such as its distribution type). 
@@
 From this bootstrap sample, a bootstrap replication of the test statistic can be computed using $\hat{\theta}^* = \hat{\theta}(X^*)$. 
-A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated. 
+A large number, $B$, of bootstrap samples are drawn independently, and the corresponding bootstrap replication of the test statistic is calculated. 
 $$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B.$$ 
-The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications. 
-As $B$ increases, $\hat{F}$ approaches $F$ which means that the test statistic of interest approaches its true value as well.
+The test statistic's bootstrap estimate is the test statistic's empirical value from all of the $\hat{\theta}^{*b}$ replications. 
+As $B$ increases, $\hat{F}$ approaches $F$, which means that the test statistic of interest approaches its true value as well.
 
@@
 
-We demonstrate performing a non-parametric bootstrap below using `SnowGR` which gives the official snowfall dataset by month for Grand Rapids, MI, starting in 1893. 
-We will be using the `Dec` variable which is the number of inches of snow that fell in December of each year. 
-In particular, we are interested in the sample mean and later finding confidence intervals for population mean of `Dec`. 
-The distribution is below (Figure 1).
-
-```{r SnowGR histogram, cache = TRUE}
+We demonstrate performing a non-parametric bootstrap below using `SnowGR`, which gives the official snowfall dataset by the month for Grand Rapids, MI, starting in 1893. 
+We will be using the `Dec` variable, which is the number of inches of snow that fell in December of each year. 
+In particular, we are interested in the sample mean and later finding confidence intervals for the population mean of `Dec`. 
+The distribution is shown (Figure 1).
+```{r SnowGR histogram}
 data(SnowGR)
@@
 Next, we will perform the non-parametric bootstrap using 10,000 replications.
-
-```{r non-paramteric bootstrap, cache = TRUE}
+```{r non-paramteric bootstrap}
 set.seed(495)
@@
 ```
-Below, in Figure 2, is the histogram of bootstrapped values. Since we performed a large number of bootstrap replications, the bootstrapped distribution appears to be approximately Normal.
-
+Figure 2 shows the histogram of bootstrapped values. Since we performed a large number of bootstrap replications, the bootstrapped distribution appears to be approximately Normal.
 ```{r, cache = TRUE}
@@
 An $\alpha$-level standard confidence interval is given by $$\hat{\theta}_S[\alpha] = \hat{\theta} \pm z_{\alpha}\hat{\sigma},$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation [@Efron86].
-We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.
+We say that the confidence interval constructed in this manner can capture the true parameter with a probability of $\alpha$.
 
-The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal.
-As such, the standard confidence interval is sometimes called the normal confidence interval for a bootstrapped sample.
-This means that for an unknown skewed distribution, the standard confidence interval could present an incorrect range.
+The standard confidence interval is built based on the assumption that the distribution we are sampling is Normal.
+The standard confidence interval is sometimes called the normal confidence interval for a bootstrapped sample.
+This means that the standard confidence interval could present an incorrect range for an unknown skewed distribution.
 However, the same process can be used with bootstrap sampling to form the bootstrap percentile method. 
-This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created. 
+This way, an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created. 
 For bootstrapped confidence intervals, the number of bootstrap replications $B$ must be large (around 2,000) due to the nature of confidence intervals requiring greater accuracy [@Efron86].
@@
 
-```{r, cache = TRUE}
+```{r}
 mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * 
@@
 ```
-This means that we can say we are 95% confident that the true mean number of inches of snow that fall in December is betwwen 13.86 inches and 17.66 inches.
-Our original histogram with the confidence interval is below (Figure 3).
+Therefore, we are 95% confident that the true mean number of inches of snow that fall in December is between 13.86 inches and 17.66 inches.
+Our original histogram with the confidence interval is shown (Figure 3).
 
-```{r, cache = TRUE}
+```{r}
 gf_histogram(~ Dec, data = SnowGR) +
@@
 In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval. 
-However, this is not usually the case. 
+However, this is only sometimes the case. 
 When the bootstrap distribution is non-normal, we can suppose that there exists, for all $\theta$, $$\hat{\phi} \sim N(\phi, \tau^2),$$ for some monotone transformation $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$, and $\tau$ is a constant.
@@
 This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ 
-This also can be represented as an interval, $$\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ].$$ Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$.
+This also can be represented as an interval, $$\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ].$$ Therefore, the percentile method produces a correct interval for $\phi$ and, due to the transformation invariance, also produces a correct percentile interval for $\theta$.
 This method assumes the existence of some monotone normalizing mapping $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$ and relies on that to create a correct interval.
@@
 
-```{r, cache = TRUE}
+```{r}
 qdata(~ mean, c(0.025, 0.975), data = dec_means)
@@
 Therefore, we can say that we are 95% confident that the true population mean of inches of snow that fall in December is between 13.91 inches and 17.72 inches.
-Our original histogram with the percentile confidence interval is shown below (Figure 4).
-```{r, cache = TRUE}
+Our original histogram with the percentile confidence interval is shown (Figure 4).
+```{r}
 gf_histogram(~ Dec, data = SnowGR) +
@@
 
-The next method we will be looking at is the bias-corrected percentile method (BC method) which is an improvement upon the previous percentile method because we now take into account the possibility of bias.
-It can be shown that $\hat{\theta}$ is biased upwards relative to $\theta$ which means that the confidence intervals should be adjusted downwards [@Efron86,@EfronCasi]. 
+The following method we will be looking at is the bias-corrected percentile method (BC method) which is an improvement upon the previous percentile method because we now consider the possibility of bias.
+It can be shown that $\hat{\theta}$ is biased upwards relative to $\theta$, which means that the confidence intervals should be adjusted downwards [@Efron86,@EfronCasi]. 
 From our simulated bootstrap replications $\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},$ define $$p_0 = \frac{\#\{\hat{\theta}^{*b} \leq \theta\}}{B},$$ and define the bias-correction value $$z_0 = \Phi^{-1}(p_0),$$ where $\Phi^{-1}$ is the inverse function of the standard normal cdf.
@@
 ### The BC Method in Use
-Using this method to create a 95% confidence interval has a couple more steps because we need to find the bias-correction value. First we calculate the sample mean:
+Using this method to create a 95% confidence interval has a couple more steps because we need to find the bias-correction value [@EfronCasi]. First, we calculate the sample mean:
 
-```{r, cache = TRUE}
+```{r}
 sample_mean <- mean(~Dec, data = SnowGR); sample_mean
@@
 
-```{r, cache = TRUE}
+```{r}
 less_than_sample_mean <- sum(ifelse(dec_means <= sample_mean, 1, 0))/10000
@@
 
-```{r, cache = TRUE}
+```{r}
 z0 <- qnorm(less_than_sample_mean); z0
@@
 
-```{r, cache = TRUE}
-alphalow <- 0.025; alphahigh <- 0.975
+```{r}
+alpha_lower <- 0.025; alpha_upper <- 0.975
 
-newlow <- pnorm(2*z0 + qnorm(alphalow)); #newlow
-newhigh <- pnorm(2*z0 + qnorm(alphahigh)); #newhigh
+new_lower <- pnorm(2*z0 + qnorm(alpha_lower)); 
+new_upper <- pnorm(2*z0 + qnorm(alpha_upper));
 
-qdata(~ mean, c(newlow, newhigh), data = dec_means)
+qdata(~ mean, c(new_lower, new_upper), data = dec_means)
 ```
-Therefore, we are 95% confident that the true mean inches of snow that fall in December in Grand Rapids, Michigan is between 14.01 inches and 17.82 inches. Our histogram (Figure 5) is shown below.
+Therefore, we are 95% confident that the true mean inches of snow that fall in December in Grand Rapids, Michigan is between 14.01 inches and 17.82 inches. Our histogram (Figure 5) is shown.
 
-```{r, cache = TRUE}
+```{r}
 gf_histogram(~ Dec, data = SnowGR) +
@@
 ## The Bias-Corrected and Accelerated (BCa) Method
-A further modification upon the BC interval is the bias-corrected and accelerated method (BCa). 
-For this method, we do not assume the the standard error, $\tau$, is constant as we did in the BC interval [@Efron86,@EfronCasi]. 
+The bias-corrected and accelerated method (BCa) further modifies the BC interval. 
+This method does not assume that the standard error, $\tau$, is constant as we did in the BC interval [@Efron86,@EfronCasi]. 
 Rather, we assume the existence of a monotone transformation $\hat{\phi} = g(\hat{\theta)}, \phi = g(\theta)$ such that for any $\theta$, $$\hat{\phi} \sim N(\phi - z_0\tau_\phi, \tau_\phi^2) \text{ where } \tau_\phi = 1+ a\phi.$$
@@
 In other words, $a$ is proportional to the skewness of the bootstrap distribution. 
-For example, $a=z_0$ for one-parameter exponential families, however, there are many different algorithms to compute and estimate $a$ [@Flowers18]. 
+For example, $a=z_0$ for one-parameter exponential families. However, there are many different algorithms to compute and estimate $a$ [@Flowers18]. 
 Now, our $\alpha$-level endpoint for a BCa confidence interval is $$\hat{\theta}_{BCa}[\alpha] = \hat{G}^{-1} \left [ \Phi \left ( z_0 + \frac{z_0+z_\alpha}{1-a(z_0+z_a)} \right ) \right ].$$ 
@@
 When calculating a BCa confidence interval, the acceleration value, $a$, is not a function of the bootstrap distribution and must be calculated separately.
-However the process is algorithmic and can be calculated without too much work. 
-As we saw, each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, but this means that computation increases as we loosen assumptions.
+However, the process is algorithmic and can be calculated without too much work. 
+As we saw, each of the three previous methods (percentile, BC, and BCa) all build upon each other and have less restrictive assumptions, but computation increases as we loosen assumptions.
 
 ### The BCa Confidence Interval in Use
-In practice, we can use the jackknife procedure to estimate the acceleration value for this method.
-The jackknife procedure is a different resampling technique that is often used to estimate the bias and variance of a large population.
+In practice, we can use the jackknife procedure to estimate the acceleration value for this method [@EfronCasi].
+The jackknife procedure is a different resampling technique often used to estimate the bias and variance of a large population.
 Thus, we will run the jackknife procedure:
 
-```{r, cache = TRUE}
+```{r}
 theta <- function(x){mean(x)}
@@
 We find the mean of the jackknife values below:
-
-```{r, cache = TRUE}
-jackmean <- mean(~ jackknife_results$jack.values); jackmean
+```{r}
+jack_mean <- mean(~ jackknife_results$jack.values); jack_mean
 ```
@@
 
-```{r, cache = TRUE}
-estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
-  (sum((jackknife_results$jack.values - jackmean)^2))^(1.5); estimated_a
+```{r}
+estimated_a <- (1/6)*sum((jackknife_results$jack.values - jack_mean)^3)/
+  (sum((jackknife_results$jack.values - jack_mean)^2))^(1.5); estimated_a
 ```
@@
 
-```{r, cache = TRUE}
-a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
-                    (1-estimated_a*(z0 + qnorm(alphalow)))); 
-a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
-                     (1-estimated_a*(z0 + qnorm(alphahigh)))); 
-qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
+```{r}
+a_new_lower <- pnorm(z0 + (z0 + qnorm(alpha_lower))/
+                    (1-estimated_a*(z0 + qnorm(alpha_lower)))); 
+a_new_upper <- pnorm(z0 + (z0 + qnorm(alpha_upper))/
+                     (1-estimated_a*(z0 + qnorm(alpha_upper)))); 
+qdata(~ mean, c(a_new_lower, a_new_upper), data = dec_means)
 ```
@@
 
-```{r, cache = TRUE}
+```{r}
 gf_histogram(~ Dec, data = SnowGR) +
@@
 To do this, we perform a large number, $B$, of bootstrap samples, from which we can find the bootstrap replications of the parameter of interest, $\hat{\theta^*} = \hat{\theta}(X^*)$, and the standard error, $\hat{\sigma^*} = \hat{\sigma}(X^*)$.
-From these we can calculate a t-statistic for each bootstrap sample: $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.$$ Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.$$
+From these, we can calculate a t-statistic for each bootstrap sample: $$T^* = \frac{\hat{\theta}^* - \hat{\theta}}{\hat{\sigma}^*}.$$ Using a large number of these bootstrap samples, we can estimate the percentiles of the $t$-distribution such that: $$\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap replications of }T^*.$$
 This means that for $B = 2,000$ and $\alpha = 0.90$, then $\hat{T}_{(\alpha)}$ is the 1,800th ordered point of all of the bootstrap replications of $T^*$. 
-It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is because we assume that our bootstrapped statistic is pivotal which means that the confidence interval does not depend on any other parameters.
+It follows that the $\alpha$th studentized confidence interval endpoint can be given with $$\hat{\theta}_T[\alpha] = \hat{\theta} - \hat{\sigma}T_{(\alpha)},$$ where we can estimate the standard error using $$\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.$$ One of the main factors why the studentized method is so popular is that we assume that our bootstrapped statistic is pivotal, which means that the confidence interval does not depend on any other parameters.
 Instead, we can calculate the appropriate confidence interval for the parameter of interest specifically from the bootstrapped statistics [@Efron86,@Puth15].
@@
 
-```{r, cache = TRUE}
+```{r}
 set.seed(495)
-
+# sample statistics
 orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
 orig_se <- sd(~ Dec, data = SnowGR)/sqrt(nrow(SnowGR))
-
+# initialize storage vectors
 se <- rep(0,nboot)
 t_stat <- rep(0,nboot)
-
+# use bootstrap replication statistics to find se and t-stat
 for (i in 1:nboot) {
@@
 }
-
+#find interval
 dec_t_stat <- as.data.frame(t_stat)
-
 q <- unname(quantile(dec_t_stat$t_stat, c(0.025, 0.975)))
@@
 upper <- q[2]
-
 c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)
@@
 So we are 95% confident that the true mean number of inches of snow that fall in December in Grand Rapids, Michigan is between 14.03 inches and 18.02 inches.
-This would give us the following confidence interval (Figure 7)
+This would give us the following confidence interval (Figure 7):
 
-```{r, cache = TRUE}
+```{r}
 gf_histogram(~ Dec, data = SnowGR) +
@@
   geom_vline(aes(xintercept= 18.01709)) 
-
 ```
@@
 
+## Code
 For our simulation, we will randomly sample from distributions in which we know the true population mean. 
@@
 After we sample from the distribution, we will create a bootstrapped confidence interval for a few of the methods we described in the exposition. 
-Since we know the true population mean of the distribution, we will determine if the true population mean is contained in the confidence interval for each of the methods we are testing. 
-We will perform this process a large number of times (10,000 simulations) and then average by the number of iterations to determines on average, the proportion that each bootstrapped confidence interval method contains the true population mean for a given distribution.
-We will do this for a couple different distributions as well as a range of sample sizes to show how the intervals perform with skewed distributions and larger sample sizes.
+Since we know the true population mean of the distribution, we will determine if the true population mean is contained in the confidence interval for each of the methods we are testing [@Guillaume21].
+We will perform this process a large number of times (10,000 simulations) and then average by the number of iterations to determine, on average, the proportion that each bootstrapped confidence interval method contains the true population mean for a given distribution.
+We will do this for a couple of different distributions and ranges of sample sizes to show how the intervals perform with skewed distributions and larger sample sizes.
 
-To do this simulation, we will be using the `boot` package [@boot]. 
+To do this simulation, we will use the `boot` package [@boot]. 
 This package can compute a bootstrap object which contains the output from a bootstrap calculation of a given sample and then produces confidence intervals from the bootstrap object. 
-In particular, we will use the `boot.ci` function to create four types of confidence intervals: the standard (or normal) confidence interval, the studentized confidence interval, the percentile confidence interval, and the bias-corrected with acceleration confidence interval.
+In particular, we will use the `boot.ci` function to create four confidence intervals: the standard (or normal) confidence interval, the studentized confidence interval, the percentile confidence interval, and the bias-corrected with acceleration confidence interval.
 
-To start, we will declare some constants including the sample sizes and the number of bootstrap replications we are using.
+To start, we will declare some constants, including the sample sizes and the number of bootstrap replications we use. We will be using a range of sample sizes from 5 to 150. 
+For this simulation, we will use a confidence level of 95%.
 
 ```{r pre-simulation, eval = TRUE}
-
 sample_sizes <- c(5, 10, 15, 20, 30, 40, 60, 100, 150)
@@
 Then, we create the confidence intervals from this bootstrap and determine if the true mean, our population parameter, is contained within our intervals.
-Since we are using a $Normal(0,1)$ distribution, our true population mean is equal to 0. 
-We will repeat this process 10,000 times as specified for each of the sample sizes that we are testing. 
-Since we are originally sampling from a Normal distribution, the assumptions we hold for the standard interval are true and thus, we would expect all of the methods to perform comparably to each other at large sample sizes.
+Since we are using a $Normal(0,1)$ distribution, our true population mean equals 0. 
+We will repeat this process 10,000 times as specified for each sample size we are testing. 
+Since we are initially sampling from a Normal distribution, the assumptions we hold for the standard interval are true.
+Thus, we would expect all of the methods to perform comparably to each other at large sample sizes.
 
@@
 run_sim_normal <- function(sim_reps) {
-
+  # create function to return mean and sd of bootstrap replication
   boot.stat <- function(d, i) {
@@
   }
-
+  # initialize matrix to hold different bootstrap prop. for each sample size
   master <- matrix(nrow = num_sample_sizes, ncol = 5)
-
+  # iterate through each sample size
   for(i in 1:num_sample_sizes) {
-
+    # initialize vectors that hold if the CI contains true mean by iteration
     norm_contains <- rep(0, sim_reps)
@@
     bca_contains <- rep(0, sim_reps)
-
+    # 
     n <- sample_sizes[i]
     true_mean <- 0
-
+    # perform 10,000 iterations of bootstraps
     for (j in 1:sim_reps) {
@@
       values <- data.frame(X)
+      # perform bootstrap and CIs
       results <- boot(data = values, statistic = boot.stat, R = boot_reps)
-      ci <- boot.ci(results, conf = 0.95, type = c("norm", "perc", "bca", "stud"))
-
-      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
-      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
-      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
-      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+      ci <- boot.ci(results, conf = 0.95, 
+                    type = c("norm", "perc", "bca", "stud"))
+      # update vectors depending on if the CI contains true mean
+      norm_contains[j] <- true_mean >= ci$normal[2] & 
+        true_mean <= ci$normal[3]
+      student_contains[j] <- true_mean >= ci$student[4] & 
+        true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & 
+        true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] &
+        true_mean <= ci$bca[5]
     }
-
+    # add the sample size and average proportion to matrix
     master[i, 1] <- sample_sizes[i]
@@
   }
-
+  # some wrangling
   master_df <- as.data.frame(master) %>% 
@@
 }
-
 ```
 
-Secondly, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4 ($Gamma(1,4)$). 
-Therefore, the true population mean is 4 because the true mean is given by the product of the shape and scale parameter. 
-This simulation follows the same process as above where we sampled from the Normal distribution except we are sampling from a Gamma distribution this time. 
-Since, our Gamma distribution is heavily left-skewed, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
+Secondly, we select from a Gamma Distribution with a shape parameter of one and a scale parameter of four ($Gamma(1,4)$). 
+Therefore, the true population mean is 4 because the product of the shape and scale parameters gives the true mean. 
+This simulation follows the same process as above, where we sampled from the Normal distribution, except we are sampling from a Gamma distribution this time. 
+Since our Gamma distribution is heavily left-skewed, we expect the studentized confidence interval and the BCa confidence interval to perform the best.
 
@@
 run_sim_gamma <- function(sim_reps) {
-
   boot.stat <- function(d, i) {
@@
   }
-
   master <- matrix(nrow = num_sample_sizes, ncol = 5)
-
   for(i in 1:num_sample_sizes) {
-
     norm_contains <- rep(0, sim_reps)
@@
     bca_contains <- rep(0, sim_reps)
-
     n <- sample_sizes[i]
     true_mean <- 4
-
     for (j in 1:sim_reps) {
@@
       values <- data.frame(X)
-
       results <- boot(data = values, statistic = boot.stat, R = boot_reps)
-      ci <- boot.ci(results, conf = 0.95, type = c("norm", "perc", "bca", "stud"))
-
-      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
-      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
-      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
-      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]
+      ci <- boot.ci(results, conf = 0.95, 
+                    type = c("norm", "perc", "bca", "stud"))
+      norm_contains[j] <- true_mean >= ci$normal[2] & 
+        true_mean <= ci$normal[3]
+      student_contains[j] <- true_mean >= ci$student[4] & 
+        true_mean <= ci$student[5]
+      percentile_contains[j] <- true_mean >= ci$percent[4] & 
+        true_mean <= ci$percent[5]
+      bca_contains[j] <- true_mean >= ci$bca[4] & 
+        true_mean <= ci$bca[5]
     }
@@
 This means that if we have a random variable, $X \sim Lognormal$, then the random variable, $Y = ln(X) \sim Normal$. 
-Therefore, the distribution is left-skewed, although not as heavily as the Gamma distribution we previously used.
+Therefore, the distribution is left-skewed, although not as heavily as the previously used Gamma distribution.
 The true mean of this distribution can be found using $E(X) = e^{u+\frac{\sigma^2}{2}}$ which means that for a $Lognormal(0,1)$ distribution, we expect the population mean to be $e^{\frac{1}{2}}$.
-Again, we would expect the studentized confidence interval and the BCa confidence interval to perform the best.
+Again, we expect the studentized confidence interval and the BCa confidence interval to perform the best.
 
@@
 run_sim_log_normal <- function(sim_reps) {
-
   boot.stat <- function(d, i) {
@@
     bca_contains <- rep(0, sim_reps)
-
     n <- sample_sizes[i]
     true_mean <- exp(1/2)
-
     for (j in 1:sim_reps) {
@@
 Once we have all the simulations, we can run them below.
-
 ```{r run simulations, warning = FALSE, eval = FALSE}
 set.seed(495)
-normal_df_trial2 <- run_sim_normal(10000)
-write.csv(normal_df_trial2,"normal_data_df_trial2.csv", row.names = FALSE)
+normal_df <- run_sim_normal(10000)
+write.csv(normal_df,"data/normal_data_df.csv", row.names = FALSE)
 
-log_normal_df_trial2 <- run_sim_log_normal(10000)
-write.csv(log_normal_df_trial2,"log_normal_df_trial2.csv", row.names = FALSE)
+log_normal_df <- run_sim_log_normal(10000)
+write.csv(log_normal_df,"data/log_normal_df.csv", row.names = FALSE)
 
-gamma_df_trial2 <- run_sim_gamma(10000)
-write.csv(gamma_df_trial2,"gamma_data_df_trial2.csv", row.names = FALSE)
+gamma_df <- run_sim_gamma(10000)
+write.csv(gamma_df,"data/gamma_data_df.csv", row.names = FALSE)
 ```
-
+After, we can create the graphs and output for each of the distributions and sample sizes.
 ```{r create graphs}
-normal_df <- read.csv(file = 'normal_data_df_trial2.csv')
-gamma_df <- read.csv(file = 'gamma_data_df_trial2.csv')
-log_normal_df <- read.csv(file = 'log_normal_df_trial2.csv')
+normal_df <- read.csv(file = 'data/normal_data_df.csv')
+gamma_df <- read.csv(file = 'data/gamma_data_df.csv')
+log_normal_df <- read.csv(file = 'data/log_normal_df.csv')
 
@@
   geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Normal 
-       Distibution", x = "Sample Size", 
+  labs(
+    title = "Prop. of CIs that Contain the True Mean from Normal Distibution", 
+    x = "Sample Size", 
     y = "Proportion (of 10,000 Simulations)", color = "Method",
@@
 normal_table <- normal_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
-        col.names = gsub("[_]", " ", names(normal_df)))
+  kable(booktabs = TRUE, align = "c", 
+        caption = "From a Normal distribution", 
+        col.names = gsub("[_]", " ", names(normal_df)), digits = 3)
 
@@
   geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Gamma 
-       Distibution", x = "Sample Size", 
+  labs(title = "Prop. of CIs that Contain the True Mean from Gamma Distibution", 
+       x = "Sample Size", 
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
+       caption = "Fig. 9: Graph showing the Accuracy of Bootstrap CI Methods for 
        different sample sizes on Gamma Dist.") +
@@
 gamma_table <- gamma_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled From Gamma Dist.", 
+  kable(booktabs = TRUE, align = "c", 
+        caption = "From a Gamma distribution", 
         col.names = gsub("[_]", " ", names(gamma_df)), digits = 3)
@@
   geom_point() + geom_line() + 
-  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal 
-       Distibution", x = "Sample Size", 
+  labs(title ="Prop. of CIs that Contain True Mean from Log-Normal Distibution",
+       x = "Sample Size", 
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
-       different sample sizes on Log-Normal Dist.") +
+       caption = "Fig. 10: Graph showing the Accuracy of Bootstrap CI Methods 
+       for different sample sizes on Log-Normal Dist.") +
   theme_light() +
@@
 log_normal_table <- log_normal_df %>%
-  kable(booktabs = TRUE, align = "c", caption = "Sampled from Normal Dist.", 
-        col.names = gsub("[_]", " ", names(log_normal_df)))
-
+  kable(booktabs = TRUE, align = "c", 
+        caption = "From a Log-Normal distribution", 
+        col.names = gsub("[_]", " ", names(log_normal_df)), digits = 3)
 ```
 
-```{r output the graphs/tables, cache = TRUE}
+## Results
+### Normal Distribution Simulation
+First, we have the results of the simulation where we randomly sampled from a Normal distribution.
+
+```{r}
+normal_fig
+```
+
+At small sample sizes, the studentized confidence interval performed much better than the other intervals, which all performed similarly. 
+For a sample size of 5, the studentized interval had an accuracy of around 91.3%.
+In comparison, the other three intervals had an accuracy of around 83% to 84% of creating an interval that contained the true population mean.
+The standard, percentile, and BCa confidence interval methods all have similar processes, especially when the distribution we are sampling from is Normal because the assumptions we made for the standard interval are correct.
+As the sample size increases, the performance of the intervals increases and rises to stay consistent at around 94% to 95% accuracy. The data (Table 1) is shown for reference.
+
+```{r}
+normal_table
+```
+### Gamma Distribution Simulation
+
+Second, we have the results from the simulation where we sampled from a Gamma distribution.
+
+```{r}
+gamma_fig
+```
+
+The $Gamma(1,4)$ distribution we randomly sampled from is heavily-skewed, so we did not expect all of the bootstrap confidence interval methods to work comparably.
+As shown in Figure 9, the studentized method performed the best at around 90% accuracy for creating a confidence interval that contained the true mean.
+The BCa method performed the second best at around 87% accuracy.
+The percentile method performed the following best with around 85% accuracy, while the standard method performed the worst with an accuracy of around 84.5%.
+As the sample size increased, the accuracy of each of the methods became less variable and evened out to a constant accuracy.
+The table containing the proportions (Table 2) is shown for reference.
+
+```{r}
+gamma_table
+```
+
+### Log-Normal Distribution Simulation
+
+Lastly, we have the results from the simulation where we sampled from a Log-Normal distribution.
+
+```{r}
 log_normal_fig
+```
+
+As shown in Figure 10, the studentized method had the greatest accuracy in creating the confidence intervals that captured the true mean.
+At small sample sizes such as 5, the studentized method has an accuracy of 82.3%, while the following best is the BCa method with a 73.4% accuracy.
+As the sample size increases, all methods' accuracy increases quickly and performs comparably, although the studentized and BCa methods perform slightly better.
+All the intervals stay constant at around 92.5% to 93.5% accuracy for large sample sizes.
+Again, the proportions are shown (Table 3) for each sample size for reference.
+
+```{r}
 log_normal_table
-
-normal_fig
-normal_table
-
-gamma_fig
-gamma_table
-
 ```
+\newpage
+# Conclusion
+In this paper, we demonstrated the power of using bootstrapped confidence intervals to estimate a true population parameter without using any information about the underlying distribution of the sample.
+In the exposition, we introduced the standard method, which relies on three conditions: 1) that the distribution is Normal, 2) that there is no bias, and 3) that there is a constant standard error.
+If we take away the first condition and use the bootstrap percentiles to create the interval, we are left with the percentile method.
+If we add a bias-correcting value not equal to zero, then we have the bias-correcting method.
+Furthermore, if we allow for a non-constant standard error (through the acceleration), we have the bias-corrected with acceleration method.
+Using the studentized method, we can also use bootstrap resampling to estimate a $t$-distribution from which we can create a confidence interval.
+From our simulation, the methods all performed reasonably the same for the Normal distribution at large sample sizes.
+However, when we introduced skew into the distributions, the studentized and BCa methods performed better than the others at large sample sizes.
+It is important to note that even at large sample sizes, none of our methods reached a coverage of 95%, which was our specified confidence level.
+The closest we were was when we sampled from a Normal distribution.
+This may be because our sample sizes need to be bigger; however, we can reach a close approximation using the largest sample size we tested.
+Thanks to the high computational power available, we can use bootstrapping to create confidence intervals for a population parameter without knowing much about the actual sample.

### 2022-12-09 project/PaperTemplate/paper.tex
Finished paper

@@
   \author{
-        Justin Papagelis \thanks{The authors gratefully acknowledge '\,'
+        Justin Papagelis \thanks{The authors gratefully acknowledge
 Profossor Wagaman} \\
@@
 estimation of a test statistic from an unknown distribution. In
-particular, bootstrapping is a computational heavy method which is
-useful for many different situations.
+particular, bootstrapping is a heavy computational method useful for
+many situations.
 
@@
 \citep{EfronCasi}. Ideally, the desired test statistic could be found by
-repeatedly sampling new reproductions of \(X\) from \(F\). However \(F\)
-is unknown, so this is not possible. The non-parametric bootstrap
+repeatedly sampling new reproductions of \(X\) from \(F\). However,
+\(F\) is unknown, so this is not possible. The non-parametric bootstrap
 creates an estimate \(\hat{F}\) from \(F\) using our sample, \(X\),
@@
 \(\hat{\theta}^* = \hat{\theta}(X^*)\). A large number, \(B\), of
-bootstrap samples are drawn independently and the corresponding
+bootstrap samples are drawn independently, and the corresponding
 bootstrap replication of the test statistic is calculated.
 \[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B.\]
-The bootstrap estimate of the test statistic is the empirical value of
-the test statistic from all of the \(\hat{\theta}^{*b}\) replications.
-As \(B\) increases, \(\hat{F}\) approaches \(F\) which means that the
-test statistic of interest approaches its true value as well.
+The test statistic's bootstrap estimate is the test statistic's
+empirical value from all of the \(\hat{\theta}^{*b}\) replications. As
+\(B\) increases, \(\hat{F}\) approaches \(F\), which means that the test
+statistic of interest approaches its true value as well.
 
@@
 We demonstrate performing a non-parametric bootstrap below using
-\texttt{SnowGR} which gives the official snowfall dataset by month for
-Grand Rapids, MI, starting in 1893. We will be using the \texttt{Dec}
-variable which is the number of inches of snow that fell in December of
-each year. In particular, we are interested in the sample mean and later
-finding confidence intervals for population mean of \texttt{Dec}. The
-distribution is below (Figure 1).
+\texttt{SnowGR}, which gives the official snowfall dataset by the month
+for Grand Rapids, MI, starting in 1893. We will be using the
+\texttt{Dec} variable, which is the number of inches of snow that fell
+in December of each year. In particular, we are interested in the sample
+mean and later finding confidence intervals for the population mean of
+\texttt{Dec}. The distribution is shown (Figure 1).
 
@@
 
-Below, in Figure 2, is the histogram of bootstrapped values. Since we
-performed a large number of bootstrap replications, the bootstrapped
-distribution appears to be approximately Normal.
+Figure 2 shows the histogram of bootstrapped values. Since we performed
+a large number of bootstrap replications, the bootstrapped distribution
+appears to be approximately Normal.
 
@@
 percentile of the normal deviation \citep{Efron86}. We say that the
-confidence interval constructed in this manner has a chance of capturing
-the true parameter with a probability of \(\alpha\).
+confidence interval constructed in this manner can capture the true
+parameter with a probability of \(\alpha\).
 
 The standard confidence interval is built based on the assumption that
-the distribution from which we are sampling is Normal. As such, the
-standard confidence interval is sometimes called the normal confidence
-interval for a bootstrapped sample. This means that for an unknown
-skewed distribution, the standard confidence interval could present an
-incorrect range. However, the same process can be used with bootstrap
-sampling to form the bootstrap percentile method. This means that an
-approximate bootstrap confidence interval will be created in the same
-automatic way that the standard confidence interval was created. For
-bootstrapped confidence intervals, the number of bootstrap replications
-\(B\) must be large (around 2,000) due to the nature of confidence
-intervals requiring greater accuracy \citep{Efron86}.
+the distribution we are sampling is Normal. The standard confidence
+interval is sometimes called the normal confidence interval for a
+bootstrapped sample. This means that the standard confidence interval
+could present an incorrect range for an unknown skewed distribution.
+However, the same process can be used with bootstrap sampling to form
+the bootstrap percentile method. This way, an approximate bootstrap
+confidence interval will be created in the same automatic way that the
+standard confidence interval was created. For bootstrapped confidence
+intervals, the number of bootstrap replications \(B\) must be large
+(around 2,000) due to the nature of confidence intervals requiring
+greater accuracy \citep{Efron86}.
 
@@
 
-This means that we can say we are 95\% confident that the true mean
-number of inches of snow that fall in December is betwwen 13.86 inches
-and 17.66 inches. Our original histogram with the confidence interval is
-below (Figure 3).
+Therefore, we are 95\% confident that the true mean number of inches of
+snow that fall in December is between 13.86 inches and 17.66 inches. Our
+original histogram with the confidence interval is shown (Figure 3).
 
@@
 corresponding percentile interval would be equivalent to the standard
-interval. However, this is not usually the case. When the bootstrap
+interval. However, this is only sometimes the case. When the bootstrap
 distribution is non-normal, we can suppose that there exists, for all
@@
 Therefore, the percentile method produces a correct interval for
-\(\phi\) and due to the transformation invariance, also produces a
+\(\phi\) and, due to the transformation invariance, also produces a
 correct percentile interval for \(\theta\). This method assumes the
@@
 inches and 17.72 inches. Our original histogram with the percentile
-confidence interval is shown below (Figure 4).
+confidence interval is shown (Figure 4).
 
@@
 
-The next method we will be looking at is the bias-corrected percentile
-method (BC method) which is an improvement upon the previous percentile
-method because we now take into account the possibility of bias. It can
-be shown that \(\hat{\theta}\) is biased upwards relative to \(\theta\)
-which means that the confidence intervals should be adjusted downwards
-\citep[\citet{EfronCasi}]{Efron86}. From our simulated bootstrap
-replications
+The following method we will be looking at is the bias-corrected
+percentile method (BC method) which is an improvement upon the previous
+percentile method because we now consider the possibility of bias. It
+can be shown that \(\hat{\theta}\) is biased upwards relative to
+\(\theta\), which means that the confidence intervals should be adjusted
+downwards \citep[\citet{EfronCasi}]{Efron86}. From our simulated
+bootstrap replications
 \(\hat{\theta}^{*1}, \hat{\theta}^{*2}, \dots ,\hat{\theta}^{*B},\)
@@
 Using this method to create a 95\% confidence interval has a couple more
-steps because we need to find the bias-correction value. First we
-calculate the sample mean:
+steps because we need to find the bias-correction value
+\citep{EfronCasi}. First, we calculate the sample mean:
 
@@
 \begin{Highlighting}[]
-\NormalTok{alphalow }\OtherTok{\textless{}{-}} \FloatTok{0.025}\NormalTok{; alphahigh }\OtherTok{\textless{}{-}} \FloatTok{0.975}
-
-\NormalTok{newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)); }\CommentTok{\#newlow}
-\NormalTok{newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)); }\CommentTok{\#newhigh}
-
-\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(newlow, newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
+\NormalTok{alpha\_lower }\OtherTok{\textless{}{-}} \FloatTok{0.025}\NormalTok{; alpha\_upper }\OtherTok{\textless{}{-}} \FloatTok{0.975}
+
+\NormalTok{new\_lower }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_lower)); }
+\NormalTok{new\_upper }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_upper)); }
+
+\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(new\_lower, new\_upper), }\AttributeTok{data =}\NormalTok{ dec\_means)}
 \end{Highlighting}
@@
 fall in December in Grand Rapids, Michigan is between 14.01 inches and
-17.82 inches. Our histogram (Figure 5) is shown below.
+17.82 inches. Our histogram (Figure 5) is shown.
 
@@
 
-A further modification upon the BC interval is the bias-corrected and
-accelerated method (BCa). For this method, we do not assume the the
-standard error, \(\tau\), is constant as we did in the BC interval
+The bias-corrected and accelerated method (BCa) further modifies the BC
+interval. This method does not assume that the standard error, \(\tau\),
+is constant as we did in the BC interval
 \citep[\citet{EfronCasi}]{Efron86}. Rather, we assume the existence of a
@@
 distribution. For example, \(a=z_0\) for one-parameter exponential
-families, however, there are many different algorithms to compute and
+families. However, there are many different algorithms to compute and
 estimate \(a\) \citep{Flowers18}. Now, our \(\alpha\)-level endpoint for
@@
 not a function of the bootstrap distribution and must be calculated
-separately. However the process is algorithmic and can be calculated
+separately. However, the process is algorithmic and can be calculated
 without too much work. As we saw, each of the three previous methods
 (percentile, BC, and BCa) all build upon each other and have less
-restrictive assumptions, but this means that computation increases as we
-loosen assumptions.
+restrictive assumptions, but computation increases as we loosen
+assumptions.
 
@@
 In practice, we can use the jackknife procedure to estimate the
-acceleration value for this method. The jackknife procedure is a
-different resampling technique that is often used to estimate the bias
-and variance of a large population. Thus, we will run the jackknife
+acceleration value for this method \citep{EfronCasi}. The jackknife
+procedure is a different resampling technique often used to estimate the
+bias and variance of a large population. Thus, we will run the jackknife
 procedure:
@@
 \begin{Highlighting}[]
-\NormalTok{jackmean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values); jackmean}
+\NormalTok{jack\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values); jack\_mean}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
-\NormalTok{  (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{); estimated\_a}
+\NormalTok{estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jack\_mean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
+\NormalTok{  (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jack\_mean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{); estimated\_a}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
-\NormalTok{                    (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow)))); }
-\NormalTok{a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
-\NormalTok{                     (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh)))); }
-\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ dec\_means)}
+\NormalTok{a\_new\_lower }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_lower))}\SpecialCharTok{/}
+\NormalTok{                    (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_lower)))); }
+\NormalTok{a\_new\_upper }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_upper))}\SpecialCharTok{/}
+\NormalTok{                     (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alpha\_upper)))); }
+\FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_new\_lower, a\_new\_upper), }\AttributeTok{data =}\NormalTok{ dec\_means)}
 \end{Highlighting}
@@
 \(\hat{\theta^*} = \hat{\theta}(X^*)\), and the standard error,
-\(\hat{\sigma^*} = \hat{\sigma}(X^*)\). From these we can calculate a
+\(\hat{\sigma^*} = \hat{\sigma}(X^*)\). From these, we can calculate a
 t-statistic for each bootstrap sample:
@@
 of the \(t\)-distribution such that:
-\[\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap relications of }T^*.\]
+\[\hat{T}_{(\alpha)} = B*\alpha\text{th ordered value of all the bootstrap replications of }T^*.\]
 This means that for \(B = 2,000\) and \(\alpha = 0.90\), then
@@
 \[\hat{\sigma} = \frac{1-\hat{\theta}^2}{\sqrt{n}}.\] One of the main
-factors why the studentized method is so popular is because we assume
-that our bootstrapped statistic is pivotal which means that the
-confidence interval does not depend on any other parameters. Instead, we
-can calculate the appropriate confidence interval for the parameter of
+factors why the studentized method is so popular is that we assume that
+our bootstrapped statistic is pivotal, which means that the confidence
+interval does not depend on any other parameters. Instead, we can
+calculate the appropriate confidence interval for the parameter of
 interest specifically from the bootstrapped statistics
@@
 \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-
+\CommentTok{\# sample statistics}
 \NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
 \NormalTok{orig\_se }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR)}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(SnowGR))}
-
+\CommentTok{\# initialize storage vectors}
 \NormalTok{se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
 \NormalTok{t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-
+\CommentTok{\# use bootstrap replication statistics to find se and t{-}stat}
 \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
@@
 \NormalTok{\}}
-
+\CommentTok{\#find interval}
 \NormalTok{dec\_t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(t\_stat)}
-
 \NormalTok{q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(dec\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
@@
 \NormalTok{upper }\OtherTok{\textless{}{-}}\NormalTok{ q[}\DecValTok{2}\NormalTok{]}
-
 \FunctionTok{c}\NormalTok{(orig\_mean }\SpecialCharTok{{-}}\NormalTok{ upper}\SpecialCharTok{*}\NormalTok{orig\_se, orig\_mean }\SpecialCharTok{{-}}\NormalTok{ lower}\SpecialCharTok{*}\NormalTok{orig\_se)}
@@
 and 18.02 inches. This would give us the following confidence interval
-(Figure 7)
+(Figure 7):
 
@@
 \section{Simulation}\label{simulation}}
+
+\hypertarget{code}{%
+\subsection{Code}\label{code}}
 
@@
 if the true population mean is contained in the confidence interval for
-each of the methods we are testing. We will perform this process a large
-number of times (10,000 simulations) and then average by the number of
-iterations to determines on average, the proportion that each
-bootstrapped confidence interval method contains the true population
-mean for a given distribution. We will do this for a couple different
-distributions as well as a range of sample sizes to show how the
-intervals perform with skewed distributions and larger sample sizes.
-
-To do this simulation, we will be using the \texttt{boot} package
+each of the methods we are testing \citep{Guillaume21}. We will perform
+this process a large number of times (10,000 simulations) and then
+average by the number of iterations to determine, on average, the
+proportion that each bootstrapped confidence interval method contains
+the true population mean for a given distribution. We will do this for a
+couple of different distributions and ranges of sample sizes to show how
+the intervals perform with skewed distributions and larger sample sizes.
+
+To do this simulation, we will use the \texttt{boot} package
 \citep{boot}. This package can compute a bootstrap object which contains
@@
 produces confidence intervals from the bootstrap object. In particular,
-we will use the \texttt{boot.ci} function to create four types of
-confidence intervals: the standard (or normal) confidence interval, the
-studentized confidence interval, the percentile confidence interval, and
-the bias-corrected with acceleration confidence interval.
-
-To start, we will declare some constants including the sample sizes and
-the number of bootstrap replications we are using.
+we will use the \texttt{boot.ci} function to create four confidence
+intervals: the standard (or normal) confidence interval, the studentized
+confidence interval, the percentile confidence interval, and the
+bias-corrected with acceleration confidence interval.
+
+To start, we will declare some constants, including the sample sizes and
+the number of bootstrap replications we use. We will be using a range of
+sample sizes from 5 to 150. For this simulation, we will use a
+confidence level of 95\%.
 
@@
 contained within our intervals. Since we are using a \(Normal(0,1)\)
-distribution, our true population mean is equal to 0. We will repeat
-this process 10,000 times as specified for each of the sample sizes that
-we are testing. Since we are originally sampling from a Normal
-distribution, the assumptions we hold for the standard interval are true
-and thus, we would expect all of the methods to perform comparably to
-each other at large sample sizes.
+distribution, our true population mean equals 0. We will repeat this
+process 10,000 times as specified for each sample size we are testing.
+Since we are initially sampling from a Normal distribution, the
+assumptions we hold for the standard interval are true. Thus, we would
+expect all of the methods to perform comparably to each other at large
+sample sizes.
 
@@
 \NormalTok{run\_sim\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-
+  \CommentTok{\# create function to return mean and sd of bootstrap replication}
 \NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
@@
 \NormalTok{  \}}
-
+  \CommentTok{\# initialize matrix to hold different bootstrap prop. for each sample size}
 \NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
-
+  \CommentTok{\# iterate through each sample size}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
-
+    \CommentTok{\# initialize vectors that hold if the CI contains true mean by iteration}
 \NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
@@
 \NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-
+    \CommentTok{\# }
 \NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
 \NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{0}
-
+    \CommentTok{\# perform 10,000 iterations of bootstraps}
     \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
@@
 \NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
+      \CommentTok{\# perform bootstrap and CIs}
 \NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ boot.stat, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
-\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
-
-\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
-\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }
+                    \AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
+      \CommentTok{\# update vectors depending on if the CI contains true mean}
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
 \NormalTok{    \}}
-
+    \CommentTok{\# add the sample size and average proportion to matrix}
 \NormalTok{    master[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
@@
 \NormalTok{  \}}
-
+  \CommentTok{\# some wrangling}
 \NormalTok{  master\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(master) }\SpecialCharTok{\%\textgreater{}\%} 
@@
 Secondly, we select from a Gamma Distribution with a shape parameter of
-1 and a scale parameter of 4 (\(Gamma(1,4)\)). Therefore, the true
-population mean is 4 because the true mean is given by the product of
-the shape and scale parameter. This simulation follows the same process
-as above where we sampled from the Normal distribution except we are
-sampling from a Gamma distribution this time. Since, our Gamma
-distribution is heavily left-skewed, we would expect the studentized
+one and a scale parameter of four (\(Gamma(1,4)\)). Therefore, the true
+population mean is 4 because the product of the shape and scale
+parameters gives the true mean. This simulation follows the same process
+as above, where we sampled from the Normal distribution, except we are
+sampling from a Gamma distribution this time. Since our Gamma
+distribution is heavily left-skewed, we expect the studentized
 confidence interval and the BCa confidence interval to perform the best.
@@
 \NormalTok{run\_sim\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-
 \NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
@@
 \NormalTok{  \}}
-
 \NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
-
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
-
 \NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
@@
 \NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-
 \NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
 \NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \DecValTok{4}
-
     \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
@@
 \NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
-
 \NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ boot.stat, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
-\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }\AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
-
-\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
-\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
-\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{conf =} \FloatTok{0.95}\NormalTok{, }
+                    \AttributeTok{type =} \FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"perc"}\NormalTok{, }\StringTok{"bca"}\NormalTok{, }\StringTok{"stud"}\NormalTok{))}
+\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
+\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
+\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}
+\NormalTok{        true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}
 \NormalTok{    \}}
@@
 variable, \(Y = ln(X) \sim Normal\). Therefore, the distribution is
-left-skewed, although not as heavily as the Gamma distribution we
-previously used. The true mean of this distribution can be found using
+left-skewed, although not as heavily as the previously used Gamma
+distribution. The true mean of this distribution can be found using
 \(E(X) = e^{u+\frac{\sigma^2}{2}}\) which means that for a
 \(Lognormal(0,1)\) distribution, we expect the population mean to be
-\(e^{\frac{1}{2}}\). Again, we would expect the studentized confidence
+\(e^{\frac{1}{2}}\). Again, we expect the studentized confidence
 interval and the BCa confidence interval to perform the best.
@@
 \NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
-
 \NormalTok{  boot.stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
@@
 \NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
-
 \NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
 \NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}
-
     \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
@@
 \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
-\NormalTok{normal\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(normal\_df\_trial2,}\StringTok{"normal\_data\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{log\_normal\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(log\_normal\_df\_trial2,}\StringTok{"log\_normal\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-
-\NormalTok{gamma\_df\_trial2 }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
-\FunctionTok{write.csv}\NormalTok{(gamma\_df\_trial2,}\StringTok{"gamma\_data\_df\_trial2.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
-\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
-\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}log\_normal\_df\_trial2.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(normal\_df,}\StringTok{"data/normal\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_log\_normal}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(log\_normal\_df,}\StringTok{"data/log\_normal\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{run\_sim\_gamma}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
+\FunctionTok{write.csv}\NormalTok{(gamma\_df,}\StringTok{"data/gamma\_data\_df.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+After, we can create the graphs and output for each of the distributions
+and sample sizes.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}data/normal\_data\_df.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}data/gamma\_data\_df.csv\textquotesingle{}}\NormalTok{)}
+\NormalTok{log\_normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}data/log\_normal\_df.csv\textquotesingle{}}\NormalTok{)}
 
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Normal }
-\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+  \FunctionTok{labs}\NormalTok{(}
+    \AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Normal Distibution"}\NormalTok{, }
+    \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
     \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
@@
 \NormalTok{normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ normal\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
-        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)))}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }
+        \AttributeTok{caption =} \StringTok{"From a Normal distribution"}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(normal\_df)), }\AttributeTok{digits =} \DecValTok{3}\NormalTok{)}
 
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Gamma }
-\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Gamma Distibution"}\NormalTok{, }
+       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
+       \AttributeTok{caption =} \StringTok{"Fig. 9: Graph showing the Accuracy of Bootstrap CI Methods for }
 \StringTok{       different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
@@
 \NormalTok{gamma\_table }\OtherTok{\textless{}{-}}\NormalTok{ gamma\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled From Gamma Dist."}\NormalTok{, }
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }
+        \AttributeTok{caption =} \StringTok{"From a Gamma distribution"}\NormalTok{, }
         \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(gamma\_df)), }\AttributeTok{digits =} \DecValTok{3}\NormalTok{) }
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Proportion of CIs that Contain the True Parameter from Log{-}Normal }
-\StringTok{       Distibution"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =}\StringTok{"Prop. of CIs that Contain True Mean from Log{-}Normal Distibution"}\NormalTok{,}
+       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
-\StringTok{       different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+       \AttributeTok{caption =} \StringTok{"Fig. 10: Graph showing the Accuracy of Bootstrap CI Methods }
+\StringTok{       for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
@@
 \NormalTok{log\_normal\_table }\OtherTok{\textless{}{-}}\NormalTok{ log\_normal\_df }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Sampled from Normal Dist."}\NormalTok{, }
-        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(log\_normal\_df)))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{log\_normal\_fig}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/output the graphs/tables-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{log\_normal\_table}
+  \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{align =} \StringTok{"c"}\NormalTok{, }
+        \AttributeTok{caption =} \StringTok{"From a Log{-}Normal distribution"}\NormalTok{, }
+        \AttributeTok{col.names =} \FunctionTok{gsub}\NormalTok{(}\StringTok{"[\_]"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\FunctionTok{names}\NormalTok{(log\_normal\_df)), }\AttributeTok{digits =} \DecValTok{3}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+\hypertarget{normal-distribution-simulation}{%
+\subsubsection{Normal Distribution
+Simulation}\label{normal-distribution-simulation}}
+
+First, we have the results of the simulation where we randomly sampled
+from a Normal distribution.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-18-1.pdf}
+
+At small sample sizes, the studentized confidence interval performed
+much better than the other intervals, which all performed similarly. For
+a sample size of 5, the studentized interval had an accuracy of around
+91.3\%. In comparison, the other three intervals had an accuracy of
+around 83\% to 84\% of creating an interval that contained the true
+population mean. The standard, percentile, and BCa confidence interval
+methods all have similar processes, especially when the distribution we
+are sampling from is Normal because the assumptions we made for the
+standard interval are correct. As the sample size increases, the
+performance of the intervals increases and rises to stay consistent at
+around 94\% to 95\% accuracy. The data (Table 1) is shown for reference.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{normal\_table}
 \end{Highlighting}
@@
 
-\caption{\label{tab:create graphs}Sampled from Normal Dist.}
+\caption{\label{tab:create graphs}From a Normal distribution}
 \centering
-\begin{tabular}[t]{cccccc}
+\begin{tabular}[t]{ccccc}
 \toprule
-Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
+Sample Size & Normal & Studentized & Percentile & BCa\\
 \midrule
-4 & 0.6795 & 0.6542 & 0.8186 & 0.6810 & 0.6814\\
-10 & 0.7911 & 0.7684 & 0.8526 & 0.8019 & 0.8266\\
-15 & 0.8268 & 0.8061 & 0.8705 & 0.8387 & 0.8552\\
-20 & 0.8437 & 0.8236 & 0.8797 & 0.8526 & 0.8725\\
-30 & 0.8639 & 0.8464 & 0.8951 & 0.8734 & 0.8900\\
+5 & 0.841 & 0.913 & 0.834 & 0.832\\
+10 & 0.905 & 0.930 & 0.905 & 0.901\\
+15 & 0.918 & 0.932 & 0.919 & 0.918\\
+20 & 0.930 & 0.940 & 0.930 & 0.931\\
+30 & 0.938 & 0.945 & 0.938 & 0.936\\
 \addlinespace
-40 & 0.8789 & 0.8623 & 0.9055 & 0.8881 & 0.9013\\
-60 & 0.8897 & 0.8783 & 0.9100 & 0.8978 & 0.9069\\
-80 & 0.9088 & 0.8969 & 0.9218 & 0.9136 & 0.9181\\
-100 & 0.9103 & 0.8980 & 0.9264 & 0.9162 & 0.9229\\
+40 & 0.939 & 0.944 & 0.939 & 0.938\\
+60 & 0.940 & 0.944 & 0.940 & 0.940\\
+100 & 0.949 & 0.950 & 0.949 & 0.950\\
+150 & 0.942 & 0.943 & 0.942 & 0.941\\
 \bottomrule
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_fig}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/output the graphs/tables-2.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{normal\_table}
+\hypertarget{gamma-distribution-simulation}{%
+\subsubsection{Gamma Distribution
+Simulation}\label{gamma-distribution-simulation}}
+
+Second, we have the results from the simulation where we sampled from a
+Gamma distribution.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-20-1.pdf}
+
+The \(Gamma(1,4)\) distribution we randomly sampled from is
+heavily-skewed, so we did not expect all of the bootstrap confidence
+interval methods to work comparably. As shown in Figure 9, the
+studentized method performed the best at around 90\% accuracy for
+creating a confidence interval that contained the true mean. The BCa
+method performed the second best at around 87\% accuracy. The percentile
+method performed the following best with around 85\% accuracy, while the
+standard method performed the worst with an accuracy of around 84.5\%.
+As the sample size increased, the accuracy of each of the methods became
+less variable and evened out to a constant accuracy. The table
+containing the proportions (Table 2) is shown for reference.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{gamma\_table}
 \end{Highlighting}
@@
 
-\caption{\label{tab:create graphs}Sampled from Normal Dist.}
+\caption{\label{tab:create graphs}From a Gamma distribution}
 \centering
-\begin{tabular}[t]{cccccc}
+\begin{tabular}[t]{ccccc}
 \toprule
-Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
+Sample Size & Normal & Studentized & Percentile & BCa\\
 \midrule
-4 & 0.8046 & 0.7913 & 0.9058 & 0.7941 & 0.7943\\
-10 & 0.9015 & 0.9005 & 0.9265 & 0.9007 & 0.8994\\
-15 & 0.9187 & 0.9183 & 0.9331 & 0.9184 & 0.9167\\
-20 & 0.9257 & 0.9249 & 0.9357 & 0.9242 & 0.9235\\
-30 & 0.9363 & 0.9372 & 0.9421 & 0.9351 & 0.9323\\
+5 & 0.848 & 0.902 & 0.854 & 0.873\\
+10 & 0.846 & 0.901 & 0.853 & 0.867\\
+15 & 0.856 & 0.906 & 0.862 & 0.879\\
+20 & 0.839 & 0.894 & 0.845 & 0.862\\
+30 & 0.847 & 0.898 & 0.853 & 0.869\\
 \addlinespace
-40 & 0.9421 & 0.9421 & 0.9466 & 0.9416 & 0.9416\\
-60 & 0.9381 & 0.9390 & 0.9420 & 0.9389 & 0.9386\\
-80 & 0.9403 & 0.9408 & 0.9430 & 0.9406 & 0.9396\\
-100 & 0.9483 & 0.9478 & 0.9499 & 0.9475 & 0.9480\\
+40 & 0.853 & 0.901 & 0.859 & 0.871\\
+60 & 0.846 & 0.901 & 0.852 & 0.868\\
+100 & 0.845 & 0.898 & 0.849 & 0.868\\
+150 & 0.844 & 0.896 & 0.850 & 0.866\\
 \bottomrule
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{gamma\_fig}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-latex/output the graphs/tables-3.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{gamma\_table}
+\hypertarget{log-normal-distribution-simulation}{%
+\subsubsection{Log-Normal Distribution
+Simulation}\label{log-normal-distribution-simulation}}
+
+Lastly, we have the results from the simulation where we sampled from a
+Log-Normal distribution.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{log\_normal\_fig}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-22-1.pdf}
+
+As shown in Figure 10, the studentized method had the greatest accuracy
+in creating the confidence intervals that captured the true mean. At
+small sample sizes such as 5, the studentized method has an accuracy of
+82.3\%, while the following best is the BCa method with a 73.4\%
+accuracy. As the sample size increases, all methods' accuracy increases
+quickly and performs comparably, although the studentized and BCa
+methods perform slightly better. All the intervals stay constant at
+around 92.5\% to 93.5\% accuracy for large sample sizes. Again, the
+proportions are shown (Table 3) for each sample size for reference.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{log\_normal\_table}
 \end{Highlighting}
@@
 
-\caption{\label{tab:create graphs}Sampled From Gamma Dist.}
+\caption{\label{tab:create graphs}From a Log-Normal distribution}
 \centering
-\begin{tabular}[t]{cccccc}
+\begin{tabular}[t]{ccccc}
 \toprule
-Sample Size & Normal & Basic & Studentized & Percentile & BCa\\
+Sample Size & Normal & Studentized & Percentile & BCa\\
 \midrule
-4 & 0.849 & 0.833 & 0.904 & 0.858 & 0.875\\
-10 & 0.848 & 0.829 & 0.901 & 0.854 & 0.871\\
-15 & 0.851 & 0.832 & 0.901 & 0.856 & 0.871\\
-20 & 0.846 & 0.827 & 0.903 & 0.851 & 0.867\\
-30 & 0.838 & 0.822 & 0.895 & 0.846 & 0.864\\
+5 & 0.715 & 0.823 & 0.720 & 0.734\\
+10 & 0.795 & 0.855 & 0.806 & 0.828\\
+15 & 0.829 & 0.876 & 0.839 & 0.862\\
+20 & 0.847 & 0.885 & 0.856 & 0.874\\
+30 & 0.869 & 0.901 & 0.879 & 0.893\\
 \addlinespace
-40 & 0.848 & 0.831 & 0.899 & 0.853 & 0.866\\
-60 & 0.847 & 0.829 & 0.907 & 0.857 & 0.874\\
-80 & 0.849 & 0.831 & 0.902 & 0.854 & 0.872\\
-100 & 0.848 & 0.831 & 0.897 & 0.853 & 0.866\\
+40 & 0.884 & 0.907 & 0.890 & 0.903\\
+60 & 0.901 & 0.921 & 0.911 & 0.920\\
+100 & 0.912 & 0.926 & 0.917 & 0.919\\
+150 & 0.925 & 0.935 & 0.928 & 0.927\\
 \bottomrule
@@
 \end{table}
+\newpage
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+In this paper, we demonstrated the power of using bootstrapped
+confidence intervals to estimate a true population parameter without
+using any information about the underlying distribution of the sample.
+In the exposition, we introduced the standard method, which relies on
+three conditions: 1) that the distribution is Normal, 2) that there is
+no bias, and 3) that there is a constant standard error. If we take away
+the first condition and use the bootstrap percentiles to create the
+interval, we are left with the percentile method. If we add a
+bias-correcting value not equal to zero, then we have the
+bias-correcting method. Furthermore, if we allow for a non-constant
+standard error (through the acceleration), we have the bias-corrected
+with acceleration method. Using the studentized method, we can also use
+bootstrap resampling to estimate a \(t\)-distribution from which we can
+create a confidence interval. From our simulation, the methods all
+performed reasonably the same for the Normal distribution at large
+sample sizes. However, when we introduced skew into the distributions,
+the studentized and BCa methods performed better than the others at
+large sample sizes. It is important to note that even at large sample
+sizes, none of our methods reached a coverage of 95\%, which was our
+specified confidence level. The closest we were was when we sampled from
+a Normal distribution. This may be because our sample sizes need to be
+bigger; however, we can reach a close approximation using the largest
+sample size we tested. Thanks to the high computational power available,
+we can use bootstrapping to create confidence intervals for a population
+parameter without knowing much about the actual sample.
 

### 2022-12-09 project/PaperTemplate/paper.Rmd
Minor edits

@@
   This paper explores different bootstrap methods for creating confidence intervals and tests their performance against each other for different types of distributions.
-This paper will re-introduce the ideas of bootstraps and confidence intervals, as well as the theory behind different methods of bootstrapped confidence intervals.
-Along with the theoretical details of each method, we will provide an example of each bootstrapped confidence interval method with a toy dataset.
-Then, we will run a simulation that evaluates the performance of a couple of the methods we introduced on a variety of sample sizes and types of distributions.
+This paper will re-introduce the idea of bootstraps and confidence intervals, as well as the theory behind different methods of bootstrapped confidence intervals.
+Along with the theoretical details of each method, we will provide an example of each bootstrapped confidence interval method using a toy dataset.
+Then, we will run a simulation that evaluates the performance of a couple of the methods on a variety of sample sizes and types of distributions.
 
@@
 
-We demonstrate performing a non-parametric bootstrap below using `SnowGR`, which gives the official snowfall dataset by the month for Grand Rapids, MI, starting in 1893. 
+We demonstrate performing a non-parametric bootstrap below using `SnowGR`, which gives the official snowfall dataset by the month for Grand Rapids, MI, starting in 1893 and is found in the `mosaic` package [@mosaic].
 We will be using the `Dec` variable, which is the number of inches of snow that fell in December of each year. 
@@
 The distribution is shown (Figure 1).
-```{r SnowGR histogram}
+```{r SnowGR histogram, fig.height = 4, fig.width = 5}
 data(SnowGR)
@@
 ```
+
 Next, we will perform the non-parametric bootstrap using 10,000 replications.
@@
 orig_mean <- mean(~ Dec, data = SnowGR) # theta hat
-
-set.seed(495)
 nboot <- 10000
-
+# initialize storage vectors
 mean <- rep(0,nboot)
 sd <- rep(0,nboot)
-se <- rep(0,nboot)
-t_stat <- rep(0,nboot)
 
@@
 }
-
 dec_means <- as.data.frame(mean)
@@
 Figure 2 shows the histogram of bootstrapped values. Since we performed a large number of bootstrap replications, the bootstrapped distribution appears to be approximately Normal.
-```{r, cache = TRUE}
+```{r, fig.height = 3, fig.width = 4}
 gf_dhistogram(~ mean, data = dec_means) %>%
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 gf_histogram(~ Dec, data = SnowGR) +
   labs(x = "Annual Snowfall in December", 
-       title = "Distribution of Annual Snowfall in December", y = "Count",
+       title = "Distribution of Annual Snowfall in December 
+       with Standard Interval", y = "Count",
        caption = "Fig. 3: Histogram with Standard Interval Shown") +
@@
 Our original histogram with the percentile confidence interval is shown (Figure 4).
-```{r}
+```{r,fig.height = 4, fig.width = 5}
 gf_histogram(~ Dec, data = SnowGR) +
   labs(x = "Annual Snowfall in December", 
-       title = "Distribution of Annual Snowfall in December", y = "Count",
+       title = "Distribution of Annual Snowfall in December
+       with Percentile Interval", y = "Count",
        caption = "Fig. 4: Histogram with Percentile Interval Shown") +
@@
 ```
+
 This interval is similar to the one created using the standard method, but shifted slightly to the right.
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 gf_histogram(~ Dec, data = SnowGR) +
   labs(x = "Annual Snowfall in December", 
-       title = "Distribution of Annual Snowfall in December", y = "Count",
+       title = "Distribution of Annual Snowfall in December
+       with BC interval", y = "Count",
        caption = "Fig. 5: Histogram with BC Interval Shown") +
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 gf_histogram(~ Dec, data = SnowGR) +
   labs(x = "Annual Snowfall in December", 
-       title = "Distribution of Annual Snowfall in December", y = "Count",
+       title = "Distribution of Annual Snowfall in December
+       with BCa interval", y = "Count",
        caption = "Fig. 6: Histogram with BCa Interval Shown") +
@@
   geom_vline(aes(xintercept= 17.72353))
-
 ```
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 gf_histogram(~ Dec, data = SnowGR) +
   labs(x = "Annual Snowfall in December", 
-       title = "Distribution of Annual Snowfall in December", y = "Count", 
+       title = "Distribution of Annual Snowfall in December
+       with Studentized Interval", y = "Count", 
        caption = "Fig. 7: Histogram with Studentized Interval Shown") +
@@
 We will do this for a couple of different distributions and ranges of sample sizes to show how the intervals perform with skewed distributions and larger sample sizes.
+We will define the accuracy of each method as the proportion that each bootstrapped confidence interval method contains the true population mean for a distribution
 
-To do this simulation, we will use the `boot` package [@boot]. 
+To perform this simulation, we will use the `boot` package [@boot]. 
 This package can compute a bootstrap object which contains the output from a bootstrap calculation of a given sample and then produces confidence intervals from the bootstrap object. 
@@
   }
-  # initialize matrix to hold different bootstrap prop. for each sample size
+  # initialize matrix to hold different bootstrap prop. 
+  # for each sample size
   master <- matrix(nrow = num_sample_sizes, ncol = 5)
@@
   for(i in 1:num_sample_sizes) {
-    # initialize vectors that hold if the CI contains true mean by iteration
+    # initialize vectors that hold if the CI contains true mean 
+    # by iteration
     norm_contains <- rep(0, sim_reps)
@@
   labs(
-    title = "Prop. of CIs that Contain the True Mean from Normal Distibution", 
+    title = "Accuracy of Bootstrap CIs using Normal Distibution", 
     x = "Sample Size", 
     y = "Proportion (of 10,000 Simulations)", color = "Method",
-    caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for
-       different sample sizes on Normal Dist.") +
+    caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI 
+    Methods for different sample sizes on Normal Distribution") +
   theme_light() +
@@
   geom_point() + geom_line() + 
-  labs(title = "Prop. of CIs that Contain the True Mean from Gamma Distibution", 
+  labs(title = "Accuracy of Bootstrap CIs using Gamma Distibution", 
        x = "Sample Size", 
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 9: Graph showing the Accuracy of Bootstrap CI Methods for 
-       different sample sizes on Gamma Dist.") +
+       caption = "Fig. 9: Graph showing the Accuracy of Bootstrap CI 
+       Methods for different sample sizes on Gamma Distribution") +
   theme_light() +
@@
   geom_point() + geom_line() + 
-  labs(title ="Prop. of CIs that Contain True Mean from Log-Normal Distibution",
+  labs(title ="Accuracy of Bootstrap CIs using Log-Normal 
+       Distibution",
        x = "Sample Size", 
        y = "Proportion (of 10,000 Simulations)", color = "Method",
-       caption = "Fig. 10: Graph showing the Accuracy of Bootstrap CI Methods 
-       for different sample sizes on Log-Normal Dist.") +
+       caption = "Fig. 10: Graph showing the Accuracy of Bootstrap CI 
+       Methods for different sample sizes on Log-Normal Distribution") +
   theme_light() +
@@
 
-```{r}
+```{r,fig.height = 4, fig.width = 5}
 normal_fig
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 gamma_fig
@@
 
-```{r}
+```{r, fig.height = 4, fig.width = 5}
 log_normal_fig

### 2022-12-09 project/PaperTemplate/paper.tex
Minor edits

@@
 intervals and tests their performance against each other for different
-types of distributions. This paper will re-introduce the ideas of
+types of distributions. This paper will re-introduce the idea of
 bootstraps and confidence intervals, as well as the theory behind
@@
 theoretical details of each method, we will provide an example of each
-bootstrapped confidence interval method with a toy dataset. Then, we
+bootstrapped confidence interval method using a toy dataset. Then, we
 will run a simulation that evaluates the performance of a couple of the
-methods we introduced on a variety of sample sizes and types of
-distributions.
+methods on a variety of sample sizes and types of distributions.
 \end{abstract}
@@
 \texttt{SnowGR}, which gives the official snowfall dataset by the month
-for Grand Rapids, MI, starting in 1893. We will be using the
+for Grand Rapids, MI, starting in 1893 and is found in the
+\texttt{mosaic} package \citep{mosaic}. We will be using the
 \texttt{Dec} variable, which is the number of inches of snow that fell
@@
 
-\includegraphics{paper_files/figure-latex/SnowGR histogram-1.pdf} Next,
-we will perform the non-parametric bootstrap using 10,000 replications.
+\includegraphics{paper_files/figure-latex/SnowGR histogram-1.pdf}
+
+Next, we will perform the non-parametric bootstrap using 10,000
+replications.
 
@@
 \NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
-
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
 \NormalTok{nboot }\OtherTok{\textless{}{-}} \DecValTok{10000}
-
+\CommentTok{\# initialize storage vectors}
 \NormalTok{mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
 \NormalTok{sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-\NormalTok{se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
-\NormalTok{t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
 
@@
 \NormalTok{\}}
-
 \NormalTok{dec\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
@@
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December }
+\StringTok{       with Standard Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
        \AttributeTok{caption =} \StringTok{"Fig. 3: Histogram with Standard Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
@@
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
+\StringTok{       with Percentile Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
        \AttributeTok{caption =} \StringTok{"Fig. 4: Histogram with Percentile Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf} This
-interval is similar to the one created using the standard method, but
-shifted slightly to the right.
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
+
+This interval is similar to the one created using the standard method,
+but shifted slightly to the right.
 
@@
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
+\StringTok{       with BC interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
        \AttributeTok{caption =} \StringTok{"Fig. 5: Histogram with BC Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
@@
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
+\StringTok{       with BCa interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
        \AttributeTok{caption =} \StringTok{"Fig. 6: Histogram with BCa Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
@@
   \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
-       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
+       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
+\StringTok{       with Studentized Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
        \AttributeTok{caption =} \StringTok{"Fig. 7: Histogram with Studentized Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
@@
 the intervals perform with skewed distributions and larger sample sizes.
-
-To do this simulation, we will use the \texttt{boot} package
+We will define the accuracy of each method as the proportion that each
+bootstrapped confidence interval method contains the true population
+mean for a distribution
+
+To perform this simulation, we will use the \texttt{boot} package
 \citep{boot}. This package can compute a bootstrap object which contains
@@
 \NormalTok{  \}}
-  \CommentTok{\# initialize matrix to hold different bootstrap prop. for each sample size}
+  \CommentTok{\# initialize matrix to hold different bootstrap prop. }
+  \CommentTok{\# for each sample size}
 \NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{5}\NormalTok{)}
@@
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}
-    \CommentTok{\# initialize vectors that hold if the CI contains true mean by iteration}
+    \CommentTok{\# initialize vectors that hold if the CI contains true mean }
+    \CommentTok{\# by iteration}
 \NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
@@
   \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Normal Distibution"}\NormalTok{, }
+    \AttributeTok{title =} \StringTok{"Accuracy of Bootstrap CIs using Normal Distibution"}\NormalTok{, }
     \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
     \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-    \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
-\StringTok{       different sample sizes on Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+    \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI }
+\StringTok{    Methods for different sample sizes on Normal Distribution"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Gamma Distibution"}\NormalTok{, }
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Accuracy of Bootstrap CIs using Gamma Distibution"}\NormalTok{, }
        \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 9: Graph showing the Accuracy of Bootstrap CI Methods for }
-\StringTok{       different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
+       \AttributeTok{caption =} \StringTok{"Fig. 9: Graph showing the Accuracy of Bootstrap CI }
+\StringTok{       Methods for different sample sizes on Gamma Distribution"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
@@
   \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =}\StringTok{"Prop. of CIs that Contain True Mean from Log{-}Normal Distibution"}\NormalTok{,}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =}\StringTok{"Accuracy of Bootstrap CIs using Log{-}Normal }
+\StringTok{       Distibution"}\NormalTok{,}
        \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
        \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
-       \AttributeTok{caption =} \StringTok{"Fig. 10: Graph showing the Accuracy of Bootstrap CI Methods }
-\StringTok{       for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
+       \AttributeTok{caption =} \StringTok{"Fig. 10: Graph showing the Accuracy of Bootstrap CI }
+\StringTok{       Methods for different sample sizes on Log{-}Normal Distribution"}\NormalTok{) }\SpecialCharTok{+}
   \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}

### 2022-12-09 project/PaperTemplate/paper.Rmd
Minor edit

@@
     bca_contains <- rep(0, sim_reps)
-    # 
+
     n <- sample_sizes[i]
